### 2018-05-29 Article.tex
Ajout des fichiers

% Author: Cyrille Chenavier, Christophe Cordero, Samuele Giraudo
% Creation: may. 2018
% Modifications: may. 2018

\documentclass[10pt,reqno]{amsart}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[utf8x]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath,amsfonts,amssymb,amsthm,shuffle}
\usepackage[T1]{fontenc}
\usepackage[math]{anttor}

% Layout.
\usepackage[top=3.5cm,bottom=3.5cm,left=3.6cm,right=3.6cm]{geometry}

% Colors of hyperlinks.
\usepackage{xcolor}
\input{Colors}

\usepackage[hyperindex=true,frenchlinks=true,colorlinks=true,
citecolor=Col2,linkcolor=Col3,urlcolor=Col4,linktocpage,
pagebackref=true]{hyperref}

% Tikz.
\usepackage{tikz}
\usetikzlibrary{shapes}
\usetikzlibrary{fit}
\usetikzlibrary{decorations.pathmorphing}

% Misc.
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{wasysym}
\usepackage{stmaryrd}
\usepackage{cite}
\usepackage{subfig}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{cancel}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Line space.
\linespread{1.15}
\renewcommand{\arraystretch}{1.4}

% Vertical space for equations.
\setlength{\abovedisplayskip}{5pt}
\setlength{\belowdisplayskip}{5pt}

% Alphabetic footnote marks.
\renewcommand{\thefootnote}{\alph{footnote}}

% To allow cutting equations in several pages.
\allowdisplaybreaks

% Numbering of equations.
\numberwithin{equation}{subsection}

% Depth of the table of contents.
\setcounter{tocdepth}{2}

% Indentation in the table of contents.
\makeatletter
\def\l@section{\@tocline{1}{3pt}{1pc}{5pc}{}}
\def\l@subsection{\@tocline{2}{2pt}{2pc}{5pc}{}}
\makeatother

% Environments definitions.
\newtheorem{Theorem}{Theorem}[subsection]
\newtheorem{Proposition}[Theorem]{Proposition}
\newtheorem{Lemma}[Theorem]{Lemma}

% Better comparison symbols.
\renewcommand{\leq}{\leqslant}
\renewcommand{\geq}{\geqslant}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Comb associative operads}
\keywords{Operad; trees; Rewrite rule; Presentation; Enumeration.}
\subjclass[2010]{\Todo{}}
\date{\today}
\author{Cyrille Chenavier \and Christophe Cordero \and Samuele Giraudo}
\address{\scriptsize Université Paris-Est, LIGM (UMR $8049$), CNRS,
    ENPC, ESIEE Paris, UPEM, F-$77454$, Marne-la-Vallée, France}
\email{cyrille.chenavier@u-pem.fr}
\email{christophe.cordero@u-pem.fr}
\email{samuele.giraudo@u-pem.fr}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{Tools}

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}

\newcommand{\Oca}{\mathcal{O}}
\newcommand{\Rfr}{\mathfrak{r}}
\newcommand{\Sfr}{\mathfrak{s}}
\newcommand{\Tfr}{\mathfrak{t}}

\newcommand{\Zero}{\mathtt{0}}
\newcommand{\Two}{\mathtt{2}}
\newcommand{\HilbertSeries}{\mathcal{H}}
\newcommand{\GeneratingSet}{\mathfrak{G}}
\newcommand{\FreeOperad}{\mathrm{F}}
\newcommand{\Mag}{\mathsf{Mag}}
\newcommand{\As}{\mathsf{As}}
\newcommand{\CAs}[1]{\mathsf{CAs}^{(#1)}}
\newcommand{\PrefixWord}{\mathrm{p}}
\newcommand{\Deg}{\mathrm{deg}}
\newcommand{\LC}[1]{\text{LC}^{(#1)}}
\newcommand{\RC}[1]{\text{RC}^{(#1)}}

\DeclareMathOperator{\Product}{\star}
\DeclareMathOperator{\Congr}{\equiv}
\DeclareMathOperator{\Rew}{\to}
\DeclareMathOperator{\RewRT}{\overset{*}{\Rew}}
\DeclareMathOperator{\RewT}{\overset{+}{\Rew}}
\DeclareMathOperator{\RewContext}{\Rightarrow}
\DeclareMathOperator{\RewContextRT}{\overset{*}{\RewContext}}
\DeclareMathOperator{\RewContextT}{\overset{+}{\RewContext}}

\newcommand{\CongrCAs}[1]{\Congr^{(#1)}}

% Tree drawings.
\tikzstyle{Node}=[circle,draw=Col1!80,fill=Col1!8,inner sep=1pt,
minimum size=2mm,thick,font=\scriptsize]
\tikzstyle{Edge}=[draw=Col2!80,cap=round,thick]
\tikzstyle{Leaf}=[rectangle,draw=ColBlack!70,fill=ColBlack!16,
inner sep=0pt,minimum size=1mm,thick]
\tikzstyle{NodeST}=[font=\footnotesize]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
    The associative operad is the quotient of the magmatic operad by
    the operad congruence identifying the two binary trees of degree
    $2$. We introduce here a generalization of the associative operad
    depending on a nonnegative integer $d$, called $d$-comb associative
    operad, as the quotient of the magmatic operad by the operad
    congruence identifying the left and the right comb binary trees of
    degree $d$. We study the case $d = 3$ and provide an orientation
    of its space of relations by using rewrite systems on trees and
    the Buchberger algorithm for operads to obtain a convergent
    rewrite system.
\end{abstract}

\maketitle

\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Introduction}
Associative algebras are spaces endowed with a binary product $\Product$
satisfying among others the associativity law
\begin{math}
    (x_1 \Product x_2) \Product x_3 = x_1 \Product (x_2 \Product x_3)
\end{math}.
It is well-known that the associative algebras are representations of 
the associative (nonsymmetric) operad $\As$. This operad can be seen as 
the quotient of the magmatic operad $\Mag$ (the free operad of binary
trees on the binary generator~$\Product$) by the operad congruence
$\Congr$ satisfying
\begin{equation} \label{equ:congruence_as}
    \begin{tikzpicture}[xscale=.24,yscale=.24,Centering]
        \node(0)at(0.00,-3.33){};
        \node(2)at(2.00,-3.33){};
        \node(4)at(4.00,-1.67){};
        \node[NodeST](1)at(1.00,-1.67)
            {\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,0.00)
            {\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](1)--(3);
        \draw[Edge](2)--(1);
        \draw[Edge](4)--(3);
        \node(r)at(3.00,1.5){};
        \draw[Edge](r)--(3);
    \end{tikzpicture}
    \Congr
    \begin{tikzpicture}[xscale=.24,yscale=.24,Centering]
        \node(0)at(0.00,-1.67){};
        \node(2)at(2.00,-3.33){};
        \node(4)at(4.00,-3.33){};
        \node[NodeST](1)at(1.00,0.00)
                {\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,-1.67)
                {\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](2)--(3);
        \draw[Edge](3)--(1);
        \draw[Edge](4)--(3);
        \node(r)at(1.00,1.5){};
        \draw[Edge](r)--(1);
    \end{tikzpicture}\,.
\end{equation}
These two binary trees are the syntax trees of the expressions appearing
in the above associativity law.

In a more combinatorial context and regardless of the theory of operads,
the Tamari order is a partial order on the set of the binary trees
having a fixed number of internal nodes $d$. This order is generated by
the covering relation consisting in rewriting a tree $\Tfr$ into a tree
$\Tfr'$ by replacing a subtree of $\Tfr$ of the form of the left member
of~\eqref{equ:congruence_as} into a tree of the form of the right member
of~\eqref{equ:congruence_as}. This transformation is known in a computer
science context as the right rotation operation~\cite{Knu98} and
intervenes in algorithms involving binary search trees~\cite{AVL62}. The
partial order hence generated by the right rotation operation is known
as the Tamari order~\cite{Tam62} and has a lot of combinatorial and
algebraic properties (see for instance~\cite{HT72,Cha06}).

A first connection between the associative operad and the Tamari order
is based upon the fact that the orientation of~\eqref{equ:congruence_as}
from left to right provides a convergent orientation (a terminating and 
confluent rewrite relation) of the congruence $\Congr$. The normal 
forms of the rewrite relation induced by the rewrite rule obtained by 
orienting~\eqref{equ:congruence_as} from left to right are right comb 
binary trees and are hence in one-to-one correspondence with the 
elements of~$\As$.

This work is intended to be a first strike in the study of the eventual
links between the Tamari order and some quotients of the operad $\Mag$.
In the long run, we would like to study quotients $\Mag/_{\Congr}$ of
$\Mag$ where $\Congr$ is an operad congruence generated by equivalence
classes of trees of a fixed degree. In particular, we would like to know
if $\Congr$ is generated by equivalence classes of trees forming
intervals of the Tamari order leads to algebraic properties for
$\Mag/_{\Congr}$ (like the description of orientations of its space of
relations, nice bases and Hilbert series).

We focus here on one of these quotients $\CAs{3}$ which is the operad
describing the category of the algebras equipped with a binary product
$\Product$ and subjected to the relation
\begin{math}
    ((x_1 \Product x_2) \Product x_3) \Product x_4
    =
    x_1 \Product (x_2 \Product (x_3 \Product x_4))
\end{math}.
This is a kind of associativity law in higher degree $d = 3$. This
operad is generated by an equivalence class of trees which is not an
interval for the Tamari order. As preliminary computer experiments show,
$\CAs{3}$ has oscillating first dimensions
(see~\eqref{equ:dimensions_CAs_3}), what is rather unusual among all
known operads. In this paper, we provide an orientation of the space of
relations of $\CAs{3}$. For this, we use rewrite systems on
trees~\cite{BN98} and the Buchberger algorithm for operads~\cite{DK10}.

This text is presented as follows. Section~\ref{sec:operad_Mag} contains
preliminaries about the magmatic operad and rewrite relations on trees.
In Section~\ref{sec:CAs_d}, we define the operad $\CAs{3}$ as a
particular case of a more general construction of generalizations
$\CAs{d}$, $d \geq 1$, of $\As$. Finally, Section~\ref{sec:CAs_3}
contains the orientation of the space of relations of
$\CAs{3}$ (Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}). As
consequences, we obtain for $\CAs{3}$
the description of one of its Poincaré-Birkhoff-Witt bases
(Proposition~\ref{prop:PBW_basis_CAs_3}) and the description of
its Hilbert series (Proposition~\ref{prop:Hilbert_series_CAs_3}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The magmatic operad, quotients, and rewrite relations}
\label{sec:operad_Mag}
We consider nonsymmetric set-theoretic operads. Let $\Oca$ be such an
operad. We denote respectively by $\circ_i$ and $\circ$ the partial and
complete compositions of $\Oca$. For any $n \geq 1$, $\Oca(n)$ is the
set of the elements $x$ of $\Oca$ of arity $|x| = n$. We denote
by $\Mag$ the magmatic operad, that is the free operad over one binary
generator $\Product$, and we represent the elements of $\Mag$ by binary
trees. The \Def{arity} $|\Tfr|$ (resp. \Def{degree} $\Deg(\Tfr)$) of a
binary tree $\Tfr$ is its number of leaves (resp. internal nodes).
Given a binary tree $\Tfr$, we denote by $ \PrefixWord(\Tfr)$ the
\Def{prefix word} of $\Tfr$, that is the word on $\{\Zero, \Two\}$
obtained by a left to right depth-first traversal of $\Tfr$ and by
writing $\Zero$ (resp. $\Two$) when a leaf (resp. an internal node) is
encountered. The set of all words on $\{\Zero, \Two\}$ is endowed with
the lexicographic order $\leq$ induced by $\Zero < \Two$.

If $\Rew$ is a rewrite rule on $\Mag$ such that $\Sfr \Rew \Sfr'$ 
implies $|\Sfr| = |\Sfr'|$, we denote by $\RewContext$ the
\Def{rewrite relation induced} by $\Rew$. Formally we have
\begin{math}
    \Tfr\circ_i\left(\Sfr\circ\left[\Rfr_1,\dots,\Rfr_{n}\right]\right)
    \RewContext
    \Tfr\circ_i\left(\Sfr'\circ\left[\Rfr_1,\dots,\Rfr_{n}\right]\right)
\end{math},
if $\Sfr \Rew \Sfr'$ where $n = |\Sfr|$, and $\Tfr$, $\Rfr_1$, \dots,
$\Rfr_n$ are binary trees. In other words, one has
$\Tfr \RewContext \Tfr'$ if it is possible to obtain $\Tfr'$ from $\Tfr$
by replacing a subtree $\Sfr$ of $\Tfr$ by $\Sfr'$ whenever
$\Sfr \Rew \Sfr'$. We use here the standard terminology
(\Def{terminating}, \Def{confluent}, \Def{convergent}, \Def{branching
pair}, \Def{joinable}, \Def{normal form}, {\em etc.}) about rewrite
relations and rewrite systems~\cite{BN98}.

Given an operad $\Oca \simeq \Mag/_{\Congr}$ where $\Congr$ is an operad
congruence of $\Mag$, we say that $\Rew$ is an \Def{orientation} of
$\Congr$ if the reflexive, transitive, and symmetric closure of
$\RewContext$ is $\Congr$. We say that $\Rew$ is a \Def{convergent
orientation} if $\RewContext$ is convergent. When $\Rew$ is a convergent
orientation of $\Congr$, the set of all normal forms of $\RewContext$ is
a \Def{Poincaré-Birkhoff-Witt basis} of the operad $\Oca$ and its
elements are exactly the binary trees avoiding, as subtrees, the trees
appearing as left members in $\Rew$.

We shall use the following criterion to prove that a rewrite relation on
$\Mag$ is terminating.

\begin{Lemma}\label{lem:prefix_word_termination}
    Let $\Rew$ be a rewrite rule on $\Mag$. If for any
    $\Tfr, \Tfr' \in \Mag$ such that $\Tfr \Rew \Tfr'$ one has
    $\PrefixWord(\Tfr) > \PrefixWord(\Tfr')$, then the rewrite relation
    induced by $\Rew$ is terminating.
\end{Lemma}

Moreover, we shall use the following result appearing in~\cite{Gir16}
specialized on rewrite relation on $\Mag$ to prove that a terminating
rewrite relation is convergent.

\begin{Lemma} \label{lem:degree_confluence}
    Let $\Rew$ be a rewrite rule on $\Mag$ wherein all trees $\Tfr$ and 
    $\Tfr'$ such that $\Tfr \Rew \Tfr'$ have degrees at most $\ell$. 
    Then, if the rewrite relation $\RewContext$ induced by $\Rew$ is
    terminating and all its branching pairs of degrees at most
    $2\ell - 1$ are joinable, $\RewContext$ is convergent.
\end{Lemma}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Generalizations of the associative operad} \label{sec:CAs_d}
It is known that the rewrite rule $\Rew$
orienting~\eqref{equ:congruence_as} from left to right is a convergent
orientation of (\ref{equ:congruence_as}). Then, a Poincaré-Birkhoff-Witt
basis of $\As$ is the set of all right comb binary trees.

Let us now define for any $d \geq 1$ the \Def{$d$-comb associative
operad} $\CAs{d}$ as the quotient operad $\Mag/_{\CongrCAs{d}}$ where
$\CongrCAs{d}$ is the smallest operad congruence of $\Mag$
satisfying
\begin{equation} \label{equ:congruence_Asd}
    \underbrace{(\dots (\Product \circ_1 \Product) \circ_1 \dots)
        \circ_1 \Product}
    _{d \mbox{ \footnotesize operands}}
    \enspace \CongrCAs{d} \enspace
    \underbrace{\Product \circ_2
        (\dots \circ_2 (\Product \circ_2 \Product) \dots)}
    _{d \mbox{ \footnotesize operands}}.
\end{equation}
In words, \eqref{equ:congruence_Asd} says that the left and the right
comb binary trees of degree $d$ are equivalent for $\CongrCAs{d}$.
Notice that $\CongrCAs{1}$ is trivial so that $\CAs{1} = \Mag$ and that
$\CongrCAs{2}$ is the operad congruence defined
by~\eqref{equ:congruence_as} so that $\CAs{2} = \As$.

In the sequel we denote by $\LC{d}$ and $\RC{d}$ the left comb and the
right comb of degree $d$, respectively. Hence, $\CongrCAs{d}$ is the
congruence relation induced by $\LC{d}\CongrCAs{d}\RC{d}$.

We denote by CAs the set of $d$-comb associative operads where $d$ belongs
the set of strictly positive integers:
\[\text{CAs}=\left\{\CAs{d}\mid d\geq 1\right\}.\]
Our purpose is to show that CAs admits a lattice structure. For that, we provide
a description of operads morphisms between the elements of CAs.

\begin{Proposition}\label{prop:morphisms_CAs_d}

  Let $d$ and $d'$ be two strictly positive integers. There exists at most
  one operads morphism $\varphi:\CAs{d'}\longrightarrow\CAs{d}$. This morphism
  exists if and only if $\LC{d'}\CongrCAs{d}\RC{d'}$ and it is surjective in this
  case. Moreover, $\varphi$ is injective if and only if $d=d'$, that is if and only
  if $\varphi$ is the identity morphism.

  \end{Proposition}

\begin{proof}
  The operad $\CAs{d'}$ is generated by one binary generator $t^{(d')}$, so that
  $\varphi$ is entirely determined by $\varphi\left(t^{(d')}\right)$. Moreover,
  $\varphi\left(t^{(d')}\right)$ has to be of arity $2$ in $\CAs{d}$, so that
  $\varphi\left(t^{(d')}\right)$ has to be equal to $t^{(d)}$. Hence, if $\varphi$
  exists, it is the unique operads morphism from $\CAs{d'}$ and $\CAs{d}$,
  and in this case, $t^{(d)}$ being in the image of $\varphi$, the latter is
  surjective. Moreover, $\varphi$ is well defined if and only if
  $\varphi\left(\LC{d'}\right)$ and $\varphi\left(\RC{d'}\right)$ are equal in
  $\CAs{d}$, that is if and only if $\LC{d'}\CongrCAs{d}\RC{d'}$. In particular,
  if $d'$ is strictly smaller than $d$, then there does not exist any morphism
  $\varphi:\CAs{d'}\longrightarrow\CAs{d}$. Moreover, if $d'$ is strictly smaller
  than $d$, the cardinality of $\CAs{d'}\left(d\right)$ is equal to the cardinality
  of $\CAs{d}(d)$ plus one. Hence, if there exists an injective morphism
  $\varphi:\CAs{d'}\longrightarrow\CAs{d}$, we must have $d=d'$, and in this case,
  $\varphi$ is the identity morphism.
\end{proof}

We define the binary relation $\preceq$ on CAs as follows: we have $\CAs{d}\preceq\CAs{d'}$
if and only if there exists a morphism $\varphi:\CAs{d'}\longrightarrow\CAs{d}$.

\begin{Theorem}\label{thm:poset_CAs}
  The binary relation $\preceq$ is a partially order on \emph{CAs}, that is
  $\left(\emph{CAs},\ \preceq\right)$ is a poset.
  \end{Theorem}

\begin{proof}
  The binary relation $\preceq$ is reflexive since there exists the identity morphism
  of $\CAs{d}$ for every strictly positive integer $d$. It is transitive since if
  there exist two morphismsk  $\varphi:\CAs{d}\longrightarrow\CAs{d'}$ and
  $\psi:\CAs{d''}\longrightarrow\CAs{d'}$, then $\psi\circ\varphi$ is a morphism from
  $\CAs{d''}$ to $\CAs{d}$. Now, let us assume that there exist morphisms
  $\varphi:\CAs{d'}\longrightarrow\CAs{d}$ and $\psi:\CAs{d}\longrightarrow\CAs{d'}$.
  In particular, $\psi\circ\varphi$ and $\varphi\circ\psi$ are endomorphisms of $\CAs{d'}$
  and $\CAs{d}$, respectively. From Proposition~\ref{prop:morphisms_CAs_d}, these two
  morphisms are identity morphisms, so that $\varphi$ and $\psi$ are injective. From
  Proposition~\ref{prop:morphisms_CAs_d}, $d$ and $d'$ are equal, which proves that
  $\preceq$ is anti-symmetric, hence a partial order.
  \end{proof}

In order to show that the poset $\left(\text{CAs},\ \preceq\right)$ extends into a lattice,
that is two elements of CAs admit lower-bounds and upper-bounds, we relate
$\left(\text{CAs},\ \preceq\right)$ to the lattice of integers
$\left(\N,\ \mid,\ \text{gcd},\ \text{lcm}\right)$, where $\mid$ denotes the division
relation, gcd denotes the \emph{greatest common divisor} and lcm the \emph{least common multiple}
operators, respectively. In order to obtain this relationship, we introduce the notion of
\Def{left rank} of an element $t\in\Mag$: this is the length $\text{lr}\left(t\right)$ of
the left branch beginning at the root of $t$. The left rank of $t$ is represented as follows:
\[\textbf{PICTURE}\]

\begin{Lemma}\label{lem:left_rank_and_CongrCAs}
  Let $d$ be a strictly positive integer and let $t$ and $t'$ be two elements of $\Mag$. If
  $t\CongrCAs{d}t'$, then $\emph{lr}\left(t\right)-\emph{lr}\left(t'\right)$ is divisible by
  $d-1$.
\end{Lemma}

\begin{proof}
  Let $\Rew$ be the rewrite relation on $\Mag$ induced by the rewrite rule
  $\LC{d}\Rew\RC{d}$. In the rest of the proof we fix two elements $t$ and $t'$ of $\Mag$.

  First, we show that $t\Rew t'$ implies that $\text{lr}\left(t'\right)-\text{lr}\left(t\right)$
  is divisible by $d-1$ \textbf{TODO}.

  Assume that $t\overset{*}{\Rew}t'$, so that there exist elements $t_1,\ \cdots,\ t_n$
  of $\Mag$ such that $t_1=t$, $t_n=t'$ and for every $i\in\{1,\cdots,n-1\}$, we have
  $t_i\Rew t_{i+1}$. The integer $\text{lr}\left(t_{i+1}\right)-\text{lr}\left(t_i\right)$
  is divisible by $d-1$ from the first part of the proof, so that
  $\text{lr}\left(t'\right)-\text{lr}\left(t\right)$ is divisible by $d-1$.

  Assume that $t\overset{*}{\leftrightarrow}t'$, so that there exist elements $t_1,\ \cdots,\ t_n$
  of $\Mag$ such that $t_1=t$, $t_n=t'$ and for every $i\in\{1,\cdots,n-1\}$, we have
  $t_i\overset{*}{\Rew}t_{i+1}$ or $t_{i+1}\overset{*}{\Rew}t_i$. From the second part of the proof,
  $\text{lr}\left(t_{i+1}\right)-\text{lr}\left(t_i\right)$ is divisible by $d-1$, so that
  $\text{lr}\left(t'\right)-\text{lr}\left(t\right)$ is divisible by $d-1$.

  The congruence relation $\CongrCAs{d}$ is the equivalence relation induced by $\Rew$, that
  is we have $t\CongrCAs{d}t'$ if and only if $t\overset{*}{\leftrightarrow}t'$. Hence, from the
  third part of the proof, $t\CongrCAs{d}t'$ implies that
  $\text{lr}\left(t'\right)-\text{lr}\left(t\right)$ is divisible by $d-1$.
  \end{proof}

\begin{Proposition} \label{prop:division_CAs}
  Let $d$ and $d'$ be two strictly positive integers. There exists a morphism
  $\varphi:\CAs{d'}\longrightarrow\CAs{d}$ if and only if $\left(d-1\right)\mid\left(d'-1\right)$.
\end{Proposition}
\begin{proof}
  From Proposition~\ref{prop:morphisms_CAs_d}, it is sufficient to show that $\LC{d'}\CongrCAs{d}\RC{d'}$
  if and only if $\left(d-1\right)\mid\left(d'-1\right)$. If $\LC{d'}\CongrCAs{d}\RC{d'}$, from
  Lemma~\ref{lem:left_rank_and_CongrCAs}, $\text{lr}\left(\LC{d'}\right)-\text{lr}\left(\RC{d'}\right)=d'-1$
  is divisible by $d-1$, which shows the direct implication. Conversely, if
  $\left(d-1\right)\mid\left(d'-1\right)$, the rewrite rule $\LC{d}\Rew\RC{d}$ induces the
  following sequence of rewriting steps:
  \[\textbf{Rewriting sequence from left comb of degree d' to right comb of degree d'}\]
  Hence, we have $\LC{d'}\CongrCAs{d}\RC{d'}$.
   \end{proof}

Proposition~\ref{prop:division_CAs} implies the following:
\begin{Theorem}\label{thm:lattice_CAs}
  The poset $\left(\emph{CAs},\ \preceq\right)$ extends into a lattice
  $\left(\emph{CAs},\ \preceq,\ \wedge,\ \vee\right)$, where the lower-
  bound $\wedge$ and the upper-bound $\vee$ are defined as follows:
  \[\CAs{d}\wedge\CAs{d'}=\CAs{\text{gcd}\left(d-1,\ d'-1\right)}\
  \text{and}\ \CAs{d}\vee\CAs{d'}=\CAs{\text{lcm}\left(d-1,\ d'-1\right)}.\]
  \end{Theorem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The \texorpdfstring{$3$}{3}-comb associative operad}
\label{sec:CAs_3}
We now focus on the study of the operad $\CAs{3}$. By definition, this
operad is the quotient of $\Mag$ by the operad congruence spanned by the
relation
\begin{equation} \label{equ:rew_1}
    \begin{tikzpicture}[xscale=.22,yscale=.23,Centering]
        \node(0)at(0.00,-5.25){};
        \node(2)at(2.00,-5.25){};
        \node(4)at(4.00,-3.50){};
        \node(6)at(6.00,-1.75){};
        \node[NodeST](1)at(1.00,-3.50){\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
        \node[NodeST](5)at(5.00,0.00){\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](1)--(3);
        \draw[Edge](2)--(1);
        \draw[Edge](3)--(5);
        \draw[Edge](4)--(3);
        \draw[Edge](6)--(5);
        \node(r)at(5.00,1.5){};
        \draw[Edge](r)--(5);
    \end{tikzpicture}
    \enspace \Rew \enspace
    \begin{tikzpicture}[xscale=.22,yscale=.23,Centering]
        \node(0)at(0.00,-1.75){};
        \node(2)at(2.00,-3.50){};
        \node(4)at(4.00,-5.25){};
        \node(6)at(6.00,-5.25){};
        \node[NodeST](1)at(1.00,0.00){\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
        \node[NodeST](5)at(5.00,-3.50){\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](2)--(3);
        \draw[Edge](3)--(1);
        \draw[Edge](4)--(5);
        \draw[Edge](5)--(3);
        \draw[Edge](6)--(5);
        \node(r)at(1.00,1.5){};
        \draw[Edge](r)--(1);
    \end{tikzpicture}\,.
\end{equation}
This rewrite rule is compatible with the lexicographic order on prefix 
words presented at the beginning of Section~\ref{sec:operad_Mag} in the 
sense that the prefix word of the left member of~\eqref{equ:rew_1} is 
lexicographically greater than the prefix word of the right one.

However, the rewrite relation $\RewContext$ induced by $\Rew$ is not
confluent. Indeed, we have
\begin{equation} \label{equ:branching_pair_CAs_3}
    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
        \node(0)at(0.00,-7.20){};
        \node(2)at(2.00,-7.20){};
        \node(4)at(4.00,-5.40){};
        \node(6)at(6.00,-3.60){};
        \node(8)at(8.00,-1.80){};
        \node[NodeST](1)at(1.00,-5.40){\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,-3.60){\begin{math}\Product\end{math}};
        \node[NodeST](5)at(5.00,-1.80){\begin{math}\Product\end{math}};
        \node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](1)--(3);
        \draw[Edge](2)--(1);
        \draw[Edge](3)--(5);
        \draw[Edge](4)--(3);
        \draw[Edge](5)--(7);
        \draw[Edge](6)--(5);
        \draw[Edge](8)--(7);
        \node(r)at(7.00,1.35){};
        \draw[Edge](r)--(7);
    \end{tikzpicture}
    \enspace \RewContext \enspace
    \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
        \node(0)at(0.00,-4.50){};
        \node(2)at(2.00,-4.50){};
        \node(4)at(4.00,-4.50){};
        \node(6)at(6.00,-6.75){};
        \node(8)at(8.00,-6.75){};
        \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
        \node[NodeST](5)at(5.00,-2.25){\begin{math}\Product\end{math}};
        \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](1)--(3);
        \draw[Edge](2)--(1);
        \draw[Edge](4)--(5);
        \draw[Edge](5)--(3);
        \draw[Edge](6)--(7);
        \draw[Edge](7)--(5);
        \draw[Edge](8)--(7);
        \node(r)at(3.00,1.74){};
        \draw[Edge](r)--(3);
    \end{tikzpicture}
    \qquad \mbox{and} \qquad
    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
        \node(0)at(0.00,-7.20){};
        \node(2)at(2.00,-7.20){};
        \node(4)at(4.00,-5.40){};
        \node(6)at(6.00,-3.60){};
        \node(8)at(8.00,-1.80){};
        \node[NodeST](1)at(1.00,-5.40){\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,-3.60){\begin{math}\Product\end{math}};
        \node[NodeST](5)at(5.00,-1.80){\begin{math}\Product\end{math}};
        \node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](1)--(3);
        \draw[Edge](2)--(1);
        \draw[Edge](3)--(5);
        \draw[Edge](4)--(3);
        \draw[Edge](5)--(7);
        \draw[Edge](6)--(5);
        \draw[Edge](8)--(7);
        \node(r)at(7.00,1.35){};
        \draw[Edge](r)--(7);
    \end{tikzpicture}
    \enspace \RewContext \enspace
    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
        \node(0)at(0.00,-3.60){};
        \node(2)at(2.00,-5.40){};
        \node(4)at(4.00,-7.20){};
        \node(6)at(6.00,-7.20){};
        \node(8)at(8.00,-1.80){};
        \node[NodeST](1)at(1.00,-1.80){\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,-3.60){\begin{math}\Product\end{math}};
        \node[NodeST](5)at(5.00,-5.40){\begin{math}\Product\end{math}};
        \node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](1)--(7);
        \draw[Edge](2)--(3);
        \draw[Edge](3)--(1);
        \draw[Edge](4)--(5);
        \draw[Edge](5)--(3);
        \draw[Edge](6)--(5);
        \draw[Edge](8)--(7);
        \node(r)at(7.00,1.5){};
        \draw[Edge](r)--(7);
    \end{tikzpicture}\,,
\end{equation}
and the two right members of~\eqref{equ:branching_pair_CAs_3} form a
branching pair which is not joinable.

In order to transform the rewrite relation induced by~\eqref{equ:rew_1} 
into a convergent one, we apply the Buchberger algorithm for
operads~\cite[Section 3.7]{DK10} with respect to the lexicographic order
on prefix words. Following this algorithm, we need to put the right
members of~\eqref{equ:branching_pair_CAs_3} in relation by $\Rew$. To
respect the lexicographic property of the prefix words, this leads to
the new relation
\begin{equation} \label{equ:rew_2}
    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
        \node(0)at(0.00,-3.60){};
        \node(2)at(2.00,-5.40){};
        \node(4)at(4.00,-7.20){};
        \node(6)at(6.00,-7.20){};
        \node(8)at(8.00,-1.80){};
        \node[NodeST](1)at(1.00,-1.80){\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,-3.60){\begin{math}\Product\end{math}};
        \node[NodeST](5)at(5.00,-5.40){\begin{math}\Product\end{math}};
        \node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](1)--(7);
        \draw[Edge](2)--(3);
        \draw[Edge](3)--(1);
        \draw[Edge](4)--(5);
        \draw[Edge](5)--(3);
        \draw[Edge](6)--(5);
        \draw[Edge](8)--(7);
        \node(r)at(7.00,1.5){};
        \draw[Edge](r)--(7);
    \end{tikzpicture}
    \enspace \Rew \enspace
    \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
        \node(0)at(0.00,-4.50){};
        \node(2)at(2.00,-4.50){};
        \node(4)at(4.00,-4.50){};
        \node(6)at(6.00,-6.75){};
        \node(8)at(8.00,-6.75){};
        \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
        \node[NodeST](5)at(5.00,-2.25){\begin{math}\Product\end{math}};
        \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](1)--(3);
        \draw[Edge](2)--(1);
        \draw[Edge](4)--(5);
        \draw[Edge](5)--(3);
        \draw[Edge](6)--(7);
        \draw[Edge](7)--(5);
        \draw[Edge](8)--(7);
        \node(r)at(3.00,1.74){};
        \draw[Edge](r)--(3);
    \end{tikzpicture}\,.
\end{equation}
The Buchberger algorithm applied on binary trees of degrees $5$, $6$,
and $7$ provides the new relations \\
\input{Buchberger_relations_5-7}

\noindent
We claim that the rewrite relation $\RewContext$ induced by
rewrite rule $\Rew$ satisfying~\eqref{equ:rew_1}, \eqref{equ:rew_2}, 
\eqref{equ:rew_3}---\eqref{equ:rew_11} is convergent. First, for every 
relation $\Tfr \Rew \Tfr'$, we have
$\PrefixWord(\Tfr) > \PrefixWord(\Tfr')$. Therefore, by
Lemma~\ref{lem:prefix_word_termination}, $\RewContext$ is terminating.
Moreover, the greatest degree of a tree appearing in $\Rew$ is~$7$ so
that, from Lemma~\ref{lem:degree_confluence}, to show that $\RewContext$
is convergent, it is enough to prove that each tree of degree at most
$13$ admits exactly one normal form. Equivalently, this amounts to
show that the number of normal forms of trees of arity $n$ is equal
to $\#\CAs{3}(n)$. By computer exploration, we get the same sequence
\begin{equation} \label{equ:dimensions_CAs_3}
    1, 1, 2, 4, 8, 14, 20, 19, 16, 14, 14, 15, 16, 17
\end{equation}
for $\#\CAs{3}(n)$ and for the numbers of normal forms of arity $n$,
when $ 1 \leq n \leq 14$. Hence, we get our following main result.

\begin{Theorem} \label{thm:convergent_rewrite_rule_CAs_3}
    The rewrite rule $\Rew$ satisfying~\eqref{equ:rew_1},
    \eqref{equ:rew_2}, \eqref{equ:rew_3}---\eqref{equ:rew_11} is a
    convergent orientation of the congruence $\CongrCAs{3}$
    of~$\CAs{3}$.
\end{Theorem}

The rewrite rule $\Rew$ has, arity by arity, the cardinalities
\begin{equation}
    0, 0, 0, 1, 1, 2, 3, 4, 0, \dots~.
\end{equation}
We obtain from Theorem~\ref{thm:convergent_rewrite_rule_CAs_3} also
the following consequences.

\begin{Proposition} \label{prop:PBW_basis_CAs_3}
    The set of the trees avoiding as subtrees the ones appearing as
    left members of $\Rew$ is a Poincaré-Birkhoff-Witt basis
    of~$\CAs{3}$.
\end{Proposition}

From Proposition~\ref{prop:PBW_basis_CAs_3}, and by using a result
of~\cite{Gir18} describing a system of equations for the generating
series of syntax trees avoiding some sets of subtrees, we obtain the
following result.

\begin{Proposition} \label{prop:Hilbert_series_CAs_3}
    The Hilbert series of $\CAs{3}$ is
    \begin{equation} \label{equ:Hilbert_series_CAs_3}
        \HilbertSeries_{\CAs{3}}(t) = \frac{t}{(1 - t)^2}
        \left(1 - t + t^2 + t^3 + 2t^4 + 2t^5 - 7t^7 - 2t^8 + t^9 +
        2t^{10} + t^{11}\right).
    \end{equation}
\end{Proposition}

For $n \leq 10$, the dimensions of $\CAs{3}(n)$ are provided by
Sequence~\eqref{equ:dimensions_CAs_3} and for all $n \geq 11$, the
Taylor expansion of~\eqref{equ:Hilbert_series_CAs_3} shows that
$\# \CAs{3}(n) = n + 3$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Perspectives}
Our first axis of perspectives consists in collecting properties about
the operads $\CAs{d}$. A natural question consists in finding all the
morphisms between the operads $\CAs{d}$. Some surjective morphisms are
described by Proposition~\ref{prop:quotients_CAs_d} and we can hope to a
full description of these, as well as some possible injections.
Moreover, we can try to obtain a convergent orientation of
$\CongrCAs{d}$ and general expressions of the Hilbert series of
$\CAs{d}$ when $d \geq 4$. By computer exploration, we have the sequence
\begin{equation}
    1, 1, 2, 5, 13, 35, 96, 264, 724, 1973, 5355, 14390
\end{equation}
for the first dimensions for $\CAs{4}$. By applying the Buchberger
algorithm on trees of degrees until $10$, we obtain that a convergent
orientation of $\CongrCAs{4}$ has, arity by arity, the sequence
\begin{math}
    0, 0, 0, 0, 1, 1, 0, 3, 4, 5, 18, 22
\end{math}
for its first cardinalities. Moreover, for $\CAs{5}$, we get the
sequence
\begin{equation}
    1, 1, 2, 5, 14, 41, 124, 384, 1210, 3861, 12440
\end{equation}
of dimensions and the first cardinalities
\begin{math}
    0, 0, 0, 0, 0, 1, 1, 0, 0, 4, 5
\end{math}
for any convergent orientation of $\CongrCAs{5}$. Finally, for
$\CAs{6}$, we get the sequence
\begin{equation}
    1, 1, 2, 5, 14, 42, 131, 420, 1375, 4576, 15431
\end{equation}
of dimensions and the first cardinalities
\begin{math}
    0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0
\end{math}
for any convergent orientation of $\CongrCAs{6}$. We can notice that
only $\CAs{3}$ seems to have oscillating first dimensions.

A second axis concerns a complete understanding of $\CAs{3}$. We can
try to construct an explicit basis of this operad.
Proposition~\ref{prop:PBW_basis_CAs_3} describes a basis in terms of
trees avoiding some patterns but, we can hope to find a simpler
description. This includes the description of a family of combinatorial
objects forming a basis of $\CAs{3}$ and an adequate definition of a
partial composition map $\circ_i$ on these. Moreover, a natural
question is to explore the suboperads $\CAs{3}$ in the category of
vector spaces.

In a last axis, we can consider further generalizations of $\As$ being
quotients of $\Mag$ by congruences defined by identifying certain binary
trees of a same fixed degree. A possible question is, as presented in
the introduction, to investigate if combinatorial properties of the
trees belonging to a same equivalence class imply algebraic properties
on the obtained operads.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{alpha}
\bibliography{Bibliography}

\end{document}

### 2018-05-30 Article.tex
Modification notation : d changé par des gamma

@@
 
-Let us now define for any $d \geq 1$ the \Def{$d$-comb associative
-operad} $\CAs{d}$ as the quotient operad $\Mag/_{\CongrCAs{d}}$ where
-$\CongrCAs{d}$ is the smallest operad congruence of $\Mag$
+Let us now define for any $d \geq 1$ the \Def{$\gamma$-comb associative
+operad} $\CAs{\gamma}$ as the quotient operad $\Mag/_{\CongrCAs{\gamma}}$ where
+$\CongrCAs{\gamma}$ is the smallest operad congruence of $\Mag$
 satisfying
@@
         \circ_1 \Product}
-    _{d \mbox{ \footnotesize operands}}
-    \enspace \CongrCAs{d} \enspace
+    _{\gamma \mbox{ \footnotesize operands}}
+    \enspace \CongrCAs{\gamma} \enspace
     \underbrace{\Product \circ_2
         (\dots \circ_2 (\Product \circ_2 \Product) \dots)}
-    _{d \mbox{ \footnotesize operands}}.
+    _{\gamma \mbox{ \footnotesize operands}}.
 \end{equation}
 In words, \eqref{equ:congruence_Asd} says that the left and the right
-comb binary trees of degree $d$ are equivalent for $\CongrCAs{d}$.
+comb binary trees of degree $\gamma$ are equivalent for $\CongrCAs{\gamma}$.
 Notice that $\CongrCAs{1}$ is trivial so that $\CAs{1} = \Mag$ and that
@@
 
-In the sequel we denote by $\LC{d}$ and $\RC{d}$ the left comb and the
-right comb of degree $d$, respectively. Hence, $\CongrCAs{d}$ is the
-congruence relation induced by $\LC{d}\CongrCAs{d}\RC{d}$.
+In the sequel we denote by $\LC{\gamma}$ and $\RC{\gamma}$ the left comb and the
+right comb of degree $\gamma$, respectively. Hence, $\CongrCAs{\gamma}$ is the
+congruence relation induced by $\LC{\gamma}\CongrCAs{\gamma}\RC{\gamma}$.
 
-We denote by CAs the set of $d$-comb associative operads where $d$ belongs
+We denote by CAs the set of $\gamma$-comb associative operads where $\gamma$ belongs
 the set of strictly positive integers:
-\[\text{CAs}=\left\{\CAs{d}\mid d\geq 1\right\}.\]
+\[\text{CAs}=\left\{\CAs{\gamma}\mid\gamma\geq 1\right\}.\]
 Our purpose is to show that CAs admits a lattice structure. For that, we provide
@@
 
-  Let $d$ and $d'$ be two strictly positive integers. There exists at most
-  one operads morphism $\varphi:\CAs{d'}\longrightarrow\CAs{d}$. This morphism
-  exists if and only if $\LC{d'}\CongrCAs{d}\RC{d'}$ and it is surjective in this
-  case. Moreover, $\varphi$ is injective if and only if $d=d'$, that is if and only
+  Let $\gamma$ and $\gamma'$ be two strictly positive integers. There exists at most
+  one operads morphism $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$. This morphism
+  exists if and only if $\emph{LC}\left(\gamma'\right)\CongrCAs{\gamma}\emph{RC}\left(\gamma'\right)$ and it is surjective in this
+  case. Moreover, $\varphi$ is injective if and only if $\gamma=\gamma'$, that is if and only
   if $\varphi$ is the identity morphism.
@@
 \begin{proof}
-  The operad $\CAs{d'}$ is generated by one binary generator $t^{(d')}$, so that
-  $\varphi$ is entirely determined by $\varphi\left(t^{(d')}\right)$. Moreover,
-  $\varphi\left(t^{(d')}\right)$ has to be of arity $2$ in $\CAs{d}$, so that
-  $\varphi\left(t^{(d')}\right)$ has to be equal to $t^{(d)}$. Hence, if $\varphi$
-  exists, it is the unique operads morphism from $\CAs{d'}$ and $\CAs{d}$,
-  and in this case, $t^{(d)}$ being in the image of $\varphi$, the latter is
+  The operad $\CAs{\gamma'}$ is generated by one binary generator $t^{(\gamma')}$, so that
+  $\varphi$ is entirely determined by $\varphi\left(t^{(\gamma')}\right)$. Moreover,
+  $\varphi\left(t^{(\gamma')}\right)$ has to be of arity $2$ in $\CAs{\gamma}$, so that
+  $\varphi\left(t^{(\gamma')}\right)$ has to be equal to $t^{(\gamma)}$. Hence, if $\varphi$
+  exists, it is the unique operads morphism from $\CAs{\gamma'}$ and $\CAs{\gamma}$,
+  and in this case, $t^{(\gamma)}$ being in the image of $\varphi$, the latter is
   surjective. Moreover, $\varphi$ is well defined if and only if
-  $\varphi\left(\LC{d'}\right)$ and $\varphi\left(\RC{d'}\right)$ are equal in
-  $\CAs{d}$, that is if and only if $\LC{d'}\CongrCAs{d}\RC{d'}$. In particular,
-  if $d'$ is strictly smaller than $d$, then there does not exist any morphism
-  $\varphi:\CAs{d'}\longrightarrow\CAs{d}$. Moreover, if $d'$ is strictly smaller
-  than $d$, the cardinality of $\CAs{d'}\left(d\right)$ is equal to the cardinality
-  of $\CAs{d}(d)$ plus one. Hence, if there exists an injective morphism
-  $\varphi:\CAs{d'}\longrightarrow\CAs{d}$, we must have $d=d'$, and in this case,
+  $\varphi\left(\LC{\gamma'}\right)$ and $\varphi\left(\RC{\gamma'}\right)$ are equal in
+  $\CAs{\gamma}$, that is if and only if $\LC{\gamma'}\CongrCAs{\gamma}\RC{\gamma'}$. In particular,
+  if $\gamma'$ is strictly smaller than $\gamma$, then there does not exist any morphism
+  $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$. Moreover, if $\gamma'$ is strictly smaller
+  than $\gamma$, the cardinality of $\CAs{\gamma'}\left(\gamma\right)$ is equal to the cardinality
+  of $\CAs{\gamma}(\gamma)$ plus one. Hence, if there exists an injective morphism
+  $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$, we must have $\gamma=\gamma'$, and in this case,
   $\varphi$ is the identity morphism.
@@
 
-We define the binary relation $\preceq$ on CAs as follows: we have $\CAs{d}\preceq\CAs{d'}$
-if and only if there exists a morphism $\varphi:\CAs{d'}\longrightarrow\CAs{d}$.
+We define the binary relation $\preceq$ on CAs as follows: we have $\CAs{\gamma}\preceq\CAs{\gamma'}$
+if and only if there exists a morphism $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$.
 
-\begin{Theorem}\label{thm:poset_CAs}
+\begin{Proposition}\label{prop:poset_CAs}
   The binary relation $\preceq$ is a partially order on \emph{CAs}, that is
   $\left(\emph{CAs},\ \preceq\right)$ is a poset.
-  \end{Theorem}
+  \end{Proposition}
 
@@
   The binary relation $\preceq$ is reflexive since there exists the identity morphism
-  of $\CAs{d}$ for every strictly positive integer $d$. It is transitive since if
-  there exist two morphismsk  $\varphi:\CAs{d}\longrightarrow\CAs{d'}$ and
-  $\psi:\CAs{d''}\longrightarrow\CAs{d'}$, then $\psi\circ\varphi$ is a morphism from
-  $\CAs{d''}$ to $\CAs{d}$. Now, let us assume that there exist morphisms
-  $\varphi:\CAs{d'}\longrightarrow\CAs{d}$ and $\psi:\CAs{d}\longrightarrow\CAs{d'}$.
-  In particular, $\psi\circ\varphi$ and $\varphi\circ\psi$ are endomorphisms of $\CAs{d'}$
-  and $\CAs{d}$, respectively. From Proposition~\ref{prop:morphisms_CAs_d}, these two
+  of $\CAs{\gamma}$ for every strictly positive integer $\gamma$. It is transitive since if
+  there exist two morphisms  $\varphi:\CAs{\gamma}\to\CAs{\gamma'}$ and
+  $\psi:\CAs{\gamma''}\to\CAs{\gamma'}$, then $\psi\circ\varphi$ is a morphism from
+  $\CAs{\gamma''}$ to $\CAs{\gamma}$. Now, let us assume that there exist morphisms
+  $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$ and $\psi:\CAs{\gamma}\to\CAs{\gamma'}$.
+  In particular, $\psi\circ\varphi$ and $\varphi\circ\psi$ are endomorphisms of $\CAs{\gamma'}$
+  and $\CAs{\gamma}$, respectively. From Proposition~\ref{prop:morphisms_CAs_d}, these two
   morphisms are identity morphisms, so that $\varphi$ and $\psi$ are injective. From
-  Proposition~\ref{prop:morphisms_CAs_d}, $d$ and $d'$ are equal, which proves that
+  Proposition~\ref{prop:morphisms_CAs_d}, $\gamma$ and $\gamma'$ are equal, which proves that
   $\preceq$ is anti-symmetric, hence a partial order.
@@
 \begin{Lemma}\label{lem:left_rank_and_CongrCAs}
-  Let $d$ be a strictly positive integer and let $t$ and $t'$ be two elements of $\Mag$. If
-  $t\CongrCAs{d}t'$, then $\emph{lr}\left(t\right)-\emph{lr}\left(t'\right)$ is divisible by
-  $d-1$.
+  Let $\gamma$ be a strictly positive integer and let $t$ and $t'$ be two elements of $\Mag$. If
+  $t\CongrCAs{\gamma}t'$, then $\emph{lr}\left(t\right)$ and $\emph{lr}\left(t'\right)$ are equal modulo $\gamma-1$: $\emph{lr}\left(t\right)\equiv\emph{lr}\left(t'\right) [\gamma-1]$.
 \end{Lemma}
@@
   Let $\Rew$ be the rewrite relation on $\Mag$ induced by the rewrite rule
-  $\LC{d}\Rew\RC{d}$. In the rest of the proof we fix two elements $t$ and $t'$ of $\Mag$.
+  $\LC{\gamma}\Rew\RC{\gamma}$. In the rest of the proof we fix two elements $t$ and $t'$ of $\Mag$.
 
   First, we show that $t\Rew t'$ implies that $\text{lr}\left(t'\right)-\text{lr}\left(t\right)$
-  is divisible by $d-1$ \textbf{TODO}.
+  is divisible by $\gamma-1$ \textbf{TODO}.
 
@@
   $t_i\Rew t_{i+1}$. The integer $\text{lr}\left(t_{i+1}\right)-\text{lr}\left(t_i\right)$
-  is divisible by $d-1$ from the first part of the proof, so that
-  $\text{lr}\left(t'\right)-\text{lr}\left(t\right)$ is divisible by $d-1$.
+  is divisible by $\gamma-1$ from the first part of the proof, so that
+  $\text{lr}\left(t'\right)-\text{lr}\left(t\right)$ is divisible by $\gamma-1$.
 
@@
   $t_i\overset{*}{\Rew}t_{i+1}$ or $t_{i+1}\overset{*}{\Rew}t_i$. From the second part of the proof,
-  $\text{lr}\left(t_{i+1}\right)-\text{lr}\left(t_i\right)$ is divisible by $d-1$, so that
-  $\text{lr}\left(t'\right)-\text{lr}\left(t\right)$ is divisible by $d-1$.
+  $\text{lr}\left(t_{i+1}\right)-\text{lr}\left(t_i\right)$ is divisible by $\gamma-1$, so that
+  $\text{lr}\left(t'\right)-\text{lr}\left(t\right)$ is divisible by $\gamma-1$.
 
-  The congruence relation $\CongrCAs{d}$ is the equivalence relation induced by $\Rew$, that
-  is we have $t\CongrCAs{d}t'$ if and only if $t\overset{*}{\leftrightarrow}t'$. Hence, from the
-  third part of the proof, $t\CongrCAs{d}t'$ implies that
-  $\text{lr}\left(t'\right)-\text{lr}\left(t\right)$ is divisible by $d-1$.
+  The congruence relation $\CongrCAs{\gamma}$ is the equivalence relation induced by $\Rew$, that
+  is we have $t\CongrCAs{\gamma}t'$ if and only if $t\overset{*}{\leftrightarrow}t'$. Hence, from the
+  third part of the proof, $t\CongrCAs{\gamma}t'$ implies that
+  $\text{lr}\left(t'\right)-\text{lr}\left(t\right)$ is divisible by $\gamma-1$.
   \end{proof}
@@
 \begin{Proposition} \label{prop:division_CAs}
-  Let $d$ and $d'$ be two strictly positive integers. There exists a morphism
-  $\varphi:\CAs{d'}\longrightarrow\CAs{d}$ if and only if $\left(d-1\right)\mid\left(d'-1\right)$.
+  Let $\gamma$ and $\gamma'$ be two strictly positive integers. There exists a morphism
+  $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$ if and only if $\left(\gamma-1\right)\mid\left(\gamma'-1\right)$.
 \end{Proposition}
 \begin{proof}
-  From Proposition~\ref{prop:morphisms_CAs_d}, it is sufficient to show that $\LC{d'}\CongrCAs{d}\RC{d'}$
-  if and only if $\left(d-1\right)\mid\left(d'-1\right)$. If $\LC{d'}\CongrCAs{d}\RC{d'}$, from
-  Lemma~\ref{lem:left_rank_and_CongrCAs}, $\text{lr}\left(\LC{d'}\right)-\text{lr}\left(\RC{d'}\right)=d'-1$
-  is divisible by $d-1$, which shows the direct implication. Conversely, if
-  $\left(d-1\right)\mid\left(d'-1\right)$, the rewrite rule $\LC{d}\Rew\RC{d}$ induces the
+  From Proposition~\ref{prop:morphisms_CAs_d}, it is sufficient to show that $\LC{\gamma'}\CongrCAs{\gamma}\RC{\gamma'}$
+  if and only if $\left(\gamma-1\right)\mid\left(\gamma'-1\right)$. If $\LC{\gamma'}\CongrCAs{d}\RC{\gamma'}$, from
+  Lemma~\ref{lem:left_rank_and_CongrCAs}, $\text{lr}\left(\LC{\gamma'}\right)-\text{lr}\left(\RC{\gamma'}\right)=\gamma'-1$
+  is divisible by $\gamma-1$, which shows the direct implication. Conversely, if
+  $\left(\gamma-1\right)\mid\left(\gamma'-1\right)$, the rewrite rule $\LC{\gamma}\Rew\RC{\gamma}$ induces the
   following sequence of rewriting steps:
   \[\textbf{Rewriting sequence from left comb of degree d' to right comb of degree d'}\]
-  Hence, we have $\LC{d'}\CongrCAs{d}\RC{d'}$.
+  Hence, we have $\LC{\gamma'}\CongrCAs{\gamma}\RC{\gamma'}$.
    \end{proof}
@@
   bound $\wedge$ and the upper-bound $\vee$ are defined as follows:
-  \[\CAs{d}\wedge\CAs{d'}=\CAs{\text{gcd}\left(d-1,\ d'-1\right)}\
-  \text{and}\ \CAs{d}\vee\CAs{d'}=\CAs{\text{lcm}\left(d-1,\ d'-1\right)}.\]
+  \[\CAs{\gamma}\wedge\CAs{\gamma'}=\CAs{\text{gcd}\left(\gamma-1,\ \gamma'-1\right)}\
+  \text{and}\ \CAs{\gamma}\vee\CAs{\gamma'}=\CAs{\text{lcm}\left(\gamma-1,\ \gamma'-1\right)}.\]
   \end{Theorem}

### 2018-06-05 Article.tex
Petites corrections

@@
 % Creation: may. 2018
-% Modifications: may. 2018
+% Modifications: may. 2018, june 2018
 
@@
 \newcommand{\CAs}[1]{\mathsf{CAs}^{(#1)}}
+\newcommand{\CAsAll}{\mathsf{CAs}}
 \newcommand{\PrefixWord}{\mathrm{p}}
 \newcommand{\Deg}{\mathrm{deg}}
-\newcommand{\LC}[1]{\text{LC}^{(#1)}}
-\newcommand{\RC}[1]{\text{RC}^{(#1)}}
+\newcommand{\LC}[1]{\mathfrak{lc}^{(#1)}}
+\newcommand{\RC}[1]{\mathfrak{lr}^{(#1)}}
+\newcommand{\LBranch}{\mathrm{lb}}
+\newcommand{\RBranch}{\mathrm{rb}}
 
@@
 \DeclareMathOperator{\RewContextT}{\overset{+}{\RewContext}}
+\DeclareMathOperator{\lcm}{lcm}
 
@@
 
-Let us now define for any $d \geq 1$ the \Def{$\gamma$-comb associative
-operad} $\CAs{\gamma}$ as the quotient operad $\Mag/_{\CongrCAs{\gamma}}$ where
-$\CongrCAs{\gamma}$ is the smallest operad congruence of $\Mag$
-satisfying
+Let us now define for any $\gamma \geq 1$ the \Def{$\gamma$-comb
+associative operad} $\CAs{\gamma}$ as the quotient operad
+$\Mag/_{\CongrCAs{\gamma}}$ where $\CongrCAs{\gamma}$ is the smallest
+operad congruence of $\Mag$ satisfying
 \begin{equation} \label{equ:congruence_Asd}
@@
 In words, \eqref{equ:congruence_Asd} says that the left and the right
-comb binary trees of degree $\gamma$ are equivalent for $\CongrCAs{\gamma}$.
-Notice that $\CongrCAs{1}$ is trivial so that $\CAs{1} = \Mag$ and that
-$\CongrCAs{2}$ is the operad congruence defined
-by~\eqref{equ:congruence_as} so that $\CAs{2} = \As$.
+comb binary trees of degree $\gamma$ are equivalent for
+$\CongrCAs{\gamma}$. Notice that $\CongrCAs{1}$ is trivial so that
+$\CAs{1} = \Mag$ and that $\CongrCAs{2}$ is the operad congruence
+defined by~\eqref{equ:congruence_as} so that $\CAs{2} = \As$.
 
-In the sequel we denote by $\LC{\gamma}$ and $\RC{\gamma}$ the left comb and the
-right comb of degree $\gamma$, respectively. Hence, $\CongrCAs{\gamma}$ is the
-congruence relation induced by $\LC{\gamma}\CongrCAs{\gamma}\RC{\gamma}$.
+In the sequel we denote by $\LC{\gamma}$ and $\RC{\gamma}$ the left
+comb and the right comb of degree $\gamma$, respectively. Hence,
+$\CongrCAs{\gamma}$ is the congruence relation induced by
+$\LC{\gamma}\CongrCAs{\gamma}\RC{\gamma}$.
 
-We denote by CAs the set of $\gamma$-comb associative operads where $\gamma$ belongs
-the set of strictly positive integers:
-\[\text{CAs}=\left\{\CAs{\gamma}\mid\gamma\geq 1\right\}.\]
-Our purpose is to show that CAs admits a lattice structure. For that, we provide
-a description of operads morphisms between the elements of CAs.
+Let
+\begin{equation}
+    \CAsAll := \left\{\CAs{\gamma} : \gamma\geq 1\right\}
+\end{equation}
+be the set of all the $\gamma$-comb associative operads
+Our purpose is to show that $\CAsAll$ admits a lattice structure. For
+that, we provide a description of operads morphisms between the
+elements of $\CAsAll$.
 
 \begin{Proposition}\label{prop:morphisms_CAs_d}
-
-  Let $\gamma$ and $\gamma'$ be two strictly positive integers. There exists at most
-  one operads morphism $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$. This morphism
-  exists if and only if $\emph{LC}\left(\gamma'\right)\CongrCAs{\gamma}\emph{RC}\left(\gamma'\right)$ and it is surjective in this
-  case. Moreover, $\varphi$ is injective if and only if $\gamma=\gamma'$, that is if and only
-  if $\varphi$ is the identity morphism.
-
+    Let $\gamma$ and $\gamma'$ be two positive integers. There exists at
+    most one operad morphism $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$.
+    This  morphism exists if and only if
+    \begin{math}
+        \LC{\gamma'}\CongrCAs{\gamma}\RC{\gamma'}
+    \end{math}
+    and it is surjective in this case. Moreover, $\varphi$ is injective
+    if and only if $\gamma = \gamma'$, that is if and only if
+    $\varphi$ is the identity morphism.
 \end{Proposition}
-
 \begin{proof}
-  The operad $\CAs{\gamma'}$ is generated by one binary generator $t^{(\gamma')}$, so that
-  $\varphi$ is entirely determined by $\varphi\left(t^{(\gamma')}\right)$. Moreover,
-  $\varphi\left(t^{(\gamma')}\right)$ has to be of arity $2$ in $\CAs{\gamma}$, so that
-  $\varphi\left(t^{(\gamma')}\right)$ has to be equal to $t^{(\gamma)}$. Hence, if $\varphi$
-  exists, it is the unique operads morphism from $\CAs{\gamma'}$ and $\CAs{\gamma}$,
-  and in this case, $t^{(\gamma)}$ being in the image of $\varphi$, the latter is
-  surjective. Moreover, $\varphi$ is well defined if and only if
-  $\varphi\left(\LC{\gamma'}\right)$ and $\varphi\left(\RC{\gamma'}\right)$ are equal in
-  $\CAs{\gamma}$, that is if and only if $\LC{\gamma'}\CongrCAs{\gamma}\RC{\gamma'}$. In particular,
-  if $\gamma'$ is strictly smaller than $\gamma$, then there does not exist any morphism
-  $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$. Moreover, if $\gamma'$ is strictly smaller
-  than $\gamma$, the cardinality of $\CAs{\gamma'}\left(\gamma\right)$ is equal to the cardinality
-  of $\CAs{\gamma}(\gamma)$ plus one. Hence, if there exists an injective morphism
-  $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$, we must have $\gamma=\gamma'$, and in this case,
-  $\varphi$ is the identity morphism.
+    The operad $\CAs{\gamma'}$ is generated by one binary generator
+    $\Product$, so that $\varphi$ is entirely determined by
+    $\varphi\left(\Product\right)$. Moreover, $\varphi(\Product)$ has
+    to be of arity $2$ in $\CAs{\gamma}$, so that $\varphi(\Product)$
+    has to be equal to $\Product \in \CAs{\gamma}$. Hence, if $\varphi$
+    exists, it is the unique operad morphism from $\CAs{\gamma'}$ and
+    $\CAs{\gamma}$, and in this case, $\Product \in \CAs{\gamma'}$
+    being in the image of $\varphi$, the latter is surjective.
+    Moreover, $\varphi$ is well defined if and only if
+    $\varphi\left(\LC{\gamma'}\right)$ and
+    $\varphi\left(\RC{\gamma'}\right)$ are equal in $\CAs{\gamma}$,
+    that is if and only if
+    $\LC{\gamma'} \CongrCAs{\gamma} \RC{\gamma'}$. In particular, if
+    $\gamma'$ is smaller than $\gamma$, then there does not exist any
+    morphism $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$.
+    \Todo{Faux car on peut avoir $\gamma' = 1$, puisque
+    $\LC{1} = \RC{1}$.}
+    Moreover, if $\gamma'$ is smaller than $\gamma$, the cardinality of
+    $\CAs{\gamma'}\left(\gamma\right)$ is equal to the cardinality of
+    $\CAs{\gamma}(\gamma)$ plus one. Hence, if there exists an injective
+    morphism $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$, we must have
+    $\gamma = \gamma'$, and in this case, $\varphi$ is the identity
+    morphism.
 \end{proof}
 
-We define the binary relation $\preceq$ on CAs as follows: we have $\CAs{\gamma}\preceq\CAs{\gamma'}$
-if and only if there exists a morphism $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$.
+We define the binary relation $\preceq$ on $\CAsAll$ as follows: we have
+$\CAs{\gamma}\preceq\CAs{\gamma'}$ if and only if there exists a
+morphism $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$.
 
 \begin{Proposition}\label{prop:poset_CAs}
-  The binary relation $\preceq$ is a partially order on \emph{CAs}, that is
-  $\left(\emph{CAs},\ \preceq\right)$ is a poset.
+    The binary relation $\preceq$ is a partially order on $\CAsAll$,
+    that is $\left(\CAsAll,\ \preceq\right)$ is a poset.
 \end{Proposition}
-
 \begin{proof}
-  The binary relation $\preceq$ is reflexive since there exists the identity morphism
-  of $\CAs{\gamma}$ for every strictly positive integer $\gamma$. It is transitive since if
-  there exist two morphisms  $\varphi:\CAs{\gamma}\to\CAs{\gamma'}$ and
-  $\psi:\CAs{\gamma''}\to\CAs{\gamma'}$, then $\psi\circ\varphi$ is a morphism from
-  $\CAs{\gamma''}$ to $\CAs{\gamma}$. Now, let us assume that there exist morphisms
-  $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$ and $\psi:\CAs{\gamma}\to\CAs{\gamma'}$.
-  In particular, $\psi\circ\varphi$ and $\varphi\circ\psi$ are endomorphisms of $\CAs{\gamma'}$
-  and $\CAs{\gamma}$, respectively. From Proposition~\ref{prop:morphisms_CAs_d}, these two
-  morphisms are identity morphisms, so that $\varphi$ and $\psi$ are injective. From
-  Proposition~\ref{prop:morphisms_CAs_d}, $\gamma$ and $\gamma'$ are equal, which proves that
-  $\preceq$ is anti-symmetric, hence a partial order.
+    The binary relation $\preceq$ is reflexive since there exists the
+    identity morphism of $\CAs{\gamma}$ for every positive integer
+    $\gamma$. It is transitive since if there exist two morphisms
+    $\varphi:\CAs{\gamma}\to\CAs{\gamma'}$ and
+    $\psi:\CAs{\gamma''}\to\CAs{\gamma'}$, then $\psi\circ\varphi$ is a
+    morphism from $\CAs{\gamma''}$ to $\CAs{\gamma}$. Now, let us assume
+    that there exist morphisms $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$
+    and $\psi:\CAs{\gamma}\to\CAs{\gamma'}$. In particular,
+    $\psi\circ\varphi$ and $\varphi\circ\psi$ are endomorphisms of
+    $\CAs{\gamma'}$ and $\CAs{\gamma}$, respectively. From
+    Proposition~\ref{prop:morphisms_CAs_d}, these two morphisms are
+    identity morphisms, so that $\varphi$ and $\psi$ are injective. From
+    Proposition~\ref{prop:morphisms_CAs_d}, $\gamma$ and $\gamma'$ are
+    equal, which proves that $\preceq$ is anti-symmetric, hence a
+    partial order.
 \end{proof}
 
-In order to show that the poset $\left(\text{CAs},\ \preceq\right)$ extends into a lattice,
-that is two elements of CAs admit lower-bounds and upper-bounds, we relate
-$\left(\text{CAs},\ \preceq\right)$ to the lattice of integers
-$\left(\N,\ \mid,\ \text{gcd},\ \text{lcm}\right)$, where $\mid$ denotes the division
-relation, gcd denotes the \emph{greatest common divisor} and lcm the \emph{least common multiple}
+In order to show that the poset $\left(\CAsAll,\ \preceq\right)$
+extends into a lattice, that is two elements of $\CAsAll$ admit
+lower-bounds and upper-bounds, we relate
+$\left(\CAsAll,\ \preceq\right)$ to the lattice of integers
+$\left(\N,\ \mid,\ \gcd,\ \lcm\right)$, where $\mid$
+denotes the division relation, $\gcd$ denotes the \emph{greatest common divisor} and $\lcm$ the \emph{least common multiple}
 operators, respectively. In order to obtain this relationship, we introduce the notion of
-\Def{left rank} of an element $t\in\Mag$: this is the length $\text{lr}\left(t\right)$ of
-the left branch beginning at the root of $t$. The left rank of $t$ is represented as follows:
+\Def{left rank} of an element $\Tfr \in\Mag$: this is the number
+$\LBranch(\Tfr)$ of internal nodes in the left branch
+beginning at the root of $\Tfr$. The left rank of $\Tfr$ is represented as follows:
 \[\textbf{PICTURE}\]

### 2018-06-07 Article.tex
Modifs importantes jusqu'a part. 2

@@
 \newcommand{\CAs}[1]{\mathsf{CAs}^{(#1)}}
-\newcommand{\CAsAll}{\mathsf{CAs}}
+\newcommand{\CAsAll}{\mathbf{CAs}}
 \newcommand{\PrefixWord}{\mathrm{p}}
 \newcommand{\Deg}{\mathrm{deg}}
-\newcommand{\LC}[1]{\mathfrak{lc}^{(#1)}}
-\newcommand{\RC}[1]{\mathfrak{lr}^{(#1)}}
+\newcommand{\LComb}[1]{\mathfrak{c}^{(#1)}_{\diagup}}
+\newcommand{\RComb}[1]{\mathfrak{c}^{(#1)}_{\diagdown}}
 \newcommand{\LBranch}{\mathrm{lb}}
 \newcommand{\RBranch}{\mathrm{rb}}
+\newcommand{\Catalan}{\mathrm{cat}}
+\newcommand{\OrdCAs}{\preceq}
 
@@
 \DeclareMathOperator{\RewT}{\overset{+}{\Rew}}
+\DeclareMathOperator{\RewRTS}{\overset{*}{\leftrightarrow}}
 \DeclareMathOperator{\RewContext}{\Rightarrow}
@@
 in the above associativity law.
+\medbreak
 
@@
 algebraic properties (see for instance~\cite{HT72,Cha06}).
+\medbreak
 
@@
 elements of~$\As$.
+\medbreak
 
@@
 relations, nice bases and Hilbert series).
+\medbreak
 
@@
 trees~\cite{BN98} and the Buchberger algorithm for operads~\cite{DK10}.
+\medbreak
 
@@
 its Hilbert series (Proposition~\ref{prop:Hilbert_series_CAs_3}).
+\medbreak
 
@@
 binary tree $\Tfr$ is its number of leaves (resp. internal nodes).
+Recall that for any positive integer $n$,
+$\# \Mag(n)$ is the $n$th Catalan number
+$\Catalan(n) := \binom{2n - 2}{n - 1}\frac{1}{n}$.
+\medbreak
+
 Given a binary tree $\Tfr$, we denote by $ \PrefixWord(\Tfr)$ the
@@
 the lexicographic order $\leq$ induced by $\Zero < \Two$.
+\medbreak
 
@@
 relations and rewrite systems~\cite{BN98}.
+\medbreak
 
 Given an operad $\Oca \simeq \Mag/_{\Congr}$ where $\Congr$ is an operad
-congruence of $\Mag$, we say that $\Rew$ is an \Def{orientation} of
-$\Congr$ if the reflexive, transitive, and symmetric closure of
-$\RewContext$ is $\Congr$. We say that $\Rew$ is a \Def{convergent
-orientation} if $\RewContext$ is convergent. When $\Rew$ is a convergent
-orientation of $\Congr$, the set of all normal forms of $\RewContext$ is
-a \Def{Poincaré-Birkhoff-Witt basis} of the operad $\Oca$ and its
-elements are exactly the binary trees avoiding, as subtrees, the trees
-appearing as left members in $\Rew$.
+congruence of $\Mag$, we denote by $[\Tfr]_{\Congr}$ the
+$\Congr$-equivalence class of any $\Tfr \in \Mag$. Besides, we say that
+$\Rew$ is an \Def{orientation} of $\Congr$ if the reflexive, transitive,
+and symmetric closure of $\RewContext$ is $\Congr$. We say that $\Rew$
+is a \Def{convergent orientation} if $\RewContext$ is convergent. When
+$\Rew$ is a convergent orientation of $\Congr$, the set of all normal
+forms of $\RewContext$ is a \Def{Poincaré-Birkhoff-Witt basis} of the
+operad $\Oca$ and its elements are exactly the binary trees avoiding,
+as subtrees, the trees appearing as left members in~$\Rew$.
+\medbreak
 
@@
 $\Mag$ is terminating.
+\medbreak
 
@@
 \end{Lemma}
+\medbreak
 
@@
 rewrite relation is convergent.
+\medbreak
 
@@
 \section{Generalizations of the associative operad} \label{sec:CAs_d}
+\Todo{Write mini intro.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Comb associative operads}
+\Todo{Write mini intro.}
+
 It is known that the rewrite rule $\Rew$
@@
 basis of $\As$ is the set of all right comb binary trees.
-
+\Todo{SG: to maybe to move at another place. }
+\medbreak
+
+Let, for any $\gamma \geq 1$, the binary trees
+\begin{equation}
+    \LComb{\gamma} :=
+    \underbrace{(\dots (\Product \circ_1 \Product) \circ_1 \dots)
+        \circ_1 \Product}
+    _{\gamma \mbox{ \footnotesize operands}}
+\end{equation}
+and
+\begin{equation}
+    \RComb{\gamma} :=
+    \underbrace{\Product \circ_2
+        (\dots \circ_2 (\Product \circ_2 \Product) \dots)}
+    _{\gamma \mbox{ \footnotesize operands}}
+\end{equation}
+be respectively the left and the right comb of degree $\gamma$.
 Let us now define for any $\gamma \geq 1$ the \Def{$\gamma$-comb
@@
 operad congruence of $\Mag$ satisfying
-\begin{equation} \label{equ:congruence_Asd}
-    \underbrace{(\dots (\Product \circ_1 \Product) \circ_1 \dots)
-        \circ_1 \Product}
-    _{\gamma \mbox{ \footnotesize operands}}
-    \enspace \CongrCAs{\gamma} \enspace
-    \underbrace{\Product \circ_2
-        (\dots \circ_2 (\Product \circ_2 \Product) \dots)}
-    _{\gamma \mbox{ \footnotesize operands}}.
-\end{equation}
-In words, \eqref{equ:congruence_Asd} says that the left and the right
-comb binary trees of degree $\gamma$ are equivalent for
-$\CongrCAs{\gamma}$. Notice that $\CongrCAs{1}$ is trivial so that
+\begin{equation} \label{equ:congruence_CAs_gamma}
+    \LComb{\gamma} \enspace \CongrCAs{\gamma} \enspace \RComb{\gamma}
+\end{equation}
+Notice that $\CongrCAs{1}$ is trivial so that
 $\CAs{1} = \Mag$ and that $\CongrCAs{2}$ is the operad congruence
 defined by~\eqref{equ:congruence_as} so that $\CAs{2} = \As$.
-
-In the sequel we denote by $\LC{\gamma}$ and $\RC{\gamma}$ the left
-comb and the right comb of degree $\gamma$, respectively. Hence,
-$\CongrCAs{\gamma}$ is the congruence relation induced by
-$\LC{\gamma}\CongrCAs{\gamma}\RC{\gamma}$.
-
-Let
+Let also
 \begin{equation}
@@
 that, we provide a description of operads morphisms between the
-elements of $\CAsAll$.
-
-\begin{Proposition}\label{prop:morphisms_CAs_d}
-    Let $\gamma$ and $\gamma'$ be two positive integers. There exists at
-    most one operad morphism $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$.
-    This  morphism exists if and only if
-    \begin{math}
-        \LC{\gamma'}\CongrCAs{\gamma}\RC{\gamma'}
-    \end{math}
-    and it is surjective in this case. Moreover, $\varphi$ is injective
-    if and only if $\gamma = \gamma'$, that is if and only if
-    $\varphi$ is the identity morphism.
+elements of~$\CAsAll$.
+\medbreak
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{A lattice of operads}
+\Todo{Write mini intro.}
+
+\begin{Lemma} \label{lem:first_dimensions_CAs}
+    For any positive integers $\gamma$ and $n$ such that $\gamma \geq 2$
+    and $n \leq \gamma + 1$,
+    \begin{equation}
+        \# \CAs{\gamma}(n) =
+        \begin{cases}
+            \Catalan(n)
+                & \mbox{ if } n \leq \gamma, \\
+            \Catalan(\gamma + 1) - 1
+                & \mbox{ otherwise } (n = \gamma + 1).
+        \end{cases}
+    \end{equation}
+\end{Lemma}
+\begin{proof}
+    Since the equivalence relation $\CongrCAs{\gamma}$ is trivial on the
+    binary trees of degrees $d < \gamma$, and since a binary tree of
+    degree $d$ has arity $n := d + 1$, one has
+    $\# \CAs{\gamma}(n) = \# \Mag(n) = \Catalan(n)$ with $n \leq \gamma$.
+    Besides, by definition of $\CongrCAs{\gamma}$, all the
+    $\CongrCAs{\gamma}$-equivalence classes of binary trees of degree
+    $\gamma$ are trivial, except one consisting in the pair
+    $\left\{\LComb{\gamma}, \RComb{\gamma}\right\}$. Therefore, since a
+    binary tree of degree $d$ has arity $n := \gamma + 1$,
+    \begin{math}
+        \# \CAs{\gamma}(n)
+        = \# \Mag(\gamma + 1) - 1
+        = \Catalan(\gamma + 1) - 1.
+    \end{math}
+\end{proof}
+\medbreak
+
+\begin{Lemma} \label{lem:surjective_morphisms_CAs}
+    Let $\gamma$ and $\gamma'$ be two positive integers. If
+    $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$ is an operad morphism, then
+    it is surjective and is unique.
+\end{Lemma}
+\begin{proof}
+    The operad $\CAs{\gamma'}$ is generated by one binary generator
+    $[\Product]_{\CongrCAs{\gamma'}}$, so that $\varphi$ is entirely
+    determined by the image
+    $\varphi\left([\Product]_{\CongrCAs{\gamma'}}\right)$. Moreover,
+    $\varphi([\Product]_{\CongrCAs{\gamma'}})$ has to be of arity $2$ in
+    $\CAs{\gamma}$, so that we necessarily have
+    \begin{math}
+        \varphi\left([\Product]_{\CongrCAs{\gamma'}}\right)
+        =
+        [\Product]_{\CongrCAs{\gamma}}.
+    \end{math}
+    Hence, if $\varphi$ exists, it is the unique operad morphism from
+    $\CAs{\gamma'}$ to $\CAs{\gamma}$. In this case,
+    $[\Product]_{\CongrCAs{\gamma'}}$ being in the image of $\varphi$,
+    the latter is surjective.
+\end{proof}
+\medbreak
+
+\begin{Lemma} \label{lem:injective_morphisms_CAs}
+    Let $\gamma$ and $\gamma'$ be two positive integers and
+    $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$ be an operad morphism.
+    Then, $\varphi$ is injective if and only if $\gamma = \gamma'$.
+\end{Lemma}
+\begin{proof}
+    Assume that $\varphi$ is injective. By
+    Lemma~\ref{lem:surjective_morphisms_CAs}, $\varphi$ is also
+    surjective, so that $\varphi$ is an isomorphism. If
+    $\gamma \ne \gamma'$, by Lemma~\ref{lem:first_dimensions_CAs}, there
+    is a positive integer $n$ such that
+    $\# \CAs{\gamma}(n) \ne \# \CAs{\gamma'}(n)$. This is contradictory
+    with the fact that $\CAs{\gamma}$ and $\CAs{\gamma'}$ are
+    isomorphic. Hence, $\gamma = \gamma'$.
+    \smallbreak
+
+    Conversely, if $\gamma = \gamma'$, the only operad morphism from
+    $\CAs{\gamma}$ to itself sends the generator
+    $[\Product]_{\CongrCAs{\gamma}}$ to itself. This maps extends as
+    an operad morphism into the identity morphism which is of course
+    injective.
+\end{proof}
+\medbreak
+
+\begin{Lemma} \label{lem:morphism_CAs}
+    Let $\gamma$ and $\gamma'$ be two positive integers. There exists an
+    operad morphism $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$ if and only
+    if
+    \begin{math}
+        \LComb{\gamma'} \CongrCAs{\gamma} \RComb{\gamma'}.
+    \end{math}
+\end{Lemma}
+\begin{proof}
+    Assume that $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$ is an operad
+    morphism. By Lemma~\ref{lem:surjective_morphisms_CAs}, $\varphi$
+    satisfies
+    \begin{math}
+        \varphi\left(\left[\Tfr\right]_{\CongrCAs{\gamma'}}\right)
+        = \left[\Tfr\right]_{\CongrCAs{\gamma}}
+    \end{math}
+    for any binary tree $\Tfr$,
+    Since
+    \begin{math}
+        \varphi\left(
+        \left[\LComb{\gamma'}\right]_{\CongrCAs{\gamma'}}
+        \right)
+        =
+        \varphi\left(
+        \left[\RComb{\gamma'}\right]_{\CongrCAs{\gamma'}}
+        \right),
+    \end{math}
+    we have
+    \begin{math}
+        \left[\LComb{\gamma'}\right]_{\CongrCAs{\gamma}}
+        =
+        \left[\RComb{\gamma'}\right]_{\CongrCAs{\gamma}},
+    \end{math}
+    which is equivalent to the fact that
+    \begin{math}
+        \LComb{\gamma'} \CongrCAs{\gamma} \RComb{\gamma'}.
+    \end{math}
+    \smallbreak
+
+    Conversely, when
+    \begin{math}
+        \LComb{\gamma'}\CongrCAs{\gamma}\RComb{\gamma'},
+    \end{math}
+    let $\varphi:\CAs{\gamma'}(2) \to \CAs{\gamma}(2)$ be the map
+    defined by
+    \begin{math}
+        \varphi\left(
+        \left[\Product\right]_{\CongrCAs{\gamma'}}\right)
+        :=
+        \left[\Product\right]_{\CongrCAs{\gamma}}.
+    \end{math}
+    Now, since $\CongrCAs{\gamma}$ is coarser than $\CongrCAs{\gamma'}$,
+    $\varphi$ extends (in a unique way) into an operad morphism, whence
+    the statement of the lemma.
+\end{proof}
+\medbreak
+
+We define the binary relation $\OrdCAs$ on $\CAsAll$ as follows: we have
+$\CAs{\gamma} \OrdCAs \CAs{\gamma'}$ if and only if there exists a
+morphism $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$.
+\medbreak
+
+\begin{Proposition}\label{prop:poset_CAs}
+    The binary relation $\OrdCAs$ is a partial order relation on
+    $\CAsAll$.
 \end{Proposition}
 \begin{proof}
-    The operad $\CAs{\gamma'}$ is generated by one binary generator
-    $\Product$, so that $\varphi$ is entirely determined by
-    $\varphi\left(\Product\right)$. Moreover, $\varphi(\Product)$ has
-    to be of arity $2$ in $\CAs{\gamma}$, so that $\varphi(\Product)$
-    has to be equal to $\Product \in \CAs{\gamma}$. Hence, if $\varphi$
-    exists, it is the unique operad morphism from $\CAs{\gamma'}$ and
-    $\CAs{\gamma}$, and in this case, $\Product \in \CAs{\gamma'}$
-    being in the image of $\varphi$, the latter is surjective.
-    Moreover, $\varphi$ is well defined if and only if
-    $\varphi\left(\LC{\gamma'}\right)$ and
-    $\varphi\left(\RC{\gamma'}\right)$ are equal in $\CAs{\gamma}$,
-    that is if and only if
-    $\LC{\gamma'} \CongrCAs{\gamma} \RC{\gamma'}$. In particular, if
-    $\gamma'$ is smaller than $\gamma$, then there does not exist any
-    morphism $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$.
-    \Todo{Faux car on peut avoir $\gamma' = 1$, puisque
-    $\LC{1} = \RC{1}$.}
-    Moreover, if $\gamma'$ is smaller than $\gamma$, the cardinality of
-    $\CAs{\gamma'}\left(\gamma\right)$ is equal to the cardinality of
-    $\CAs{\gamma}(\gamma)$ plus one. Hence, if there exists an injective
-    morphism $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$, we must have
-    $\gamma = \gamma'$, and in this case, $\varphi$ is the identity
-    morphism.
+    The binary relation $\OrdCAs$ is reflexive since there exists the
+    identity morphism of $\CAs{\gamma}$ for every positive integer
+    $\gamma$. Let us now assume that
+    $\varphi:\CAs{\gamma''} \to \CAs{\gamma'}$ and
+    $\psi:\CAs{\gamma'} \to \CAs{\gamma}$ are two operad morphisms. By
+    Lemma~\ref{lem:morphism_CAs}, one has
+    $\LComb{\gamma''} \CongrCAs{\gamma'} \RComb{\gamma''}$ and
+    $\LComb{\gamma'} \CongrCAs{\gamma} \RComb{\gamma'}$. This implies
+    that $\CongrCAs{\gamma}$ is coarser than $\CongrCAs{\gamma'}$ and
+    that $\CongrCAs{\gamma'}$ is coarser that $\CongrCAs{\gamma''}$. Now,
+    again by Lemma~\ref{lem:morphism_CAs}, $\psi \circ \varphi$ is an
+    operad morphism. Hence, $\OrdCAs$ is transitive. Finally, let us
+    assume that there exist morphisms
+    $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$ and
+    $\psi:\CAs{\gamma}\to\CAs{\gamma'}$. In particular,
+    $\psi \circ \varphi$ and $\varphi \circ \psi$ are endomorphisms of
+    $\CAs{\gamma'}$ and $\CAs{\gamma}$, respectively. From
+    Lemma~\ref{lem:injective_morphisms_CAs}, these two morphisms are
+    identity morphisms, so that $\varphi$ and $\psi$ are injective. From
+    Lemma~\ref{lem:injective_morphisms_CAs}, $\gamma$ and $\gamma'$ are
+    equal, which proves that $\OrdCAs$ is anti-symmetric. Hence,
+    $\OrdCAs$ is a partial order.
 \end{proof}
-
-We define the binary relation $\preceq$ on $\CAsAll$ as follows: we have
-$\CAs{\gamma}\preceq\CAs{\gamma'}$ if and only if there exists a
-morphism $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$.
-
-\begin{Proposition}\label{prop:poset_CAs}
-    The binary relation $\preceq$ is a partially order on $\CAsAll$,
-    that is $\left(\CAsAll,\ \preceq\right)$ is a poset.
+\medbreak
+
+In order to show that the poset $\left(\CAsAll, \OrdCAs\right)$ is also
+a lattice, that is two elements of $\CAsAll$ admit lower-bounds and
+upper-bounds, we relate $\left(\CAsAll, \OrdCAs\right)$ with the lattice
+of integers $\left(\N,\mid, \gcd, \lcm\right)$, where $\mid$ denotes the
+division relation, $\gcd$ denotes the greatest common divisor, and
+$\lcm$ the least common multiple operators, respectively. In order to
+obtain this relationship, we introduce the notion of \Def{left rank} for
+any binary tree $\Tfr$ as the number $\LBranch(\Tfr)$ of internal nodes
+in the left branch beginning at the root of $\Tfr$.
+For instance,
+\begin{equation}
+    \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
+        \node(0)at(0.00,-4.50){};
+        \node(2)at(2.00,-4.50){};
+        \node(4)at(4.00,-4.50){};
+        \node(6)at(6.00,-6.75){};
+        \node(8)at(8.00,-6.75){};
+        \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
+        \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
+        \node[NodeST](5)at(5.00,-2.25){\begin{math}\Product\end{math}};
+        \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
+        \draw[Edge](0)--(1);
+        \draw[Edge](1)--(3);
+        \draw[Edge](2)--(1);
+        \draw[Edge](4)--(5);
+        \draw[Edge](5)--(3);
+        \draw[Edge](6)--(7);
+        \draw[Edge](7)--(5);
+        \draw[Edge](8)--(7);
+        \node(r)at(3.00,1.74){};
+        \draw[Edge](r)--(3);
+    \end{tikzpicture}
+    \xmapsto{\; \LBranch\; } 2
+    \qquad \mbox{and} \qquad
+    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
+        \node(0)at(0.00,-3.60){};
+        \node(2)at(2.00,-5.40){};
+        \node(4)at(4.00,-7.20){};
+        \node(6)at(6.00,-7.20){};
+        \node(8)at(8.00,-1.80){};
+        \node[NodeST](1)at(1.00,-1.80){\begin{math}\Product\end{math}};
+        \node[NodeST](3)at(3.00,-3.60){\begin{math}\Product\end{math}};
+        \node[NodeST](5)at(5.00,-5.40){\begin{math}\Product\end{math}};
+        \node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
+        \draw[Edge](0)--(1);
+        \draw[Edge](1)--(7);
+        \draw[Edge](2)--(3);
+        \draw[Edge](3)--(1);
+        \draw[Edge](4)--(5);
+        \draw[Edge](5)--(3);
+        \draw[Edge](6)--(5);
+        \draw[Edge](8)--(7);
+        \node(r)at(7.00,1.5){};
+        \draw[Edge](r)--(7);
+    \end{tikzpicture}
+    \xmapsto{\; \LBranch\; } 2.
+\end{equation}
+The left rank of $\Tfr$ is represented as follows: \Todo{???}
+\medbreak
+
+\begin{Lemma}\label{lem:left_rank_and_CongrCAs}
+    Let $\gamma$ be a strictly positive integer and let $\Tfr$ and
+    $\Tfr'$ be two binary trees. If $\Tfr \CongrCAs{\gamma} \Tfr'$, then
+    \begin{equation}
+        \LBranch(\Tfr) \mod \gamma - 1
+        \enspace = \enspace
+        \LBranch(\Tfr') \mod \gamma - 1.
+    \end{equation}
+\end{Lemma}
+\begin{proof}
+    Let $\Rew$ be the rewrite relation on $\Mag$ induced by the rewrite
+    rule $\LComb{\gamma} \Rew \RComb{\gamma}$. In the rest of the
+    proof, $\Tfr$ and $\Tfr$ are two binary trees.
+    \smallbreak
+
+    First, we show that $\Tfr \Rew \Tfr'$ implies that
+    $\LBranch\left(\Tfr'\right) - \LBranch\left(\Tfr\right)$ is
+    divisible by $\gamma - 1$. \Todo{à faire.}
+    \smallbreak
+
+    Assume that $\Tfr \RewRT \Tfr'$, so that there exist binary trees
+    $\Tfr_1$, \dots, $\Tfr_k$ such that $\Tfr_1 = \Tfr$,
+    $\Tfr_k = \Tfr'$ and for every $i \in \{1, \dots, k - 1\}$, we have
+    $\Tfr_i\Rew \Tfr_{i + 1}$. The integer
+    \begin{math}
+        \LBranch\left(\Tfr_{i + 1}\right)
+        -
+        \LBranch\left(\Tfr_i\right)
+    \end{math}
+    is divisible by $\gamma - 1$ from the first part of the proof, so
+    that $\LBranch\left(\Tfr'\right) - \LBranch\left(\Tfr\right)$ is
+    divisible by $\gamma-1$.
+    \smallbreak
+
+    Assume that $\Tfr \RewRTS \Tfr'$, so that there exist binary trees
+    $\Tfr_1$, \dots, $\Tfr_k$ such that $\Tfr_1 = \Tfr$,
+    $\Tfr_k = \Tfr'$ and for every $i \in \{1, \dots, k - 1\}$, we have
+    $\Tfr_i \RewRTS \Tfr_{i + 1}$ or $\Tfr_{i + 1} \RewRTS \Tfr_i$.
+    From the second part of the proof, the integer
+    \begin{math}
+        \LBranch\left(\Tfr_{i + 1}\right)
+        -
+        \LBranch\left(\Tfr_i\right)
+    \end{math}
+    is divisible by $\gamma - 1$, so that
+    $\LBranch\left(\Tfr'\right) - \LBranch\left(\Tfr\right)$ is
+    divisible by $\gamma - 1$.
+    \smallbreak
+
+    The congruence $\CongrCAs{\gamma}$ is the equivalence relation
+    induced by $\Rew$, that is we have $\Tfr \CongrCAs{\gamma} \Tfr'$ if
+    and only if $\Tfr \RewRTS \Tfr'$. Hence, from the third part of
+    the proof, $\Tfr \CongrCAs{\gamma} \Tfr'$ implies that
+    \begin{math}
+        \LBranch\left(\Tfr'\right) - \LBranch\left(\Tfr\right)
+    \end{math}
+    is divisible by $\gamma - 1$.
+\end{proof}
+\medbreak
+
+\begin{Proposition} \label{prop:division_CAs}
+    Let $\gamma$ and $\gamma'$ be two positive integers.Then, there
+    exists a morphism $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$ if and
+    only if $\left(\gamma - 1\right) \mid \left(\gamma' - 1\right)$.
 \end{Proposition}
 \begin{proof}
-    The binary relation $\preceq$ is reflexive since there exists the
-    identity morphism of $\CAs{\gamma}$ for every positive integer
-    $\gamma$. It is transitive since if there exist two morphisms
-    $\varphi:\CAs{\gamma}\to\CAs{\gamma'}$ and
-    $\psi:\CAs{\gamma''}\to\CAs{\gamma'}$, then $\psi\circ\varphi$ is a
-    morphism from $\CAs{\gamma''}$ to $\CAs{\gamma}$. Now, let us assume
-    that there exist morphisms $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$
-    and $\psi:\CAs{\gamma}\to\CAs{\gamma'}$. In particular,
-    $\psi\circ\varphi$ and $\varphi\circ\psi$ are endomorphisms of
-    $\CAs{\gamma'}$ and $\CAs{\gamma}$, respectively. From
-    Proposition~\ref{prop:morphisms_CAs_d}, these two morphisms are
-    identity morphisms, so that $\varphi$ and $\psi$ are injective. From
-    Proposition~\ref{prop:morphisms_CAs_d}, $\gamma$ and $\gamma'$ are
-    equal, which proves that $\preceq$ is anti-symmetric, hence a
-    partial order.
+    From Lemma~\ref{lem:morphism_CAs}, it is enough to show that
+    $\LComb{\gamma'} \CongrCAs{\gamma} \RComb{\gamma'}$ if and only if
+    $\left(\gamma-1\right) \mid \left(\gamma'-1\right)$. If
+    $\LComb{\gamma'}\CongrCAs{\gamma}\RComb{\gamma'}$, from
+    Lemma~\ref{lem:left_rank_and_CongrCAs},
+    \begin{math}
+        \LBranch\left(\LComb{\gamma'}\right)
+        - \LBranch\left(\RComb{\gamma'}\right)
+        = \gamma' - 1
+    \end{math}
+    is divisible by $\gamma-1$, which shows the direct implication.
+    \smallbreak
+
+    Conversely, if
+    $\left(\gamma-1\right) \mid \left(\gamma'-1\right)$, the rewrite
+    rule $\LComb{\gamma} \Rew \RComb{\gamma}$ induces the
+    sequence
+    \begin{multline}
+        \LComb{\gamma'} \enspace = \enspace
+        \begin{tikzpicture}[xscale=.19,yscale=.25,Centering]
+            \node(0)at(0.00,-13.12){};
+            \node(10)at(10.00,-5.62){};
+            \node(12)at(12.00,-3.75){};
+            \node(14)at(14.00,-1.88){};
+            \node(2)at(2.00,-13.12){};
+            \node(4)at(4.00,-11.25){};
+            \node(6)at(6.00,-9.38){};
+            \node(8)at(8.00,-7.50){};
+            \node[NodeST](1)at(1.00,-11.25)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](11)at(11.00,-1.88)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](13)at(13.00,0.00)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](3)at(3.00,-9.38)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](5)at(5.00,-7.50)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](7)at(7.00,-5.62)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](9)at(9.00,-3.75)
+                {\begin{math}\Product\end{math}};
+            \draw[Edge](0)--(1);
+            \draw[Edge,dotted](1)--(3);
+            \draw[Edge](10)--(9);
+            \draw[Edge](11)--(13);
+            \draw[Edge](12)--(11);
+            \draw[Edge](14)--(13);
+            \draw[Edge](2)--(1);
+            \draw[Edge,dotted](3)--(5);
+            \draw[Edge](4)--(3);
+            \draw[Edge,dotted](5)--(7);
+            \draw[Edge](6)--(5);
+            \draw[Edge](7)--(9);
+            \draw[Edge](8)--(7);
+            \draw[Edge,dotted](9)--(11);
+            \node(r)at(13.00,1.41){};
+            \draw[Edge](r)--(13);
+            %
+            \node[fit=(1)(3),rotate fit=0,inner sep=0pt,
+                rounded corners,draw=Col5!80]{};
+            \node[fit=(5)(7),rotate fit=0,inner sep=0pt,
+                rounded corners,draw=Col5!80]{};
+            \node[fit=(9)(11),rotate fit=0,inner sep=0pt,
+                rounded corners,draw=Col5!80]{};
+        \end{tikzpicture}
+        \enspace \Rew \enspace
+            \begin{tikzpicture}[xscale=.19,yscale=.2,Centering]
+            \node(0)at(0.00,-12.50){};
+            \node(10)at(10.00,-5.00){};
+            \node(12)at(12.00,-7.50){};
+            \node(14)at(14.00,-7.50){};
+            \node(2)at(2.00,-12.50){};
+            \node(4)at(4.00,-10.00){};
+            \node(6)at(6.00,-7.50){};
+            \node(8)at(8.00,-5.00){};
+            \node[NodeST](1)at(1.00,-10.00)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](11)at(11.00,-2.50)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](13)at(13.00,-5.00)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](3)at(3.00,-7.50)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](5)at(5.00,-5.00)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](7)at(7.00,-2.50)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](9)at(9.00,0.00)
+                {\begin{math}\Product\end{math}};
+            \draw[Edge](0)--(1);
+            \draw[Edge,dotted](1)--(3);
+            \draw[Edge](10)--(11);
+            \draw[Edge](11)--(9);
+            \draw[Edge](12)--(13);
+            \draw[Edge,dotted](13)--(11);
+            \draw[Edge](14)--(13);
+            \draw[Edge](2)--(1);
+            \draw[Edge,dotted](3)--(5);
+            \draw[Edge](4)--(3);
+            \draw[Edge,dotted](5)--(7);
+            \draw[Edge](6)--(5);
+            \draw[Edge](7)--(9);
+            \draw[Edge](8)--(7);
+            \node(r)at(9.00,1.88){};
+            \draw[Edge](r)--(9);
+            %
+            \node[fit=(1)(3),rotate fit=0,inner sep=0pt,
+                rounded corners,draw=Col5!80]{};
+            \node[fit=(5)(7),rotate fit=0,inner sep=0pt,
+                rounded corners,draw=Col5!80]{};
+            \node[fit=(11)(13),rotate fit=0,inner sep=0pt,
+                rounded corners,draw=Col5!80]{};
+        \end{tikzpicture}
+        \enspace \Rew \enspace
+        \begin{tikzpicture}[xscale=.19,yscale=.2,Centering]
+            \node(0)at(0.00,-7.50){};
+            \node(10)at(10.00,-10.00){};
+            \node(12)at(12.00,-12.50){};
+            \node(14)at(14.00,-12.50){};
+            \node(2)at(2.00,-7.50){};
+            \node(4)at(4.00,-5.00){};
+            \node(6)at(6.00,-5.00){};
+            \node(8)at(8.00,-7.50){};
+            \node[NodeST](1)at(1.00,-5.00)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](11)at(11.00,-7.50)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](13)at(13.00,-10.00)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](3)at(3.00,-2.50)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](5)at(5.00,0.00)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](7)at(7.00,-2.50)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](9)at(9.00,-5.00)
+                {\begin{math}\Product\end{math}};
+            \draw[Edge](0)--(1);
+            \draw[Edge,dotted](1)--(3);
+            \draw[Edge](10)--(11);
+            \draw[Edge](11)--(9);
+            \draw[Edge](12)--(13);
+            \draw[Edge,dotted](13)--(11);
+            \draw[Edge](14)--(13);
+            \draw[Edge](2)--(1);
+            \draw[Edge,dotted](3)--(5);
+            \draw[Edge](4)--(3);
+            \draw[Edge](6)--(7);
+            \draw[Edge](7)--(5);
+            \draw[Edge](8)--(9);
+            \draw[Edge,dotted](9)--(7);
+            \node(r)at(5.00,1.88){};
+            \draw[Edge](r)--(5);
+            %
+            \node[fit=(1)(3),rotate fit=0,inner sep=0pt,
+                rounded corners,draw=Col5!80]{};
+            \node[fit=(7)(9),rotate fit=0,inner sep=0pt,
+                rounded corners,draw=Col5!80]{};
+            \node[fit=(11)(13),rotate fit=0,inner sep=0pt,
+                rounded corners,draw=Col5!80]{};
+        \end{tikzpicture} \\
+        \enspace \RewRT \enspace
+        \begin{tikzpicture}[xscale=.19,yscale=.25,Centering]
+            \node(0)at(0.00,-1.88){};
+            \node(10)at(10.00,-11.25){};
+            \node(12)at(12.00,-13.12){};
+            \node(14)at(14.00,-13.12){};
+            \node(2)at(2.00,-3.75){};
+            \node(4)at(4.00,-5.62){};
+            \node(6)at(6.00,-7.50){};
+            \node(8)at(8.00,-9.38){};
+            \node[NodeST](1)at(1.00,0.00)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](11)at(11.00,-9.38)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](13)at(13.00,-11.25)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](3)at(3.00,-1.88)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](5)at(5.00,-3.75)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](7)at(7.00,-5.62)
+                {\begin{math}\Product\end{math}};
+            \node[NodeST](9)at(9.00,-7.50)
+                {\begin{math}\Product\end{math}};
+            \draw[Edge](0)--(1);
+            \draw[Edge](10)--(11);
+            \draw[Edge,dotted](11)--(9);
+            \draw[Edge](12)--(13);
+            \draw[Edge,dotted](13)--(11);
+            \draw[Edge](14)--(13);
+            \draw[Edge](2)--(3);
+            \draw[Edge](3)--(1);
+            \draw[Edge](4)--(5);
+            \draw[Edge,dotted](5)--(3);
+            \draw[Edge](6)--(7);
+            \draw[Edge](7)--(5);
+            \draw[Edge](8)--(9);
+            \draw[Edge,dotted](9)--(7);
+            \node(r)at(1.00,1.41){};
+            \draw[Edge](r)--(1);
+            %
+            \node[fit=(3)(5),rotate fit=0,inner sep=0pt,
+                rounded corners,draw=Col5!80]{};
+            \node[fit=(7)(9),rotate fit=0,inner sep=0pt,
+                rounded corners,draw=Col5!80]{};
+            \node[fit=(11)(13),rotate fit=0,inner sep=0pt,
+                rounded corners,draw=Col5!80]{};
+        \end{tikzpicture}
+        \enspace = \enspace
+        \RComb{\gamma'}
+    \end{multline}
+    of rewriting steps, where squared regions denotes left or right
+    comb trees of degree $\gamma - 1$. Hence, we have
+    $\LComb{\gamma'}\CongrCAs{\gamma}\RComb{\gamma'}$.
 \end{proof}
-
-In order to show that the poset $\left(\CAsAll,\ \preceq\right)$
-extends into a lattice, that is two elements of $\CAsAll$ admit
-lower-bounds and upper-bounds, we relate
-$\left(\CAsAll,\ \preceq\right)$ to the lattice of integers
-$\left(\N,\ \mid,\ \gcd,\ \lcm\right)$, where $\mid$
-denotes the division relation, $\gcd$ denotes the \emph{greatest common divisor} and $\lcm$ the \emph{least common multiple}
-operators, respectively. In order to obtain this relationship, we introduce the notion of
-\Def{left rank} of an element $\Tfr \in\Mag$: this is the number
-$\LBranch(\Tfr)$ of internal nodes in the left branch
-beginning at the root of $\Tfr$. The left rank of $\Tfr$ is represented as follows:
-\[\textbf{PICTURE}\]
-
-\begin{Lemma}\label{lem:left_rank_and_CongrCAs}
-  Let $\gamma$ be a strictly positive integer and let $t$ and $t'$ be two elements of $\Mag$. If
-  $t\CongrCAs{\gamma}t'$, then $\emph{lr}\left(t\right)$ and $\emph{lr}\left(t'\right)$ are equal modulo $\gamma-1$: $\emph{lr}\left(t\right)\equiv\emph{lr}\left(t'\right) [\gamma-1]$.
-\end{Lemma}
-
-\begin{proof}
-  Let $\Rew$ be the rewrite relation on $\Mag$ induced by the rewrite rule
-  $\LC{\gamma}\Rew\RC{\gamma}$. In the rest of the proof we fix two elements $t$ and $t'$ of $\Mag$.
-
-  First, we show that $t\Rew t'$ implies that $\text{lr}\left(t'\right)-\text{lr}\left(t\right)$
-  is divisible by $\gamma-1$ \textbf{TODO}.
-
-  Assume that $t\overset{*}{\Rew}t'$, so that there exist elements $t_1,\ \cdots,\ t_n$
-  of $\Mag$ such that $t_1=t$, $t_n=t'$ and for every $i\in\{1,\cdots,n-1\}$, we have
-  $t_i\Rew t_{i+1}$. The integer $\text{lr}\left(t_{i+1}\right)-\text{lr}\left(t_i\right)$
-  is divisible by $\gamma-1$ from the first part of the proof, so that
-  $\text{lr}\left(t'\right)-\text{lr}\left(t\right)$ is divisible by $\gamma-1$.
-
-  Assume that $t\overset{*}{\leftrightarrow}t'$, so that there exist elements $t_1,\ \cdots,\ t_n$
-  of $\Mag$ such that $t_1=t$, $t_n=t'$ and for every $i\in\{1,\cdots,n-1\}$, we have
-  $t_i\overset{*}{\Rew}t_{i+1}$ or $t_{i+1}\overset{*}{\Rew}t_i$. From the second part of the proof,
-  $\text{lr}\left(t_{i+1}\right)-\text{lr}\left(t_i\right)$ is divisible by $\gamma-1$, so that
-  $\text{lr}\left(t'\right)-\text{lr}\left(t\right)$ is divisible by $\gamma-1$.
-
-  The congruence relation $\CongrCAs{\gamma}$ is the equivalence relation induced by $\Rew$, that
-  is we have $t\CongrCAs{\gamma}t'$ if and only if $t\overset{*}{\leftrightarrow}t'$. Hence, from the
-  third part of the proof, $t\CongrCAs{\gamma}t'$ implies that
-  $\text{lr}\left(t'\right)-\text{lr}\left(t\right)$ is divisible by $\gamma-1$.
-  \end{proof}
-
-\begin{Proposition} \label{prop:division_CAs}
-  Let $\gamma$ and $\gamma'$ be two strictly positive integers. There exists a morphism
-  $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$ if and only if $\left(\gamma-1\right)\mid\left(\gamma'-1\right)$.
-\end{Proposition}
-\begin{proof}
-  From Proposition~\ref{prop:morphisms_CAs_d}, it is sufficient to show that $\LC{\gamma'}\CongrCAs{\gamma}\RC{\gamma'}$
-  if and only if $\left(\gamma-1\right)\mid\left(\gamma'-1\right)$. If $\LC{\gamma'}\CongrCAs{d}\RC{\gamma'}$, from
-  Lemma~\ref{lem:left_rank_and_CongrCAs}, $\text{lr}\left(\LC{\gamma'}\right)-\text{lr}\left(\RC{\gamma'}\right)=\gamma'-1$
-  is divisible by $\gamma-1$, which shows the direct implication. Conversely, if
-  $\left(\gamma-1\right)\mid\left(\gamma'-1\right)$, the rewrite rule $\LC{\gamma}\Rew\RC{\gamma}$ induces the
-  following sequence of rewriting steps:
-  \[\textbf{Rewriting sequence from left comb of degree d' to right comb of degree d'}\]
-  Hence, we have $\LC{\gamma'}\CongrCAs{\gamma}\RC{\gamma'}$.
-   \end{proof}
-
-Proposition~\ref{prop:division_CAs} implies the following:
+\medbreak
+
+Proposition~\ref{prop:division_CAs} implies the following result.
+\medbreak
+
 \begin{Theorem}\label{thm:lattice_CAs}
-  The poset $\left(\emph{CAs},\ \preceq\right)$ extends into a lattice
-  $\left(\emph{CAs},\ \preceq,\ \wedge,\ \vee\right)$, where the lower-
-  bound $\wedge$ and the upper-bound $\vee$ are defined as follows:
-  \[\CAs{\gamma}\wedge\CAs{\gamma'}=\CAs{\text{gcd}\left(\gamma-1,\ \gamma'-1\right)}\
-  \text{and}\ \CAs{\gamma}\vee\CAs{\gamma'}=\CAs{\text{lcm}\left(\gamma-1,\ \gamma'-1\right)}.\]
+    The poset $\left(\CAsAll, \OrdCAs\right)$ is a lattice where
+    the lower-bound and upper-bound satisfy, for any positive integers
+    $\gamma$ and $\gamma'$,
+    \begin{equation}
+        \CAs{\gamma} \wedge \CAs{\gamma'}
+        = \CAs{\gcd \left(\gamma-1, \gamma'-1\right)}
+    \end{equation}
+    and
+    \begin{equation}
+        \CAs{\gamma} \vee \CAs{\gamma'}
+        = \CAs{\lcm \left(\gamma-1, \gamma'-1\right)}.
+    \end{equation}
 \end{Theorem}
+\medbreak
 
@@
 lexicographically greater than the prefix word of the right one.
+\medbreak
 
@@
 branching pair which is not joinable.
+\medbreak
 
@@
 when $ 1 \leq n \leq 14$. Hence, we get our following main result.
+\medbreak
 
@@
 \end{Theorem}
+\medbreak
 
@@
 the following consequences.
+\medbreak
 
@@
 \end{Proposition}
+\medbreak
 
@@
 following result.
+\medbreak
 
@@
 $\# \CAs{3}(n) = n + 3$.
+\medbreak
 
@@
 only $\CAs{3}$ seems to have oscillating first dimensions.
+\medbreak
 
@@
 vector spaces.
+\medbreak
 
@@
 on the obtained operads.
+\medbreak
 

### 2018-06-29 Article.tex
Ajout fichier section opérads magamtiques
Restructuration

--- 2018-06-05 Article.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Introduction}
-Associative algebras are spaces endowed with a binary product $\Product$
-satisfying among others the associativity law
-\begin{math}
-    (x_1 \Product x_2) \Product x_3 = x_1 \Product (x_2 \Product x_3)
-\end{math}.
-It is well-known that the associative algebras are representations of
-the associative (nonsymmetric) operad $\As$. This operad can be seen as
-the quotient of the magmatic operad $\Mag$ (the free operad of binary
-trees on the binary generator~$\Product$) by the operad congruence
-$\Congr$ satisfying
-\begin{equation} \label{equ:congruence_as}
-    \begin{tikzpicture}[xscale=.24,yscale=.24,Centering]
-        \node(0)at(0.00,-3.33){};
-        \node(2)at(2.00,-3.33){};
-        \node(4)at(4.00,-1.67){};
-        \node[NodeST](1)at(1.00,-1.67)
-            {\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,0.00)
-            {\begin{math}\Product\end{math}};
-        \draw[Edge](0)--(1);
-        \draw[Edge](1)--(3);
-        \draw[Edge](2)--(1);
-        \draw[Edge](4)--(3);
-        \node(r)at(3.00,1.5){};
-        \draw[Edge](r)--(3);
-    \end{tikzpicture}
-    \Congr
-    \begin{tikzpicture}[xscale=.24,yscale=.24,Centering]
-        \node(0)at(0.00,-1.67){};
-        \node(2)at(2.00,-3.33){};
-        \node(4)at(4.00,-3.33){};
-        \node[NodeST](1)at(1.00,0.00)
-                {\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,-1.67)
-                {\begin{math}\Product\end{math}};
-        \draw[Edge](0)--(1);
-        \draw[Edge](2)--(3);
-        \draw[Edge](3)--(1);
-        \draw[Edge](4)--(3);
-        \node(r)at(1.00,1.5){};
-        \draw[Edge](r)--(1);
-    \end{tikzpicture}\,.
-\end{equation}
-These two binary trees are the syntax trees of the expressions appearing
-in the above associativity law.
-
-In a more combinatorial context and regardless of the theory of operads,
-the Tamari order is a partial order on the set of the binary trees
-having a fixed number of internal nodes $d$. This order is generated by
-the covering relation consisting in rewriting a tree $\Tfr$ into a tree
-$\Tfr'$ by replacing a subtree of $\Tfr$ of the form of the left member
-of~\eqref{equ:congruence_as} into a tree of the form of the right member
-of~\eqref{equ:congruence_as}. This transformation is known in a computer
-science context as the right rotation operation~\cite{Knu98} and
-intervenes in algorithms involving binary search trees~\cite{AVL62}. The
-partial order hence generated by the right rotation operation is known
-as the Tamari order~\cite{Tam62} and has a lot of combinatorial and
-algebraic properties (see for instance~\cite{HT72,Cha06}).
-
-A first connection between the associative operad and the Tamari order
-is based upon the fact that the orientation of~\eqref{equ:congruence_as}
-from left to right provides a convergent orientation (a terminating and
-confluent rewrite relation) of the congruence $\Congr$. The normal
-forms of the rewrite relation induced by the rewrite rule obtained by
-orienting~\eqref{equ:congruence_as} from left to right are right comb
-binary trees and are hence in one-to-one correspondence with the
-elements of~$\As$.
-
-This work is intended to be a first strike in the study of the eventual
-links between the Tamari order and some quotients of the operad $\Mag$.
-In the long run, we would like to study quotients $\Mag/_{\Congr}$ of
-$\Mag$ where $\Congr$ is an operad congruence generated by equivalence
-classes of trees of a fixed degree. In particular, we would like to know
-if $\Congr$ is generated by equivalence classes of trees forming
-intervals of the Tamari order leads to algebraic properties for
-$\Mag/_{\Congr}$ (like the description of orientations of its space of
-relations, nice bases and Hilbert series).
-
-We focus here on one of these quotients $\CAs{3}$ which is the operad
-describing the category of the algebras equipped with a binary product
-$\Product$ and subjected to the relation
-\begin{math}
-    ((x_1 \Product x_2) \Product x_3) \Product x_4
-    =
-    x_1 \Product (x_2 \Product (x_3 \Product x_4))
-\end{math}.
-This is a kind of associativity law in higher degree $d = 3$. This
-operad is generated by an equivalence class of trees which is not an
-interval for the Tamari order. As preliminary computer experiments show,
-$\CAs{3}$ has oscillating first dimensions
-(see~\eqref{equ:dimensions_CAs_3}), what is rather unusual among all
-known operads. In this paper, we provide an orientation of the space of
-relations of $\CAs{3}$. For this, we use rewrite systems on
-trees~\cite{BN98} and the Buchberger algorithm for operads~\cite{DK10}.
-
-This text is presented as follows. Section~\ref{sec:operad_Mag} contains
-preliminaries about the magmatic operad and rewrite relations on trees.
-In Section~\ref{sec:CAs_d}, we define the operad $\CAs{3}$ as a
-particular case of a more general construction of generalizations
-$\CAs{d}$, $d \geq 1$, of $\As$. Finally, Section~\ref{sec:CAs_3}
-contains the orientation of the space of relations of
-$\CAs{3}$ (Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}). As
-consequences, we obtain for $\CAs{3}$
-the description of one of its Poincaré-Birkhoff-Witt bases
-(Proposition~\ref{prop:PBW_basis_CAs_3}) and the description of
-its Hilbert series (Proposition~\ref{prop:Hilbert_series_CAs_3}).
+\input{Introduction}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The magmatic operad, quotients, and rewrite relations}
-\label{sec:operad_Mag}
-We consider nonsymmetric set-theoretic operads. Let $\Oca$ be such an
-operad. We denote respectively by $\circ_i$ and $\circ$ the partial and
-complete compositions of $\Oca$. For any $n \geq 1$, $\Oca(n)$ is the
-set of the elements $x$ of $\Oca$ of arity $|x| = n$. We denote
-by $\Mag$ the magmatic operad, that is the free operad over one binary
-generator $\Product$, and we represent the elements of $\Mag$ by binary
-trees. The \Def{arity} $|\Tfr|$ (resp. \Def{degree} $\Deg(\Tfr)$) of a
-binary tree $\Tfr$ is its number of leaves (resp. internal nodes).
-Given a binary tree $\Tfr$, we denote by $ \PrefixWord(\Tfr)$ the
-\Def{prefix word} of $\Tfr$, that is the word on $\{\Zero, \Two\}$
-obtained by a left to right depth-first traversal of $\Tfr$ and by
-writing $\Zero$ (resp. $\Two$) when a leaf (resp. an internal node) is
-encountered. The set of all words on $\{\Zero, \Two\}$ is endowed with
-the lexicographic order $\leq$ induced by $\Zero < \Two$.
-
-If $\Rew$ is a rewrite rule on $\Mag$ such that $\Sfr \Rew \Sfr'$
-implies $|\Sfr| = |\Sfr'|$, we denote by $\RewContext$ the
-\Def{rewrite relation induced} by $\Rew$. Formally we have
-\begin{math}
-    \Tfr\circ_i\left(\Sfr\circ\left[\Rfr_1,\dots,\Rfr_{n}\right]\right)
-    \RewContext
-    \Tfr\circ_i\left(\Sfr'\circ\left[\Rfr_1,\dots,\Rfr_{n}\right]\right)
-\end{math},
-if $\Sfr \Rew \Sfr'$ where $n = |\Sfr|$, and $\Tfr$, $\Rfr_1$, \dots,
-$\Rfr_n$ are binary trees. In other words, one has
-$\Tfr \RewContext \Tfr'$ if it is possible to obtain $\Tfr'$ from $\Tfr$
-by replacing a subtree $\Sfr$ of $\Tfr$ by $\Sfr'$ whenever
-$\Sfr \Rew \Sfr'$. We use here the standard terminology
-(\Def{terminating}, \Def{confluent}, \Def{convergent}, \Def{branching
-pair}, \Def{joinable}, \Def{normal form}, {\em etc.}) about rewrite
-relations and rewrite systems~\cite{BN98}.
-
-Given an operad $\Oca \simeq \Mag/_{\Congr}$ where $\Congr$ is an operad
-congruence of $\Mag$, we say that $\Rew$ is an \Def{orientation} of
-$\Congr$ if the reflexive, transitive, and symmetric closure of
-$\RewContext$ is $\Congr$. We say that $\Rew$ is a \Def{convergent
-orientation} if $\RewContext$ is convergent. When $\Rew$ is a convergent
-orientation of $\Congr$, the set of all normal forms of $\RewContext$ is
-a \Def{Poincaré-Birkhoff-Witt basis} of the operad $\Oca$ and its
-elements are exactly the binary trees avoiding, as subtrees, the trees
-appearing as left members in $\Rew$.
-
-We shall use the following criterion to prove that a rewrite relation on
-$\Mag$ is terminating.
-
-\begin{Lemma}\label{lem:prefix_word_termination}
-    Let $\Rew$ be a rewrite rule on $\Mag$. If for any
-    $\Tfr, \Tfr' \in \Mag$ such that $\Tfr \Rew \Tfr'$ one has
-    $\PrefixWord(\Tfr) > \PrefixWord(\Tfr')$, then the rewrite relation
-    induced by $\Rew$ is terminating.
-\end{Lemma}
-
-Moreover, we shall use the following result appearing in~\cite{Gir16}
-specialized on rewrite relation on $\Mag$ to prove that a terminating
-rewrite relation is convergent.
-
-\begin{Lemma} \label{lem:degree_confluence}
-    Let $\Rew$ be a rewrite rule on $\Mag$ wherein all trees $\Tfr$ and
-    $\Tfr'$ such that $\Tfr \Rew \Tfr'$ have degrees at most $\ell$.
-    Then, if the rewrite relation $\RewContext$ induced by $\Rew$ is
-    terminating and all its branching pairs of degrees at most
-    $2\ell - 1$ are joinable, $\RewContext$ is convergent.
-\end{Lemma}
+\input{Operads_rewrite}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Generalizations of the associative operad} \label{sec:CAs_d}
-It is known that the rewrite rule $\Rew$
-orienting~\eqref{equ:congruence_as} from left to right is a convergent
-orientation of (\ref{equ:congruence_as}). Then, a Poincaré-Birkhoff-Witt
-basis of $\As$ is the set of all right comb binary trees.
-
-Let us now define for any $\gamma \geq 1$ the \Def{$\gamma$-comb
-associative operad} $\CAs{\gamma}$ as the quotient operad
-$\Mag/_{\CongrCAs{\gamma}}$ where $\CongrCAs{\gamma}$ is the smallest
-operad congruence of $\Mag$ satisfying
-\begin{equation} \label{equ:congruence_Asd}
-    \underbrace{(\dots (\Product \circ_1 \Product) \circ_1 \dots)
-        \circ_1 \Product}
-    _{\gamma \mbox{ \footnotesize operands}}
-    \enspace \CongrCAs{\gamma} \enspace
-    \underbrace{\Product \circ_2
-        (\dots \circ_2 (\Product \circ_2 \Product) \dots)}
-    _{\gamma \mbox{ \footnotesize operands}}.
-\end{equation}
-In words, \eqref{equ:congruence_Asd} says that the left and the right
-comb binary trees of degree $\gamma$ are equivalent for
-$\CongrCAs{\gamma}$. Notice that $\CongrCAs{1}$ is trivial so that
-$\CAs{1} = \Mag$ and that $\CongrCAs{2}$ is the operad congruence
-defined by~\eqref{equ:congruence_as} so that $\CAs{2} = \As$.
-
-In the sequel we denote by $\LC{\gamma}$ and $\RC{\gamma}$ the left
-comb and the right comb of degree $\gamma$, respectively. Hence,
-$\CongrCAs{\gamma}$ is the congruence relation induced by
-$\LC{\gamma}\CongrCAs{\gamma}\RC{\gamma}$.
-
-Let
-\begin{equation}
-    \CAsAll := \left\{\CAs{\gamma} : \gamma\geq 1\right\}
-\end{equation}
-be the set of all the $\gamma$-comb associative operads
-Our purpose is to show that $\CAsAll$ admits a lattice structure. For
-that, we provide a description of operads morphisms between the
-elements of $\CAsAll$.
-
-\begin{Proposition}\label{prop:morphisms_CAs_d}
-    Let $\gamma$ and $\gamma'$ be two positive integers. There exists at
-    most one operad morphism $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$.
-    This  morphism exists if and only if
-    \begin{math}
-        \LC{\gamma'}\CongrCAs{\gamma}\RC{\gamma'}
-    \end{math}
-    and it is surjective in this case. Moreover, $\varphi$ is injective
-    if and only if $\gamma = \gamma'$, that is if and only if
-    $\varphi$ is the identity morphism.
-\end{Proposition}
-\begin{proof}
-    The operad $\CAs{\gamma'}$ is generated by one binary generator
-    $\Product$, so that $\varphi$ is entirely determined by
-    $\varphi\left(\Product\right)$. Moreover, $\varphi(\Product)$ has
-    to be of arity $2$ in $\CAs{\gamma}$, so that $\varphi(\Product)$
-    has to be equal to $\Product \in \CAs{\gamma}$. Hence, if $\varphi$
-    exists, it is the unique operad morphism from $\CAs{\gamma'}$ and
-    $\CAs{\gamma}$, and in this case, $\Product \in \CAs{\gamma'}$
-    being in the image of $\varphi$, the latter is surjective.
-    Moreover, $\varphi$ is well defined if and only if
-    $\varphi\left(\LC{\gamma'}\right)$ and
-    $\varphi\left(\RC{\gamma'}\right)$ are equal in $\CAs{\gamma}$,
-    that is if and only if
-    $\LC{\gamma'} \CongrCAs{\gamma} \RC{\gamma'}$. In particular, if
-    $\gamma'$ is smaller than $\gamma$, then there does not exist any
-    morphism $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$.
-    \Todo{Faux car on peut avoir $\gamma' = 1$, puisque
-    $\LC{1} = \RC{1}$.}
-    Moreover, if $\gamma'$ is smaller than $\gamma$, the cardinality of
-    $\CAs{\gamma'}\left(\gamma\right)$ is equal to the cardinality of
-    $\CAs{\gamma}(\gamma)$ plus one. Hence, if there exists an injective
-    morphism $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$, we must have
-    $\gamma = \gamma'$, and in this case, $\varphi$ is the identity
-    morphism.
-\end{proof}
-
-We define the binary relation $\preceq$ on $\CAsAll$ as follows: we have
-$\CAs{\gamma}\preceq\CAs{\gamma'}$ if and only if there exists a
-morphism $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$.
-
-\begin{Proposition}\label{prop:poset_CAs}
-    The binary relation $\preceq$ is a partially order on $\CAsAll$,
-    that is $\left(\CAsAll,\ \preceq\right)$ is a poset.
-\end{Proposition}
-\begin{proof}
-    The binary relation $\preceq$ is reflexive since there exists the
-    identity morphism of $\CAs{\gamma}$ for every positive integer
-    $\gamma$. It is transitive since if there exist two morphisms
-    $\varphi:\CAs{\gamma}\to\CAs{\gamma'}$ and
-    $\psi:\CAs{\gamma''}\to\CAs{\gamma'}$, then $\psi\circ\varphi$ is a
-    morphism from $\CAs{\gamma''}$ to $\CAs{\gamma}$. Now, let us assume
-    that there exist morphisms $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$
-    and $\psi:\CAs{\gamma}\to\CAs{\gamma'}$. In particular,
-    $\psi\circ\varphi$ and $\varphi\circ\psi$ are endomorphisms of
-    $\CAs{\gamma'}$ and $\CAs{\gamma}$, respectively. From
-    Proposition~\ref{prop:morphisms_CAs_d}, these two morphisms are
-    identity morphisms, so that $\varphi$ and $\psi$ are injective. From
-    Proposition~\ref{prop:morphisms_CAs_d}, $\gamma$ and $\gamma'$ are
-    equal, which proves that $\preceq$ is anti-symmetric, hence a
-    partial order.
-\end{proof}
-
-In order to show that the poset $\left(\CAsAll,\ \preceq\right)$
-extends into a lattice, that is two elements of $\CAsAll$ admit
-lower-bounds and upper-bounds, we relate
-$\left(\CAsAll,\ \preceq\right)$ to the lattice of integers
-$\left(\N,\ \mid,\ \gcd,\ \lcm\right)$, where $\mid$
-denotes the division relation, $\gcd$ denotes the \emph{greatest common divisor} and $\lcm$ the \emph{least common multiple}
-operators, respectively. In order to obtain this relationship, we introduce the notion of
-\Def{left rank} of an element $\Tfr \in\Mag$: this is the number
-$\LBranch(\Tfr)$ of internal nodes in the left branch
-beginning at the root of $\Tfr$. The left rank of $\Tfr$ is represented as follows:
-\[\textbf{PICTURE}\]
-
-\begin{Lemma}\label{lem:left_rank_and_CongrCAs}
-  Let $\gamma$ be a strictly positive integer and let $t$ and $t'$ be two elements of $\Mag$. If
-  $t\CongrCAs{\gamma}t'$, then $\emph{lr}\left(t\right)$ and $\emph{lr}\left(t'\right)$ are equal modulo $\gamma-1$: $\emph{lr}\left(t\right)\equiv\emph{lr}\left(t'\right) [\gamma-1]$.
-\end{Lemma}
-
-\begin{proof}
-  Let $\Rew$ be the rewrite relation on $\Mag$ induced by the rewrite rule
-  $\LC{\gamma}\Rew\RC{\gamma}$. In the rest of the proof we fix two elements $t$ and $t'$ of $\Mag$.
-
-  First, we show that $t\Rew t'$ implies that $\text{lr}\left(t'\right)-\text{lr}\left(t\right)$
-  is divisible by $\gamma-1$ \textbf{TODO}.
-
-  Assume that $t\overset{*}{\Rew}t'$, so that there exist elements $t_1,\ \cdots,\ t_n$
-  of $\Mag$ such that $t_1=t$, $t_n=t'$ and for every $i\in\{1,\cdots,n-1\}$, we have
-  $t_i\Rew t_{i+1}$. The integer $\text{lr}\left(t_{i+1}\right)-\text{lr}\left(t_i\right)$
-  is divisible by $\gamma-1$ from the first part of the proof, so that
-  $\text{lr}\left(t'\right)-\text{lr}\left(t\right)$ is divisible by $\gamma-1$.
-
-  Assume that $t\overset{*}{\leftrightarrow}t'$, so that there exist elements $t_1,\ \cdots,\ t_n$
-  of $\Mag$ such that $t_1=t$, $t_n=t'$ and for every $i\in\{1,\cdots,n-1\}$, we have
-  $t_i\overset{*}{\Rew}t_{i+1}$ or $t_{i+1}\overset{*}{\Rew}t_i$. From the second part of the proof,
-  $\text{lr}\left(t_{i+1}\right)-\text{lr}\left(t_i\right)$ is divisible by $\gamma-1$, so that
-  $\text{lr}\left(t'\right)-\text{lr}\left(t\right)$ is divisible by $\gamma-1$.
-
-  The congruence relation $\CongrCAs{\gamma}$ is the equivalence relation induced by $\Rew$, that
-  is we have $t\CongrCAs{\gamma}t'$ if and only if $t\overset{*}{\leftrightarrow}t'$. Hence, from the
-  third part of the proof, $t\CongrCAs{\gamma}t'$ implies that
-  $\text{lr}\left(t'\right)-\text{lr}\left(t\right)$ is divisible by $\gamma-1$.
-  \end{proof}
-
-\begin{Proposition} \label{prop:division_CAs}
-  Let $\gamma$ and $\gamma'$ be two strictly positive integers. There exists a morphism
-  $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$ if and only if $\left(\gamma-1\right)\mid\left(\gamma'-1\right)$.
-\end{Proposition}
-\begin{proof}
-  From Proposition~\ref{prop:morphisms_CAs_d}, it is sufficient to show that $\LC{\gamma'}\CongrCAs{\gamma}\RC{\gamma'}$
-  if and only if $\left(\gamma-1\right)\mid\left(\gamma'-1\right)$. If $\LC{\gamma'}\CongrCAs{d}\RC{\gamma'}$, from
-  Lemma~\ref{lem:left_rank_and_CongrCAs}, $\text{lr}\left(\LC{\gamma'}\right)-\text{lr}\left(\RC{\gamma'}\right)=\gamma'-1$
-  is divisible by $\gamma-1$, which shows the direct implication. Conversely, if
-  $\left(\gamma-1\right)\mid\left(\gamma'-1\right)$, the rewrite rule $\LC{\gamma}\Rew\RC{\gamma}$ induces the
-  following sequence of rewriting steps:
-  \[\textbf{Rewriting sequence from left comb of degree d' to right comb of degree d'}\]
-  Hence, we have $\LC{\gamma'}\CongrCAs{\gamma}\RC{\gamma'}$.
-   \end{proof}
-
-Proposition~\ref{prop:division_CAs} implies the following:
-\begin{Theorem}\label{thm:lattice_CAs}
-  The poset $\left(\emph{CAs},\ \preceq\right)$ extends into a lattice
-  $\left(\emph{CAs},\ \preceq,\ \wedge,\ \vee\right)$, where the lower-
-  bound $\wedge$ and the upper-bound $\vee$ are defined as follows:
-  \[\CAs{\gamma}\wedge\CAs{\gamma'}=\CAs{\text{gcd}\left(\gamma-1,\ \gamma'-1\right)}\
-  \text{and}\ \CAs{\gamma}\vee\CAs{\gamma'}=\CAs{\text{lcm}\left(\gamma-1,\ \gamma'-1\right)}.\]
-  \end{Theorem}
+\input{Magmatic_operads}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The \texorpdfstring{$3$}{3}-comb associative operad}
-\label{sec:CAs_3}
-We now focus on the study of the operad $\CAs{3}$. By definition, this
-operad is the quotient of $\Mag$ by the operad congruence spanned by the
-relation
-\begin{equation} \label{equ:rew_1}
-    \begin{tikzpicture}[xscale=.22,yscale=.23,Centering]
-        \node(0)at(0.00,-5.25){};
-        \node(2)at(2.00,-5.25){};
-        \node(4)at(4.00,-3.50){};
-        \node(6)at(6.00,-1.75){};
-        \node[NodeST](1)at(1.00,-3.50){\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
-        \node[NodeST](5)at(5.00,0.00){\begin{math}\Product\end{math}};
-        \draw[Edge](0)--(1);
-        \draw[Edge](1)--(3);
-        \draw[Edge](2)--(1);
-        \draw[Edge](3)--(5);
-        \draw[Edge](4)--(3);
-        \draw[Edge](6)--(5);
-        \node(r)at(5.00,1.5){};
-        \draw[Edge](r)--(5);
-    \end{tikzpicture}
-    \enspace \Rew \enspace
-    \begin{tikzpicture}[xscale=.22,yscale=.23,Centering]
-        \node(0)at(0.00,-1.75){};
-        \node(2)at(2.00,-3.50){};
-        \node(4)at(4.00,-5.25){};
-        \node(6)at(6.00,-5.25){};
-        \node[NodeST](1)at(1.00,0.00){\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
-        \node[NodeST](5)at(5.00,-3.50){\begin{math}\Product\end{math}};
-        \draw[Edge](0)--(1);
-        \draw[Edge](2)--(3);
-        \draw[Edge](3)--(1);
-        \draw[Edge](4)--(5);
-        \draw[Edge](5)--(3);
-        \draw[Edge](6)--(5);
-        \node(r)at(1.00,1.5){};
-        \draw[Edge](r)--(1);
-    \end{tikzpicture}\,.
-\end{equation}
-This rewrite rule is compatible with the lexicographic order on prefix
-words presented at the beginning of Section~\ref{sec:operad_Mag} in the
-sense that the prefix word of the left member of~\eqref{equ:rew_1} is
-lexicographically greater than the prefix word of the right one.
-
-However, the rewrite relation $\RewContext$ induced by $\Rew$ is not
-confluent. Indeed, we have
-\begin{equation} \label{equ:branching_pair_CAs_3}
-    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
-        \node(0)at(0.00,-7.20){};
-        \node(2)at(2.00,-7.20){};
-        \node(4)at(4.00,-5.40){};
-        \node(6)at(6.00,-3.60){};
-        \node(8)at(8.00,-1.80){};
-        \node[NodeST](1)at(1.00,-5.40){\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,-3.60){\begin{math}\Product\end{math}};
-        \node[NodeST](5)at(5.00,-1.80){\begin{math}\Product\end{math}};
-        \node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
-        \draw[Edge](0)--(1);
-        \draw[Edge](1)--(3);
-        \draw[Edge](2)--(1);
-        \draw[Edge](3)--(5);
-        \draw[Edge](4)--(3);
-        \draw[Edge](5)--(7);
-        \draw[Edge](6)--(5);
-        \draw[Edge](8)--(7);
-        \node(r)at(7.00,1.35){};
-        \draw[Edge](r)--(7);
-    \end{tikzpicture}
-    \enspace \RewContext \enspace
-    \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
-        \node(0)at(0.00,-4.50){};
-        \node(2)at(2.00,-4.50){};
-        \node(4)at(4.00,-4.50){};
-        \node(6)at(6.00,-6.75){};
-        \node(8)at(8.00,-6.75){};
-        \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
-        \node[NodeST](5)at(5.00,-2.25){\begin{math}\Product\end{math}};
-        \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
-        \draw[Edge](0)--(1);
-        \draw[Edge](1)--(3);
-        \draw[Edge](2)--(1);
-        \draw[Edge](4)--(5);
-        \draw[Edge](5)--(3);
-        \draw[Edge](6)--(7);
-        \draw[Edge](7)--(5);
-        \draw[Edge](8)--(7);
-        \node(r)at(3.00,1.74){};
-        \draw[Edge](r)--(3);
-    \end{tikzpicture}
-    \qquad \mbox{and} \qquad
-    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
-        \node(0)at(0.00,-7.20){};
-        \node(2)at(2.00,-7.20){};
-        \node(4)at(4.00,-5.40){};
-        \node(6)at(6.00,-3.60){};
-        \node(8)at(8.00,-1.80){};
-        \node[NodeST](1)at(1.00,-5.40){\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,-3.60){\begin{math}\Product\end{math}};
-        \node[NodeST](5)at(5.00,-1.80){\begin{math}\Product\end{math}};
-        \node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
-        \draw[Edge](0)--(1);
-        \draw[Edge](1)--(3);
-        \draw[Edge](2)--(1);
-        \draw[Edge](3)--(5);
-        \draw[Edge](4)--(3);
-        \draw[Edge](5)--(7);
-        \draw[Edge](6)--(5);
-        \draw[Edge](8)--(7);
-        \node(r)at(7.00,1.35){};
-        \draw[Edge](r)--(7);
-    \end{tikzpicture}
-    \enspace \RewContext \enspace
-    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
-        \node(0)at(0.00,-3.60){};
-        \node(2)at(2.00,-5.40){};
-        \node(4)at(4.00,-7.20){};
-        \node(6)at(6.00,-7.20){};
-        \node(8)at(8.00,-1.80){};
-        \node[NodeST](1)at(1.00,-1.80){\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,-3.60){\begin{math}\Product\end{math}};
-        \node[NodeST](5)at(5.00,-5.40){\begin{math}\Product\end{math}};
-        \node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
-        \draw[Edge](0)--(1);
-        \draw[Edge](1)--(7);
-        \draw[Edge](2)--(3);
-        \draw[Edge](3)--(1);
-        \draw[Edge](4)--(5);
-        \draw[Edge](5)--(3);
-        \draw[Edge](6)--(5);
-        \draw[Edge](8)--(7);
-        \node(r)at(7.00,1.5){};
-        \draw[Edge](r)--(7);
-    \end{tikzpicture}\,,
-\end{equation}
-and the two right members of~\eqref{equ:branching_pair_CAs_3} form a
-branching pair which is not joinable.
-
-In order to transform the rewrite relation induced by~\eqref{equ:rew_1}
-into a convergent one, we apply the Buchberger algorithm for
-operads~\cite[Section 3.7]{DK10} with respect to the lexicographic order
-on prefix words. Following this algorithm, we need to put the right
-members of~\eqref{equ:branching_pair_CAs_3} in relation by $\Rew$. To
-respect the lexicographic property of the prefix words, this leads to
-the new relation
-\begin{equation} \label{equ:rew_2}
-    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
-        \node(0)at(0.00,-3.60){};
-        \node(2)at(2.00,-5.40){};
-        \node(4)at(4.00,-7.20){};
-        \node(6)at(6.00,-7.20){};
-        \node(8)at(8.00,-1.80){};
-        \node[NodeST](1)at(1.00,-1.80){\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,-3.60){\begin{math}\Product\end{math}};
-        \node[NodeST](5)at(5.00,-5.40){\begin{math}\Product\end{math}};
-        \node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
-        \draw[Edge](0)--(1);
-        \draw[Edge](1)--(7);
-        \draw[Edge](2)--(3);
-        \draw[Edge](3)--(1);
-        \draw[Edge](4)--(5);
-        \draw[Edge](5)--(3);
-        \draw[Edge](6)--(5);
-        \draw[Edge](8)--(7);
-        \node(r)at(7.00,1.5){};
-        \draw[Edge](r)--(7);
-    \end{tikzpicture}
-    \enspace \Rew \enspace
-    \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
-        \node(0)at(0.00,-4.50){};
-        \node(2)at(2.00,-4.50){};
-        \node(4)at(4.00,-4.50){};
-        \node(6)at(6.00,-6.75){};
-        \node(8)at(8.00,-6.75){};
-        \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
-        \node[NodeST](5)at(5.00,-2.25){\begin{math}\Product\end{math}};
-        \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
-        \draw[Edge](0)--(1);
-        \draw[Edge](1)--(3);
-        \draw[Edge](2)--(1);
-        \draw[Edge](4)--(5);
-        \draw[Edge](5)--(3);
-        \draw[Edge](6)--(7);
-        \draw[Edge](7)--(5);
-        \draw[Edge](8)--(7);
-        \node(r)at(3.00,1.74){};
-        \draw[Edge](r)--(3);
-    \end{tikzpicture}\,.
-\end{equation}
-The Buchberger algorithm applied on binary trees of degrees $5$, $6$,
-and $7$ provides the new relations \\
-\input{Buchberger_relations_5-7}
-
-\noindent
-We claim that the rewrite relation $\RewContext$ induced by
-rewrite rule $\Rew$ satisfying~\eqref{equ:rew_1}, \eqref{equ:rew_2},
-\eqref{equ:rew_3}---\eqref{equ:rew_11} is convergent. First, for every
-relation $\Tfr \Rew \Tfr'$, we have
-$\PrefixWord(\Tfr) > \PrefixWord(\Tfr')$. Therefore, by
-Lemma~\ref{lem:prefix_word_termination}, $\RewContext$ is terminating.
-Moreover, the greatest degree of a tree appearing in $\Rew$ is~$7$ so
-that, from Lemma~\ref{lem:degree_confluence}, to show that $\RewContext$
-is convergent, it is enough to prove that each tree of degree at most
-$13$ admits exactly one normal form. Equivalently, this amounts to
-show that the number of normal forms of trees of arity $n$ is equal
-to $\#\CAs{3}(n)$. By computer exploration, we get the same sequence
-\begin{equation} \label{equ:dimensions_CAs_3}
-    1, 1, 2, 4, 8, 14, 20, 19, 16, 14, 14, 15, 16, 17
-\end{equation}
-for $\#\CAs{3}(n)$ and for the numbers of normal forms of arity $n$,
-when $ 1 \leq n \leq 14$. Hence, we get our following main result.
-
-\begin{Theorem} \label{thm:convergent_rewrite_rule_CAs_3}
-    The rewrite rule $\Rew$ satisfying~\eqref{equ:rew_1},
-    \eqref{equ:rew_2}, \eqref{equ:rew_3}---\eqref{equ:rew_11} is a
-    convergent orientation of the congruence $\CongrCAs{3}$
-    of~$\CAs{3}$.
-\end{Theorem}
-
-The rewrite rule $\Rew$ has, arity by arity, the cardinalities
-\begin{equation}
-    0, 0, 0, 1, 1, 2, 3, 4, 0, \dots~.
-\end{equation}
-We obtain from Theorem~\ref{thm:convergent_rewrite_rule_CAs_3} also
-the following consequences.
-
-\begin{Proposition} \label{prop:PBW_basis_CAs_3}
-    The set of the trees avoiding as subtrees the ones appearing as
-    left members of $\Rew$ is a Poincaré-Birkhoff-Witt basis
-    of~$\CAs{3}$.
-\end{Proposition}
-
-From Proposition~\ref{prop:PBW_basis_CAs_3}, and by using a result
-of~\cite{Gir18} describing a system of equations for the generating
-series of syntax trees avoiding some sets of subtrees, we obtain the
-following result.
-
-\begin{Proposition} \label{prop:Hilbert_series_CAs_3}
-    The Hilbert series of $\CAs{3}$ is
-    \begin{equation} \label{equ:Hilbert_series_CAs_3}
-        \HilbertSeries_{\CAs{3}}(t) = \frac{t}{(1 - t)^2}
-        \left(1 - t + t^2 + t^3 + 2t^4 + 2t^5 - 7t^7 - 2t^8 + t^9 +
-        2t^{10} + t^{11}\right).
-    \end{equation}
-\end{Proposition}
-
-For $n \leq 10$, the dimensions of $\CAs{3}(n)$ are provided by
-Sequence~\eqref{equ:dimensions_CAs_3} and for all $n \geq 11$, the
-Taylor expansion of~\eqref{equ:Hilbert_series_CAs_3} shows that
-$\# \CAs{3}(n) = n + 3$.
+\input{CAs_operads}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Perspectives}
-Our first axis of perspectives consists in collecting properties about
-the operads $\CAs{d}$. A natural question consists in finding all the
-morphisms between the operads $\CAs{d}$. Some surjective morphisms are
-described by Proposition~\ref{prop:quotients_CAs_d} and we can hope to a
-full description of these, as well as some possible injections.
-Moreover, we can try to obtain a convergent orientation of
-$\CongrCAs{d}$ and general expressions of the Hilbert series of
-$\CAs{d}$ when $d \geq 4$. By computer exploration, we have the sequence
-\begin{equation}
-    1, 1, 2, 5, 13, 35, 96, 264, 724, 1973, 5355, 14390
-\end{equation}
-for the first dimensions for $\CAs{4}$. By applying the Buchberger
-algorithm on trees of degrees until $10$, we obtain that a convergent
-orientation of $\CongrCAs{4}$ has, arity by arity, the sequence
-\begin{math}
-    0, 0, 0, 0, 1, 1, 0, 3, 4, 5, 18, 22
-\end{math}
-for its first cardinalities. Moreover, for $\CAs{5}$, we get the
-sequence
-\begin{equation}
-    1, 1, 2, 5, 14, 41, 124, 384, 1210, 3861, 12440
-\end{equation}
-of dimensions and the first cardinalities
-\begin{math}
-    0, 0, 0, 0, 0, 1, 1, 0, 0, 4, 5
-\end{math}
-for any convergent orientation of $\CongrCAs{5}$. Finally, for
-$\CAs{6}$, we get the sequence
-\begin{equation}
-    1, 1, 2, 5, 14, 42, 131, 420, 1375, 4576, 15431
-\end{equation}
-of dimensions and the first cardinalities
-\begin{math}
-    0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0
-\end{math}
-for any convergent orientation of $\CongrCAs{6}$. We can notice that
-only $\CAs{3}$ seems to have oscillating first dimensions.
-
-A second axis concerns a complete understanding of $\CAs{3}$. We can
-try to construct an explicit basis of this operad.
-Proposition~\ref{prop:PBW_basis_CAs_3} describes a basis in terms of
-trees avoiding some patterns but, we can hope to find a simpler
-description. This includes the description of a family of combinatorial
-objects forming a basis of $\CAs{3}$ and an adequate definition of a
-partial composition map $\circ_i$ on these. Moreover, a natural
-question is to explore the suboperads $\CAs{3}$ in the category of
-vector spaces.
-
-In a last axis, we can consider further generalizations of $\As$ being
-quotients of $\Mag$ by congruences defined by identifying certain binary
-trees of a same fixed degree. A possible question is, as presented in
-the introduction, to investigate if combinatorial properties of the
-trees belonging to a same equivalence class imply algebraic properties
-on the obtained operads.
+\input{Conclusion}
 

### 2018-06-29 Conclusion.tex
Restructuration

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Perspectives}
Our first axis of perspectives consists in collecting properties about
the operads $\CAs{d}$. A natural question consists in finding all the
morphisms between the operads $\CAs{d}$. Some surjective morphisms are
described by Proposition~\ref{prop:quotients_CAs_d} and we can hope to a
full description of these, as well as some possible injections.
Moreover, we can try to obtain a convergent orientation of
$\CongrCAs{d}$ and general expressions of the Hilbert series of
$\CAs{d}$ when $d \geq 4$. By computer exploration, we have the sequence
\begin{equation}
    1, 1, 2, 5, 13, 35, 96, 264, 724, 1973, 5355, 14390
\end{equation}
for the first dimensions for $\CAs{4}$. By applying the Buchberger
algorithm on trees of degrees until $10$, we obtain that a convergent
orientation of $\CongrCAs{4}$ has, arity by arity, the sequence
\begin{math}
    0, 0, 0, 0, 1, 1, 0, 3, 4, 5, 18, 22
\end{math}
for its first cardinalities. Moreover, for $\CAs{5}$, we get the
sequence
\begin{equation}
    1, 1, 2, 5, 14, 41, 124, 384, 1210, 3861, 12440
\end{equation}
of dimensions and the first cardinalities
\begin{math}
    0, 0, 0, 0, 0, 1, 1, 0, 0, 4, 5
\end{math}
for any convergent orientation of $\CongrCAs{5}$. Finally, for
$\CAs{6}$, we get the sequence
\begin{equation}
    1, 1, 2, 5, 14, 42, 131, 420, 1375, 4576, 15431
\end{equation}
of dimensions and the first cardinalities
\begin{math}
    0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0
\end{math}
for any convergent orientation of $\CongrCAs{6}$. We can notice that
only $\CAs{3}$ seems to have oscillating first dimensions.
\medbreak

A second axis concerns a complete understanding of $\CAs{3}$. We can
try to construct an explicit basis of this operad.
Proposition~\ref{prop:PBW_basis_CAs_3} describes a basis in terms of
trees avoiding some patterns but, we can hope to find a simpler
description. This includes the description of a family of combinatorial
objects forming a basis of $\CAs{3}$ and an adequate definition of a
partial composition map $\circ_i$ on these. Moreover, a natural
question is to explore the suboperads $\CAs{3}$ in the category of
vector spaces.
\medbreak

In a last axis, we can consider further generalizations of $\As$ being
quotients of $\Mag$ by congruences defined by identifying certain binary
trees of a same fixed degree. A possible question is, as presented in
the introduction, to investigate if combinatorial properties of the
trees belonging to a same equivalence class imply algebraic properties
on the obtained operads.
\medbreak

### 2018-06-29 Magmatic_operads.tex
Restructuration

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Magmatic operads}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Category of the magmatic quotients}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A lattice of magmatic quotients}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Magmatic quotients and combinatorics}

% Hilbert series, enumeration, a little of rewrite systems, etc.

### 2018-06-29 Magmatic_operads.tex
Rédaction première partie opérades magmatiques

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Magmatic operads}
+\section{Quotients of the magmatic operad}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Category of the magmatic quotients}
+\Todo{Write mini intro.}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{A lattice of magmatic quotients}
+\subsection{Lattice structure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Magmatic quotients and combinatorics}
+We denote by $\IMag$ the set of operadic of $\Mag$, and
+\begin{equation} \label{equ:definition_of_QMag}
+  \QMag =\Big\{\Mag/ I\mid I\in\IMag\Big\},
+  \end{equation}
+the set of quotients of the magmatic operad. Given two elements $\Oca_1$
+and $\Oca_2$ of $\QMag$, we denote by $\text{hom}\left(\Oca_1,\Oca_2\right)$
+the set of operads morphisms from $\Oca_1$ to $\Oca_2$.
 
-% Hilbert series, enumeration, a little of rewrite systems, etc.
+\begin{Proposition} \label{prop:endomorphisms_of_magmatic_operads}
+  The set $\emph{hom}\left(\Oca_1,\Oca_2\right)$ admits a vector space
+  structure. Moreover, its dimension is equal to $0$ or $1$ and every
+  nonzero morphism is surjective.
+\end{Proposition}
+
+\begin{proof}
+  The operad $\Oca_1$ is spanned by the binary generator~$\Product$, so
+  that a morphism $\varphi:\Oca_1\to\Oca_2$ is uniquely determined by
+  $\varphi(\Product)$. Moreover, $\varphi(\Product)$ has arity $2$ is
+  $\Oca_2$. Hence, $\varphi(\Product)$ belongs to the line spanned by
+  the binary generator of $\Oca_2$, that is there exists a scalar
+  $\lambda\in\K$ such that $\varphi(\Product)=\lambda\Product$. If there
+  exists such a $\lambda$ different from zero, then for every nonzero
+  scalar $\mu$, we have a well-defined operads morphism
+  $\psi:\Oca_1\to\Oca_2$ satisfying $\psi(\Product)=\mu\Product=\left(
+  \mu/\lambda\right)\varphi(\Product)$. Hence,
+  $\text{hom}\left(\Oca_1,\Oca_2\right)$ is either reduced to the zero
+  morphism or it is in one-to-one correspondance with $\K$, which
+  proves that $\text{hom}\left(\Oca_1,\Oca_2\right)$ is a vector space
+  of dimension at most $1$. Moreover, if $\varphi$ is different from $0$,
+  that is there is a nonzero scalar such that
+  $\varphi(\Product)=\lambda\Product$, we have
+  $\varphi(1/\lambda\Product)=\Product$, so that $\varphi$ is
+  surjective.
+\end{proof}
+
+We introduce the binary relation $\preceq$ on $\QMag$ as follows: we
+have $\Oca_2\preceq\Oca_1$ if the dimension of
+$\text{hom}\left(\Oca_1,\Oca_2\right)$ is equal to $1$.
+
+\begin{Proposition} \label{prop:order_relations_on_QMag_and_ideals}
+  Let $\Oca_1=\Mag/I_1$ and $\Oca_2=\Mag/I_2$ be two elements of $\QMag$.
+  We have $\Oca_2\preceq\Oca_1$ if and only if $I_1\subseteq I_2$.
+\end{Proposition}
+
+\begin{proof}
+  Since $\text{hom}\left(\Oca_1,\Oca_2\right)$ is a vector space of
+  dimension at most $1$, it contains a nonzero morphism if and only if
+  the morphism
+  $\overline{\varphi}:\Oca_1\to\Oca_2$ satisfying
+  $\overline{\varphi}(\Product)=\Product$ is well-defined, which means
+  that $\Oca_2\preceq\Oca_1$ is equivalent to this condition. Moreover,
+  by the universal property of the quotient, $\overline{\varphi}$ is
+  well-defined if and only if $I_1$ is included in the kernel of the
+  morphism $\varphi:\Mag\to\Oca_2$ defined by
+  $\varphi(\Product)=\Product$. This kernel is equal to $I_2$, so that
+  $\overline{\varphi}$ is well-defined if and only if $I_1$ is included
+  in $I_2$, which concludes the proof.
+\end{proof}
+
+Recall that a \Def{lattice} is a tuple $\left(E,\leq,\wedge,\vee\right)$,
+where $\left(E,\leq\right)$ is a poset such that any two elements $e$
+and $e'$ of $E$ admit a lower-bound $e\wedge e'$ and an upper-bound
+$e\vee e'$. In particular, $\left(\IMag,\subseteq,\cap,+\right)$ is a
+lattice, where $\cap$ and $+$ are the intersection and the sum of
+operadic ideals, respectively.
+
+Given two elements $\Oca_1=\Mag/I_1$ and $\Oca_2=\Mag/I_2$ of $\QMag$,
+we let
+\begin{equation} \label{equ:definition_of_lattice_operations_of_QMag}
+  \Oca_1\wedge \Oca_2=\Mag/\left(I_1+I_2\right)\ \ \text{and}\ \
+  \Oca_1\wedge \Oca_2=\Mag/\left(I_1\cap I_2\right).
+  \end{equation}
+
+\begin{Theorem} \label{thm:lattice_structure_of_QMag}
+  The tuple $\left(\QMag,\preceq,\wedge,\vee\right)$ is a lattice.
+\end{Theorem}
+
+\begin{proof}
+  The map $\mathcal{Q}:\IMag\to\QMag$ defined by $\mathcal{Q}(I)=\Mag/I$
+  is a bijection by definition of $\QMag$. Moreover, from
+  Proposition~\ref{prop:order_relations_on_QMag_and_ideals},
+  $\Oca_2\preceq\Oca_1$ is equivalent to $I_1\subseteq I_2$, so that
+  $\left(\QMag,\preceq\right)$ is a poset and $\mathcal{Q}$ is a
+  decreasing bijection. The tuple $\left(\IMag,\subseteq,\cap,+\right)$
+  being a lattice, the decreasing bijection $\mathcal{Q}$ induces
+  lattice operations on $\QMag$, precisely $\wedge$ and $\vee$ by
+  definition.
+  \end{proof}
+\subsection{Kernels of magmatic operads}

### 2018-06-29 CAs_operads.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Generalizations of the associative operad} \label{sec:CAs_d}
\Todo{Write mini intro.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comb associative operads}
\Todo{Write mini intro.}

It is known that the rewrite rule $\Rew$
orienting~\eqref{equ:congruence_as} from left to right is a convergent
orientation of (\ref{equ:congruence_as}). Then, a Poincaré-Birkhoff-Witt
basis of $\As$ is the set of all right comb binary trees.
\Todo{SG: to maybe to move at another place. }
\medbreak

Let, for any $\gamma \geq 1$, the binary trees
\begin{equation}
    \LComb{\gamma} :=
    \underbrace{(\dots (\Product \circ_1 \Product) \circ_1 \dots)
        \circ_1 \Product}
    _{\gamma \mbox{ \footnotesize operands}}
\end{equation}
and
\begin{equation}
    \RComb{\gamma} :=
    \underbrace{\Product \circ_2
        (\dots \circ_2 (\Product \circ_2 \Product) \dots)}
    _{\gamma \mbox{ \footnotesize operands}}
\end{equation}
be respectively the left and the right comb of degree $\gamma$.
Let us now define for any $\gamma \geq 1$ the \Def{$\gamma$-comb
associative operad} $\CAs{\gamma}$ as the quotient operad
$\Mag/_{\CongrCAs{\gamma}}$ where $\CongrCAs{\gamma}$ is the smallest
operad congruence of $\Mag$ satisfying
\begin{equation} \label{equ:congruence_CAs_gamma}
    \LComb{\gamma} \enspace \CongrCAs{\gamma} \enspace \RComb{\gamma}
\end{equation}
Notice that $\CongrCAs{1}$ is trivial so that
$\CAs{1} = \Mag$ and that $\CongrCAs{2}$ is the operad congruence
defined by~\eqref{equ:congruence_as} so that $\CAs{2} = \As$.
Let also
\begin{equation}
    \CAsAll := \left\{\CAs{\gamma} : \gamma\geq 1\right\}
\end{equation}
be the set of all the $\gamma$-comb associative operads
Our purpose is to show that $\CAsAll$ admits a lattice structure. For
that, we provide a description of operads morphisms between the
elements of~$\CAsAll$.
\medbreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A lattice of operads}
\Todo{Write mini intro.}

\begin{Lemma} \label{lem:first_dimensions_CAs}
    For any positive integers $\gamma$ and $n$ such that $\gamma \geq 2$
    and $n \leq \gamma + 1$,
    \begin{equation}
        \# \CAs{\gamma}(n) =
        \begin{cases}
            \Catalan(n)
                & \mbox{ if } n \leq \gamma, \\
            \Catalan(\gamma + 1) - 1
                & \mbox{ otherwise } (n = \gamma + 1).
        \end{cases}
    \end{equation}
\end{Lemma}
\begin{proof}
    Since the equivalence relation $\CongrCAs{\gamma}$ is trivial on the
    binary trees of degrees $d < \gamma$, and since a binary tree of
    degree $d$ has arity $n := d + 1$, one has
    $\# \CAs{\gamma}(n) = \# \Mag(n) = \Catalan(n)$ with $n \leq \gamma$.
    Besides, by definition of $\CongrCAs{\gamma}$, all the
    $\CongrCAs{\gamma}$-equivalence classes of binary trees of degree
    $\gamma$ are trivial, except one consisting in the pair
    $\left\{\LComb{\gamma}, \RComb{\gamma}\right\}$. Therefore, since a
    binary tree of degree $d$ has arity $n := \gamma + 1$,
    \begin{math}
        \# \CAs{\gamma}(n)
        = \# \Mag(\gamma + 1) - 1
        = \Catalan(\gamma + 1) - 1.
    \end{math}
\end{proof}
\medbreak

\begin{Lemma} \label{lem:surjective_morphisms_CAs}
    Let $\gamma$ and $\gamma'$ be two positive integers. If
    $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$ is an operad morphism, then
    it is surjective and is unique.
\end{Lemma}
\begin{proof}
    The operad $\CAs{\gamma'}$ is generated by one binary generator
    $[\Product]_{\CongrCAs{\gamma'}}$, so that $\varphi$ is entirely
    determined by the image
    $\varphi\left([\Product]_{\CongrCAs{\gamma'}}\right)$. Moreover,
    $\varphi([\Product]_{\CongrCAs{\gamma'}})$ has to be of arity $2$ in
    $\CAs{\gamma}$, so that we necessarily have
    \begin{math}
        \varphi\left([\Product]_{\CongrCAs{\gamma'}}\right)
        =
        [\Product]_{\CongrCAs{\gamma}}.
    \end{math}
    Hence, if $\varphi$ exists, it is the unique operad morphism from
    $\CAs{\gamma'}$ to $\CAs{\gamma}$. In this case,
    $[\Product]_{\CongrCAs{\gamma'}}$ being in the image of $\varphi$,
    the latter is surjective.
\end{proof}
\medbreak

\begin{Lemma} \label{lem:injective_morphisms_CAs}
    Let $\gamma$ and $\gamma'$ be two positive integers and
    $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$ be an operad morphism.
    Then, $\varphi$ is injective if and only if $\gamma = \gamma'$.
\end{Lemma}
\begin{proof}
    Assume that $\varphi$ is injective. By
    Lemma~\ref{lem:surjective_morphisms_CAs}, $\varphi$ is also
    surjective, so that $\varphi$ is an isomorphism. If
    $\gamma \ne \gamma'$, by Lemma~\ref{lem:first_dimensions_CAs}, there
    is a positive integer $n$ such that
    $\# \CAs{\gamma}(n) \ne \# \CAs{\gamma'}(n)$. This is contradictory
    with the fact that $\CAs{\gamma}$ and $\CAs{\gamma'}$ are
    isomorphic. Hence, $\gamma = \gamma'$.
    \smallbreak

    Conversely, if $\gamma = \gamma'$, the only operad morphism from
    $\CAs{\gamma}$ to itself sends the generator
    $[\Product]_{\CongrCAs{\gamma}}$ to itself. This maps extends as
    an operad morphism into the identity morphism which is of course
    injective.
\end{proof}
\medbreak

\begin{Lemma} \label{lem:morphism_CAs}
    Let $\gamma$ and $\gamma'$ be two positive integers. There exists an
    operad morphism $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$ if and only
    if
    \begin{math}
        \LComb{\gamma'} \CongrCAs{\gamma} \RComb{\gamma'}.
    \end{math}
\end{Lemma}
\begin{proof}
    Assume that $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$ is an operad
    morphism. By Lemma~\ref{lem:surjective_morphisms_CAs}, $\varphi$
    satisfies
    \begin{math}
        \varphi\left(\left[\Tfr\right]_{\CongrCAs{\gamma'}}\right)
        = \left[\Tfr\right]_{\CongrCAs{\gamma}}
    \end{math}
    for any binary tree $\Tfr$,
    Since
    \begin{math}
        \varphi\left(
        \left[\LComb{\gamma'}\right]_{\CongrCAs{\gamma'}}
        \right)
        =
        \varphi\left(
        \left[\RComb{\gamma'}\right]_{\CongrCAs{\gamma'}}
        \right),
    \end{math}
    we have
    \begin{math}
        \left[\LComb{\gamma'}\right]_{\CongrCAs{\gamma}}
        =
        \left[\RComb{\gamma'}\right]_{\CongrCAs{\gamma}},
    \end{math}
    which is equivalent to the fact that
    \begin{math}
        \LComb{\gamma'} \CongrCAs{\gamma} \RComb{\gamma'}.
    \end{math}
    \smallbreak

    Conversely, when
    \begin{math}
        \LComb{\gamma'}\CongrCAs{\gamma}\RComb{\gamma'},
    \end{math}
    let $\varphi:\CAs{\gamma'}(2) \to \CAs{\gamma}(2)$ be the map
    defined by
    \begin{math}
        \varphi\left(
        \left[\Product\right]_{\CongrCAs{\gamma'}}\right)
        :=
        \left[\Product\right]_{\CongrCAs{\gamma}}.
    \end{math}
    Now, since $\CongrCAs{\gamma}$ is coarser than $\CongrCAs{\gamma'}$,
    $\varphi$ extends (in a unique way) into an operad morphism, whence
    the statement of the lemma.
\end{proof}
\medbreak

We define the binary relation $\OrdCAs$ on $\CAsAll$ as follows: we have
$\CAs{\gamma} \OrdCAs \CAs{\gamma'}$ if and only if there exists a
morphism $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$.
\medbreak

\begin{Proposition}\label{prop:poset_CAs}
    The binary relation $\OrdCAs$ is a partial order relation on
    $\CAsAll$.
\end{Proposition}
\begin{proof}
    The binary relation $\OrdCAs$ is reflexive since there exists the
    identity morphism of $\CAs{\gamma}$ for every positive integer
    $\gamma$. Let us now assume that
    $\varphi:\CAs{\gamma''} \to \CAs{\gamma'}$ and
    $\psi:\CAs{\gamma'} \to \CAs{\gamma}$ are two operad morphisms. By
    Lemma~\ref{lem:morphism_CAs}, one has
    $\LComb{\gamma''} \CongrCAs{\gamma'} \RComb{\gamma''}$ and
    $\LComb{\gamma'} \CongrCAs{\gamma} \RComb{\gamma'}$. This implies
    that $\CongrCAs{\gamma}$ is coarser than $\CongrCAs{\gamma'}$ and
    that $\CongrCAs{\gamma'}$ is coarser that $\CongrCAs{\gamma''}$. Now,
    again by Lemma~\ref{lem:morphism_CAs}, $\psi \circ \varphi$ is an
    operad morphism. Hence, $\OrdCAs$ is transitive. Finally, let us
    assume that there exist morphisms
    $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$ and
    $\psi:\CAs{\gamma}\to\CAs{\gamma'}$. In particular,
    $\psi \circ \varphi$ and $\varphi \circ \psi$ are endomorphisms of
    $\CAs{\gamma'}$ and $\CAs{\gamma}$, respectively. From
    Lemma~\ref{lem:injective_morphisms_CAs}, these two morphisms are
    identity morphisms, so that $\varphi$ and $\psi$ are injective. From
    Lemma~\ref{lem:injective_morphisms_CAs}, $\gamma$ and $\gamma'$ are
    equal, which proves that $\OrdCAs$ is anti-symmetric. Hence,
    $\OrdCAs$ is a partial order.
\end{proof}
\medbreak

In order to show that the poset $\left(\CAsAll, \OrdCAs\right)$ is also
a lattice, that is two elements of $\CAsAll$ admit lower-bounds and
upper-bounds, we relate $\left(\CAsAll, \OrdCAs\right)$ with the lattice
of integers $\left(\N,\mid, \gcd, \lcm\right)$, where $\mid$ denotes the
division relation, $\gcd$ denotes the greatest common divisor, and
$\lcm$ the least common multiple operators, respectively. In order to
obtain this relationship, we introduce the notion of \Def{left rank} for
any binary tree $\Tfr$ as the number $\LBranch(\Tfr)$ of internal nodes
in the left branch beginning at the root of $\Tfr$.
For instance,
\begin{equation}
    \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
        \node(0)at(0.00,-4.50){};
        \node(2)at(2.00,-4.50){};
        \node(4)at(4.00,-4.50){};
        \node(6)at(6.00,-6.75){};
        \node(8)at(8.00,-6.75){};
        \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
        \node[NodeST](5)at(5.00,-2.25){\begin{math}\Product\end{math}};
        \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](1)--(3);
        \draw[Edge](2)--(1);
        \draw[Edge](4)--(5);
        \draw[Edge](5)--(3);
        \draw[Edge](6)--(7);
        \draw[Edge](7)--(5);
        \draw[Edge](8)--(7);
        \node(r)at(3.00,1.74){};
        \draw[Edge](r)--(3);
    \end{tikzpicture}
    \xmapsto{\; \LBranch\; } 2
    \qquad \mbox{and} \qquad
    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
        \node(0)at(0.00,-3.60){};
        \node(2)at(2.00,-5.40){};
        \node(4)at(4.00,-7.20){};
        \node(6)at(6.00,-7.20){};
        \node(8)at(8.00,-1.80){};
        \node[NodeST](1)at(1.00,-1.80){\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,-3.60){\begin{math}\Product\end{math}};
        \node[NodeST](5)at(5.00,-5.40){\begin{math}\Product\end{math}};
        \node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](1)--(7);
        \draw[Edge](2)--(3);
        \draw[Edge](3)--(1);
        \draw[Edge](4)--(5);
        \draw[Edge](5)--(3);
        \draw[Edge](6)--(5);
        \draw[Edge](8)--(7);
        \node(r)at(7.00,1.5){};
        \draw[Edge](r)--(7);
    \end{tikzpicture}
    \xmapsto{\; \LBranch\; } 2.
\end{equation}
The left rank of $\Tfr$ is represented as follows: \Todo{???}
\medbreak

\begin{Lemma}\label{lem:left_rank_and_CongrCAs}
    Let $\gamma$ be a strictly positive integer and let $\Tfr$ and
    $\Tfr'$ be two binary trees. If $\Tfr \CongrCAs{\gamma} \Tfr'$, then
    \begin{equation}
        \LBranch(\Tfr) \mod \gamma - 1
        \enspace = \enspace
        \LBranch(\Tfr') \mod \gamma - 1.
    \end{equation}
\end{Lemma}
\begin{proof}
    Let $\Rew$ be the rewrite relation on $\Mag$ induced by the rewrite
    rule $\LComb{\gamma} \Rew \RComb{\gamma}$. In the rest of the
    proof, $\Tfr$ and $\Tfr$ are two binary trees.
    \smallbreak

    First, we show that $\Tfr \Rew \Tfr'$ implies that
    $\LBranch\left(\Tfr'\right) - \LBranch\left(\Tfr\right)$ is
    divisible by $\gamma - 1$. \Todo{à faire.}
    \smallbreak

    Assume that $\Tfr \RewRT \Tfr'$, so that there exist binary trees
    $\Tfr_1$, \dots, $\Tfr_k$ such that $\Tfr_1 = \Tfr$,
    $\Tfr_k = \Tfr'$ and for every $i \in \{1, \dots, k - 1\}$, we have
    $\Tfr_i\Rew \Tfr_{i + 1}$. The integer
    \begin{math}
        \LBranch\left(\Tfr_{i + 1}\right)
        -
        \LBranch\left(\Tfr_i\right)
    \end{math}
    is divisible by $\gamma - 1$ from the first part of the proof, so
    that $\LBranch\left(\Tfr'\right) - \LBranch\left(\Tfr\right)$ is
    divisible by $\gamma-1$.
    \smallbreak

    Assume that $\Tfr \RewRTS \Tfr'$, so that there exist binary trees
    $\Tfr_1$, \dots, $\Tfr_k$ such that $\Tfr_1 = \Tfr$,
    $\Tfr_k = \Tfr'$ and for every $i \in \{1, \dots, k - 1\}$, we have
    $\Tfr_i \RewRTS \Tfr_{i + 1}$ or $\Tfr_{i + 1} \RewRTS \Tfr_i$.
    From the second part of the proof, the integer
    \begin{math}
        \LBranch\left(\Tfr_{i + 1}\right)
        -
        \LBranch\left(\Tfr_i\right)
    \end{math}
    is divisible by $\gamma - 1$, so that
    $\LBranch\left(\Tfr'\right) - \LBranch\left(\Tfr\right)$ is
    divisible by $\gamma - 1$.
    \smallbreak

    The congruence $\CongrCAs{\gamma}$ is the equivalence relation
    induced by $\Rew$, that is we have $\Tfr \CongrCAs{\gamma} \Tfr'$ if
    and only if $\Tfr \RewRTS \Tfr'$. Hence, from the third part of
    the proof, $\Tfr \CongrCAs{\gamma} \Tfr'$ implies that
    \begin{math}
        \LBranch\left(\Tfr'\right) - \LBranch\left(\Tfr\right)
    \end{math}
    is divisible by $\gamma - 1$.
\end{proof}
\medbreak

\begin{Proposition} \label{prop:division_CAs}
    Let $\gamma$ and $\gamma'$ be two positive integers.Then, there
    exists a morphism $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$ if and
    only if $\left(\gamma - 1\right) \mid \left(\gamma' - 1\right)$.
\end{Proposition}
\begin{proof}
    From Lemma~\ref{lem:morphism_CAs}, it is enough to show that
    $\LComb{\gamma'} \CongrCAs{\gamma} \RComb{\gamma'}$ if and only if
    $\left(\gamma-1\right) \mid \left(\gamma'-1\right)$. If
    $\LComb{\gamma'}\CongrCAs{\gamma}\RComb{\gamma'}$, from
    Lemma~\ref{lem:left_rank_and_CongrCAs},
    \begin{math}
        \LBranch\left(\LComb{\gamma'}\right)
        - \LBranch\left(\RComb{\gamma'}\right)
        = \gamma' - 1
    \end{math}
    is divisible by $\gamma-1$, which shows the direct implication.
    \smallbreak

    Conversely, if
    $\left(\gamma-1\right) \mid \left(\gamma'-1\right)$, the rewrite
    rule $\LComb{\gamma} \Rew \RComb{\gamma}$ induces the
    sequence
    \begin{multline}
        \LComb{\gamma'} \enspace = \enspace
        \begin{tikzpicture}[xscale=.19,yscale=.25,Centering]
            \node(0)at(0.00,-13.12){};
            \node(10)at(10.00,-5.62){};
            \node(12)at(12.00,-3.75){};
            \node(14)at(14.00,-1.88){};
            \node(2)at(2.00,-13.12){};
            \node(4)at(4.00,-11.25){};
            \node(6)at(6.00,-9.38){};
            \node(8)at(8.00,-7.50){};
            \node[NodeST](1)at(1.00,-11.25)
                {\begin{math}\Product\end{math}};
            \node[NodeST](11)at(11.00,-1.88)
                {\begin{math}\Product\end{math}};
            \node[NodeST](13)at(13.00,0.00)
                {\begin{math}\Product\end{math}};
            \node[NodeST](3)at(3.00,-9.38)
                {\begin{math}\Product\end{math}};
            \node[NodeST](5)at(5.00,-7.50)
                {\begin{math}\Product\end{math}};
            \node[NodeST](7)at(7.00,-5.62)
                {\begin{math}\Product\end{math}};
            \node[NodeST](9)at(9.00,-3.75)
                {\begin{math}\Product\end{math}};
            \draw[Edge](0)--(1);
            \draw[Edge,dotted](1)--(3);
            \draw[Edge](10)--(9);
            \draw[Edge](11)--(13);
            \draw[Edge](12)--(11);
            \draw[Edge](14)--(13);
            \draw[Edge](2)--(1);
            \draw[Edge,dotted](3)--(5);
            \draw[Edge](4)--(3);
            \draw[Edge,dotted](5)--(7);
            \draw[Edge](6)--(5);
            \draw[Edge](7)--(9);
            \draw[Edge](8)--(7);
            \draw[Edge,dotted](9)--(11);
            \node(r)at(13.00,1.41){};
            \draw[Edge](r)--(13);
            %
            \node[fit=(1)(3),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
            \node[fit=(5)(7),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
            \node[fit=(9)(11),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
        \end{tikzpicture}
        \enspace \Rew \enspace
            \begin{tikzpicture}[xscale=.19,yscale=.2,Centering]
            \node(0)at(0.00,-12.50){};
            \node(10)at(10.00,-5.00){};
            \node(12)at(12.00,-7.50){};
            \node(14)at(14.00,-7.50){};
            \node(2)at(2.00,-12.50){};
            \node(4)at(4.00,-10.00){};
            \node(6)at(6.00,-7.50){};
            \node(8)at(8.00,-5.00){};
            \node[NodeST](1)at(1.00,-10.00)
                {\begin{math}\Product\end{math}};
            \node[NodeST](11)at(11.00,-2.50)
                {\begin{math}\Product\end{math}};
            \node[NodeST](13)at(13.00,-5.00)
                {\begin{math}\Product\end{math}};
            \node[NodeST](3)at(3.00,-7.50)
                {\begin{math}\Product\end{math}};
            \node[NodeST](5)at(5.00,-5.00)
                {\begin{math}\Product\end{math}};
            \node[NodeST](7)at(7.00,-2.50)
                {\begin{math}\Product\end{math}};
            \node[NodeST](9)at(9.00,0.00)
                {\begin{math}\Product\end{math}};
            \draw[Edge](0)--(1);
            \draw[Edge,dotted](1)--(3);
            \draw[Edge](10)--(11);
            \draw[Edge](11)--(9);
            \draw[Edge](12)--(13);
            \draw[Edge,dotted](13)--(11);
            \draw[Edge](14)--(13);
            \draw[Edge](2)--(1);
            \draw[Edge,dotted](3)--(5);
            \draw[Edge](4)--(3);
            \draw[Edge,dotted](5)--(7);
            \draw[Edge](6)--(5);
            \draw[Edge](7)--(9);
            \draw[Edge](8)--(7);
            \node(r)at(9.00,1.88){};
            \draw[Edge](r)--(9);
            %
            \node[fit=(1)(3),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
            \node[fit=(5)(7),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
            \node[fit=(11)(13),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
        \end{tikzpicture}
        \enspace \Rew \enspace
        \begin{tikzpicture}[xscale=.19,yscale=.2,Centering]
            \node(0)at(0.00,-7.50){};
            \node(10)at(10.00,-10.00){};
            \node(12)at(12.00,-12.50){};
            \node(14)at(14.00,-12.50){};
            \node(2)at(2.00,-7.50){};
            \node(4)at(4.00,-5.00){};
            \node(6)at(6.00,-5.00){};
            \node(8)at(8.00,-7.50){};
            \node[NodeST](1)at(1.00,-5.00)
                {\begin{math}\Product\end{math}};
            \node[NodeST](11)at(11.00,-7.50)
                {\begin{math}\Product\end{math}};
            \node[NodeST](13)at(13.00,-10.00)
                {\begin{math}\Product\end{math}};
            \node[NodeST](3)at(3.00,-2.50)
                {\begin{math}\Product\end{math}};
            \node[NodeST](5)at(5.00,0.00)
                {\begin{math}\Product\end{math}};
            \node[NodeST](7)at(7.00,-2.50)
                {\begin{math}\Product\end{math}};
            \node[NodeST](9)at(9.00,-5.00)
                {\begin{math}\Product\end{math}};
            \draw[Edge](0)--(1);
            \draw[Edge,dotted](1)--(3);
            \draw[Edge](10)--(11);
            \draw[Edge](11)--(9);
            \draw[Edge](12)--(13);
            \draw[Edge,dotted](13)--(11);
            \draw[Edge](14)--(13);
            \draw[Edge](2)--(1);
            \draw[Edge,dotted](3)--(5);
            \draw[Edge](4)--(3);
            \draw[Edge](6)--(7);
            \draw[Edge](7)--(5);
            \draw[Edge](8)--(9);
            \draw[Edge,dotted](9)--(7);
            \node(r)at(5.00,1.88){};
            \draw[Edge](r)--(5);
            %
            \node[fit=(1)(3),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
            \node[fit=(7)(9),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
            \node[fit=(11)(13),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
        \end{tikzpicture} \\
        \enspace \RewRT \enspace
        \begin{tikzpicture}[xscale=.19,yscale=.25,Centering]
            \node(0)at(0.00,-1.88){};
            \node(10)at(10.00,-11.25){};
            \node(12)at(12.00,-13.12){};
            \node(14)at(14.00,-13.12){};
            \node(2)at(2.00,-3.75){};
            \node(4)at(4.00,-5.62){};
            \node(6)at(6.00,-7.50){};
            \node(8)at(8.00,-9.38){};
            \node[NodeST](1)at(1.00,0.00)
                {\begin{math}\Product\end{math}};
            \node[NodeST](11)at(11.00,-9.38)
                {\begin{math}\Product\end{math}};
            \node[NodeST](13)at(13.00,-11.25)
                {\begin{math}\Product\end{math}};
            \node[NodeST](3)at(3.00,-1.88)
                {\begin{math}\Product\end{math}};
            \node[NodeST](5)at(5.00,-3.75)
                {\begin{math}\Product\end{math}};
            \node[NodeST](7)at(7.00,-5.62)
                {\begin{math}\Product\end{math}};
            \node[NodeST](9)at(9.00,-7.50)
                {\begin{math}\Product\end{math}};
            \draw[Edge](0)--(1);
            \draw[Edge](10)--(11);
            \draw[Edge,dotted](11)--(9);
            \draw[Edge](12)--(13);
            \draw[Edge,dotted](13)--(11);
            \draw[Edge](14)--(13);
            \draw[Edge](2)--(3);
            \draw[Edge](3)--(1);
            \draw[Edge](4)--(5);
            \draw[Edge,dotted](5)--(3);
            \draw[Edge](6)--(7);
            \draw[Edge](7)--(5);
            \draw[Edge](8)--(9);
            \draw[Edge,dotted](9)--(7);
            \node(r)at(1.00,1.41){};
            \draw[Edge](r)--(1);
            %
            \node[fit=(3)(5),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
            \node[fit=(7)(9),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
            \node[fit=(11)(13),rotate fit=0,inner sep=0pt,
                rounded corners,draw=Col5!80]{};
        \end{tikzpicture}
        \enspace = \enspace
        \RComb{\gamma'}
    \end{multline}
    of rewriting steps, where squared regions denotes left or right
    comb trees of degree $\gamma - 1$. Hence, we have
    $\LComb{\gamma'}\CongrCAs{\gamma}\RComb{\gamma'}$.
\end{proof}
\medbreak

Proposition~\ref{prop:division_CAs} implies the following result.
\medbreak

\begin{Theorem}\label{thm:lattice_CAs}
    The poset $\left(\CAsAll, \OrdCAs\right)$ is a lattice where
    the lower-bound and upper-bound satisfy, for any positive integers
    $\gamma$ and $\gamma'$,
    \begin{equation}
        \CAs{\gamma} \wedge \CAs{\gamma'}
        = \CAs{\gcd \left(\gamma-1, \gamma'-1\right)}
    \end{equation}
    and
    \begin{equation}
        \CAs{\gamma} \vee \CAs{\gamma'}
        = \CAs{\lcm \left(\gamma-1, \gamma'-1\right)}.
    \end{equation}
\end{Theorem}
\medbreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The \texorpdfstring{$3$}{3}-comb associative operad}
\label{sec:CAs_3}
We now focus on the study of the operad $\CAs{3}$. By definition, this
operad is the quotient of $\Mag$ by the operad congruence spanned by the
relation
\begin{equation} \label{equ:rew_1}
    \begin{tikzpicture}[xscale=.22,yscale=.23,Centering]
        \node(0)at(0.00,-5.25){};
        \node(2)at(2.00,-5.25){};
        \node(4)at(4.00,-3.50){};
        \node(6)at(6.00,-1.75){};
        \node[NodeST](1)at(1.00,-3.50){\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
        \node[NodeST](5)at(5.00,0.00){\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](1)--(3);
        \draw[Edge](2)--(1);
        \draw[Edge](3)--(5);
        \draw[Edge](4)--(3);
        \draw[Edge](6)--(5);
        \node(r)at(5.00,1.5){};
        \draw[Edge](r)--(5);
    \end{tikzpicture}
    \enspace \Rew \enspace
    \begin{tikzpicture}[xscale=.22,yscale=.23,Centering]
        \node(0)at(0.00,-1.75){};
        \node(2)at(2.00,-3.50){};
        \node(4)at(4.00,-5.25){};
        \node(6)at(6.00,-5.25){};
        \node[NodeST](1)at(1.00,0.00){\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
        \node[NodeST](5)at(5.00,-3.50){\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](2)--(3);
        \draw[Edge](3)--(1);
        \draw[Edge](4)--(5);
        \draw[Edge](5)--(3);
        \draw[Edge](6)--(5);
        \node(r)at(1.00,1.5){};
        \draw[Edge](r)--(1);
    \end{tikzpicture}\,.
\end{equation}
This rewrite rule is compatible with the lexicographic order on prefix
words presented at the beginning of Section~\ref{sec:operad_Mag} in the
sense that the prefix word of the left member of~\eqref{equ:rew_1} is
lexicographically greater than the prefix word of the right one.
\medbreak

However, the rewrite relation $\RewContext$ induced by $\Rew$ is not
confluent. Indeed, we have
\begin{equation} \label{equ:branching_pair_CAs_3}
    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
        \node(0)at(0.00,-7.20){};
        \node(2)at(2.00,-7.20){};
        \node(4)at(4.00,-5.40){};
        \node(6)at(6.00,-3.60){};
        \node(8)at(8.00,-1.80){};
        \node[NodeST](1)at(1.00,-5.40){\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,-3.60){\begin{math}\Product\end{math}};
        \node[NodeST](5)at(5.00,-1.80){\begin{math}\Product\end{math}};
        \node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](1)--(3);
        \draw[Edge](2)--(1);
        \draw[Edge](3)--(5);
        \draw[Edge](4)--(3);
        \draw[Edge](5)--(7);
        \draw[Edge](6)--(5);
        \draw[Edge](8)--(7);
        \node(r)at(7.00,1.35){};
        \draw[Edge](r)--(7);
    \end{tikzpicture}
    \enspace \RewContext \enspace
    \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
        \node(0)at(0.00,-4.50){};
        \node(2)at(2.00,-4.50){};
        \node(4)at(4.00,-4.50){};
        \node(6)at(6.00,-6.75){};
        \node(8)at(8.00,-6.75){};
        \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
        \node[NodeST](5)at(5.00,-2.25){\begin{math}\Product\end{math}};
        \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](1)--(3);
        \draw[Edge](2)--(1);
        \draw[Edge](4)--(5);
        \draw[Edge](5)--(3);
        \draw[Edge](6)--(7);
        \draw[Edge](7)--(5);
        \draw[Edge](8)--(7);
        \node(r)at(3.00,1.74){};
        \draw[Edge](r)--(3);
    \end{tikzpicture}
    \qquad \mbox{and} \qquad
    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
        \node(0)at(0.00,-7.20){};
        \node(2)at(2.00,-7.20){};
        \node(4)at(4.00,-5.40){};
        \node(6)at(6.00,-3.60){};
        \node(8)at(8.00,-1.80){};
        \node[NodeST](1)at(1.00,-5.40){\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,-3.60){\begin{math}\Product\end{math}};
        \node[NodeST](5)at(5.00,-1.80){\begin{math}\Product\end{math}};
        \node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](1)--(3);
        \draw[Edge](2)--(1);
        \draw[Edge](3)--(5);
        \draw[Edge](4)--(3);
        \draw[Edge](5)--(7);
        \draw[Edge](6)--(5);
        \draw[Edge](8)--(7);
        \node(r)at(7.00,1.35){};
        \draw[Edge](r)--(7);
    \end{tikzpicture}
    \enspace \RewContext \enspace
    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
        \node(0)at(0.00,-3.60){};
        \node(2)at(2.00,-5.40){};
        \node(4)at(4.00,-7.20){};
        \node(6)at(6.00,-7.20){};
        \node(8)at(8.00,-1.80){};
        \node[NodeST](1)at(1.00,-1.80){\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,-3.60){\begin{math}\Product\end{math}};
        \node[NodeST](5)at(5.00,-5.40){\begin{math}\Product\end{math}};
        \node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](1)--(7);
        \draw[Edge](2)--(3);
        \draw[Edge](3)--(1);
        \draw[Edge](4)--(5);
        \draw[Edge](5)--(3);
        \draw[Edge](6)--(5);
        \draw[Edge](8)--(7);
        \node(r)at(7.00,1.5){};
        \draw[Edge](r)--(7);
    \end{tikzpicture}\,,
\end{equation}
and the two right members of~\eqref{equ:branching_pair_CAs_3} form a
branching pair which is not joinable.
\medbreak

In order to transform the rewrite relation induced by~\eqref{equ:rew_1}
into a convergent one, we apply the Buchberger algorithm for
operads~\cite[Section 3.7]{DK10} with respect to the lexicographic order
on prefix words. Following this algorithm, we need to put the right
members of~\eqref{equ:branching_pair_CAs_3} in relation by $\Rew$. To
respect the lexicographic property of the prefix words, this leads to
the new relation
\begin{equation} \label{equ:rew_2}
    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
        \node(0)at(0.00,-3.60){};
        \node(2)at(2.00,-5.40){};
        \node(4)at(4.00,-7.20){};
        \node(6)at(6.00,-7.20){};
        \node(8)at(8.00,-1.80){};
        \node[NodeST](1)at(1.00,-1.80){\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,-3.60){\begin{math}\Product\end{math}};
        \node[NodeST](5)at(5.00,-5.40){\begin{math}\Product\end{math}};
        \node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](1)--(7);
        \draw[Edge](2)--(3);
        \draw[Edge](3)--(1);
        \draw[Edge](4)--(5);
        \draw[Edge](5)--(3);
        \draw[Edge](6)--(5);
        \draw[Edge](8)--(7);
        \node(r)at(7.00,1.5){};
        \draw[Edge](r)--(7);
    \end{tikzpicture}
    \enspace \Rew \enspace
    \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
        \node(0)at(0.00,-4.50){};
        \node(2)at(2.00,-4.50){};
        \node(4)at(4.00,-4.50){};
        \node(6)at(6.00,-6.75){};
        \node(8)at(8.00,-6.75){};
        \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
        \node[NodeST](5)at(5.00,-2.25){\begin{math}\Product\end{math}};
        \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](1)--(3);
        \draw[Edge](2)--(1);
        \draw[Edge](4)--(5);
        \draw[Edge](5)--(3);
        \draw[Edge](6)--(7);
        \draw[Edge](7)--(5);
        \draw[Edge](8)--(7);
        \node(r)at(3.00,1.74){};
        \draw[Edge](r)--(3);
    \end{tikzpicture}\,.
\end{equation}
The Buchberger algorithm applied on binary trees of degrees $5$, $6$,
and $7$ provides the new relations \\
\input{Buchberger_relations_5-7}

\noindent
We claim that the rewrite relation $\RewContext$ induced by
rewrite rule $\Rew$ satisfying~\eqref{equ:rew_1}, \eqref{equ:rew_2},
\eqref{equ:rew_3}---\eqref{equ:rew_11} is convergent. First, for every
relation $\Tfr \Rew \Tfr'$, we have
$\PrefixWord(\Tfr) > \PrefixWord(\Tfr')$. Therefore, by
Lemma~\ref{lem:prefix_word_termination}, $\RewContext$ is terminating.
Moreover, the greatest degree of a tree appearing in $\Rew$ is~$7$ so
that, from Lemma~\ref{lem:degree_confluence}, to show that $\RewContext$
is convergent, it is enough to prove that each tree of degree at most
$13$ admits exactly one normal form. Equivalently, this amounts to
show that the number of normal forms of trees of arity $n$ is equal
to $\#\CAs{3}(n)$. By computer exploration, we get the same sequence
\begin{equation} \label{equ:dimensions_CAs_3}
    1, 1, 2, 4, 8, 14, 20, 19, 16, 14, 14, 15, 16, 17
\end{equation}
for $\#\CAs{3}(n)$ and for the numbers of normal forms of arity $n$,
when $ 1 \leq n \leq 14$. Hence, we get our following main result.
\medbreak

\begin{Theorem} \label{thm:convergent_rewrite_rule_CAs_3}
    The rewrite rule $\Rew$ satisfying~\eqref{equ:rew_1},
    \eqref{equ:rew_2}, \eqref{equ:rew_3}---\eqref{equ:rew_11} is a
    convergent orientation of the congruence $\CongrCAs{3}$
    of~$\CAs{3}$.
\end{Theorem}
\medbreak

The rewrite rule $\Rew$ has, arity by arity, the cardinalities
\begin{equation}
    0, 0, 0, 1, 1, 2, 3, 4, 0, \dots~.
\end{equation}
We obtain from Theorem~\ref{thm:convergent_rewrite_rule_CAs_3} also
the following consequences.
\medbreak

\begin{Proposition} \label{prop:PBW_basis_CAs_3}
    The set of the trees avoiding as subtrees the ones appearing as
    left members of $\Rew$ is a Poincaré-Birkhoff-Witt basis
    of~$\CAs{3}$.
\end{Proposition}
\medbreak

From Proposition~\ref{prop:PBW_basis_CAs_3}, and by using a result
of~\cite{Gir18} describing a system of equations for the generating
series of syntax trees avoiding some sets of subtrees, we obtain the
following result.
\medbreak

\begin{Proposition} \label{prop:Hilbert_series_CAs_3}
    The Hilbert series of $\CAs{3}$ is
    \begin{equation} \label{equ:Hilbert_series_CAs_3}
        \HilbertSeries_{\CAs{3}}(t) = \frac{t}{(1 - t)^2}
        \left(1 - t + t^2 + t^3 + 2t^4 + 2t^5 - 7t^7 - 2t^8 + t^9 +
        2t^{10} + t^{11}\right).
    \end{equation}
\end{Proposition}
\medbreak

For $n \leq 10$, the dimensions of $\CAs{3}(n)$ are provided by
Sequence~\eqref{equ:dimensions_CAs_3} and for all $n \geq 11$, the
Taylor expansion of~\eqref{equ:Hilbert_series_CAs_3} shows that
$\# \CAs{3}(n) = n + 3$.
\medbreak

### 2018-06-29 Introduction.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Introduction}
Associative algebras are spaces endowed with a binary product $\Product$
satisfying among others the associativity law
\begin{math}
    (x_1 \Product x_2) \Product x_3 = x_1 \Product (x_2 \Product x_3)
\end{math}.
It is well-known that the associative algebras are representations of
the associative (nonsymmetric) operad $\As$. This operad can be seen as
the quotient of the magmatic operad $\Mag$ (the free operad of binary
trees on the binary generator~$\Product$) by the operad congruence
$\Congr$ satisfying
\begin{equation} \label{equ:congruence_as}
    \begin{tikzpicture}[xscale=.24,yscale=.24,Centering]
        \node(0)at(0.00,-3.33){};
        \node(2)at(2.00,-3.33){};
        \node(4)at(4.00,-1.67){};
        \node[NodeST](1)at(1.00,-1.67)
            {\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,0.00)
            {\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](1)--(3);
        \draw[Edge](2)--(1);
        \draw[Edge](4)--(3);
        \node(r)at(3.00,1.5){};
        \draw[Edge](r)--(3);
    \end{tikzpicture}
    \Congr
    \begin{tikzpicture}[xscale=.24,yscale=.24,Centering]
        \node(0)at(0.00,-1.67){};
        \node(2)at(2.00,-3.33){};
        \node(4)at(4.00,-3.33){};
        \node[NodeST](1)at(1.00,0.00)
                {\begin{math}\Product\end{math}};
        \node[NodeST](3)at(3.00,-1.67)
                {\begin{math}\Product\end{math}};
        \draw[Edge](0)--(1);
        \draw[Edge](2)--(3);
        \draw[Edge](3)--(1);
        \draw[Edge](4)--(3);
        \node(r)at(1.00,1.5){};
        \draw[Edge](r)--(1);
    \end{tikzpicture}\,.
\end{equation}
These two binary trees are the syntax trees of the expressions appearing
in the above associativity law.
\medbreak

In a more combinatorial context and regardless of the theory of operads,
the Tamari order is a partial order on the set of the binary trees
having a fixed number of internal nodes $d$. This order is generated by
the covering relation consisting in rewriting a tree $\Tfr$ into a tree
$\Tfr'$ by replacing a subtree of $\Tfr$ of the form of the left member
of~\eqref{equ:congruence_as} into a tree of the form of the right member
of~\eqref{equ:congruence_as}. This transformation is known in a computer
science context as the right rotation operation~\cite{Knu98} and
intervenes in algorithms involving binary search trees~\cite{AVL62}. The
partial order hence generated by the right rotation operation is known
as the Tamari order~\cite{Tam62} and has a lot of combinatorial and
algebraic properties (see for instance~\cite{HT72,Cha06}).
\medbreak

A first connection between the associative operad and the Tamari order
is based upon the fact that the orientation of~\eqref{equ:congruence_as}
from left to right provides a convergent orientation (a terminating and
confluent rewrite relation) of the congruence $\Congr$. The normal
forms of the rewrite relation induced by the rewrite rule obtained by
orienting~\eqref{equ:congruence_as} from left to right are right comb
binary trees and are hence in one-to-one correspondence with the
elements of~$\As$.
\medbreak

This work is intended to be a first strike in the study of the eventual
links between the Tamari order and some quotients of the operad $\Mag$.
In the long run, we would like to study quotients $\Mag/_{\Congr}$ of
$\Mag$ where $\Congr$ is an operad congruence generated by equivalence
classes of trees of a fixed degree. In particular, we would like to know
if $\Congr$ is generated by equivalence classes of trees forming
intervals of the Tamari order leads to algebraic properties for
$\Mag/_{\Congr}$ (like the description of orientations of its space of
relations, nice bases and Hilbert series).
\medbreak

We focus here on one of these quotients $\CAs{3}$ which is the operad
describing the category of the algebras equipped with a binary product
$\Product$ and subjected to the relation
\begin{math}
    ((x_1 \Product x_2) \Product x_3) \Product x_4
    =
    x_1 \Product (x_2 \Product (x_3 \Product x_4))
\end{math}.
This is a kind of associativity law in higher degree $d = 3$. This
operad is generated by an equivalence class of trees which is not an
interval for the Tamari order. As preliminary computer experiments show,
$\CAs{3}$ has oscillating first dimensions
(see~\eqref{equ:dimensions_CAs_3}), what is rather unusual among all
known operads. In this paper, we provide an orientation of the space of
relations of $\CAs{3}$. For this, we use rewrite systems on
trees~\cite{BN98} and the Buchberger algorithm for operads~\cite{DK10}.
\medbreak

This text is presented as follows. Section~\ref{sec:operad_Mag} contains
preliminaries about the magmatic operad and rewrite relations on trees.
In Section~\ref{sec:CAs_d}, we define the operad $\CAs{3}$ as a
particular case of a more general construction of generalizations
$\CAs{d}$, $d \geq 1$, of $\As$. Finally, Section~\ref{sec:CAs_3}
contains the orientation of the space of relations of
$\CAs{3}$ (Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}). As
consequences, we obtain for $\CAs{3}$
the description of one of its Poincaré-Birkhoff-Witt bases
(Proposition~\ref{prop:PBW_basis_CAs_3}) and the description of
its Hilbert series (Proposition~\ref{prop:Hilbert_series_CAs_3}).
\medbreak

### 2018-06-29 Operads_rewrite.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The magmatic operad, quotients, and rewrite relations}
\label{sec:operad_Mag}
We consider nonsymmetric set-theoretic operads. Let $\Oca$ be such an
operad. We denote respectively by $\circ_i$ and $\circ$ the partial and
complete compositions of $\Oca$. For any $n \geq 1$, $\Oca(n)$ is the
set of the elements $x$ of $\Oca$ of arity $|x| = n$. We denote
by $\Mag$ the magmatic operad, that is the free operad over one binary
generator $\Product$, and we represent the elements of $\Mag$ by binary
trees. The \Def{arity} $|\Tfr|$ (resp. \Def{degree} $\Deg(\Tfr)$) of a
binary tree $\Tfr$ is its number of leaves (resp. internal nodes).
Recall that for any positive integer $n$,
$\# \Mag(n)$ is the $n$th Catalan number
$\Catalan(n) := \binom{2n - 2}{n - 1}\frac{1}{n}$.
\medbreak

Given a binary tree $\Tfr$, we denote by $ \PrefixWord(\Tfr)$ the
\Def{prefix word} of $\Tfr$, that is the word on $\{\Zero, \Two\}$
obtained by a left to right depth-first traversal of $\Tfr$ and by
writing $\Zero$ (resp. $\Two$) when a leaf (resp. an internal node) is
encountered. The set of all words on $\{\Zero, \Two\}$ is endowed with
the lexicographic order $\leq$ induced by $\Zero < \Two$.
\medbreak

If $\Rew$ is a rewrite rule on $\Mag$ such that $\Sfr \Rew \Sfr'$
implies $|\Sfr| = |\Sfr'|$, we denote by $\RewContext$ the
\Def{rewrite relation induced} by $\Rew$. Formally we have
\begin{math}
    \Tfr\circ_i\left(\Sfr\circ\left[\Rfr_1,\dots,\Rfr_{n}\right]\right)
    \RewContext
    \Tfr\circ_i\left(\Sfr'\circ\left[\Rfr_1,\dots,\Rfr_{n}\right]\right)
\end{math},
if $\Sfr \Rew \Sfr'$ where $n = |\Sfr|$, and $\Tfr$, $\Rfr_1$, \dots,
$\Rfr_n$ are binary trees. In other words, one has
$\Tfr \RewContext \Tfr'$ if it is possible to obtain $\Tfr'$ from $\Tfr$
by replacing a subtree $\Sfr$ of $\Tfr$ by $\Sfr'$ whenever
$\Sfr \Rew \Sfr'$. We use here the standard terminology
(\Def{terminating}, \Def{confluent}, \Def{convergent}, \Def{branching
pair}, \Def{joinable}, \Def{normal form}, {\em etc.}) about rewrite
relations and rewrite systems~\cite{BN98}.
\medbreak

Given an operad $\Oca \simeq \Mag/_{\Congr}$ where $\Congr$ is an operad
congruence of $\Mag$, we denote by $[\Tfr]_{\Congr}$ the
$\Congr$-equivalence class of any $\Tfr \in \Mag$. Besides, we say that
$\Rew$ is an \Def{orientation} of $\Congr$ if the reflexive, transitive,
and symmetric closure of $\RewContext$ is $\Congr$. We say that $\Rew$
is a \Def{convergent orientation} if $\RewContext$ is convergent. When
$\Rew$ is a convergent orientation of $\Congr$, the set of all normal
forms of $\RewContext$ is a \Def{Poincaré-Birkhoff-Witt basis} of the
operad $\Oca$ and its elements are exactly the binary trees avoiding,
as subtrees, the trees appearing as left members in~$\Rew$.
\medbreak

We shall use the following criterion to prove that a rewrite relation on
$\Mag$ is terminating.
\medbreak

\begin{Lemma}\label{lem:prefix_word_termination}
    Let $\Rew$ be a rewrite rule on $\Mag$. If for any
    $\Tfr, \Tfr' \in \Mag$ such that $\Tfr \Rew \Tfr'$ one has
    $\PrefixWord(\Tfr) > \PrefixWord(\Tfr')$, then the rewrite relation
    induced by $\Rew$ is terminating.
\end{Lemma}
\medbreak

Moreover, we shall use the following result appearing in~\cite{Gir16}
specialized on rewrite relation on $\Mag$ to prove that a terminating
rewrite relation is convergent.
\medbreak

\begin{Lemma} \label{lem:degree_confluence}
    Let $\Rew$ be a rewrite rule on $\Mag$ wherein all trees $\Tfr$ and
    $\Tfr'$ such that $\Tfr \Rew \Tfr'$ have degrees at most $\ell$.
    Then, if the rewrite relation $\RewContext$ induced by $\Rew$ is
    terminating and all its branching pairs of degrees at most
    $2\ell - 1$ are joinable, $\RewContext$ is convergent.
\end{Lemma}
\medbreak

### 2018-07-02 Magmatic_operads.tex
fin de la rédaction section opérades magmatiques

@@
-\section{Quotients of the magmatic operad}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Magmatic operads}
 
@@
 
-\subsection{Lattice structure}
+\subsection{Lattice of magmatic quotients}
 
-We denote by $\IMag$ the set of operadic of $\Mag$, and
+We denote by $\IMag$ the set of operadic ideals of $\Mag$, and
 \begin{equation} \label{equ:definition_of_QMag}
@@
 \end{equation}
+Explicitely, for every integer $n$, $\left(\Oca_1\wedge\Oca_2\right)(n)$ (respectively, $\left(\Oca_1\vee\Oca_2\right)(n)$) is the quotient of vector spaces $\Mag(n)/\left(I_1(n)+I_2(n)\right)$ (respectively, $\Mag(n)/\left(I_1(n)\cap I_2(n)\right)$), and the operadic compitions are induced by the operadic compositions of $\Mag$.
 
@@
 \end{proof}
-\subsection{Kernels of magmatic operads}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Hilbert series and magmatic quotients}
+
+Given an operad $\Oca$, we denote by $H_{\Oca}$ the \Def{Hiblert serie} of $\Oca$, that is
+\begin{equation} \label{equ:definition_of_Hilbert_series}
+  H_{\Oca}(t)=\sum_{n\in\N}\dim{\left(\Oca(n)\right)}t^n.
+\end{equation}
+
+In Theorem~\ref{thm:Grassmann_formula_for__Hilbert_series_of_QMag}, we show the Grassman formula for the lattice $\left(\QMag,\preceq,\wedge,\vee\right)$. For that, we need the following lemma:
+
+\begin{Lemma} \label{lem:lattice_structure_and_coefficients_of_Hiblert_series}
+  Let $\Oca_1$ and $\Oca_2$ be two elements of $\QMag$. For every integer $n$, we have
+  \begin{equation} \label{equ:lattice_structure_and_coefficients_of_the_Hiblert_series}
+    \dim{\left(\Oca_1\wedge\Oca_2(n)\right)}+\dim{\left(\Oca_1\vee\Oca_2(n)\right)}=\dim{\left(\Oca_1(n)\right)}+\dim{\left(\Oca_2(n)\right)}.    \end{equation}
+\end{Lemma}
+
+\begin{proof}
+  Let $I_1$ and $I_2$ be the two operadic ideals of $\Mag$ such that $\Oca_1$ and $\Oca_2$ are equal to $\Mag/I_1$ and $\Mag/I_2$, respectively. For every integer $n$, we have
+  \[\begin{split}
+  &\dim{\left(\Oca_1\wedge\Oca_2(n)\right)}+\dim{\left(\Oca_1\vee\Oca_2(n)\right)}\\
+  &=\dim{\Big(\Mag(n)/\left(I_1+I_2\right)(n)\Big)}+\dim{\Big(\Mag(n)/\left(I_1\cap I_2\right)(n)\Big)}\\
+  &=\dim{\left(\Mag(n)\right)}-\dim{\left(I_1(n)+I_2(n)\right)}+\dim{\left(\Mag(n)\right)}-\dim{\left(I_1(n)\cap I_2(n)\right)}\\
+  &=\dim{\left(\Mag(n)\right)}-\dim{\left(I_1(n)\right)}+\dim{\left(\Mag(n)\right)}-\dim{\left(I_2(n)\right)}\\
+  &=\dim{\Big(\Mag(n)/I_1(n)\Big)}+\dim{\Big(\Mag(n)/I_2(n)\Big)}\\
+  &=\dim{\left(\Oca_1(n)\right)}+\dim{\left(\Oca_2(n)\right)}.
+  \end{split}\]
+  The third equality is due to the Grassmann formula applied to the subspaces $I_1(n)$ and $I_2(n)$ of $\Mag(n)$.
+\end{proof}
+
+\begin{Theorem} \label{thm:Grassmann_formula_for__Hilbert_series_of_QMag}
+  Let $\Oca_1$ and $\Oca_2$ be two elements of $\QMag$. We have
+  \begin{equation} \label{equ:lattice_structure_and_Hiblert_series}
+    H_{\Oca_1\wedge\Oca_2}(t)+H_{\Oca_1\vee\Oca_2}(t)=H_{\Oca_1}(t)+H_{\Oca_2}(t).
+    \end{equation}
+  \end{Theorem}
+
+\begin{proof}
+  We have
+  \[\begin{split}
+  H_{\Oca_1\wedge\Oca_2}(t)+H_{\Oca_1\vee\Oca_2}(t)&=\sum_{n\in\N}\dim{\left(\Oca_1\wedge\Oca_2(n)\right)}t^n+\sum_{n\in\N}\dim{\left(\Oca_1\vee\Oca_2(n)\right)}t^n\\
+  &=\sum_{n\in\N}\Big(\dim{\left(\Oca_1\wedge\Oca_2(n)\right)}+\dim{\left(\Oca_1\vee\Oca_2(n)\right)}\Big)t^n\\
+  &=\sum_{n\in\N}\Big(\dim{\left(\Oca_1(n)\right)}+\dim{\left(\Oca_2(n)\right)}\Big)t^n\\
+  &=\sum_{n\in\N}\dim{\left(\Oca_1(n)\right)}t^n+\sum_{n\in\N}\dim{\left(\Oca_2(n)\right)}t^n\\
+  &=H_{\Oca_1}(t)+H_{\Oca_2}(t).
+  \end{split}\]
+\end{proof}
+The third equality is due to Lemma~\ref{lem:lattice_structure_and_coefficients_of_Hiblert_series}.
+% Hilbert series, enumeration, a little of rewrite systems, etc.

### 2018-07-05 Operads_rewrite.tex
Debut 1re section

@@
 \label{sec:operad_Mag}
+We set in this preliminary section our notations about operads. We also
+provide a definition for the magmatic operad and introduce tools to
+handle with some of its quotients involving rewrite systems on
+syntax trees.
+\medbreak
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Nonsymmetric operads}
+A \Def{nonsymmetric operad in the category of sets}, or a
+\Def{nonsymmetric operad} for short, is a graded set
+\begin{equation}
+    \Oca = \bigsqcup_{n \geq 1} \Oca(n)
+\end{equation}
+together with maps
+\begin{equation}
+    \circ_i : \Oca(n) \times \Oca(m) \to \Oca(n + m - 1),
+    \qquad 1 \leq i \leq n, 1 \leq m,
+\end{equation}
+called \Def{partial compositions}, and a distinguished element
+$\Unit \in \Oca(1)$, the \Def{unit} of $\Oca$. This data has to satisfy,
+for any $x, y, z \in \Oca$, the three relations
+\begin{subequations}
+\begin{equation} \label{equ:operad_axiom_1}
+    (x \circ_i y) \circ_{i + j - 1} z = x \circ_i (y \circ_j z),
+    \qquad
+    1 \leq i \leq |x|, 1 \leq j \leq |y|,
+\end{equation}
+\begin{equation} \label{equ:operad_axiom_2}
+    (x \circ_i y) \circ_{j + |y| - 1} z = (x \circ_j z) \circ_i y,
+    \qquad
+    1 \leq i < j \leq |x|,
+\end{equation}
+\begin{equation} \label{equ:operad_axiom_3}
+    \Unit \circ_1 x = x = x \circ_i \Unit,
+    \qquad 1 \leq i \leq |x|.
+\end{equation}
+\end{subequations}
+Since we consider in this work only nonsymmetric operads, we shall call
+these simply \Def{operads}.
+\medbreak
+
+Let us provide some elementary definitions and notations about operads.
+If $x$ is an element of $\Oca$ such that $x \in \Oca(n)$ for an
+$n \geq 1$, the \Def{arity} $|x|$ of $x$ is $n$. If $\Oca_1$ and
+$\Oca_2$ are two operads, a map $\phi : \Oca_1 \to \Oca_2$ is an
+\Def{operad morphism} is it respects the arities, sends the unit of
+$\Oca_1$ to the unit of $\Oca_2$, and commutes with partial composition
+maps. We say that $\Oca_2$ is a \Def{suboperad} of $\Oca_1$ if $\Oca_2$
+is a subset of $\Oca_1$ containing the unit of $\Oca_1$ and the partial
+composition maps of $\Oca_2$ are the ones of $\Oca_1$ restricted on
+$\Oca_2$. For any subset $\GeneratingSet$ of $\Oca$, the
+\Def{operad generated} by $\GeneratingSet$ is the smallest suboperad
+$\Oca^\GeneratingSet$ of $\Oca$ containing $\GeneratingSet$. When
+$\Oca = \Oca^\GeneratingSet$, we say that $\GeneratingSet$ is a
+\Def{generating set} of $\Oca$. In this case, and when additionally
+$\GeneratingSet$ is minimal among all the subsets of $\Oca$ satisfying
+this property, $\GeneratingSet$ is a \Def{minimal} generating set of
+$\Oca$. An \Def{operad congruence} is an equivalence relation
+$\Congr$ on $\Oca$ such that $\Congr$ respects the arities, and
+for any $x, x', y, y' \in \Oca$ such that
+$x \Congr x'$ and $y \Congr y'$, $x \circ_i y$ is $\Congr$-equivalent to
+$x' \circ_i y'$ for any valid integer $i$. Given an operad congruence
+$\Congr$, the \Def{quotient operad} $\Oca/_{\Congr}$ of $\Oca$ by
+$\Congr$ is the operad of all $\Congr$-equivalence classes endowed
+with the partial composition maps defined in the obvious way.
+In the case where all the sets $\Oca(n)$, $n \geq 1$, are finite, the
+\Def{Hilbert series} $\HilbertSeries_\Oca(t)$ of $\Oca$ is the series
+defined by
+\begin{equation}
+    \HilbertSeries_\Oca(t) := \sum_{n \geq 1} \# \Oca(n) t^n.
+\end{equation}
+
+\Todo{TO DO}
+
 We consider nonsymmetric set-theoretic operads. Let $\Oca$ be such an
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Magmatic operad}
+
 Given a binary tree $\Tfr$, we denote by $ \PrefixWord(\Tfr)$ the
@@
 \medbreak
+
+\Todo{TO DO}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Rewrite systems and presentations}
+
+\Todo{TO DO}
 

### 2018-07-05 Operads_rewrite.tex
Partie 1 (chantier)

@@
 provide a definition for the magmatic operad and introduce tools to
-handle with some of its quotients involving rewrite systems on
-syntax trees.
+handle with some of its quotients involving rewrite systems on syntax
+trees.
 \medbreak
@@
 $\Oca$. An \Def{operad congruence} is an equivalence relation
-$\Congr$ on $\Oca$ such that $\Congr$ respects the arities, and
-for any $x, x', y, y' \in \Oca$ such that
-$x \Congr x'$ and $y \Congr y'$, $x \circ_i y$ is $\Congr$-equivalent to
-$x' \circ_i y'$ for any valid integer $i$. Given an operad congruence
-$\Congr$, the \Def{quotient operad} $\Oca/_{\Congr}$ of $\Oca$ by
-$\Congr$ is the operad of all $\Congr$-equivalence classes endowed
-with the partial composition maps defined in the obvious way.
-In the case where all the sets $\Oca(n)$, $n \geq 1$, are finite, the
-\Def{Hilbert series} $\HilbertSeries_\Oca(t)$ of $\Oca$ is the series
-defined by
+$\Congr$ on $\Oca$ such that $\Congr$ respects the arities, and for any
+$x, x', y, y' \in \Oca$ such that $x \Congr x'$ and $y \Congr y'$,
+$x \circ_i y$ is $\Congr$-equivalent to $x' \circ_i y'$ for any valid
+integer $i$. Given an operad congruence $\Congr$, the
+\Def{quotient operad} $\Oca/_{\Congr}$ of $\Oca$ by $\Congr$ is the
+operad of all $\Congr$-equivalence classes endowed with the partial
+composition maps defined in the obvious way. In the case where all the
+sets $\Oca(n)$, $n \geq 1$, are finite, the \Def{Hilbert series}
+$\HilbertSeries_\Oca(t)$ of $\Oca$ is the series defined by
 \begin{equation}
@@
 \end{equation}
-
-\Todo{TO DO}
-
-We consider nonsymmetric set-theoretic operads. Let $\Oca$ be such an
-operad. We denote respectively by $\circ_i$ and $\circ$ the partial and
-complete compositions of $\Oca$. For any $n \geq 1$, $\Oca(n)$ is the
-set of the elements $x$ of $\Oca$ of arity $|x| = n$. We denote
-by $\Mag$ the magmatic operad, that is the free operad over one binary
-generator $\Product$, and we represent the elements of $\Mag$ by binary
-trees. The \Def{arity} $|\Tfr|$ (resp. \Def{degree} $\Deg(\Tfr)$) of a
-binary tree $\Tfr$ is its number of leaves (resp. internal nodes).
-Recall that for any positive integer $n$,
-$\# \Mag(n)$ is the $n$th Catalan number
-$\Catalan(n) := \binom{2n - 2}{n - 1}\frac{1}{n}$.
 \medbreak
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Magmatic operad}
+\subsection{Binary trees and magmatic operad}
+A \Def{binary tree} is either the \Def{leaf} $\Leaf$ or a pair
+$(\Tfr_1, \Tfr_2)$ of binary trees. We use the standard terminology
+about binary trees (such as \Def{root}, \Def{internal node},
+\Def{child}, {\em etc.}) in this work. Let us recall the main notions.
+The \Def{arity} $|\Tfr|$ (resp. \Def{degree} $\Deg(\Tfr)$) of a binary
+tree $\Tfr$ is its number of leaves (resp. internal nodes). We shall
+draw binary trees the root to the top. For instance,
+\begin{equation}
+    \begin{tikzpicture}[xscale=.15,yscale=.18,Centering]
+        \node(0)at(0.00,-4.50){};
+        \node(2)at(2.00,-6.75){};
+        \node(4)at(4.00,-6.75){};
+        \node(6)at(6.00,-4.50){};
+        \node(8)at(8.00,-4.50){};
+        \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
+        \node[NodeST](3)at(3.00,-4.50){\begin{math}\Product\end{math}};
+        \node[NodeST](5)at(5.00,0.00){\begin{math}\Product\end{math}};
+        \node[NodeST](7)at(7.00,-2.25){\begin{math}\Product\end{math}};
+        \draw[Edge](0)--(1);
+        \draw[Edge](1)--(5);
+        \draw[Edge](2)--(3);
+        \draw[Edge](3)--(1);
+        \draw[Edge](4)--(3);
+        \draw[Edge](6)--(7);
+        \draw[Edge](7)--(5);
+        \draw[Edge](8)--(7);
+        \node(r)at(5.00,2){};
+        \draw[Edge](r)--(5);
+    \end{tikzpicture}
+\end{equation}
+is the graphical representation of the binary tree
+\begin{math}
+    ((\Leaf, (\Leaf, \Leaf)), (\Leaf, \Leaf)).
+\end{math}
+\medbreak
+
+The \Def{magmatic operad} $\Mag$ is the graded set of all binary trees
+where $\Mag(n)$, $n \geq 1$, is the set of all binary trees of arity
+$n$. The partial composition maps of $\Mag$ are grafting of trees: given
+two binary trees $\Tfr$ and $\Sfr$, $\Tfr \circ_i \Sfr$ is the binary
+tree obtained by grafting the root of $\Sfr$ onto the $i$th leaf
+(numbered from left to right) of $\Tfr$. For instance,
+\begin{equation}
+    \begin{tikzpicture}[xscale=.15,yscale=.18,Centering]
+        \node(0)at(0.00,-4.50){};
+        \node(2)at(2.00,-6.75){};
+        \node(4)at(4.00,-6.75){};
+        \node(6)at(6.00,-4.50){};
+        \node(8)at(8.00,-4.50){};
+        \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
+        \node[NodeST](3)at(3.00,-4.50){\begin{math}\Product\end{math}};
+        \node[NodeST](5)at(5.00,0.00){\begin{math}\Product\end{math}};
+        \node[NodeST](7)at(7.00,-2.25){\begin{math}\Product\end{math}};
+        \draw[Edge](0)--(1);
+        \draw[Edge](1)--(5);
+        \draw[Edge](2)--(3);
+        \draw[Edge](3)--(1);
+        \draw[Edge](4)--(3);
+        \draw[Edge](6)--(7);
+        \draw[Edge](7)--(5);
+        \draw[Edge](8)--(7);
+        \node(r)at(5.00,2){};
+        \draw[Edge](r)--(5);
+    \end{tikzpicture}
+    \enspace \circ_4 \enspace
+    \begin{tikzpicture}[xscale=.17,yscale=.18,Centering]
+        \node(0)at(0.00,-4.67){};
+        \node(2)at(2.00,-4.67){};
+        \node(4)at(4.00,-4.67){};
+        \node(6)at(6.00,-4.67){};
+        \node[NodeST](1)at(1.00,-2.33){\begin{math}\Product\end{math}};
+        \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
+        \node[NodeST](5)at(5.00,-2.33){\begin{math}\Product\end{math}};
+        \draw[Edge](0)--(1);
+        \draw[Edge](1)--(3);
+        \draw[Edge](2)--(1);
+        \draw[Edge](4)--(5);
+        \draw[Edge](5)--(3);
+        \draw[Edge](6)--(5);
+        \node(r)at(3.00,2){};
+        \draw[Edge](r)--(3);
+    \end{tikzpicture}
+    \enspace = \enspace
+    \begin{tikzpicture}[xscale=.15,yscale=.14,Centering]
+        \node(0)at(0.00,-6.00){};
+        \node(10)at(10.00,-12.00){};
+        \node(12)at(12.00,-12.00){};
+        \node(14)at(14.00,-6.00){};
+        \node(2)at(2.00,-9.00){};
+        \node(4)at(4.00,-9.00){};
+        \node(6)at(6.00,-12.00){};
+        \node(8)at(8.00,-12.00){};
+        \node[NodeST](1)at(1.00,-3.00){\begin{math}\Product\end{math}};
+        \node[NodeST](11)at(11.00,-9.00){\begin{math}\Product\end{math}};
+        \node[NodeST](13)at(13.00,-3.00){\begin{math}\Product\end{math}};
+        \node[NodeST](3)at(3.00,-6.00){\begin{math}\Product\end{math}};
+        \node[NodeST](5)at(5.00,0.00){\begin{math}\Product\end{math}};
+        \node[NodeST](7)at(7.00,-9.00){\begin{math}\Product\end{math}};
+        \node[NodeST](9)at(9.00,-6.00){\begin{math}\Product\end{math}};
+        \draw[Edge](0)--(1);
+        \draw[Edge](1)--(5);
+        \draw[Edge](10)--(11);
+        \draw[Edge](11)--(9);
+        \draw[Edge](12)--(11);
+        \draw[Edge](13)--(5);
+        \draw[Edge](14)--(13);
+        \draw[Edge](2)--(3);
+        \draw[Edge](3)--(1);
+        \draw[Edge](4)--(3);
+        \draw[Edge](6)--(7);
+        \draw[Edge](7)--(9);
+        \draw[Edge](8)--(7);
+        \draw[Edge](9)--(13);
+        \node(r)at(5.00,2.5){};
+        \draw[Edge](r)--(5);
+    \end{tikzpicture}
+\end{equation}
+is a partial composition in $\Mag$. The number of binary of arity
+$n \geq 1$ is the $n$th Catalan number $\Catalan(n)$ and hence, the
+Hilbert series of $\Mag$ is
+\begin{equation}
+    \HilbertSeries_{\Mag}(t)
+    = \sum_{n \geq 1} \Catalan(n) t^n
+    = \sum_{n \geq 1} \binom{2n - 1}{n - 1} \frac{1}{n} t^n.
+\end{equation}
+\medbreak
+
+The operad $\Mag$ is the free operad generated by one binary element. It
+satisfies the following universality property. Let
+$\GeneratingSet := \GeneratingSet(2) := \{\Product\}$
+be the graded set containing exactly one element $\Product$ of arity
+$2$. For any operad $\Oca$ and any map
+$f : \GeneratingSet(2) \to \Oca(2)$, there exists a unique operad
+morphism $\phi : \Mag \to \Oca$ such that $f = \phi \circ \Corolla$,
+where $\Corolla$ is the map sending $\Product$ to the unique binary tree
+of degree $1$. In other terms, the diagram
+\begin{equation}
+    \begin{tikzpicture}[xscale=1.4,yscale=1.2,Centering]
+        \node(G)at(0,0){\begin{math}\GeneratingSet\end{math}};
+        \node(O)at(2,0){\begin{math}\Oca\end{math}};
+        \node(AG)at(0,-2){\begin{math}\Mag\end{math}};
+        \draw[Map](G)--(O)node[midway,above]{\begin{math}f\end{math}};
+        \draw[Injection](G)--(AG)node[midway,left]
+            {\begin{math}\Corolla\end{math}};
+        \draw[Map,dashed](AG)--(O)node[midway,right]
+            {\begin{math}\phi\end{math}};
+    \end{tikzpicture}
+\end{equation}
+commutes.
+\medbreak
+
+\Todo{TO DO}
 
@@
 \medbreak
-
-\Todo{TO DO}
 

### 2018-07-06 Operads_rewrite.tex
Partie 1 chantier (suite)

@@
 If $x$ is an element of $\Oca$ such that $x \in \Oca(n)$ for an
-$n \geq 1$, the \Def{arity} $|x|$ of $x$ is $n$. If $\Oca_1$ and
-$\Oca_2$ are two operads, a map $\phi : \Oca_1 \to \Oca_2$ is an
-\Def{operad morphism} is it respects the arities, sends the unit of
-$\Oca_1$ to the unit of $\Oca_2$, and commutes with partial composition
-maps. We say that $\Oca_2$ is a \Def{suboperad} of $\Oca_1$ if $\Oca_2$
-is a subset of $\Oca_1$ containing the unit of $\Oca_1$ and the partial
-composition maps of $\Oca_2$ are the ones of $\Oca_1$ restricted on
-$\Oca_2$. For any subset $\GeneratingSet$ of $\Oca$, the
-\Def{operad generated} by $\GeneratingSet$ is the smallest suboperad
-$\Oca^\GeneratingSet$ of $\Oca$ containing $\GeneratingSet$. When
-$\Oca = \Oca^\GeneratingSet$, we say that $\GeneratingSet$ is a
-\Def{generating set} of $\Oca$. In this case, and when additionally
-$\GeneratingSet$ is minimal among all the subsets of $\Oca$ satisfying
-this property, $\GeneratingSet$ is a \Def{minimal} generating set of
-$\Oca$. An \Def{operad congruence} is an equivalence relation
-$\Congr$ on $\Oca$ such that $\Congr$ respects the arities, and for any
-$x, x', y, y' \in \Oca$ such that $x \Congr x'$ and $y \Congr y'$,
-$x \circ_i y$ is $\Congr$-equivalent to $x' \circ_i y'$ for any valid
-integer $i$. Given an operad congruence $\Congr$, the
+$n \geq 1$, the \Def{arity} $|x|$ of $x$ is $n$. The
+\Def{complete composition maps} of $\Oca$ are the map
+\begin{equation}
+    \circ : \Oca(n) \times \Oca(m_1) \times \dots \times \Oca(m_n)
+    \to \Oca(m_1 + \dots + m_n)
+\end{equation}
+defined, for any $x \in \Oca(n)$ and $y_1, \dots, y_n \in \Oca$, by
+\begin{equation}
+    x \circ [y_1, \dots, y_n] :=
+    (\dots ((x \circ_n y_n) \circ_{n - 1} y_{n - 1}) \dots) \circ_1 y_1.
+\end{equation}
+If $\Oca_1$ and $\Oca_2$ are two operads, a map
+$\phi : \Oca_1 \to \Oca_2$ is an \Def{operad morphism} is it respects
+the arities, sends the unit of $\Oca_1$ to the unit of $\Oca_2$, and
+commutes with partial composition maps. We say that $\Oca_2$ is a
+\Def{suboperad} of $\Oca_1$ if $\Oca_2$ is a subset of $\Oca_1$
+containing the unit of $\Oca_1$ and the partial composition maps of
+$\Oca_2$ are the ones of $\Oca_1$ restricted on $\Oca_2$. For any subset
+$\GeneratingSet$ of $\Oca$, the \Def{operad generated} by
+$\GeneratingSet$ is the smallest suboperad $\Oca^\GeneratingSet$ of
+$\Oca$ containing $\GeneratingSet$. When $\Oca = \Oca^\GeneratingSet$,
+we say that $\GeneratingSet$ is a \Def{generating set} of $\Oca$. In
+this case, and when additionally $\GeneratingSet$ is minimal among all
+the subsets of $\Oca$ satisfying this property, $\GeneratingSet$ is a
+\Def{minimal} generating set of $\Oca$. An \Def{operad congruence} is an
+equivalence relation $\Congr$ on $\Oca$ such that $\Congr$ respects the
+arities, and for any $x, x', y, y' \in \Oca$ such that $x \Congr x'$ and
+$y \Congr y'$, $x \circ_i y$ is $\Congr$-equivalent to $x' \circ_i y'$
+for any valid integer $i$. Given an operad congruence $\Congr$, the
 \Def{quotient operad} $\Oca/_{\Congr}$ of $\Oca$ by $\Congr$ is the
@@
 about binary trees (such as \Def{root}, \Def{internal node},
-\Def{child}, {\em etc.}) in this work. Let us recall the main notions.
-The \Def{arity} $|\Tfr|$ (resp. \Def{degree} $\Deg(\Tfr)$) of a binary
-tree $\Tfr$ is its number of leaves (resp. internal nodes). We shall
-draw binary trees the root to the top. For instance,
+\Def{left child}, \Def{right child}, {\em etc.}) in this work. Let us
+recall the main notions. The \Def{arity} $|\Tfr|$ (resp. \Def{degree}
+$\Deg(\Tfr)$) of a binary tree $\Tfr$ is its number of leaves (resp.
+internal nodes). We shall draw binary trees the root to the top. For
+instance,
 \begin{equation}
@@
 (numbered from left to right) of $\Tfr$. For instance,
-\begin{equation}
+\begin{equation} \label{equ:example_composition_mag}
     \begin{tikzpicture}[xscale=.15,yscale=.18,Centering]
@@
 \end{equation}
-is a partial composition in $\Mag$. The number of binary of arity
+is a partial composition in $\Mag$. This leads, by definition, to the
+following complete composition maps of $\Mag$. Given $\Tfr \in \Mag(n)$
+and $\Sfr_1, \dots, \Sfr_n \in \Mag$,
+\begin{math}
+    \Tfr \circ [\Sfr_1, \dots, \Sfr_n]
+\end{math}
+is the binary tree obtained by grafting simultaneously the roots of all
+$\Sfr_i$ of the $i$th leaves of $\Tfr$. The number of binary of arity
 $n \geq 1$ is the $n$th Catalan number $\Catalan(n)$ and hence, the
@@
 satisfies the following universality property. Let
-$\GeneratingSet := \GeneratingSet(2) := \{\Product\}$
+\begin{math}
+    \GeneratingSet := \GeneratingSet(2) := \{\Product\}
+\end{math}
 be the graded set containing exactly one element $\Product$ of arity
 $2$. For any operad $\Oca$ and any map
-$f : \GeneratingSet(2) \to \Oca(2)$, there exists a unique operad
-morphism $\phi : \Mag \to \Oca$ such that $f = \phi \circ \Corolla$,
-where $\Corolla$ is the map sending $\Product$ to the unique binary tree
-of degree $1$. In other terms, the diagram
+\begin{math}
+    f : \GeneratingSet(2) \to \Oca(2),
+\end{math}
+there exists a unique operad morphism $\phi : \Mag \to \Oca$ such that
+$f = \phi \circ \Corolla$, where $\Corolla$ is the map sending
+$\Product$ to the unique binary tree of degree $1$ (and then, arity
+$2$). In other terms, the diagram
 \begin{equation}
-    \begin{tikzpicture}[xscale=1.4,yscale=1.2,Centering]
+    \begin{tikzpicture}[xscale=1.3,yscale=1.1,Centering]
         \node(G)at(0,0){\begin{math}\GeneratingSet\end{math}};
@@
 
-\Todo{TO DO}
-
+We now provide some useful tools about binary trees.
 Given a binary tree $\Tfr$, we denote by $ \PrefixWord(\Tfr)$ the
@@
 writing $\Zero$ (resp. $\Two$) when a leaf (resp. an internal node) is
-encountered. The set of all words on $\{\Zero, \Two\}$ is endowed with
+encountered. For instance,
+\begin{equation}
+    \begin{tikzpicture}[xscale=.15,yscale=.14,Centering]
+        \node(0)at(0.00,-6.00){};
+        \node(10)at(10.00,-12.00){};
+        \node(12)at(12.00,-12.00){};
+        \node(14)at(14.00,-6.00){};
+        \node(2)at(2.00,-9.00){};
+        \node(4)at(4.00,-9.00){};
+        \node(6)at(6.00,-12.00){};
+        \node(8)at(8.00,-12.00){};
+        \node[NodeST](1)at(1.00,-3.00){\begin{math}\Product\end{math}};
+        \node[NodeST](11)at(11.00,-9.00){\begin{math}\Product\end{math}};
+        \node[NodeST](13)at(13.00,-3.00){\begin{math}\Product\end{math}};
+        \node[NodeST](3)at(3.00,-6.00){\begin{math}\Product\end{math}};
+        \node[NodeST](5)at(5.00,0.00){\begin{math}\Product\end{math}};
+        \node[NodeST](7)at(7.00,-9.00){\begin{math}\Product\end{math}};
+        \node[NodeST](9)at(9.00,-6.00){\begin{math}\Product\end{math}};
+        \draw[Edge](0)--(1);
+        \draw[Edge](1)--(5);
+        \draw[Edge](10)--(11);
+        \draw[Edge](11)--(9);
+        \draw[Edge](12)--(11);
+        \draw[Edge](13)--(5);
+        \draw[Edge](14)--(13);
+        \draw[Edge](2)--(3);
+        \draw[Edge](3)--(1);
+        \draw[Edge](4)--(3);
+        \draw[Edge](6)--(7);
+        \draw[Edge](7)--(9);
+        \draw[Edge](8)--(7);
+        \draw[Edge](9)--(13);
+        \node(r)at(5.00,2.5){};
+        \draw[Edge](r)--(5);
+    \end{tikzpicture}
+    \xmapsto{\; \PrefixWord \;}
+    \Two \Two \Zero \Two \Zero \Zero \Two \Two \Two \Zero \Zero \Two
+    \Zero \Zero \Zero.
+\end{equation}
+The set of all words on $\{\Zero, \Two\}$ is endowed with
 the lexicographic order $\leq$ induced by $\Zero < \Two$.
+The \Def{left rank} of $\Tfr$ as the number $\LBranch(\Tfr)$ of internal
+nodes in the left branch beginning at the root of $\Tfr$. For instance,
+\begin{equation}
+    \begin{tikzpicture}[xscale=.15,yscale=.14,Centering]
+        \node(0)at(0.00,-9.00){};
+        \node(10)at(10.00,-9.00){};
+        \node(12)at(12.00,-9.00){};
+        \node(14)at(14.00,-9.00){};
+        \node(2)at(2.00,-12.00){};
+        \node(4)at(4.00,-12.00){};
+        \node(6)at(6.00,-6.00){};
+        \node(8)at(8.00,-9.00){};
+        \node[NodeST](1)at(1.00,-6.00){\begin{math}\Product\end{math}};
+        \node[NodeST](11)at(11.00,-3.00){\begin{math}\Product\end{math}};
+        \node[NodeST](13)at(13.00,-6.00){\begin{math}\Product\end{math}};
+        \node[NodeST](3)at(3.00,-9.00){\begin{math}\Product\end{math}};
+        \node[NodeST](5)at(5.00,-3.00){\begin{math}\Product\end{math}};
+        \node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
+        \node[NodeST](9)at(9.00,-6.00){\begin{math}\Product\end{math}};
+        \draw[Edge](0)--(1);
+        \draw[Edge](1)--(5);
+        \draw[Edge](10)--(9);
+        \draw[Edge](11)--(7);
+        \draw[Edge](12)--(13);
+        \draw[Edge](13)--(11);
+        \draw[Edge](14)--(13);
+        \draw[Edge](2)--(3);
+        \draw[Edge](3)--(1);
+        \draw[Edge](4)--(3);
+        \draw[Edge](5)--(7);
+        \draw[Edge](6)--(5);
+        \draw[Edge](8)--(9);
+        \draw[Edge](9)--(11);
+        \node(r)at(7.00,2.25){};
+        \draw[Edge](r)--(7);
+    \end{tikzpicture}
+    \xmapsto{\; \LBranch\; } 3.
+\end{equation}
+Equivalently, $\LBranch(\Tfr)$ is the length of the prefix of
+$\PrefixWord(\Tfr)$ containing only the letter $\Two$. A binary tree
+$\Sfr$ is a \Def{subtree} of $\Tfr$ if it possible to stack $\Sfr$ onto
+$\Tfr$ by possibly superimposing leaves of $\Sfr$ onto internal nodes of
+$\Tfr$. More formally, by using the operad $\Mag$, this is equivalent to
+the fact that $\Tfr$ expresses as
+\begin{equation}
+    \Tfr = \Rfr \circ_i
+    \left(\Sfr \circ \left[\Rfr_1, \dots, \Rfr_n\right]\right)
+\end{equation}
+where $\Rfr$ and $\Rfr_1$, \dots, $\Rfr_n$ are binary trees,
+$i \in [|\Rfr|]$, and $n$ is the arity of $\Sfr$. When, on the contrary,
+$\Sfr$ is not a subtree of $\Tfr$, we say that $\Tfr$ \Def{avoids}
+$\Sfr$.
 \medbreak
@@
 \subsection{Rewrite systems and presentations}
+We present here notions about rewrite systems on binary trees. General
+notations and notions appear in~\cite{BN98}.
+\medbreak
 
-\Todo{TO DO}
+A \Def{rewrite rule} is an ordered pair $(\Sfr, \Sfr')$ of binary trees
+such that $|\Sfr| = |\Sfr'|$. A set $S$ of rewrite rules is a binary
+relation on $\Mag$ and it shall be denoted by $\Rew$. We denote by
+$\Sfr \Rew \Sfr'$ the fact that $(\Sfr, \Sfr') \in \Rew$. In the sequel,
+to define a set of rewrite rules $\Rew$, we shall simply list all
+the pairs $\Sfr \Rew \Sfr'$ contained in $\Rew$.
+\medbreak
 
-If $\Rew$ is a rewrite rule on $\Mag$ such that $\Sfr \Rew \Sfr'$
-implies $|\Sfr| = |\Sfr'|$, we denote by $\RewContext$ the
+If $\Rew$ is a set of rewrite rules, we denote by $\RewContext$ the
 \Def{rewrite relation induced} by $\Rew$. Formally we have
-\begin{math}
-    \Tfr\circ_i\left(\Sfr\circ\left[\Rfr_1,\dots,\Rfr_{n}\right]\right)
+\begin{equation}
+    \Tfr \circ_i
+    \left(\Sfr \circ \left[\Rfr_1, \dots, \Rfr_{n}\right]\right)
     \RewContext
-    \Tfr\circ_i\left(\Sfr'\circ\left[\Rfr_1,\dots,\Rfr_{n}\right]\right)
-\end{math},
+    \Tfr \circ_i
+    \left(\Sfr' \circ \left[\Rfr_1, \dots, \Rfr_{n}\right]\right),
+\end{equation}
 if $\Sfr \Rew \Sfr'$ where $n = |\Sfr|$, and $\Tfr$, $\Rfr_1$, \dots,
@@
 by replacing a subtree $\Sfr$ of $\Tfr$ by $\Sfr'$ whenever
-$\Sfr \Rew \Sfr'$. We use here the standard terminology
-(\Def{terminating}, \Def{confluent}, \Def{convergent}, \Def{branching
-pair}, \Def{joinable}, \Def{normal form}, {\em etc.}) about rewrite
-relations and rewrite systems~\cite{BN98}.
+$\Sfr \Rew \Sfr'$. For instance, if $\Rew$ is the set of rewrite rules
+satisfying
+\begin{equation}
+    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
+        \node(0)at(0.00,-3.50){};
+        \node(2)at(2.00,-5.25){};
+        \node(4)at(4.00,-5.25){};
+        \node(6)at(6.00,-1.75){};
+        \node[NodeST](1)at(1.00,-1.75){\begin{math}\Product\end{math}};
+        \node[NodeST](3)at(3.00,-3.50){\begin{math}\Product\end{math}};
+        \node[NodeST](5)at(5.00,0.00){\begin{math}\Product\end{math}};
+        \draw[Edge](0)--(1);
+        \draw[Edge,ultra thick](1)--(5);
+        \draw[Edge](2)--(3);
+        \draw[Edge,ultra thick](3)--(1);
+        \draw[Edge](4)--(3);
+        \draw[Edge](6)--(5);
+        \node(r)at(5.00,1.31){};
+        \draw[Edge](r)--(5);
+    \end{tikzpicture}
+    \enspace \Rew \enspace
+    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
+        \node(0)at(0.00,-1.75){};
+        \node(2)at(2.00,-3.50){};
+        \node(4)at(4.00,-5.25){};
+        \node(6)at(6.00,-5.25){};
+        \node[NodeST](1)at(1.00,0.00){\begin{math}\Product\end{math}};
+        \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
+        \node[NodeST](5)at(5.00,-3.50){\begin{math}\Product\end{math}};
+        \draw[Edge](0)--(1);
+        \draw[Edge](2)--(3);
+        \draw[Edge,ultra thick](3)--(1);
+        \draw[Edge](4)--(5);
+        \draw[Edge,ultra thick](5)--(3);
+        \draw[Edge](6)--(5);
+        \node(r)at(1.00,1.31){};
+        \draw[Edge](r)--(1);
+    \end{tikzpicture}
+\end{equation}
+one has
+\begin{equation}
+    \begin{tikzpicture}[xscale=.19,yscale=.14,Centering]
+        \node(0)at(0.00,-9.00){};
+        \node(10)at(10.00,-12.00){};
+        \node(12)at(12.00,-18.00){};
+        \node(14)at(14.00,-18.00){};
+        \node(16)at(16.00,-15.00){};
+        \node(18)at(18.00,-9.00){};
+        \node(2)at(2.00,-9.00){};
+        \node(20)at(20.00,-9.00){};
+        \node(4)at(4.00,-6.00){};
+        \node(6)at(6.00,-12.00){};
+        \node(8)at(8.00,-12.00){};
+        \node[NodeST](1)at(1.00,-6.00){\begin{math}\Product\end{math}};
+        \node[NodeST](11)at(11.00,-9.00)
+            {\begin{math}\Product\end{math}};
+        \node[NodeST](13)at(13.00,-15.00)
+            {\begin{math}\Product\end{math}};
+        \node[NodeST](15)at(15.00,-12.00)
+            {\begin{math}\Product\end{math}};
+        \node[NodeST](17)at(17.00,-3.00)
+            {\begin{math}\Product\end{math}};
+        \node[NodeST](19)at(19.00,-6.00)
+            {\begin{math}\Product\end{math}};
+        \node[NodeST](3)at(3.00,-3.00){\begin{math}\Product\end{math}};
+        \node[NodeST](5)at(5.00,0.00){\begin{math}\Product\end{math}};
+        \node[NodeST](7)at(7.00,-9.00){\begin{math}\Product\end{math}};
+        \node[NodeST](9)at(9.00,-6.00){\begin{math}\Product\end{math}};
+        \draw[Edge](0)--(1);
+        \draw[Edge](1)--(3);
+        \draw[Edge](10)--(11);
+        \draw[Edge,ultra thick](11)--(9);
+        \draw[Edge](12)--(13);
+        \draw[Edge](13)--(15);
+        \draw[Edge](14)--(13);
+        \draw[Edge](15)--(11);
+        \draw[Edge](16)--(15);
+        \draw[Edge](17)--(5);
+        \draw[Edge](18)--(19);
+        \draw[Edge](19)--(17);
+        \draw[Edge](2)--(1);
+        \draw[Edge](20)--(19);
+        \draw[Edge](3)--(5);
+        \draw[Edge](4)--(3);
+        \draw[Edge](6)--(7);
+        \draw[Edge](7)--(9);
+        \draw[Edge](8)--(7);
+        \draw[Edge,ultra thick](9)--(17);
+        \node(r)at(5.00,2.25){};
+        \draw[Edge](r)--(5);
+    \end{tikzpicture}
+    \enspace \RewContext \enspace
+    \begin{tikzpicture}[xscale=.19,yscale=.14,Centering]
+        \node(0)at(0.00,-9.00){};
+        \node(10)at(10.00,-9.00){};
+        \node(12)at(12.00,-18.00){};
+        \node(14)at(14.00,-18.00){};
+        \node(16)at(16.00,-15.00){};
+        \node(18)at(18.00,-15.00){};
+        \node(2)at(2.00,-9.00){};
+        \node(20)at(20.00,-15.00){};
+        \node(4)at(4.00,-6.00){};
+        \node(6)at(6.00,-9.00){};
+        \node(8)at(8.00,-9.00){};
+        \node[NodeST](1)at(1.00,-6.00){\begin{math}\Product\end{math}};
+        \node[NodeST](11)at(11.00,-6.00)
+            {\begin{math}\Product\end{math}};
+        \node[NodeST](13)at(13.00,-15.00)
+            {\begin{math}\Product\end{math}};
+        \node[NodeST](15)at(15.00,-12.00)
+            {\begin{math}\Product\end{math}};
+        \node[NodeST](17)at(17.00,-9.00)
+            {\begin{math}\Product\end{math}};
+        \node[NodeST](19)at(19.00,-12.00)
+            {\begin{math}\Product\end{math}};
+        \node[NodeST](3)at(3.00,-3.00){\begin{math}\Product\end{math}};
+        \node[NodeST](5)at(5.00,0.00){\begin{math}\Product\end{math}};
+        \node[NodeST](7)at(7.00,-6.00){\begin{math}\Product\end{math}};
+        \node[NodeST](9)at(9.00,-3.00){\begin{math}\Product\end{math}};
+        \draw[Edge](0)--(1);
+        \draw[Edge](1)--(3);
+        \draw[Edge](10)--(11);
+        \draw[Edge,ultra thick](11)--(9);
+        \draw[Edge](12)--(13);
+        \draw[Edge](13)--(15);
+        \draw[Edge](14)--(13);
+        \draw[Edge](15)--(17);
+        \draw[Edge](16)--(15);
+        \draw[Edge,ultra thick](17)--(11);
+        \draw[Edge](18)--(19);
+        \draw[Edge](19)--(17);
+        \draw[Edge](2)--(1);
+        \draw[Edge](20)--(19);
+        \draw[Edge](3)--(5);
+        \draw[Edge](4)--(3);
+        \draw[Edge](6)--(7);
+        \draw[Edge](7)--(9);
+        \draw[Edge](8)--(7);
+        \draw[Edge](9)--(5);
+        \node(r)at(5.00,2.25){};
+        \draw[Edge](r)--(5);
+    \end{tikzpicture}\,.
+\end{equation}
 \medbreak
 
-Given an operad $\Oca \simeq \Mag/_{\Congr}$ where $\Congr$ is an operad
-congruence of $\Mag$, we denote by $[\Tfr]_{\Congr}$ the
-$\Congr$-equivalence class of any $\Tfr \in \Mag$. Besides, we say that
-$\Rew$ is an \Def{orientation} of $\Congr$ if the reflexive, transitive,
-and symmetric closure of $\RewContext$ is $\Congr$. We say that $\Rew$
-is a \Def{convergent orientation} if $\RewContext$ is convergent. When
-$\Rew$ is a convergent orientation of $\Congr$, the set of all normal
-forms of $\RewContext$ is a \Def{Poincaré-Birkhoff-Witt basis} of the
-operad $\Oca$ and its elements are exactly the binary trees avoiding,
-as subtrees, the trees appearing as left members in~$\Rew$.
+Let $\Rew$ be a set of rewrite rules and $\RewContext$ be rewrite
+relation induced by $\Rew$. Since $\RewContext$ is in particular a
+binary relation on $\Mag$, the classical notations about closures apply
+here: we denote by $\RewContextT$ (resp. $\RewContextRT$,
+$\RewContextRST$) the transitive (resp. reflexive and transitive,
+reflexive, symmetric, and transitive) closure of $\RewContext$.
 \medbreak
 
-We shall use the following criterion to prove that a rewrite relation on
-$\Mag$ is terminating.
+When $\Tfr_0$, $\Tfr_1$, \dots, $\Tfr_k$ are binary trees such that
+\begin{equation}
+    \Tfr_0 \RewContext \Tfr_1 \RewContext \cdots \RewContext \Tfr_k,
+\end{equation}
+we say that $\Tfr_0$ is \Def{rewritable} by $\RewContext$ into $\Tfr_k$
+in $k$ \Def{steps}. When there is no infinite chain
+\begin{equation} \label{equ:infinite_chain}
+    \Tfr_0 \RewContext \Tfr_2 \RewContext \Tfr_3 \RewContext \Tfr_4
+    \cdots
+\end{equation}
+we say that $\RewContext$ is terminating. To establish the termination
+of a rewrite relation is terminating, we will use the following
+criterion.
 \medbreak
@@
 \begin{Lemma}\label{lem:prefix_word_termination}
-    Let $\Rew$ be a rewrite rule on $\Mag$. If for any
+    Let $\Rew$ be a set of rewrite rules on $\Mag$. If for any
     $\Tfr, \Tfr' \in \Mag$ such that $\Tfr \Rew \Tfr'$ one has
@@
 \end{Lemma}
+\begin{proof}
+    \Todo{à faire}
+    % 1. Montrer la compatibilité des compo aux mots prefixes
+    % 2. Supposer qu'il existe une chaine infinie de reecritures
+    % 3. Absurde car il n'existe qu'un nombre fini de mots sur {0, 2}.
+\end{proof}
+\medbreak
+
+A \Def{normal form} for $\RewContext$ is a binary tree $\Tfr$ such
+that for all $\Tfr'$, $\Tfr \RewContextRT \Tfr'$ imply $\Tfr' = \Tfr$.
+In other words, a normal form for $\RewContext$ is a tree which is not
+rewritable by $\RewContext$. The set of all the normal forms of
+$\RewContext$ is denoted by $\NormalForms_{\RewContext}$.
+\medbreak
+
+\begin{Lemma} \label{lem:normal_forms_avoiding}
+    Let $\Rew$ be a set of rewrite rules on $\Mag$ and $\RewContext$ be
+    the rewrite relation induced by $\Rew$. Then, if $\RewContext$ is
+    terminating, $\NormalForms_{\RewContext}$ is the set of all the
+    binary trees that avoid all the trees appearing as left members
+    of $\Rew$.
+\end{Lemma}
+\begin{proof}
+    \Todo{à faire}
+\end{proof}
+\medbreak
+
+When for any binary trees $\Tfr$, $\Sfr_1$, and $\Sfr_2$ such that
+$\Tfr \RewContextRT \Sfr_1$ and $\Tfr \RewContextRT \Sfr_2$,
+there exists a binary tree $\Tfr'$ such that
+$\Sfr_1 \RewContextRT \Tfr'$ and $\Sfr_2 \RewContextRT \Tfr'$,
+we say that $\RewContext$ is \Def{convergent}.
+
+We use here the standard terminology
+(\Def{terminating}, \Def{confluent}, \Def{convergent}, \Def{branching
+pair}, \Def{joinable}, \Def{normal form}, {\em etc.}) about rewrite
+relations and rewrite systems~\cite{BN98}.
 \medbreak
@@
 \medbreak
+
+Given an operad $\Oca \simeq \Mag/_{\Congr}$ where $\Congr$ is an operad
+congruence of $\Mag$, we denote by $[\Tfr]_{\Congr}$ the
+$\Congr$-equivalence class of any $\Tfr \in \Mag$. Besides, we say that
+$\Rew$ is an \Def{orientation} of $\Congr$ if the reflexive, transitive,
+and symmetric closure of $\RewContext$ is $\Congr$. We say that $\Rew$
+is a \Def{convergent orientation} if $\RewContext$ is convergent. When
+$\Rew$ is a convergent orientation of $\Congr$, the set of all normal
+forms of $\RewContext$ is a \Def{Poincaré-Birkhoff-Witt basis} of the
+operad $\Oca$ and its elements are exactly the binary trees avoiding,
+as subtrees, the trees appearing as left members in~$\Rew$.
+\medbreak

### 2018-07-06 Operads_rewrite.tex
Partie 1 suite (pas encore relue)

@@
 \subsection{Nonsymmetric operads}
-A \Def{nonsymmetric operad in the category of sets}, or a
-\Def{nonsymmetric operad} for short, is a graded set
+A \Def{nonsymmetric operad in the category of sets} (or a
+\Def{nonsymmetric operad} for short) is a graded set
 \begin{equation}
@@
 The set of all words on $\{\Zero, \Two\}$ is endowed with
-the lexicographic order $\leq$ induced by $\Zero < \Two$.
+the lexicographic order $\leq$ induced by $\Zero < \Two$. By
+extension, this defines a total order on each set $\Mag(n)$. Indeed,
+we set $\Tfr \leq \Tfr'$ if
+$\Tfr$ and $\Tfr'$ have the same arity and
+$\PrefixWord(\Tfr) \leq \PrefixWord(\Tfr')$.
 The \Def{left rank} of $\Tfr$ as the number $\LBranch(\Tfr)$ of internal
@@
 to define a set of rewrite rules $\Rew$, we shall simply list all
-the pairs $\Sfr \Rew \Sfr'$ contained in $\Rew$.
+the pairs $\Sfr \Rew \Sfr'$ contained in $\Rew$. The \Def{degree}
+$\Deg(\Rew)$ of $\Rew$ is the maximal degree of the binary trees in
+relation through $\Rew$. Note that $\Deg(\Rew)$ can be not defined when
+$\Rew$ is infinite.
 \medbreak
@@
 When for any binary trees $\Tfr$, $\Sfr_1$, and $\Sfr_2$ such that
-$\Tfr \RewContextRT \Sfr_1$ and $\Tfr \RewContextRT \Sfr_2$,
-there exists a binary tree $\Tfr'$ such that
-$\Sfr_1 \RewContextRT \Tfr'$ and $\Sfr_2 \RewContextRT \Tfr'$,
-we say that $\RewContext$ is \Def{convergent}.
-
-We use here the standard terminology
-(\Def{terminating}, \Def{confluent}, \Def{convergent}, \Def{branching
-pair}, \Def{joinable}, \Def{normal form}, {\em etc.}) about rewrite
-relations and rewrite systems~\cite{BN98}.
+$\Tfr \RewContextRT \Sfr_1$ and $\Tfr \RewContextRT \Sfr_2$, there
+exists a binary tree $\Tfr'$ such that
+$\Sfr_1 \RewContextRT \Tfr'$ and $\Sfr_2 \RewContextRT \Tfr'$, we say
+that $\RewContext$ is \Def{confluent}. Besides, a tree $\Tfr$ is a
+\Def{branching tree} for $\RewContext$ if there exists two different
+trees $\Sfr_1$ and $\Sfr_2$ satisfying $\Tfr \RewContext \Sfr_1$ and
+$\Tfr \RewContext \Sfr_2$. In this case, the pair $\{\Sfr_1, \Sfr_2\}$
+is a \Def{branching pair} for $\Tfr$. Moreover, the branching pair
+$\{\Sfr_1, \Sfr_2\}$ is \Def{joinable} if there exists a binary tree
+$\Tfr'$ such that $\Sfr_1 \RewContextRT \Tfr'$ and
+$\Sfr_2 \RewContextRT \Tfr'$. The diamond lemma~\cite{New42} is based
+upon the inspection of the branching pairs of a terminating rewrite
+relation $\RewContext$ in order to prove its confluence.
 \medbreak
 
-Moreover, we shall use the following result appearing in~\cite{Gir16}
-specialized on rewrite relation on $\Mag$ to prove that a terminating
-rewrite relation is convergent.
+\begin{Lemma} \label{lem:diamond_lemma}
+    Let $\Rew$ be a set of rewrite rules on $\Mag$ and $\RewContext$ be
+    the rewrite relation induced by $\Rew$. Then, it $\RewContext$ is
+    terminating and all its branching pairs are joinable, $\RewContext$
+    is convergent.
+\end{Lemma}
+\medbreak
+
+When $\RewContext$ is terminating and confluent, $\RewContext$ is
+\Def{convergent}. We shall use the following result appearing
+in~\cite{Gir16} specialized on rewrite relations on $\Mag$ to prove that
+a terminating rewrite relation is convergent.
 \medbreak
@@
 \begin{Lemma} \label{lem:degree_confluence}
-    Let $\Rew$ be a rewrite rule on $\Mag$ wherein all trees $\Tfr$ and
-    $\Tfr'$ such that $\Tfr \Rew \Tfr'$ have degrees at most $\ell$.
-    Then, if the rewrite relation $\RewContext$ induced by $\Rew$ is
-    terminating and all its branching pairs of degrees at most
-    $2\ell - 1$ are joinable, $\RewContext$ is convergent.
+    Let $\Rew$ be a set of rewrite rules on $\Mag$ having a degree
+    $\Deg(\Rew)$. Then, if the rewrite relation $\RewContext$ induced by
+    $\Rew$ is terminating and all its branching pairs made of trees of
+    degrees at most $2 \, \Deg(\Rew) - 1$ are joinable, $\RewContext$ is
+    convergent.
 \end{Lemma}
+\begin{proof}
+    \Todo{à faire}
+\end{proof}
 \medbreak
 
-Given an operad $\Oca \simeq \Mag/_{\Congr}$ where $\Congr$ is an operad
-congruence of $\Mag$, we denote by $[\Tfr]_{\Congr}$ the
-$\Congr$-equivalence class of any $\Tfr \in \Mag$. Besides, we say that
-$\Rew$ is an \Def{orientation} of $\Congr$ if the reflexive, transitive,
-and symmetric closure of $\RewContext$ is $\Congr$. We say that $\Rew$
-is a \Def{convergent orientation} if $\RewContext$ is convergent. When
-$\Rew$ is a convergent orientation of $\Congr$, the set of all normal
-forms of $\RewContext$ is a \Def{Poincaré-Birkhoff-Witt basis} of the
-operad $\Oca$ and its elements are exactly the binary trees avoiding,
-as subtrees, the trees appearing as left members in~$\Rew$.
+Let us now go back on operads. Let $\Congr$ be an operad congruence of
+$\Mag$. If $\Tfr$ is a binary tree, we denote by $[\Tfr]_{\Congr}$ the
+$\Congr$-equivalence class of $\Tfr$. By definition, $[\Tfr]_{\Congr}$
+is an element of the quotient operad
+\begin{equation}
+    \Oca := \Mag/_{\Congr}.
+\end{equation}
+A set of rewrite rules $\Rew$ is an \Def{orientation} of $\Congr$ if
+$\RewContextRST$ and $\Congr$ are equal as binary relations, where
+$\RewContext$ is the rewrite relation induced by $\Rew$. Moreover,
+$\Rew$ is a \Def{convergent} (resp. \Def{terminating}, \Def{confluent})
+orientation of $\Congr$ if $\RewContext$ is convergent (resp.
+terminating, confluent). When $\Rew$ is a convergent orientation of
+$\Congr$, the set $\NormalForms_{\RewContext}$ of all normal forms of
+$\RewContext$ is called \Def{Poincaré-Birkhoff-Witt basis} (or a
+\Def{PBW basis} for short) of the quotient operad $\Oca$
+(see~\cite{Hof10,DK10}). This forms a one-to-one correspondence between
+the sets $\NormalForms_{\RewContext}(n)$ and $\Oca(n)$, $n \geq 1$. In
+other words, a PBW basis offers a way to assign with each
+$\Congr$-equivalence class $[\Tfr]_{\Congr}$ a representative
+\begin{math}
+    \Tfr' \in [\Tfr]_{\Congr} \cap \NormalForms_{\RewContext}.
+\end{math}
 \medbreak
+
+When $\Rew$ is a terminating but not convergent orientation of $\Congr$,
+we shall use a variant of the \Def{Buchberger semi-algorithm} for
+operads~\cite[Section 3.7]{DK10} to compute a set of rewrite rules
+$\Rew'$ such that, as binary relations $\Rew \subseteq \Rew'$, and
+$\Rew'$ is a convergent orientation of $\Congr$. This semi-algorithm
+takes as input a finite set of rewrite rules $\Rew$ and outputs the set
+of rewrite rules $\Rew'$ satisfying the property stated above. Here is,
+step by step, a description of its execution:
+\begin{enumerate}[label={(\it\arabic*)}]
+    \item Set $\Rew' := \Rew$.
+    \item \label{item:loop_start_buchberger}
+    If there is no branching pairs for $\RewContext'$ of trees of
+    degrees $k$ for all $0 \leq k \leq 2 \, \Deg(\Rew') - 1$, the
+    execution stops and the output is $\Rew'$.
+    \item Otherwise, let $\Tfr$ be the branching tree for $\RewContext'$
+    with the minimal degree and the minimal prefix word.
+    \item Let $\{\Sfr_1, \Sfr_2\}$ be the branching pair for $\Tfr$ such
+    that $\Sfr_1$ and $\Sfr_2$ have the minimal prefix words.
+    \item Add to $\Rew'$ the rewrite rule
+    \begin{math}
+        \max_\leq\{\Sfr_1, \Sfr_2\}
+        \Rew'
+        \min_\leq\{\Sfr_1, \Sfr_2\}.
+    \end{math}
+    \item Go to Step~\ref{item:loop_start_buchberger}.
+\end{enumerate}
+The set of rewrite rules $\Rew'$ outputted by this semi-algorithm is the
+\Def{completion} of $\Rew$. Notice that, for certain inputs $\Rew$, this
+semi-algorithm never stops. Notice also that the computed completion
+depend on the total order $\leq$ on the binary trees of a same arity.
+\medbreak

### 2018-07-06 Operads_rewrite.tex
Partie 1 : relecture

@@
 provide a definition for the magmatic operad and introduce tools to
-handle with some of its quotients involving rewrite systems on syntax
+handle with some of its quotients involving rewrite systems on binary
 trees.
@@
 $\Unit \in \Oca(1)$, the \Def{unit} of $\Oca$. This data has to satisfy,
-for any $x, y, z \in \Oca$, the three relations
+for any $x \in \Oca(n)$, $y \in \Oca(m)$, and $z \in \Oca$, the three
+relations
 \begin{subequations}
@@
     \qquad
-    1 \leq i \leq |x|, 1 \leq j \leq |y|,
+    1 \leq i \leq n, 1 \leq j \leq m,
 \end{equation}
 \begin{equation} \label{equ:operad_axiom_2}
-    (x \circ_i y) \circ_{j + |y| - 1} z = (x \circ_j z) \circ_i y,
+    (x \circ_i y) \circ_{j + m - 1} z = (x \circ_j z) \circ_i y,
     \qquad
-    1 \leq i < j \leq |x|,
+    1 \leq i < j \leq n,
 \end{equation}
@@
     \Unit \circ_1 x = x = x \circ_i \Unit,
-    \qquad 1 \leq i \leq |x|.
+    \qquad 1 \leq i \leq n.
 \end{equation}
@@
 \begin{equation}
-    \circ : \Oca(n) \times \Oca(m_1) \times \dots \times \Oca(m_n)
-    \to \Oca(m_1 + \dots + m_n)
+    \circ : \Oca(n) \times
+    \Oca\left(m_1\right) \times \dots \times \Oca\left(m_n\right)
+    \to \Oca\left(m_1 + \dots + m_n\right)
 \end{equation}
@@
 \begin{equation}
-    x \circ [y_1, \dots, y_n] :=
-    (\dots ((x \circ_n y_n) \circ_{n - 1} y_{n - 1}) \dots) \circ_1 y_1.
+    x \circ \left[y_1, \dots, y_n\right] :=
+    \left(\dots \left(\left(x \circ_n y_n\right)
+    \circ_{n - 1} y_{n - 1}\right) \dots\right) \circ_1 y_1.
 \end{equation}
 If $\Oca_1$ and $\Oca_2$ are two operads, a map
-$\phi : \Oca_1 \to \Oca_2$ is an \Def{operad morphism} is it respects
+$\phi : \Oca_1 \to \Oca_2$ is an \Def{operad morphism} if it respects
 the arities, sends the unit of $\Oca_1$ to the unit of $\Oca_2$, and
@@
 \begin{equation}
-    \HilbertSeries_\Oca(t) := \sum_{n \geq 1} \# \Oca(n) t^n.
+    \HilbertSeries_\Oca(t) := \sum_{n \geq 1} \# \Oca(n) \; t^n.
 \end{equation}
@@
 
-The \Def{magmatic operad} $\Mag$ is the graded set of all binary trees
-where $\Mag(n)$, $n \geq 1$, is the set of all binary trees of arity
-$n$. The partial composition maps of $\Mag$ are grafting of trees: given
-two binary trees $\Tfr$ and $\Sfr$, $\Tfr \circ_i \Sfr$ is the binary
-tree obtained by grafting the root of $\Sfr$ onto the $i$th leaf
+The \Def{magmatic operad} $\Mag$ is the graded set of all the binary
+trees where $\Mag(n)$, $n \geq 1$, is the set of all the binary trees of
+arity $n$. The partial composition maps of $\Mag$ are grafting of trees:
+given two binary trees $\Tfr$ and $\Sfr$, $\Tfr \circ_i \Sfr$ is the
+binary tree obtained by grafting the root of $\Sfr$ onto the $i$th leaf
 (numbered from left to right) of $\Tfr$. For instance,
@@
 \begin{math}
-    \Tfr \circ [\Sfr_1, \dots, \Sfr_n]
+    \Tfr \circ \left[\Sfr_1, \dots, \Sfr_n\right]
 \end{math}
 is the binary tree obtained by grafting simultaneously the roots of all
-$\Sfr_i$ of the $i$th leaves of $\Tfr$. The number of binary of arity
-$n \geq 1$ is the $n$th Catalan number $\Catalan(n)$ and hence, the
-Hilbert series of $\Mag$ is
+the $\Sfr_i$ onto the $i$th leaves of $\Tfr$. The unit of $\Mag$ is the
+leaf. The number of binary trees of arity $n \geq 1$ is the $n$th
+Catalan number $\Catalan(n)$ and hence, the Hilbert series of $\Mag$ is
 \begin{equation}
@@
 
-The operad $\Mag$ is the free operad generated by one binary element. It
-satisfies the following universality property. Let
+The operad $\Mag$ can be seen as the free operad generated by one binary
+element. It satisfies the following universality property. Let
 \begin{math}
@@
 
-We now provide some useful tools about binary trees.
-Given a binary tree $\Tfr$, we denote by $ \PrefixWord(\Tfr)$ the
-\Def{prefix word} of $\Tfr$, that is the word on $\{\Zero, \Two\}$
-obtained by a left to right depth-first traversal of $\Tfr$ and by
-writing $\Zero$ (resp. $\Two$) when a leaf (resp. an internal node) is
-encountered. For instance,
+We now provide some useful tools about binary trees. Given a binary tree
+$\Tfr$, we denote by $ \PrefixWord(\Tfr)$ the \Def{prefix word} of
+$\Tfr$, that is the word on $\{\Zero, \Two\}$ obtained by a left to
+right depth-first traversal of $\Tfr$ and by writing $\Zero$ (resp.
+$\Two$) when a leaf (resp. an internal node) is encountered. For
+instance,
 \begin{equation}
@@
 \end{equation}
-The set of all words on $\{\Zero, \Two\}$ is endowed with
-the lexicographic order $\leq$ induced by $\Zero < \Two$. By
-extension, this defines a total order on each set $\Mag(n)$. Indeed,
-we set $\Tfr \leq \Tfr'$ if
-$\Tfr$ and $\Tfr'$ have the same arity and
-$\PrefixWord(\Tfr) \leq \PrefixWord(\Tfr')$.
-The \Def{left rank} of $\Tfr$ as the number $\LBranch(\Tfr)$ of internal
+The set of all the words on $\{\Zero, \Two\}$ is endowed with the
+lexicographic order $\leq$ induced by $\Zero < \Two$. By extension, this
+defines a total order on each set $\Mag(n)$, $n \geq 1$. Indeed, we set
+$\Tfr \leq \Tfr'$ if $\Tfr$ and $\Tfr'$ have the same arity and
+$\PrefixWord(\Tfr) \leq \PrefixWord(\Tfr')$. Let also the
+\Def{left rank} of $\Tfr$ as the number $\LBranch(\Tfr)$ of internal
 nodes in the left branch beginning at the root of $\Tfr$. For instance,
@@
 $\Tfr$ by possibly superimposing leaves of $\Sfr$ onto internal nodes of
-$\Tfr$. More formally, by using the operad $\Mag$, this is equivalent to
-the fact that $\Tfr$ expresses as
+$\Tfr$. More formally, by using the operad $\Mag$ and its composition
+maps, this is equivalent to the fact that $\Tfr$ expresses as
 \begin{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Rewrite systems and presentations}
+\subsection{Rewrite systems on binary trees}
 We present here notions about rewrite systems on binary trees. General
@@
 $\Sfr \Rew \Sfr'$ the fact that $(\Sfr, \Sfr') \in \Rew$. In the sequel,
-to define a set of rewrite rules $\Rew$, we shall simply list all
-the pairs $\Sfr \Rew \Sfr'$ contained in $\Rew$. The \Def{degree}
+to define a set of rewrite rules $\Rew$, we shall simply list all the
+pairs $\Sfr \Rew \Sfr'$ contained in $\Rew$. The \Def{degree}
 $\Deg(\Rew)$ of $\Rew$ is the maximal degree of the binary trees in
@@
 \begin{equation} \label{equ:infinite_chain}
-    \Tfr_0 \RewContext \Tfr_2 \RewContext \Tfr_3 \RewContext \Tfr_4
-    \cdots
+    \Tfr_0 \RewContext \Tfr_1 \RewContext \Tfr_2 \RewContext \cdots
 \end{equation}
 we say that $\RewContext$ is terminating. To establish the termination
-of a rewrite relation is terminating, we will use the following
-criterion.
+of a rewrite relation, we will use the following criterion.
 \medbreak
@@
     $\Tfr, \Tfr' \in \Mag$ such that $\Tfr \Rew \Tfr'$ one has
-    $\PrefixWord(\Tfr) > \PrefixWord(\Tfr')$, then the rewrite relation
-    induced by $\Rew$ is terminating.
+    $\Tfr > \Tfr'$, then the rewrite relation induced by $\Rew$ is
+    terminating.
 \end{Lemma}
@@
 A \Def{normal form} for $\RewContext$ is a binary tree $\Tfr$ such
-that for all $\Tfr'$, $\Tfr \RewContextRT \Tfr'$ imply $\Tfr' = \Tfr$.
-In other words, a normal form for $\RewContext$ is a tree which is not
-rewritable by $\RewContext$. The set of all the normal forms of
-$\RewContext$ is denoted by $\NormalForms_{\RewContext}$.
+that for all binary trees $\Tfr'$, $\Tfr \RewContextRT \Tfr'$ imply
+$\Tfr' = \Tfr$. In other words, a normal form for $\RewContext$ is a
+tree which is not rewritable by $\RewContext$. The set of all the normal
+forms of $\RewContext$ is denoted by $\NormalForms_{\RewContext}$. The
+trees of $\NormalForms_{\RewContext}$ admit the following description,
+useful for enumerative prospects.
 \medbreak
@@
 $\Tfr \RewContextRT \Sfr_1$ and $\Tfr \RewContextRT \Sfr_2$, there
-exists a binary tree $\Tfr'$ such that
-$\Sfr_1 \RewContextRT \Tfr'$ and $\Sfr_2 \RewContextRT \Tfr'$, we say
-that $\RewContext$ is \Def{confluent}. Besides, a tree $\Tfr$ is a
-\Def{branching tree} for $\RewContext$ if there exists two different
-trees $\Sfr_1$ and $\Sfr_2$ satisfying $\Tfr \RewContext \Sfr_1$ and
-$\Tfr \RewContext \Sfr_2$. In this case, the pair $\{\Sfr_1, \Sfr_2\}$
-is a \Def{branching pair} for $\Tfr$. Moreover, the branching pair
-$\{\Sfr_1, \Sfr_2\}$ is \Def{joinable} if there exists a binary tree
-$\Tfr'$ such that $\Sfr_1 \RewContextRT \Tfr'$ and
-$\Sfr_2 \RewContextRT \Tfr'$. The diamond lemma~\cite{New42} is based
-upon the inspection of the branching pairs of a terminating rewrite
-relation $\RewContext$ in order to prove its confluence.
+exists a binary tree $\Tfr'$ such that $\Sfr_1 \RewContextRT \Tfr'$ and
+$\Sfr_2 \RewContextRT \Tfr'$, we say that $\RewContext$ is
+\Def{confluent}. Besides, a tree $\Tfr$ is a \Def{branching tree} for
+$\RewContext$ if there exists two different trees $\Sfr_1$ and $\Sfr_2$
+satisfying $\Tfr \RewContext \Sfr_1$ and $\Tfr \RewContext \Sfr_2$. In
+this case, the pair $\{\Sfr_1, \Sfr_2\}$ is a \Def{branching pair} for
+$\Tfr$. Moreover, the branching pair $\{\Sfr_1, \Sfr_2\}$ is
+\Def{joinable} if there exists a binary tree $\Tfr'$ such that
+$\Sfr_1 \RewContextRT \Tfr'$ and $\Sfr_2 \RewContextRT \Tfr'$. The
+diamond lemma~\cite{New42} is based upon the inspection of the branching
+pairs of a terminating rewrite relation $\RewContext$ in order to prove
+its confluence.
 \medbreak
@@
     Let $\Rew$ be a set of rewrite rules on $\Mag$ and $\RewContext$ be
-    the rewrite relation induced by $\Rew$. Then, it $\RewContext$ is
+    the rewrite relation induced by $\Rew$. Then, if $\RewContext$ is
     terminating and all its branching pairs are joinable, $\RewContext$
@@
 
-When $\RewContext$ is terminating and confluent, $\RewContext$ is
+When $\RewContext$ is terminating and confluent, $\RewContext$ is said
 \Def{convergent}. We shall use the following result appearing
@@
 $\Congr$, the set $\NormalForms_{\RewContext}$ of all normal forms of
-$\RewContext$ is called \Def{Poincaré-Birkhoff-Witt basis} (or a
+$\RewContext$ is called a \Def{Poincaré-Birkhoff-Witt basis} (or a
 \Def{PBW basis} for short) of the quotient operad $\Oca$
@@
     \begin{math}
-        \max_\leq\{\Sfr_1, \Sfr_2\}
+        \max_\leq \left\{\Sfr_1, \Sfr_2\right\}
         \Rew'
-        \min_\leq\{\Sfr_1, \Sfr_2\}.
+        \min_\leq \left\{\Sfr_1, \Sfr_2\right\}.
     \end{math}
@@
 The set of rewrite rules $\Rew'$ outputted by this semi-algorithm is the
-\Def{completion} of $\Rew$. Notice that, for certain inputs $\Rew$, this
-semi-algorithm never stops. Notice also that the computed completion
-depend on the total order $\leq$ on the binary trees of a same arity.
+\Def{completion} of $\Rew$. By Lemma~\ref{lem:degree_confluence},
+$\RewContext'$ is confluent. Notice that, for certain inputs $\Rew$,
+this semi-algorithm never stops. Notice also that the computed
+completion depend on the total order $\leq$ on the binary trees of a
+same arity.
 \medbreak

### 2018-07-09 CAs_operads.tex
Partie 1 chantier (suite)
Remarques de Cyrille sur partie 1

@@
 division relation, $\gcd$ denotes the greatest common divisor, and
-$\lcm$ the least common multiple operators, respectively. In order to
-obtain this relationship, we introduce the notion of \Def{left rank} for
-any binary tree $\Tfr$ as the number $\LBranch(\Tfr)$ of internal nodes
-in the left branch beginning at the root of $\Tfr$.
-For instance,
-\begin{equation}
-    \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
-        \node(0)at(0.00,-4.50){};
-        \node(2)at(2.00,-4.50){};
-        \node(4)at(4.00,-4.50){};
-        \node(6)at(6.00,-6.75){};
-        \node(8)at(8.00,-6.75){};
-        \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
-        \node[NodeST](5)at(5.00,-2.25){\begin{math}\Product\end{math}};
-        \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
-        \draw[Edge](0)--(1);
-        \draw[Edge](1)--(3);
-        \draw[Edge](2)--(1);
-        \draw[Edge](4)--(5);
-        \draw[Edge](5)--(3);
-        \draw[Edge](6)--(7);
-        \draw[Edge](7)--(5);
-        \draw[Edge](8)--(7);
-        \node(r)at(3.00,1.74){};
-        \draw[Edge](r)--(3);
-    \end{tikzpicture}
-    \xmapsto{\; \LBranch\; } 2
-    \qquad \mbox{and} \qquad
-    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
-        \node(0)at(0.00,-3.60){};
-        \node(2)at(2.00,-5.40){};
-        \node(4)at(4.00,-7.20){};
-        \node(6)at(6.00,-7.20){};
-        \node(8)at(8.00,-1.80){};
-        \node[NodeST](1)at(1.00,-1.80){\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,-3.60){\begin{math}\Product\end{math}};
-        \node[NodeST](5)at(5.00,-5.40){\begin{math}\Product\end{math}};
-        \node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
-        \draw[Edge](0)--(1);
-        \draw[Edge](1)--(7);
-        \draw[Edge](2)--(3);
-        \draw[Edge](3)--(1);
-        \draw[Edge](4)--(5);
-        \draw[Edge](5)--(3);
-        \draw[Edge](6)--(5);
-        \draw[Edge](8)--(7);
-        \node(r)at(7.00,1.5){};
-        \draw[Edge](r)--(7);
-    \end{tikzpicture}
-    \xmapsto{\; \LBranch\; } 2.
-\end{equation}
-The left rank of $\Tfr$ is represented as follows: \Todo{???}
+$\lcm$ the least common multiple operators, respectively.
 \medbreak
@@
     \begin{equation}
-        \LBranch(\Tfr) \mod \gamma - 1
+        \LRank(\Tfr) \mod \gamma - 1
         \enspace = \enspace
-        \LBranch(\Tfr') \mod \gamma - 1.
+        \LRank(\Tfr') \mod \gamma - 1.
     \end{equation}
@@
     First, we show that $\Tfr \Rew \Tfr'$ implies that
-    $\LBranch\left(\Tfr'\right) - \LBranch\left(\Tfr\right)$ is
+    $\LRank\left(\Tfr'\right) - \LRank\left(\Tfr\right)$ is
     divisible by $\gamma - 1$. \Todo{à faire.}
@@
     \begin{math}
-        \LBranch\left(\Tfr_{i + 1}\right)
+        \LRank\left(\Tfr_{i + 1}\right)
         -
-        \LBranch\left(\Tfr_i\right)
+        \LRank\left(\Tfr_i\right)
     \end{math}
     is divisible by $\gamma - 1$ from the first part of the proof, so
-    that $\LBranch\left(\Tfr'\right) - \LBranch\left(\Tfr\right)$ is
+    that $\LRank\left(\Tfr'\right) - \LRank\left(\Tfr\right)$ is
     divisible by $\gamma-1$.
@@
     \begin{math}
-        \LBranch\left(\Tfr_{i + 1}\right)
+        \LRank\left(\Tfr_{i + 1}\right)
         -
-        \LBranch\left(\Tfr_i\right)
+        \LRank\left(\Tfr_i\right)
     \end{math}
     is divisible by $\gamma - 1$, so that
-    $\LBranch\left(\Tfr'\right) - \LBranch\left(\Tfr\right)$ is
+    $\LRank\left(\Tfr'\right) - \LRank\left(\Tfr\right)$ is
     divisible by $\gamma - 1$.
@@
     \begin{math}
-        \LBranch\left(\Tfr'\right) - \LBranch\left(\Tfr\right)
+        \LRank\left(\Tfr'\right) - \LRank\left(\Tfr\right)
     \end{math}
@@
     \begin{math}
-        \LBranch\left(\LComb{\gamma'}\right)
-        - \LBranch\left(\RComb{\gamma'}\right)
+        \LRank\left(\LComb{\gamma'}\right)
+        - \LRank\left(\RComb{\gamma'}\right)
         = \gamma' - 1

### 2018-07-09 Operads_rewrite.tex
Remarques de Cyrille sur partie 1

@@
 $\HilbertSeries_\Oca(t)$ of $\Oca$ is the series defined by
-\begin{equation}
+\begin{equation} \label{equ:hilbert_series}
     \HilbertSeries_\Oca(t) := \sum_{n \geq 1} \# \Oca(n) \; t^n.
 \end{equation}
+\medbreak
+
+We have provided here definitions about operads in the category of sets.
+Nevertheless, operads can be defined in the category of $\K$-vector
+spaces, where $\K$ denotes in all this text a field of characteristic
+zero. We call them \Def{linear operads}. All the above definitions
+extend for linear operads, mainly by substituting Cartesian products
+$\times$ of sets with tensor products $\otimes$ of spaces, maps with
+linear maps, operad congruences with operad ideals, and cardinalities
+of sets with space dimensions (for instance
+in~\eqref{equ:hilbert_series}). Besides, when $\Oca$ is a linear operad
+admitting a basis $B$ such that its unit $\Unit$ belongs to $B$ and all
+partial composition maps are internal in $B$, $\Oca$ can be studied as a
+set-theoretic operad.
 \medbreak
@@
 $\PrefixWord(\Tfr) \leq \PrefixWord(\Tfr')$. Let also the
-\Def{left rank} of $\Tfr$ as the number $\LBranch(\Tfr)$ of internal
+\Def{left rank} of $\Tfr$ as the number $\LRank(\Tfr)$ of internal
 nodes in the left branch beginning at the root of $\Tfr$. For instance,
@@
     \end{tikzpicture}
-    \xmapsto{\; \LBranch\; } 3.
+    \xmapsto{\; \LRank\; } 3.
 \end{equation}
-Equivalently, $\LBranch(\Tfr)$ is the length of the prefix of
+Equivalently, $\LRank(\Tfr)$ is the length of the prefix of
 $\PrefixWord(\Tfr)$ containing only the letter $\Two$. A binary tree
@@
 $\Sfr \Rew \Sfr'$. For instance, if $\Rew$ is the set of rewrite rules
-satisfying
-\begin{equation}
+containing the single rewrite rule
+\begin{equation} \label{equ:example_rewrite_rule}
     \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
@@
         \draw[Edge](0)--(1);
-        \draw[Edge,ultra thick](1)--(5);
+        \draw[EdgeColorF](1)--(5);
         \draw[Edge](2)--(3);
-        \draw[Edge,ultra thick](3)--(1);
+        \draw[EdgeColorF](3)--(1);
         \draw[Edge](4)--(3);
@@
         \draw[Edge](2)--(3);
-        \draw[Edge,ultra thick](3)--(1);
+        \draw[EdgeColorF](3)--(1);
         \draw[Edge](4)--(5);
-        \draw[Edge,ultra thick](5)--(3);
+        \draw[EdgeColorF](5)--(3);
         \draw[Edge](6)--(5);
@@
         \draw[Edge](r)--(1);
-    \end{tikzpicture}
+    \end{tikzpicture}\,,
 \end{equation}
 one has
-\begin{equation}
+\begin{equation} \label{equ:example_rewrite_step}
     \begin{tikzpicture}[xscale=.19,yscale=.14,Centering]
@@
         \draw[Edge](10)--(11);
-        \draw[Edge,ultra thick](11)--(9);
+        \draw[EdgeColorF](11)--(9);
         \draw[Edge](12)--(13);
@@
         \draw[Edge](8)--(7);
-        \draw[Edge,ultra thick](9)--(17);
+        \draw[EdgeColorF](9)--(17);
         \node(r)at(5.00,2.25){};
@@
         \draw[Edge](16)--(15);
-        \draw[Edge,ultra thick](17)--(11);
+        \draw[EdgeColorF](17)--(11);
         \draw[Edge](18)--(19);
@@
 \end{equation}
+The right member of~\eqref{equ:example_rewrite_step} is obtained by
+replacing, in the tree of left member
+of~\eqref{equ:example_rewrite_step}, a subtree equal to the left
+member of~\eqref{equ:example_rewrite_rule} starting at the right child
+of its root by the right member of~\eqref{equ:example_rewrite_rule}.
 \medbreak

### 2018-07-09 Magmatic_operads.tex
Modification algo de Buchberger

@@
 \section{Magmatic operads}
+\label{sec:Magmatic_operads}
 
@@
 
-Given an operad $\Oca$, we denote by $H_{\Oca}$ the \Def{Hiblert serie} of $\Oca$, that is
-\begin{equation} \label{equ:definition_of_Hilbert_series}
-  H_{\Oca}(t)=\sum_{n\in\N}\dim{\left(\Oca(n)\right)}t^n.
-\end{equation}
-
 In Theorem~\ref{thm:Grassmann_formula_for__Hilbert_series_of_QMag}, we show the Grassman formula for the lattice $\left(\QMag,\preceq,\wedge,\vee\right)$. For that, we need the following lemma:
@@
   \begin{equation} \label{equ:lattice_structure_and_Hiblert_series}
-    H_{\Oca_1\wedge\Oca_2}(t)+H_{\Oca_1\vee\Oca_2}(t)=H_{\Oca_1}(t)+H_{\Oca_2}(t).
+    \HilbertSeries_{\Oca_1\wedge\Oca_2}(t)+\HilbertSeries_{\Oca_1\vee\Oca_2}(t)=\HilbertSeries_{\Oca_1}(t)+\HilbertSeries_{\Oca_2}(t).
     \end{equation}
@@
   \[\begin{split}
-  H_{\Oca_1\wedge\Oca_2}(t)+H_{\Oca_1\vee\Oca_2}(t)&=\sum_{n\in\N}\dim{\left(\Oca_1\wedge\Oca_2(n)\right)}t^n+\sum_{n\in\N}\dim{\left(\Oca_1\vee\Oca_2(n)\right)}t^n\\
+  \HilbertSeries_{\Oca_1\wedge\Oca_2}(t)+\HilbertSeries_{\Oca_1\vee\Oca_2}(t)&=\sum_{n\in\N}\dim{\left(\Oca_1\wedge\Oca_2(n)\right)}t^n+\sum_{n\in\N}\dim{\left(\Oca_1\vee\Oca_2(n)\right)}t^n\\
   &=\sum_{n\in\N}\Big(\dim{\left(\Oca_1\wedge\Oca_2(n)\right)}+\dim{\left(\Oca_1\vee\Oca_2(n)\right)}\Big)t^n\\
@@
   &=\sum_{n\in\N}\dim{\left(\Oca_1(n)\right)}t^n+\sum_{n\in\N}\dim{\left(\Oca_2(n)\right)}t^n\\
-  &=H_{\Oca_1}(t)+H_{\Oca_2}(t).
+  &=\HilbertSeries_{\Oca_1}(t)+\HilbertSeries_{\Oca_2}(t).
   \end{split}\]

### 2018-07-09 Operads_rewrite.tex
Modification algo de Buchberger

@@
 spaces, where $\K$ denotes in all this text a field of characteristic
-zero. We call them \Def{linear operads}. All the above definitions
-extend for linear operads, mainly by substituting Cartesian products
-$\times$ of sets with tensor products $\otimes$ of spaces, maps with
-linear maps, operad congruences with operad ideals, and cardinalities
-of sets with space dimensions (for instance
-in~\eqref{equ:hilbert_series}). Besides, when $\Oca$ is a linear operad
-admitting a basis $B$ such that its unit $\Unit$ belongs to $B$ and all
-partial composition maps are internal in $B$, $\Oca$ can be studied as a
-set-theoretic operad.
+zero. We call them \Def{linear operads} and we use them in
+Section~\ref{sec:Magmatic_operads}. All the above definitions extend for
+linear operads, mainly by substituting Cartesian products $\times$ of
+sets with tensor products $\otimes$ of spaces, maps with maps, operad
+congruences with operad ideals, and cardinalities of sets with space
+dimensions (for instance in~\eqref{equ:hilbert_series}). Besides, when
+$\Oca$ is a linear operad admitting a basis $B$ such that its unit
+$\Unit$ belongs to $B$ and all partial composition maps are internal in
+$B$, $\Oca$ can be studied as a set-theoretic operad. 
 \medbreak
@@
 $\RewContextRST$) the transitive (resp. reflexive and transitive,
-reflexive, symmetric, and transitive) closure of $\RewContext$.
+reflexive, symmetric, and sitive) closure of $\RewContext$.
 \medbreak
@@
 A \Def{normal form} for $\RewContext$ is a binary tree $\Tfr$ such
-that for all binary trees $\Tfr'$, $\Tfr \RewContextRT \Tfr'$ imply
+that for all binary tree $\Tfr'$, $\Tfr \RewContextRT \Tfr'$ implies
 $\Tfr' = \Tfr$. In other words, a normal form for $\RewContext$ is a
-tree which is not rewritable by $\RewContext$. The set of all the normal
-forms of $\RewContext$ is denoted by $\NormalForms_{\RewContext}$. The
-trees of $\NormalForms_{\RewContext}$ admit the following description,
-useful for enumerative prospects.
+tree which is not rewritable by $\RewContext$. A normal form for
+$\RewContext$ of a binary tree $\Tfr$ is a normal form $\overline{\Tfr}$
+for $\RewContext$ such that $\Tfr\RewContextRT\overline{\Tfr}$. When no
+confusion is possible, we simply say normal form instead of normal form
+for $\RewContext$. The set of all the normal forms is denoted by
+$\NormalForms_{\RewContext}$. The trees of $\NormalForms_{\RewContext}$
+admit the following description, useful for enumerative prospects.
 \medbreak
@@
 \begin{enumerate}[label={(\it\arabic*)}]
-    \item Set $\Rew' := \Rew$.
+\item Set $\Rew' := \Rew$ and let $\BranchingTrees$ be the set of
+  branching trees for $\RewContext$.
 \item \label{item:loop_start_buchberger}
-    If there is no branching pairs for $\RewContext'$ of trees of
-    degrees $k$ for all $0 \leq k \leq 2 \, \Deg(\Rew') - 1$, the
-    execution stops and the output is $\Rew'$.
+  If $\BranchingTrees$ is empty, the execution stops and the output
+  is $\Rew'$.
 \item Otherwise, let $\Tfr$ be the branching tree for $\RewContext'$
-    with the minimal degree and the minimal prefix word.
+  with the minimal degree and the minimal prefix word and remove $\Tfr$
+  from $\BranchingTrees$.
 \item Let $\{\Sfr_1, \Sfr_2\}$ be the branching pair for $\Tfr$ such
   that $\Sfr_1$ and $\Sfr_2$ have the minimal prefix words.
-    \item Add to $\Rew'$ the rewrite rule
+\item Let $\overline{\Sfr_1}$ and $\overline{\Sfr_2}$ be normal forms of
+  $\Sfr_1$ and $\Sfr_2$, respectively.
+\item If $\overline{\Sfr_1}$ is different from $\overline{\Sfr_2}$, add
+  to $\Rew'$ the rewrite rule
     \begin{math}
-        \max_\leq \left\{\Sfr_1, \Sfr_2\right\}
+      \max_\leq \left\{\overline{\Sfr_1}, \overline{\Sfr_2}\right\}
       \Rew'
-        \min_\leq \left\{\Sfr_1, \Sfr_2\right\}.
+      \min_\leq \left\{\overline{\Sfr_1}, \overline{\Sfr_2}\right\}.
     \end{math}

### 2018-07-09 Operads_rewrite.tex
Modification algo de Buchberger v2

@@
     $\Sfr_1$ and $\Sfr_2$, respectively.
-\item If $\overline{\Sfr_1}$ is different from $\overline{\Sfr_2}$, add
+  \item \label{item:new_rewrite_rule_buchberger}
+    If $\overline{\Sfr_1}$ is different from $\overline{\Sfr_2}$, add
     to $\Rew'$ the rewrite rule
@@
     \end{math}
+  \item Add to $\BranchingTrees$ all new branching trees of degrees at
+    most $2 \Deg(\Rew') - 1$ created by the rewrite rule of
+    Step~\ref{item:new_rewrite_rule_buchberger}.
   \item Go to Step~\ref{item:loop_start_buchberger}.

### 2018-07-11 CAs_operads.tex
Harmonisation 3 premières sections

@@
 \begin{equation} \label{equ:congruence_CAs_gamma}
-    \LComb{\gamma} \enspace \CongrCAs{\gamma} \enspace \RComb{\gamma}
+    \LComb{\gamma} \enspace \CongrCAs{\gamma} \enspace \RComb{\gamma}.
 \end{equation}
@@
 $\CAs{1} = \Mag$ and that $\CongrCAs{2}$ is the operad congruence
-defined by~\eqref{equ:congruence_as} so that $\CAs{2} = \As$.
+defined by
+\begin{equation}
+    \begin{tikzpicture}[xscale=.24,yscale=.24,Centering]
+        \node(0)at(0.00,-3.33){};
+        \node(2)at(2.00,-3.33){};
+        \node(4)at(4.00,-1.67){};
+        \node[NodeST](1)at(1.00,-1.67)
+            {\begin{math}\Product\end{math}};
+        \node[NodeST](3)at(3.00,0.00)
+            {\begin{math}\Product\end{math}};
+        \draw[Edge](0)--(1);
+        \draw[Edge](1)--(3);
+        \draw[Edge](2)--(1);
+        \draw[Edge](4)--(3);
+        \node(r)at(3.00,1.5){};
+        \draw[Edge](r)--(3);
+    \end{tikzpicture}
+    \Congr
+    \begin{tikzpicture}[xscale=.24,yscale=.24,Centering]
+        \node(0)at(0.00,-1.67){};
+        \node(2)at(2.00,-3.33){};
+        \node(4)at(4.00,-3.33){};
+        \node[NodeST](1)at(1.00,0.00)
+                {\begin{math}\Product\end{math}};
+        \node[NodeST](3)at(3.00,-1.67)
+                {\begin{math}\Product\end{math}};
+        \draw[Edge](0)--(1);
+        \draw[Edge](2)--(3);
+        \draw[Edge](3)--(1);
+        \draw[Edge](4)--(3);
+        \node(r)at(1.00,1.5){};
+        \draw[Edge](r)--(1);
+    \end{tikzpicture}\,
+\end{equation}
+so that $\CAs{2} = \As$.
 Let also
@@
 \end{equation}
-be the set of all the $\gamma$-comb associative operads
+be the set of all the $\gamma$-comb associative operads.
 Our purpose is to show that $\CAsAll$ admits a lattice structure. For
@@
     The operad $\CAs{\gamma'}$ is generated by one binary generator
-    $[\Product]_{\CongrCAs{\gamma'}}$, so that $\varphi$ is entirely
-    determined by the image
-    $\varphi\left([\Product]_{\CongrCAs{\gamma'}}\right)$. Moreover,
-    $\varphi([\Product]_{\CongrCAs{\gamma'}})$ has to be of arity $2$ in
-    $\CAs{\gamma}$, so that we necessarily have
+    $[\Product]_{\CongrCAs{\gamma'}}$, which is the image of $\Product$
+    in $\CAs{\gamma'}$. Hence, $\varphi$ is entirely determined by the
+    image $\varphi\left([\Product]_{\CongrCAs{\gamma'}}\right)$.
+    Moreover, $\varphi([\Product]_{\CongrCAs{\gamma'}})$ has to be of
+    arity $2$ in $\CAs{\gamma}$, so that we necessarily have
     \begin{math}
@@
     \end{math}
-    for any binary tree $\Tfr$,
+    for any binary tree $\Tfr$.
     Since
@@
     $\CAs{\gamma'}$ and $\CAs{\gamma}$, respectively. From
-    Lemma~\ref{lem:injective_morphisms_CAs}, these two morphisms are
+    Lemma~\ref{lem:surjective_morphisms_CAs}, these two morphisms are
     identity morphisms, so that $\varphi$ and $\psi$ are injective. From
@@
 
-In order to show that the poset $\left(\CAsAll, \OrdCAs\right)$ is also
-a lattice, that is two elements of $\CAsAll$ admit lower-bounds and
-upper-bounds, we relate $\left(\CAsAll, \OrdCAs\right)$ with the lattice
-of integers $\left(\N,\mid, \gcd, \lcm\right)$, where $\mid$ denotes the
+In order to show that the poset $\left(\CAsAll, \OrdCAs\right)$ is also a
+lattice, we relate $\left(\CAsAll, \OrdCAs\right)$ with the lattice of
+integers $\left(\N,\mid, \gcd, \lcm\right)$, where $\mid$ denotes the
 division relation, $\gcd$ denotes the greatest common divisor, and
 $\lcm$ the least common multiple operators, respectively.
+
+Recall that
+$\LRank(\Tfr)$ denotes the left rank of a binary tree $\Tfr$, defined in
+Section~\ref{sec:operad_Mag}.
 \medbreak
@@
 \begin{proof}
-    Let $\Rew$ be the rewrite relation on $\Mag$ induced by the rewrite
-    rule $\LComb{\gamma} \Rew \RComb{\gamma}$. In the rest of the
-    proof, $\Tfr$ and $\Tfr$ are two binary trees.
+  We consider the rewrite rule $\LComb{\gamma} \Rew \RComb{\gamma}$ on
+  $\Mag$. 
     \smallbreak
 
-    First, we show that $\Tfr \Rew \Tfr'$ implies that
+    First, we show that $\Tfr \RewContext \Tfr'$ implies that
     $\LRank\left(\Tfr'\right) - \LRank\left(\Tfr\right)$ is
@@
 
-    Assume that $\Tfr \RewRT \Tfr'$, so that there exist binary trees
+    Assume that $\Tfr \RewContextRT \Tfr'$, so that there exist binary trees
     $\Tfr_1$, \dots, $\Tfr_k$ such that $\Tfr_1 = \Tfr$,
     $\Tfr_k = \Tfr'$ and for every $i \in \{1, \dots, k - 1\}$, we have
-    $\Tfr_i\Rew \Tfr_{i + 1}$. The integer
+    $\Tfr_i\RewContext \Tfr_{i + 1}$. The integer
     \begin{math}
@@
 
-    Assume that $\Tfr \RewRTS \Tfr'$, so that there exist binary trees
+    Assume that $\Tfr \RewContextRST \Tfr'$, so that there exist binary trees
     $\Tfr_1$, \dots, $\Tfr_k$ such that $\Tfr_1 = \Tfr$,
     $\Tfr_k = \Tfr'$ and for every $i \in \{1, \dots, k - 1\}$, we have
-    $\Tfr_i \RewRTS \Tfr_{i + 1}$ or $\Tfr_{i + 1} \RewRTS \Tfr_i$.
-    From the second part of the proof, the integer
+    $\Tfr_i \RewContextRT \Tfr_{i + 1}$ or $\Tfr_{i + 1} \RewContextRT
+    \Tfr_i$. From the second part of the proof, the integer
     \begin{math}
@@
     The congruence $\CongrCAs{\gamma}$ is the equivalence relation
-    induced by $\Rew$, that is we have $\Tfr \CongrCAs{\gamma} \Tfr'$ if
-    and only if $\Tfr \RewRTS \Tfr'$. Hence, from the third part of
-    the proof, $\Tfr \CongrCAs{\gamma} \Tfr'$ implies that
+    induced by the rewrite relation $\RewContext$ induced by the rewrite
+    rule $\LComb{\gamma} \Rew \RComb{\gamma}$, that is we have $\Tfr
+    \CongrCAs{\gamma} \Tfr'$ if and only if $\Tfr \RewContextRST \Tfr'$.
+    Hence, from the third part of the proof, $\Tfr \CongrCAs{\gamma}
+    \Tfr'$ implies that
     \begin{math}
@@
 \begin{Proposition} \label{prop:division_CAs}
-    Let $\gamma$ and $\gamma'$ be two positive integers.Then, there
+    Let $\gamma$ and $\gamma'$ be two positive integers. Then, there
     exists a morphism $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$ if and
@@
     The poset $\left(\CAsAll, \OrdCAs\right)$ is a lattice where
-    the lower-bound and upper-bound satisfy, for any positive integers
-    $\gamma$ and $\gamma'$,
+    the lower-bound and upper-bound are, for any positive integers
+    $\gamma$ and $\gamma'$, the following operads
     \begin{equation}
-        \CAs{\gamma} \wedge \CAs{\gamma'}
-        = \CAs{\gcd \left(\gamma-1, \gamma'-1\right)}
+      \CAs{\gcd \left(\gamma-1, \gamma'-1\right)}\ \text{and}\
+      \CAs{\lcm \left(\gamma-1, \gamma'-1\right)}.
+    \end{equation}
+\end{Theorem}
+\medbreak
+
+As explained in Section~\ref{sec:operad_Mag}, a set-theoreic operad can
+be embedded into a linear operad, so that the operads $\CAs{\gamma}$ can
+be embedded into quotient operads $\KCAs{\gamma}$ of $\KMag$. Formally,
+the operad $\KCAs{\gamma}$ is equal to $\KMag/I_{\gamma}$, where
+$I_{\gamma}$ is the operadic ideal of $\KMag$ generated by
+$\LComb{\gamma}-\RComb{\gamma}$.
+
+We obtain a
+new lattice $\left(\KCAsAll,\OrdCAs,\gcd,\lcm\right)$, where $\KCAsAll$
+is the set of all operads $\KCAs{\gamma}$. In this linear framework, the
+condition $\KCAs{\gamma}\OrdCAs\KCAs{\gamma'}$ means that the dimension
+of the space $\text{hom}\left(\KCAs{\gamma'},\KCAs{\gamma}\right)$ is
+equal to $1$. Hence, $\left(\KCAsAll,\OrdCAs,\gcd,\lcm\right)$ is related
+to the lattice $\left(\QMag,\OrdKMag,\wedge,\vee\right)$ presented in
+Section~\ref{sec:Magmatic_operads} by the following proposition.
+
+\begin{Proposition}
+  The inclusion
+  $\iota:\left(\KCAsAll,\OrdCAs\right)\to\left(\QMag,\OrdKMag\right)$ is
+  non decreasing. In particular, for any positive integers $\gamma$ and
+  $\gamma'$, we have
+  \begin{equation} \label{equ:comparison_of_lattice_operations}
+    \KCAs{\gcd \left(\gamma-1, \gamma'-1\right)}\OrdKMag
+    \KCAs{\gamma}\wedge\KCAs{\gamma'}
   \end{equation}
@@
   \begin{equation}
-        \CAs{\gamma} \vee \CAs{\gamma'}
-        = \CAs{\lcm \left(\gamma-1, \gamma'-1\right)}.
+    \KCAs{\gamma}\vee\KCAs{\gamma'}\OrdKMag
+    \KCAs{\lcm \left(\gamma-1, \gamma'-1\right)}
   \end{equation}
-\end{Theorem}
-\medbreak
+
+  \end{Proposition}
 

### 2018-07-11 Magmatic_operads.tex
Harmonisation 3 premières sections

--- 2018-06-29 Magmatic_operads.tex
@@
-\section{Quotients of the magmatic operad}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\Todo{Write mini intro.}
+\section{Linear magmatic operads}
+\label{sec:Magmatic_operads}
 
-\subsection{Lattice structure}
+In this section, we fix a commutative field $\K$ and we study quotients
+of the free linear operad over one binary generator. We call this free
+operad the \Def{linear magmatic operad} and we denote it by $\KMag$. For
+each arity $n$, $\KMag(n)$ is the vector space with basis $\Mag(n)$, and
+the compositions of $\KMag$ extend by linearity the ones of $\Mag$.
 
-We denote by $\IMag$ the set of operadic of $\Mag$, and
+\subsection{Lattice of linear magmatic quotients}
+
+We denote by $\IMag$ the set of operadic ideals of $\KMag$, and
 \begin{equation} \label{equ:definition_of_QMag}
-  \QMag =\Big\{\Mag/ I\mid I\in\IMag\Big\},
+  \QMag =\Big\{\KMag/ I\mid I\in\IMag\Big\},
   \end{equation}
-the set of quotients of the magmatic operad. Given two elements $\Oca_1$
-and $\Oca_2$ of $\QMag$, we denote by $\text{hom}\left(\Oca_1,\Oca_2\right)$
-the set of operads morphisms from $\Oca_1$ to $\Oca_2$.
+the set of quotients of the linear magmatic operad. Given two elements
+$\Oca_1$ and $\Oca_2$ of $\QMag$, we denote by
+$\text{hom}\left(\Oca_1,\Oca_2\right)$ the set of operads morphisms from
+$\Oca_1$ to $\Oca_2$.
 
@@
 \begin{proof}
-  The operad $\Oca_1$ is spanned by the binary generator~$\Product$, so
-  that a morphism $\varphi:\Oca_1\to\Oca_2$ is uniquely determined by
-  $\varphi(\Product)$. Moreover, $\varphi(\Product)$ has arity $2$ is
-  $\Oca_2$. Hence, $\varphi(\Product)$ belongs to the line spanned by
-  the binary generator of $\Oca_2$, that is there exists a scalar
-  $\lambda\in\K$ such that $\varphi(\Product)=\lambda\Product$. If there
-  exists such a $\lambda$ different from zero, then for every nonzero
-  scalar $\mu$, we have a well-defined operads morphism
-  $\psi:\Oca_1\to\Oca_2$ satisfying $\psi(\Product)=\mu\Product=\left(
-  \mu/\lambda\right)\varphi(\Product)$. Hence,
+  The operad $\Oca_1$ is spanned by the binary generator
+  $[\Product]_{I_1}$, which is the class of the element
+  $\Product\in\KMag$ in $\Oca_1$. Hence, a morphism
+  $\varphi:\Oca_1\to\Oca_2$ is uniquely determined by
+  $\varphi\left([\Product]_{I_1}\right)$. Moreover,
+  $\varphi\left([\Product]_{I_1}\right)$ has arity $2$ in $\Oca_2$.
+  Hence, $\varphi\left([\Product]_{I_1}\right)$ belongs to the line
+  spanned by the binary generator of $\Oca_2$, that is there exists a
+  scalar $\lambda\in\K$ such that $\varphi\left([\Product]_{I_1}\right)
+  =\lambda[\Product]_{I_2}$. If there exists such a $\lambda$ different
+  from zero, then for every nonzero scalar $\mu$, we have a well-defined
+  operads morphism $\psi:\Oca_1\to\Oca_2$ satisfying
+  $\psi([\Product]_{I_1}) =\mu[\Product]_{I_2}=
+  \left(\mu/\lambda\right)\varphi([\Product]_{I_1})$. Hence,
   $\text{hom}\left(\Oca_1,\Oca_2\right)$ is either reduced to the zero
-  morphism or it is in one-to-one correspondance with $\K$, which
-  proves that $\text{hom}\left(\Oca_1,\Oca_2\right)$ is a vector space
-  of dimension at most $1$. Moreover, if $\varphi$ is different from $0$,
-  that is there is a nonzero scalar such that
-  $\varphi(\Product)=\lambda\Product$, we have
-  $\varphi(1/\lambda\Product)=\Product$, so that $\varphi$ is
-  surjective.
+  morphism or it is in one-to-one correspondance with $\K$, which proves
+  that $\text{hom}\left(\Oca_1,\Oca_2\right)$ is a vector space of
+  dimension at most $1$. Moreover, if $\varphi$ is different from $0$,
+  that is there is a nonzero scalar such that $\varphi([\Product]_{I_1})
+  =\lambda[\Product]_{I_2}$, we have $\varphi(1/\lambda[\Product]_{I_1})
+  =[\Product]_{I_2}$, so that $\varphi$ is surjective.
 \end{proof}
 
-We introduce the binary relation $\preceq$ on $\QMag$ as follows: we
-have $\Oca_2\preceq\Oca_1$ if the dimension of
+We introduce the binary relation $\OrdKMag$ on $\QMag$ as follows: we
+have $\Oca_2\OrdKMag\Oca_1$ if the dimension of
 $\text{hom}\left(\Oca_1,\Oca_2\right)$ is equal to $1$.
@@
 \begin{Proposition} \label{prop:order_relations_on_QMag_and_ideals}
-  Let $\Oca_1=\Mag/I_1$ and $\Oca_2=\Mag/I_2$ be two elements of $\QMag$.
-  We have $\Oca_2\preceq\Oca_1$ if and only if $I_1\subseteq I_2$.
+  Let $\Oca_1=\KMag/I_1$ and $\Oca_2=\KMag/I_2$ be two elements of
+  $\QMag$.   We have $\Oca_2\OrdKMag\Oca_1$ if and only if
+  $I_1\subseteq I_2$.
 \end{Proposition}
@@
   dimension at most $1$, it contains a nonzero morphism if and only if
-  the morphism
-  $\overline{\varphi}:\Oca_1\to\Oca_2$ satisfying
-  $\overline{\varphi}(\Product)=\Product$ is well-defined, which means
-  that $\Oca_2\preceq\Oca_1$ is equivalent to this condition. Moreover,
-  by the universal property of the quotient, $\overline{\varphi}$ is
-  well-defined if and only if $I_1$ is included in the kernel of the
-  morphism $\varphi:\Mag\to\Oca_2$ defined by
-  $\varphi(\Product)=\Product$. This kernel is equal to $I_2$, so that
+  the morphism $\overline{\varphi}:\Oca_1\to\Oca_2$ satisfying
+  $\overline{\varphi}([\Product]_{I_1})=[\Product]_{I_2}$ is well
+  -defined, which means that $\Oca_2\OrdKMag\Oca_1$ is equivalent to this
+  condition. Moreover, by the universal property of the quotient,
   $\overline{\varphi}$ is well-defined if and only if $I_1$ is included
-  in $I_2$, which concludes the proof.
+  in the kernel of the morphism $\varphi:\KMag\to\Oca_2$ defined by
+  $\varphi(\Product)=[\Product]_{I_1}$. This kernel is equal to
+  $I_2$, so that $\overline{\varphi}$ is well-defined if and only if
+  $I_1$ is included in $I_2$, which concludes the proof.
 \end{proof}
@@
 
-Given two elements $\Oca_1=\Mag/I_1$ and $\Oca_2=\Mag/I_2$ of $\QMag$,
+Given two elements $\Oca_1=\KMag/I_1$ and $\Oca_2=\KMag/I_2$ of $\QMag$,
 we let
 \begin{equation} \label{equ:definition_of_lattice_operations_of_QMag}
-  \Oca_1\wedge \Oca_2=\Mag/\left(I_1+I_2\right)\ \ \text{and}\ \
-  \Oca_1\wedge \Oca_2=\Mag/\left(I_1\cap I_2\right).
+  \Oca_1\wedge \Oca_2=\KMag/\left(I_1+I_2\right)\ \ \text{and}\ \
+  \Oca_1\wedge \Oca_2=\KMag/\left(I_1\cap I_2\right).
 \end{equation}
+Explicitely, for every integer $n$, $\left(\Oca_1\wedge\Oca_2\right)(n)$
+(respectively, $\left(\Oca_1\vee\Oca_2\right)(n)$) is the quotient of
+vector spaces $\KMag(n)/\left(I_1(n)+I_2(n)\right)$ (respectively,
+$\KMag(n)/\left(I_1(n)\cap I_2(n)\right)$).
 
 \begin{Theorem} \label{thm:lattice_structure_of_QMag}
-  The tuple $\left(\QMag,\preceq,\wedge,\vee\right)$ is a lattice.
+  The tuple $\left(\QMag,\OrdKMag,\wedge,\vee\right)$ is a lattice.
 \end{Theorem}
@@
 \begin{proof}
-  The map $\mathcal{Q}:\IMag\to\QMag$ defined by $\mathcal{Q}(I)=\Mag/I$
+  The map $\mathcal{Q}:\IMag\to\QMag$ defined by $\mathcal{Q}(I)=\KMag/I$
   is a bijection by definition of $\QMag$. Moreover, from
   Proposition~\ref{prop:order_relations_on_QMag_and_ideals},
-  $\Oca_2\preceq\Oca_1$ is equivalent to $I_1\subseteq I_2$, so that
-  $\left(\QMag,\preceq\right)$ is a poset and $\mathcal{Q}$ is a
+  $\Oca_2\OrdKMag\Oca_1$ is equivalent to $I_1\subseteq I_2$, so that
+  $\left(\QMag,\OrdKMag\right)$ is a poset and $\mathcal{Q}$ is a
   decreasing bijection. The tuple $\left(\IMag,\subseteq,\cap,+\right)$
@@
 \end{proof}
-\subsection{Kernels of magmatic operads}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Hilbert series and linear magmatic quotients}
+
+In Theorem~\ref{thm:Grassmann_formula_for__Hilbert_series_of_QMag}, we
+show a formula, analogous to the Grassman formula, for Hilbert series of
+elements of the lattice $\left(\QMag,\OrdKMag,\wedge,\vee\right)$. For
+that, we need the following :
+
+\begin{Lemma} \label{lem:lattice_structure_and_coefficients_of_Hiblert_series}
+  Let $\Oca_1$ and $\Oca_2$ be two elements of $\QMag$. For every integer
+  $n$, we have
+  \begin{equation} \label{equ:lattice_structure_and_coefficients_of_the_Hiblert_series}
+    \dim{\left(\Oca_1\wedge\Oca_2(n)\right)}+
+    \dim{\left(\Oca_1\vee\Oca_2(n)\right)}=
+    \dim{\left(\Oca_1(n)\right)}+\dim{\left(\Oca_2(n)\right)}.
+  \end{equation}
+\end{Lemma}
+
+\begin{proof}
+  Let $I_1$ and $I_2$ be the two operadic ideals of $\KMag$ such that
+  $\Oca_1$ and $\Oca_2$ are equal to $\KMag/I_1$ and $\KMag/I_2$,
+  respectively. For every integer $n$, we have
+  \[\begin{split}
+  &\dim{\left(\Oca_1\wedge\Oca_2(n)\right)}+
+  \dim{\left(\Oca_1\vee\Oca_2(n)\right)}\\
+  &=\dim{\Big(\KMag(n)/\left(I_1+I_2\right)(n)\Big)}+
+  \dim{\Big(\KMag(n)/\left(I_1\cap I_2\right)(n)\Big)}\\
+  &=\dim{\left(\KMag(n)\right)}-\dim{\left(I_1(n)+I_2(n)\right)}
+  +\dim{\left(\KMag(n)\right)}-\dim{\left(I_1(n)\cap I_2(n)\right)}\\
+  &=\dim{\left(\KMag(n)\right)}-\dim{\left(I_1(n)\right)}+
+  \dim{\left(\KMag(n)\right)}-\dim{\left(I_2(n)\right)}\\
+  &=\dim{\Big(\KMag(n)/I_1(n)\Big)}+\dim{\Big(\KMag(n)/I_2(n)\Big)}\\
+  &=\dim{\left(\Oca_1(n)\right)}+\dim{\left(\Oca_2(n)\right)}.
+  \end{split}\]
+  The third equality is due to the Grassmann formula applied to the
+  subspaces $I_1(n)$ and $I_2(n)$ of $\KMag(n)$.
+\end{proof}
+
+\begin{Theorem} \label{thm:Grassmann_formula_for__Hilbert_series_of_QMag}
+  Let $\Oca_1$ and $\Oca_2$ be two elements of $\QMag$. We have
+  \begin{equation} \label{equ:lattice_structure_and_Hiblert_series}
+    \HilbertSeries_{\Oca_1\wedge\Oca_2}(t)+\HilbertSeries_{\Oca_1\vee\Oca_2}(t)=\HilbertSeries_{\Oca_1}(t)+\HilbertSeries_{\Oca_2}(t).
+    \end{equation}
+  \end{Theorem}
+
+\begin{proof}
+  We have
+  \[\begin{split}
+  \HilbertSeries_{\Oca_1\wedge\Oca_2}(t)+\HilbertSeries_{\Oca_1\vee\Oca_2}(t)&=\sum_{n\in\N}\dim{\left(\Oca_1\wedge\Oca_2(n)\right)}t^n+\sum_{n\in\N}\dim{\left(\Oca_1\vee\Oca_2(n)\right)}t^n\\
+  &=\sum_{n\in\N}\Big(\dim{\left(\Oca_1\wedge\Oca_2(n)\right)}+\dim{\left(\Oca_1\vee\Oca_2(n)\right)}\Big)t^n\\
+  &=\sum_{n\in\N}\Big(\dim{\left(\Oca_1(n)\right)}+\dim{\left(\Oca_2(n)\right)}\Big)t^n\\
+  &=\sum_{n\in\N}\dim{\left(\Oca_1(n)\right)}t^n+\sum_{n\in\N}\dim{\left(\Oca_2(n)\right)}t^n\\
+  &=\HilbertSeries_{\Oca_1}(t)+\HilbertSeries_{\Oca_2}(t).
+  \end{split}\]
+\end{proof}
+The third equality is due to Lemma~\ref{lem:lattice_structure_and_coefficients_of_Hiblert_series}.
+% Hilbert series, enumeration, a little of rewrite systems, etc.

### 2018-07-11 Operads_rewrite.tex
Harmonisation 3 premières sections

@@
 Nevertheless, operads can be defined in the category of $\K$-vector
-spaces, where $\K$ denotes in all this text a field of characteristic
-zero. We call them \Def{linear operads} and we use them in
+spaces, where $\K$ denotes in all this text a commutative field. We call
+them \Def{linear operads} and we study a class of such operads in
 Section~\ref{sec:Magmatic_operads}. All the above definitions extend for

### 2018-07-11 CAs_operads.tex
Ajout mini-intro section comb associative operads

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Generalizations of the associative operad} \label{sec:CAs_d}
-\Todo{Write mini intro.}
+\section{Generalizations of the associative operad}
+\label{sec:CAs_d}
+
+In this section, we define comb associative operads and we show that the
+set of such operads admits a lattice structure, isomorphic to the lattice
+division for nonnegative integers. We also relate this lattice to the
+lattice of linear magmatic quotients.
 
@@
 \subsection{Comb associative operads}
-\Todo{Write mini intro.}
 
-It is known that the rewrite rule $\Rew$
-orienting~\eqref{equ:congruence_as} from left to right is a convergent
-orientation of (\ref{equ:congruence_as}). Then, a Poincaré-Birkhoff-Witt
-basis of $\As$ is the set of all right comb binary trees.
-\Todo{SG: to maybe to move at another place. }
-\medbreak
-
-Let, for any $\gamma \geq 1$, the binary trees
+Let, for any integer $\gamma \geq 1$, the binary trees
 \begin{equation}
@@
 be the set of all the $\gamma$-comb associative operads.
-Our purpose is to show that $\CAsAll$ admits a lattice structure. For
-that, we provide a description of operads morphisms between the
-elements of~$\CAsAll$.
 \medbreak
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{A lattice of operads}
-\Todo{Write mini intro.}
+\subsection{Lattice of comb associative operads}
+
+In order to introduce the lattice structure of $\CAsAll$, we study operad
+morphisms betweeen its elements by mean of intermediate lemmas.
 
@@
 \begin{Theorem}\label{thm:lattice_CAs}
-    The poset $\left(\CAsAll, \OrdCAs\right)$ is a lattice where
-    the lower-bound and upper-bound are, for any positive integers
-    $\gamma$ and $\gamma'$, the following operads
+  The tuple $\LatCAs$ is a lattice, where $\InfCAs$ and $\SupCAs$ are
+  defined, for any positive integers $\gamma$ and $\gamma'$, as follows:
     \begin{equation}
-      \CAs{\gcd \left(\gamma-1, \gamma'-1\right)}\ \text{and}\
-      \CAs{\lcm \left(\gamma-1, \gamma'-1\right)}.
+      \CAs{\gamma}\InfCAs\CAs{\gamma'}=\CAs{\gcd \left(\gamma-1, \gamma'-1\right)}
+    \end{equation}
+    and
+    \begin{equation}
+      \CAs{\gamma}\SupCAs\CAs{\gamma'}=\CAs{\lcm \left(\gamma-1, \gamma'-1\right)}.
     \end{equation}
@@
 \medbreak
+
+\begin{Remark}
+  The lattice $\left(\N,\mid, \gcd, \lcm\right)$ admits $1$ as minimum
+  element and $0$ as maximum element: any nonnegative integer is
+  divisible by $1$ and divides $0$. The corresponding property for
+  $\LatCAs$ is that it admits $\As=\CAs{2}$ as minimum element and $\Mag=
+  \CAs{1}$ as maximum element: any comb associative operad projects onto
+  $\As$ and is a quotient of $\Mag$.
+\end{Remark}
+
+We terminate this section by relating the lattice
+$\LatQMag$ introduced in Section~\ref{sec:Magmatic_operads} to the
+lattice $\LatCAs$.
 
@@
 
-We obtain a
-new lattice $\left(\KCAsAll,\OrdCAs,\gcd,\lcm\right)$, where $\KCAsAll$
-is the set of all operads $\KCAs{\gamma}$. In this linear framework, the
-condition $\KCAs{\gamma}\OrdCAs\KCAs{\gamma'}$ means that the dimension
-of the space $\text{hom}\left(\KCAs{\gamma'},\KCAs{\gamma}\right)$ is
-equal to $1$. Hence, $\left(\KCAsAll,\OrdCAs,\gcd,\lcm\right)$ is related
-to the lattice $\left(\QMag,\OrdKMag,\wedge,\vee\right)$ presented in
-Section~\ref{sec:Magmatic_operads} by the following proposition.
+We obtain a new lattice $\LatKCAs$, where $\KCAsAll$ is the set of all
+operads $\KCAs{\gamma}$. In this linear framework, the condition
+$\KCAs{\gamma}\OrdCAs\KCAs{\gamma'}$ means that the dimension of the
+space $\text{hom}\left(\KCAs{\gamma'},\KCAs{\gamma}\right)$ is equal to
+$1$. Hence, $\LatKCAs$ is related to $\LatQMag$ by the following
+theorem.
 
-\begin{Proposition}
+\begin{Theorem}
   The inclusion
-  $\iota:\left(\KCAsAll,\OrdCAs\right)\to\left(\QMag,\OrdKMag\right)$ is
+  $\iota:\left(\KCAsAll,\OrdCAs\right)\to\left(\QMag,\OrdQMag\right)$ is
   non decreasing. In particular, for any positive integers $\gamma$ and
@@
   \begin{equation} \label{equ:comparison_of_lattice_operations}
-    \KCAs{\gcd \left(\gamma-1, \gamma'-1\right)}\OrdKMag
-    \KCAs{\gamma}\wedge\KCAs{\gamma'}
+    \KCAs{\gcd \left(\gamma-1, \gamma'-1\right)}\OrdQMag
+    \KCAs{\gamma}\InfQMag\KCAs{\gamma'}
   \end{equation}
@@
   \begin{equation}
-    \KCAs{\gamma}\vee\KCAs{\gamma'}\OrdKMag
-    \KCAs{\lcm \left(\gamma-1, \gamma'-1\right)}
+    \KCAs{\gamma}\SupQMag\KCAs{\gamma'}\OrdQMag
+    \KCAs{\lcm \left(\gamma-1, \gamma'-1\right)}.
   \end{equation}
 
-  \end{Proposition}
+  \end{Theorem}
+
+\begin{Remark}
+  Note that $\LatKCAs$ does not embed into a sub-lattice of $\LatQMag$,
+  that is $\iota$ is not a lattice morphism. Consider for instance
+  $\gamma=3$ and $\gamma'=4$, then $\KCAs{\gamma}\InfCAs\KCAs{\gamma'}$
+  is equal to $\KCAs{2}=\K\As$, whereas
+  $\KCAs{\gamma}\InfQMag\KCAs{\gamma'}$ is quotient of $\KMag$ be the two
+  relations $\LComb{3}-\RComb{3}$ and $\LComb{4}-\RComb{4}$.
+\end{Remark}
 

### 2018-07-11 Magmatic_operads.tex
Ajout mini-intro section comb associative operads

@@
 
-In this section, we fix a commutative field $\K$ and we study quotients
-of the free linear operad over one binary generator. We call this free
-operad the \Def{linear magmatic operad} and we denote it by $\KMag$. For
-each arity $n$, $\KMag(n)$ is the vector space with basis $\Mag(n)$, and
-the compositions of $\KMag$ extend by linearity the ones of $\Mag$.
+In this section, we equip the set of quotients of the linear magmatic
+operad with a lattice structure. We also show the Grassmann formula
+analog for this lattice.
 
 \subsection{Lattice of linear magmatic quotients}
+
+Throughout Section~\ref{sec:Magmatic_operads}, we fix a commutative field
+$\K$. The \Def{linear magmatic operad}, written $\KMag$, is the free
+linear operad over one binary generator. For each arity $n$, $\KMag(n)$
+is the vector space with basis $\Mag(n)$, and the compositions of $\KMag$
+extend by linearity the ones of $\Mag$.
 
@@
 $\Oca_1$ and $\Oca_2$ of $\QMag$, we denote by
-$\text{hom}\left(\Oca_1,\Oca_2\right)$ the set of operads morphisms from
+$\text{hom}\left(\Oca_1,\Oca_2\right)$ the set of operads morphism from
 $\Oca_1$ to $\Oca_2$.
@@
   from zero, then for every nonzero scalar $\mu$, we have a well-defined
-  operads morphism $\psi:\Oca_1\to\Oca_2$ satisfying
+  operad morphism $\psi:\Oca_1\to\Oca_2$ satisfying
   $\psi([\Product]_{I_1}) =\mu[\Product]_{I_2}=
@@
 
-We introduce the binary relation $\OrdKMag$ on $\QMag$ as follows: we
-have $\Oca_2\OrdKMag\Oca_1$ if the dimension of
+We introduce the binary relation $\OrdQMag$ on $\QMag$ as follows: we
+have $\Oca_2\OrdQMag\Oca_1$ if the dimension of
 $\text{hom}\left(\Oca_1,\Oca_2\right)$ is equal to $1$.
@@
   Let $\Oca_1=\KMag/I_1$ and $\Oca_2=\KMag/I_2$ be two elements of
-  $\QMag$.   We have $\Oca_2\OrdKMag\Oca_1$ if and only if
+  $\QMag$.   We have $\Oca_2\OrdQMag\Oca_1$ if and only if
   $I_1\subseteq I_2$.
@@
   $\overline{\varphi}([\Product]_{I_1})=[\Product]_{I_2}$ is well
-  -defined, which means that $\Oca_2\OrdKMag\Oca_1$ is equivalent to this
+  -defined, which means that $\Oca_2\OrdQMag\Oca_1$ is equivalent to this
   condition. Moreover, by the universal property of the quotient,
@@
 \begin{equation} \label{equ:definition_of_lattice_operations_of_QMag}
-  \Oca_1\wedge \Oca_2=\KMag/\left(I_1+I_2\right)\ \ \text{and}\ \
-  \Oca_1\wedge \Oca_2=\KMag/\left(I_1\cap I_2\right).
+  \Oca_1\InfQMag \Oca_2=\KMag/\left(I_1+I_2\right)\ \ \text{and}\ \
+  \Oca_1\SupQMag \Oca_2=\KMag/\left(I_1\cap I_2\right).
 \end{equation}
-Explicitely, for every integer $n$, $\left(\Oca_1\wedge\Oca_2\right)(n)$
-(respectively, $\left(\Oca_1\vee\Oca_2\right)(n)$) is the quotient of
+Explicitely, for every integer $n$, $\left(\Oca_1\InfQMag\Oca_2\right)(n)$
+(respectively, $\left(\Oca_1\SupQMag\Oca_2\right)(n)$) is the quotient of
 vector spaces $\KMag(n)/\left(I_1(n)+I_2(n)\right)$ (respectively,
@@
 \begin{Theorem} \label{thm:lattice_structure_of_QMag}
-  The tuple $\left(\QMag,\OrdKMag,\wedge,\vee\right)$ is a lattice.
+  The tuple $\LatQMag$ is a lattice.
 \end{Theorem}
@@
   Proposition~\ref{prop:order_relations_on_QMag_and_ideals},
-  $\Oca_2\OrdKMag\Oca_1$ is equivalent to $I_1\subseteq I_2$, so that
-  $\left(\QMag,\OrdKMag\right)$ is a poset and $\mathcal{Q}$ is a
+  $\Oca_2\OrdQMag\Oca_1$ is equivalent to $I_1\subseteq I_2$, so that
+  $\left(\QMag,\OrdQMag\right)$ is a poset and $\mathcal{Q}$ is a
   decreasing bijection. The tuple $\left(\IMag,\subseteq,\cap,+\right)$
   being a lattice, the decreasing bijection $\mathcal{Q}$ induces
-  lattice operations on $\QMag$, precisely $\wedge$ and $\vee$ by
+  lattice operations on $\QMag$, precisely $\InfQMag$ and $\SupQMag$ by
   definition.
@@
 
-In Theorem~\ref{thm:Grassmann_formula_for__Hilbert_series_of_QMag}, we
-show a formula, analogous to the Grassman formula, for Hilbert series of
-elements of the lattice $\left(\QMag,\OrdKMag,\wedge,\vee\right)$. For
-that, we need the following :
+In order to show the Grassman formula analog for $\LatQMag$, we need the
+following lemma.
 
@@
   \begin{equation} \label{equ:lattice_structure_and_coefficients_of_the_Hiblert_series}
-    \dim{\left(\Oca_1\wedge\Oca_2(n)\right)}+
-    \dim{\left(\Oca_1\vee\Oca_2(n)\right)}=
+    \dim{\left(\Oca_1\InfQMag\Oca_2(n)\right)}+
+    \dim{\left(\Oca_1\SupQMag\Oca_2(n)\right)}=
     \dim{\left(\Oca_1(n)\right)}+\dim{\left(\Oca_2(n)\right)}.
@@
   \[\begin{split}
-  &\dim{\left(\Oca_1\wedge\Oca_2(n)\right)}+
-  \dim{\left(\Oca_1\vee\Oca_2(n)\right)}\\
+  &\dim{\left(\Oca_1\InfQMag\Oca_2(n)\right)}+
+  \dim{\left(\Oca_1\SupQMag\Oca_2(n)\right)}\\
   &=\dim{\Big(\KMag(n)/\left(I_1+I_2\right)(n)\Big)}+
@@
 
+The Grassman formula analog for $\LatQMag$ is given by the following
+theorem.
+
 \begin{Theorem} \label{thm:Grassmann_formula_for__Hilbert_series_of_QMag}
@@
   \begin{equation} \label{equ:lattice_structure_and_Hiblert_series}
-    \HilbertSeries_{\Oca_1\wedge\Oca_2}(t)+\HilbertSeries_{\Oca_1\vee\Oca_2}(t)=\HilbertSeries_{\Oca_1}(t)+\HilbertSeries_{\Oca_2}(t).
+    \HilbertSeries_{\Oca_1\InfQMag\Oca_2}(t)+\HilbertSeries_{\Oca_1\SupQMag\Oca_2}(t)=\HilbertSeries_{\Oca_1}(t)+\HilbertSeries_{\Oca_2}(t).
     \end{equation}
@@
   \[\begin{split}
-  \HilbertSeries_{\Oca_1\wedge\Oca_2}(t)+\HilbertSeries_{\Oca_1\vee\Oca_2}(t)&=\sum_{n\in\N}\dim{\left(\Oca_1\wedge\Oca_2(n)\right)}t^n+\sum_{n\in\N}\dim{\left(\Oca_1\vee\Oca_2(n)\right)}t^n\\
-  &=\sum_{n\in\N}\Big(\dim{\left(\Oca_1\wedge\Oca_2(n)\right)}+\dim{\left(\Oca_1\vee\Oca_2(n)\right)}\Big)t^n\\
+  \HilbertSeries_{\Oca_1\InfQMag\Oca_2}(t)+\HilbertSeries_{\Oca_1\SupQMag\Oca_2}(t)&=\sum_{n\in\N}\dim{\left(\Oca_1\InfQMag\Oca_2(n)\right)}t^n+\sum_{n\in\N}\dim{\left(\Oca_1\SupQMag\Oca_2(n)\right)}t^n\\
+  &=\sum_{n\in\N}\Big(\dim{\left(\Oca_1\InfQMag\Oca_2(n)\right)}+\dim{\left(\Oca_1\SupQMag\Oca_2(n)\right)}\Big)t^n\\
   &=\sum_{n\in\N}\Big(\dim{\left(\Oca_1(n)\right)}+\dim{\left(\Oca_2(n)\right)}\Big)t^n\\

### 2018-07-19 CAs_operads.tex
Modifications

@@
 lattice of linear magmatic quotients.
+\medbreak
 
@@
 \subsection{Comb associative operads}
-
-Let, for any integer $\gamma \geq 1$, the binary trees
-\begin{equation}
-    \LComb{\gamma} :=
-    \underbrace{(\dots (\Product \circ_1 \Product) \circ_1 \dots)
-        \circ_1 \Product}
-    _{\gamma \mbox{ \footnotesize operands}}
-\end{equation}
-and
-\begin{equation}
-    \RComb{\gamma} :=
-    \underbrace{\Product \circ_2
-        (\dots \circ_2 (\Product \circ_2 \Product) \dots)}
-    _{\gamma \mbox{ \footnotesize operands}}
-\end{equation}
-be respectively the left and the right comb of degree $\gamma$.
-Let us now define for any $\gamma \geq 1$ the \Def{$\gamma$-comb
-associative operad} $\CAs{\gamma}$ as the quotient operad
-$\Mag/_{\CongrCAs{\gamma}}$ where $\CongrCAs{\gamma}$ is the smallest
-operad congruence of $\Mag$ satisfying
-\begin{equation} \label{equ:congruence_CAs_gamma}
-    \LComb{\gamma} \enspace \CongrCAs{\gamma} \enspace \RComb{\gamma}.
-\end{equation}
-Notice that $\CongrCAs{1}$ is trivial so that
-$\CAs{1} = \Mag$ and that $\CongrCAs{2}$ is the operad congruence
-defined by
+Recall first that the \Def{associative operad} $\As$ is the quotient
+of $\Mag$ by the smallest operad congruence $\Congr$ satisfying
 \begin{equation}
@@
         \draw[Edge](r)--(1);
-    \end{tikzpicture}\,
+    \end{tikzpicture}\,.
 \end{equation}
-so that $\CAs{2} = \As$.
-Let also
+We propose here a generalization of $\Congr$ in order to define
+generalizations of $\As$.
+\medbreak
+
+Let, for any integer $\gamma \geq 1$, the binary trees $\LComb{\gamma}$
+and $\RComb{\gamma}$ be respectively the left and the right comb of
+degree $\gamma$. These trees are depicted as
+\begin{equation}
+    \LComb{\gamma} = \enspace
+    \begin{tikzpicture}[xscale=.26,yscale=.3,Centering]
+        \node(0)at(0.00,-5.25){};
+        \node(2)at(2.00,-5.25){};
+        \node(4)at(4.00,-3.50){};
+        \node(6)at(6.00,-1.75){};
+        \node[NodeST](1)at(1.00,-3.50){\begin{math}\Product\end{math}};
+        \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
+        \node[NodeST](5)at(5.00,0.00){\begin{math}\Product\end{math}};
+        \draw[Edge](0)--(1);
+        \draw[Edge,dotted](1)edge[]node[font=\tiny]{
+            \begin{math}\gamma\! -\! 1\end{math}\hspace*{.6cm}}(3);
+        \draw[Edge](2)--(1);
+        \draw[Edge](3)--(5);
+        \draw[Edge](4)--(3);
+        \draw[Edge](6)--(5);
+        \node(r)at(5.00,1.5){};
+        \draw[Edge](r)--(5);
+    \end{tikzpicture}
+    \qquad \mbox{and} \qquad
+    \RComb{\gamma} =
+    \begin{tikzpicture}[xscale=.26,yscale=.3,Centering]
+        \node(0)at(0.00,-1.75){};
+        \node(2)at(2.00,-3.50){};
+        \node(4)at(4.00,-5.25){};
+        \node(6)at(6.00,-5.25){};
+        \node[NodeST](1)at(1.00,0.00){\begin{math}\Product\end{math}};
+        \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
+        \node[NodeST](5)at(5.00,-3.50){\begin{math}\Product\end{math}};
+        \draw[Edge](0)--(1);
+        \draw[Edge](2)--(3);
+        \draw[Edge](3)--(1);
+        \draw[Edge](4)--(5);
+        \draw[Edge,dotted](5)edge[]node[font=\tiny]{
+            \hspace*{.6cm}\begin{math}\gamma\! -\! 1\end{math}}(3);
+        \draw[Edge](6)--(5);
+        \node(r)at(1.00,1.5){};
+        \draw[Edge](r)--(1);
+    \end{tikzpicture}\,,
+\end{equation}
+where the values on the dotted edges denote the number of internal
+nodes they contain. We shall employ this drawing convention in the
+sequel, combined with the convention stipulating that dotted edges
+with no value have any number of internal nodes. Let us now define for
+any $\gamma \geq 1$ the \Def{$\gamma$-comb associative operad}
+$\CAs{\gamma}$ as the quotient operad $\Mag/_{\CongrCAs{\gamma}}$ where
+$\CongrCAs{\gamma}$ is the smallest operad congruence of $\Mag$
+satisfying
+\begin{equation} \label{equ:congruence_CAs_gamma}
+    \LComb{\gamma} \enspace \CongrCAs{\gamma} \enspace \RComb{\gamma}.
+\end{equation}
+Notice that $\CongrCAs{1}$ is trivial so that
+$\CAs{1} = \Mag$ and that $\CongrCAs{2}$ is the operad congruence
+defining $\As$ so that $\CAs{2} = \As$. Let also
 \begin{equation}
@@
 $\LRank(\Tfr)$ denotes the left rank of a binary tree $\Tfr$, defined in
-Section~\ref{sec:operad_Mag}.
+Section~\ref{sec:operad_Mag}. Besides, to simplify the notation,
+we shall write $\bar{a}$ instead of $a - 1$ for any integer $a$.
 \medbreak
@@
 \begin{Lemma}\label{lem:left_rank_and_CongrCAs}
-    Let $\gamma$ be a strictly positive integer and let $\Tfr$ and
+    Let $\gamma$ be a positive integer and let $\Tfr$ and
     $\Tfr'$ be two binary trees. If $\Tfr \CongrCAs{\gamma} \Tfr'$, then
     \begin{equation}
-        \LRank(\Tfr) \mod \gamma - 1
+        \LRank(\Tfr) \pmod{\bar{\gamma}}
         \enspace = \enspace
-        \LRank(\Tfr') \mod \gamma - 1.
+        \LRank\left(\Tfr'\right) \pmod{\bar{\gamma}}.
     \end{equation}
@@
     $\LRank\left(\Tfr'\right) - \LRank\left(\Tfr\right)$ is
-    divisible by $\gamma - 1$. \Todo{à faire.}
+    divisible by $\bar{\gamma}$. \Todo{à faire.}
     \smallbreak
@@
     $\Tfr_1$, \dots, $\Tfr_k$ such that $\Tfr_1 = \Tfr$,
-    $\Tfr_k = \Tfr'$ and for every $i \in \{1, \dots, k - 1\}$, we have
+    $\Tfr_k = \Tfr'$ and for every $i \in [k - 1]$, we have
     $\Tfr_i\RewContext \Tfr_{i + 1}$. The integer
@@
     \end{math}
-    is divisible by $\gamma - 1$ from the first part of the proof, so
+    is divisible by $\bar{\gamma}$ from the first part of the proof, so
     that $\LRank\left(\Tfr'\right) - \LRank\left(\Tfr\right)$ is
-    divisible by $\gamma-1$.
+    divisible by~$\bar{\gamma}$.
     \smallbreak
@@
     $\Tfr_1$, \dots, $\Tfr_k$ such that $\Tfr_1 = \Tfr$,
-    $\Tfr_k = \Tfr'$ and for every $i \in \{1, \dots, k - 1\}$, we have
+    $\Tfr_k = \Tfr'$ and for every $i \in [k - 1]$, we have
     $\Tfr_i \RewContextRT \Tfr_{i + 1}$ or $\Tfr_{i + 1} \RewContextRT
@@
     \end{math}
-    is divisible by $\gamma - 1$, so that
+    is divisible by $\bar{\gamma}$, so that
     $\LRank\left(\Tfr'\right) - \LRank\left(\Tfr\right)$ is
-    divisible by $\gamma - 1$.
+    divisible by~$\bar{\gamma}$.
     \smallbreak
@@
     \end{math}
-    is divisible by $\gamma - 1$.
+    is divisible by~$\bar{\gamma}$.
 \end{proof}
@@
     exists a morphism $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$ if and
-    only if $\left(\gamma - 1\right) \mid \left(\gamma' - 1\right)$.
+    only if $\bar{\gamma} \mid \bar{\gamma'}$.
 \end{Proposition}
@@
     $\LComb{\gamma'} \CongrCAs{\gamma} \RComb{\gamma'}$ if and only if
-    $\left(\gamma-1\right) \mid \left(\gamma'-1\right)$. If
+    $\bar{\gamma} \mid \bar{\gamma'}$. If
     $\LComb{\gamma'}\CongrCAs{\gamma}\RComb{\gamma'}$, from
@@
         - \LRank\left(\RComb{\gamma'}\right)
-        = \gamma' - 1
+        = \bar{\gamma'}
     \end{math}
-    is divisible by $\gamma-1$, which shows the direct implication.
+    is divisible by $\bar{\gamma}$, which shows the direct implication.
     \smallbreak
@@
     Conversely, if
-    $\left(\gamma-1\right) \mid \left(\gamma'-1\right)$, the rewrite
+    $\bar{\gamma} \mid \bar{\gamma'}$, the rewrite
     rule $\LComb{\gamma} \Rew \RComb{\gamma}$ induces the
@@
             \draw[Edge](0)--(1);
-            \draw[Edge,dotted](1)--(3);
+            \draw[Edge,dotted](1)edge[]node[font=\footnotesize]{
+                \begin{math}\bar{\gamma}\end{math}\hspace*{.5cm}}(3);
             \draw[Edge](10)--(9);
@@
             \draw[Edge](4)--(3);
-            \draw[Edge,dotted](5)--(7);
+            \draw[Edge,dotted](5)edge[]node[font=\footnotesize]{
+                \begin{math}\bar{\gamma}\end{math}\hspace*{.5cm}}(7);
             \draw[Edge](6)--(5);
@@
             \draw[Edge](8)--(7);
-            \draw[Edge,dotted](9)--(11);
+            \draw[Edge,dotted](9)edge[]node[font=\footnotesize]{
+                \begin{math}\bar{\gamma}\end{math}\hspace*{.5cm}}(11);
             \node(r)at(13.00,1.41){};
@@
             %
-            \node[fit=(1)(3),rotate fit=0,inner sep=0pt,
-                rounded corners,draw=Col5!80]{};
-            \node[fit=(5)(7),rotate fit=0,inner sep=0pt,
-                rounded corners,draw=Col5!80]{};
-            \node[fit=(9)(11),rotate fit=0,inner sep=0pt,
-                rounded corners,draw=Col5!80]{};
+            %\node[fit=(1)(3),rotate fit=0,inner sep=0pt,
+                %rounded corners,draw=Col5!80]{};
+            %\node[fit=(5)(7),rotate fit=0,inner sep=0pt,
+                %rounded corners,draw=Col5!80]{};
+            %\node[fit=(9)(11),rotate fit=0,inner sep=0pt,
+                %rounded corners,draw=Col5!80]{};
         \end{tikzpicture}
-        \enspace \Rew \enspace
+        \enspace \RewContext \enspace
         \begin{tikzpicture}[xscale=.19,yscale=.2,Centering]
@@
             \draw[Edge](0)--(1);
-            \draw[Edge,dotted](1)--(3);
+            \draw[Edge,dotted](1)edge[]node[font=\footnotesize]{
+                \begin{math}\bar{\gamma}\end{math}\hspace*{.5cm}}(3);
             \draw[Edge](10)--(11);
@@
             \draw[Edge](12)--(13);
-            \draw[Edge,dotted](13)--(11);
+            \draw[Edge,dotted](13)edge[]node[font=\footnotesize]{
+                \hspace*{.5cm}\begin{math}\bar{\gamma}\end{math}}(11);
             \draw[Edge](14)--(13);
@@
             %
-            \node[fit=(1)(3),rotate fit=0,inner sep=0pt,
-                rounded corners,draw=Col5!80]{};
-            \node[fit=(5)(7),rotate fit=0,inner sep=0pt,
-                rounded corners,draw=Col5!80]{};
-            \node[fit=(11)(13),rotate fit=0,inner sep=0pt,
-                rounded corners,draw=Col5!80]{};
-        \end{tikzpicture}
-        \enspace \Rew \enspace
+            %\node[fit=(1)(3),rotate fit=0,inner sep=0pt,
+                %rounded corners,draw=Col5!80]{};
+            %\node[fit=(5)(7),rotate fit=0,inner sep=0pt,
+                %rounded corners,draw=Col5!80]{};
+            %\node[fit=(11)(13),rotate fit=0,inner sep=0pt,
+                %rounded corners,draw=Col5!80]{};
+        \end{tikzpicture} \\
+        \enspace \RewContext \enspace
         \begin{tikzpicture}[xscale=.19,yscale=.2,Centering]
@@
             \draw[Edge](8)--(9);
-            \draw[Edge,dotted](9)--(7);
+            \draw[Edge,dotted](9)edge[]node[font=\footnotesize]{
+                \hspace*{.5cm}\begin{math}\bar{\gamma}\end{math}}(7);
             \node(r)at(5.00,1.88){};
@@
             %
-            \node[fit=(1)(3),rotate fit=0,inner sep=0pt,
-                rounded corners,draw=Col5!80]{};
-            \node[fit=(7)(9),rotate fit=0,inner sep=0pt,
-                rounded corners,draw=Col5!80]{};
-            \node[fit=(11)(13),rotate fit=0,inner sep=0pt,
-                rounded corners,draw=Col5!80]{};
-        \end{tikzpicture} \\
-        \enspace \RewRT \enspace
+            %\node[fit=(1)(3),rotate fit=0,inner sep=0pt,
+                %rounded corners,draw=Col5!80]{};
+            %\node[fit=(7)(9),rotate fit=0,inner sep=0pt,
+                %rounded corners,draw=Col5!80]{};
+            %\node[fit=(11)(13),rotate fit=0,inner sep=0pt,
+                %rounded corners,draw=Col5!80]{};
+        \end{tikzpicture}
+        \enspace \RewContextRT \enspace
         \begin{tikzpicture}[xscale=.19,yscale=.25,Centering]
@@
             \draw[Edge](4)--(5);
-            \draw[Edge,dotted](5)--(3);
+            \draw[Edge,dotted](5)edge[]node[font=\footnotesize]{
+                \hspace*{.5cm}\begin{math}\bar{\gamma}\end{math}}(3);
             \draw[Edge](6)--(7);
@@
             \draw[Edge](8)--(9);
-            \draw[Edge,dotted](9)--(7);
+            \draw[Edge,dotted](9)edge[]node[font=\footnotesize]{
+                \hspace*{.5cm}\begin{math}\bar{\gamma}\end{math}}(7);
             \node(r)at(1.00,1.41){};
@@
             %
-            \node[fit=(3)(5),rotate fit=0,inner sep=0pt,
-                rounded corners,draw=Col5!80]{};
-            \node[fit=(7)(9),rotate fit=0,inner sep=0pt,
-                rounded corners,draw=Col5!80]{};
-            \node[fit=(11)(13),rotate fit=0,inner sep=0pt,
-                rounded corners,draw=Col5!80]{};
+            %\node[fit=(3)(5),rotate fit=0,inner sep=0pt,
+                %rounded corners,draw=Col5!80]{};
+            %\node[fit=(7)(9),rotate fit=0,inner sep=0pt,
+                %rounded corners,draw=Col5!80]{};
+            %\node[fit=(11)(13),rotate fit=0,inner sep=0pt,
+                %rounded corners,draw=Col5!80]{};
         \end{tikzpicture}
@@
   The tuple $\LatCAs$ is a lattice, where $\InfCAs$ and $\SupCAs$ are
-  defined, for any positive integers $\gamma$ and $\gamma'$, as follows:
+  defined, for any positive integers $\gamma$ and $\gamma'$, by
     \begin{equation}
-      \CAs{\gamma}\InfCAs\CAs{\gamma'}=\CAs{\gcd \left(\gamma-1, \gamma'-1\right)}
+      \CAs{\gamma}\InfCAs\CAs{\gamma'}
+      =\CAs{\gcd \left(\bar{\gamma}, \bar{\gamma'}\right)}
     \end{equation}
@@
     \begin{equation}
-      \CAs{\gamma}\SupCAs\CAs{\gamma'}=\CAs{\lcm \left(\gamma-1, \gamma'-1\right)}.
+      \CAs{\gamma}\SupCAs\CAs{\gamma'}
+      =\CAs{\lcm \left(\bar{\gamma}, \bar{\gamma'}\right)}.
     \end{equation}
@@
     The inclusion
-  $\iota:\left(\KCAsAll,\OrdCAs\right)\to\left(\QMag,\OrdQMag\right)$ is
-  non decreasing. In particular, for any positive integers $\gamma$ and
-  $\gamma'$, we have
+    \begin{math}
+        \iota:\left(\KCAsAll,\OrdCAs\right)
+        \to
+        \left(\QMag,\OrdQMag\right)
+    \end{math}
+    is nondecreasing. In particular, for any positive integers $\gamma$
+    and $\gamma'$, we have
     \begin{equation} \label{equ:comparison_of_lattice_operations}
-    \KCAs{\gcd \left(\gamma-1, \gamma'-1\right)}\OrdQMag
+        \KCAs{\gcd \left(\bar{\gamma}, \bar{\gamma'}\right)}
+        \OrdQMag
         \KCAs{\gamma}\InfQMag\KCAs{\gamma'}
@@
     \begin{equation}
-    \KCAs{\gamma}\SupQMag\KCAs{\gamma'}\OrdQMag
-    \KCAs{\lcm \left(\gamma-1, \gamma'-1\right)}.
+        \KCAs{\gamma}\SupQMag\KCAs{\gamma'}
+        \OrdQMag
+        \KCAs{\lcm \left(\bar{\gamma}, \bar{\gamma'}\right)}.
     \end{equation}
-
 \end{Theorem}
@@
 From Proposition~\ref{prop:PBW_basis_CAs_3}, and by using a result
-of~\cite{Gir18} describing a system of equations for the generating
-series of syntax trees avoiding some sets of subtrees, we obtain the
-following result.
+of~\cite{Gir18} (see also~\cite{Row10,KP15}) describing a system of
+equations for the generating series of syntax trees avoiding some sets
+of subtrees, we obtain the following result.
 \medbreak

### 2018-07-19 Operads_rewrite.tex
Petites modifs

@@
 linear operads, mainly by substituting Cartesian products $\times$ of
-sets with tensor products $\otimes$ of spaces, maps with maps, operad
-congruences with operad ideals, and cardinalities of sets with space
-dimensions (for instance in~\eqref{equ:hilbert_series}). Besides, when
-$\Oca$ is a linear operad admitting a basis $B$ such that its unit
-$\Unit$ belongs to $B$ and all partial composition maps are internal in
-$B$, $\Oca$ can be studied as a set-theoretic operad. 
+sets with tensor products $\otimes$ of spaces, maps with linear maps,
+operad congruences with operad ideals, and cardinalities of sets with
+space dimensions (for instance in~\eqref{equ:hilbert_series}).
+If $\Oca$ is an operad in the category of sets, we denote by
+$\K \Angle{\Oca}$ the corresponding linear operad defined on the
+linear span of $\Oca$, where the partial composition maps of $\Oca$ are
+extended by linearity on $\K \Angle{\Oca}$. Conversely, when $\Oca$ is
+a linear operad admitting a basis $B$ such that its unit $\Unit$
+belongs to $B$ and all partial composition maps are internal in $B$,
+$\Oca = \K \Angle{B}$ and this operad can be studied as a
+set-theoretic operad~$B$.
 \medbreak
@@
 A \Def{normal form} for $\RewContext$ is a binary tree $\Tfr$ such
-that for all binary tree $\Tfr'$, $\Tfr \RewContextRT \Tfr'$ implies
+that for all binary trees $\Tfr'$, $\Tfr \RewContextRT \Tfr'$ implies
 $\Tfr' = \Tfr$. In other words, a normal form for $\RewContext$ is a
@@
     branching trees for $\RewContext$.
+    \smallbreak
+
     \item \label{item:loop_start_buchberger}
@@
     is $\Rew'$.
+    \smallbreak
+
     \item Otherwise, let $\Tfr$ be the branching tree for $\RewContext'$
-    with the minimal degree and the minimal prefix word and remove $\Tfr$
-    from $\BranchingTrees$.
+    with the minimal degree and which is minimal with respect to the
+    order $\leq$. Remove $\Tfr$ from $\BranchingTrees$.
+    \smallbreak
+
     \item Let $\{\Sfr_1, \Sfr_2\}$ be the branching pair for $\Tfr$ such
-    that $\Sfr_1$ and $\Sfr_2$ have the minimal prefix words.
-  \item Let $\overline{\Sfr_1}$ and $\overline{\Sfr_2}$ be normal forms of
-    $\Sfr_1$ and $\Sfr_2$, respectively.
+    that $\Sfr_1$ and $\Sfr_2$ are minimal with respect to the
+    order $\leq$.
+    \smallbreak
+
+    \item Let $\overline{\Sfr_1}$ and $\overline{\Sfr_2}$ be two
+    different normal forms of $\Sfr_1$ and $\Sfr_2$, respectively.
+    \smallbreak
+
     \item \label{item:new_rewrite_rule_buchberger}
-    If $\overline{\Sfr_1}$ is different from $\overline{\Sfr_2}$, add
-    to $\Rew'$ the rewrite rule
+    Add to $\Rew'$ the rewrite rule
     \begin{math}
@@
     \end{math}
+    \smallbreak
+
     \item Add to $\BranchingTrees$ all new branching trees of degrees at
@@
     Step~\ref{item:new_rewrite_rule_buchberger}.
+    \smallbreak
+
     \item Go to Step~\ref{item:loop_start_buchberger}.

### 2018-07-19 Magmatic_operads.tex
Relecture partie 2

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Linear magmatic operads}
 \label{sec:Magmatic_operads}
-
 In this section, we equip the set of quotients of the linear magmatic
@@
 analog for this lattice.
+\medbreak
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Lattice of linear magmatic quotients}
+The \Def{linear magmatic operad}, written $\KMag$, is the free linear
+operad over one binary generator. By definition, for each arity $n$,
+$\KMag(n)$ is the vector space with basis $\Mag(n)$, and the
+compositions maps of $\KMag$ extend by linearity the ones of $\Mag$.
+\medbreak
 
-Throughout Section~\ref{sec:Magmatic_operads}, we fix a commutative field
-$\K$. The \Def{linear magmatic operad}, written $\KMag$, is the free
-linear operad over one binary generator. For each arity $n$, $\KMag(n)$
-is the vector space with basis $\Mag(n)$, and the compositions of $\KMag$
-extend by linearity the ones of $\Mag$.
-
-We denote by $\IMag$ the set of operadic ideals of $\KMag$, and
+We denote by $\IMag$ the set of operadic ideals of $\KMag$, and we set
 \begin{equation} \label{equ:definition_of_QMag}
-  \QMag =\Big\{\KMag/ I\mid I\in\IMag\Big\},
+    \QMag := \Big\{\KMag/_I :  I\in\IMag\Big\},
 \end{equation}
-the set of quotients of the linear magmatic operad. Given two elements
-$\Oca_1$ and $\Oca_2$ of $\QMag$, we denote by
-$\text{hom}\left(\Oca_1,\Oca_2\right)$ the set of operads morphism from
-$\Oca_1$ to $\Oca_2$.
+as the set of the quotients of the linear magmatic operad. Given
+$\KMag/_I \in \QMag$ and $x \in \KMag$, we denote by $[x]_I$ the
+$I$-equivalence of $x$. Observe that $\KMag/_I$ is generated as an
+operad by $[\Product]_I$. Moreover, given two  elements $\Oca_1$ and
+$\Oca_2$ of $\QMag$, we denote by $\Hom\left(\Oca_1,\Oca_2\right)$ the
+set of operad morphism from $\Oca_1$ to~$\Oca_2$.
+\medbreak
 
 \begin{Proposition} \label{prop:endomorphisms_of_magmatic_operads}
-  The set $\emph{hom}\left(\Oca_1,\Oca_2\right)$ admits a vector space
-  structure. Moreover, its dimension is equal to $0$ or $1$ and every
-  nonzero morphism is surjective.
+    For any $\Oca_1, \Oca_2 \in \QMag$, the set
+    $\Hom\left(\Oca_1,\Oca_2\right)$ admits a vector space structure.
+    Moreover, its dimension is equal to $0$ or $1$ and every nonzero
+    morphism is surjective.
 \end{Proposition}
-
 \begin{proof}
-  The operad $\Oca_1$ is spanned by the binary generator
-  $[\Product]_{I_1}$, which is the class of the element
-  $\Product\in\KMag$ in $\Oca_1$. Hence, a morphism
-  $\varphi:\Oca_1\to\Oca_2$ is uniquely determined by
-  $\varphi\left([\Product]_{I_1}\right)$. Moreover,
-  $\varphi\left([\Product]_{I_1}\right)$ has arity $2$ in $\Oca_2$.
-  Hence, $\varphi\left([\Product]_{I_1}\right)$ belongs to the line
-  spanned by the binary generator of $\Oca_2$, that is there exists a
-  scalar $\lambda\in\K$ such that $\varphi\left([\Product]_{I_1}\right)
-  =\lambda[\Product]_{I_2}$. If there exists such a $\lambda$ different
-  from zero, then for every nonzero scalar $\mu$, we have a well-defined
-  operad morphism $\psi:\Oca_1\to\Oca_2$ satisfying
-  $\psi([\Product]_{I_1}) =\mu[\Product]_{I_2}=
-  \left(\mu/\lambda\right)\varphi([\Product]_{I_1})$. Hence,
-  $\text{hom}\left(\Oca_1,\Oca_2\right)$ is either reduced to the zero
-  morphism or it is in one-to-one correspondance with $\K$, which proves
-  that $\text{hom}\left(\Oca_1,\Oca_2\right)$ is a vector space of
+    Let $I_1, I_2 \in \IMag$ such that $\Oca_1 = \KMag/_{I_1}$ and
+    $\Oca_2 = \KMag/_{I_2}$. Since $\Oca_1$ is generated by the binary
+    element $[\Product]_{I_1}$, a morphism $\varphi:\Oca_1\to\Oca_2$ is
+    uniquely determined by $\varphi\left([\Product]_{I_1}\right)$.
+    Moreover, $\varphi\left([\Product]_{I_1}\right)$ has arity $2$ in
+    $\Oca_2$. Hence, $\varphi\left([\Product]_{I_1}\right)$ belongs to
+    the line spanned by the binary generator of $\Oca_2$, that is there
+    exists a scalar $\lambda\in\K$ such that
+    \begin{math}
+        \varphi\left([\Product]_{I_1}\right)
+        = \lambda[\Product]_{I_2}.
+    \end{math}
+    If there exists such a $\lambda$ different from zero, then for every
+    nonzero scalar $\mu$, we have a well-defined operad morphism
+    $\psi:\Oca_1\to\Oca_2$ satisfying
+    \begin{math}
+        \psi([\Product]_{I_1}) =\mu[\Product]_{I_2}
+        = \left(\mu/\lambda\right)\varphi([\Product]_{I_1}).
+    \end{math}
+    Hence, $\Hom\left(\Oca_1,\Oca_2\right)$ is either reduced to the
+    zero morphism or it is in one-to-one correspondence with $\K$, which
+    proves that $\Hom\left(\Oca_1,\Oca_2\right)$ is a vector space of
     dimension at most $1$. Moreover, if $\varphi$ is different from $0$,
-  that is there is a nonzero scalar such that $\varphi([\Product]_{I_1})
-  =\lambda[\Product]_{I_2}$, we have $\varphi(1/\lambda[\Product]_{I_1})
-  =[\Product]_{I_2}$, so that $\varphi$ is surjective.
+    that is there is a nonzero scalar such that
+    $\varphi([\Product]_{I_1}) =\lambda[\Product]_{I_2}$, we have
+    $\varphi(1/\lambda[\Product]_{I_1}) =[\Product]_{I_2}$, so that
+    $\varphi$ is surjective.
 \end{proof}
+\medbreak
 
@@
 have $\Oca_2\OrdQMag\Oca_1$ if the dimension of
-$\text{hom}\left(\Oca_1,\Oca_2\right)$ is equal to $1$.
+$\Hom\left(\Oca_1,\Oca_2\right)$ is equal to~$1$.
+\medbreak
 
 \begin{Proposition} \label{prop:order_relations_on_QMag_and_ideals}
-  Let $\Oca_1=\KMag/I_1$ and $\Oca_2=\KMag/I_2$ be two elements of
-  $\QMag$.   We have $\Oca_2\OrdQMag\Oca_1$ if and only if
+    Let $\Oca_1=\KMag/_{I_1}$ and $\Oca_2=\KMag/_{I_2}$ be two operads
+    of $\QMag$. We have $\Oca_2\OrdQMag\Oca_1$ if and only if
     $I_1\subseteq I_2$.
 \end{Proposition}
-
 \begin{proof}
-  Since $\text{hom}\left(\Oca_1,\Oca_2\right)$ is a vector space of
-  dimension at most $1$, it contains a nonzero morphism if and only if
+  Since, by Proposition~\ref{prop:endomorphisms_of_magmatic_operads},
+  $\Hom\left(\Oca_1,\Oca_2\right)$ is a vector space of
+  dimension at most~$1$, it contains a nonzero morphism if and only if
   the morphism $\overline{\varphi}:\Oca_1\to\Oca_2$ satisfying
@@
 \end{proof}
+\medbreak
 
-Recall that a \Def{lattice} is a tuple $\left(E,\leq,\wedge,\vee\right)$,
-where $\left(E,\leq\right)$ is a poset such that any two elements $e$
-and $e'$ of $E$ admit a lower-bound $e\wedge e'$ and an upper-bound
-$e\vee e'$. In particular, $\left(\IMag,\subseteq,\cap,+\right)$ is a
-lattice, where $\cap$ and $+$ are the intersection and the sum of
-operadic ideals, respectively.
+Recall that a \Def{lattice} is a tuple
+$\left(E,\leq,\wedge,\vee\right)$, where $\left(E,\leq\right)$ is a
+poset such that any two elements $e$ and $e'$ of $E$ admit a lower-bound
+$e\wedge e'$ and an upper-bound $e\vee e'$. In particular,
+$\left(\IMag,\subseteq,\cap,+\right)$ is a lattice, where $\cap$ and $+$
+are the intersection and the sum of operadic ideals, respectively.
+\medbreak
 
-Given two elements $\Oca_1=\KMag/I_1$ and $\Oca_2=\KMag/I_2$ of $\QMag$,
-we let
+Given two operad $\Oca_1=\KMag/_{I_1}$ and $\Oca_2=\KMag/_{I_2}$ of
+$\QMag$, let us define
 \begin{equation} \label{equ:definition_of_lattice_operations_of_QMag}
-  \Oca_1\InfQMag \Oca_2=\KMag/\left(I_1+I_2\right)\ \ \text{and}\ \
-  \Oca_1\SupQMag \Oca_2=\KMag/\left(I_1\cap I_2\right).
+    \Oca_1\InfQMag \Oca_2 := \KMag/_{I_1+I_2}
+    \qquad \mbox{and} \qquad
+    \Oca_1\SupQMag \Oca_2 := \KMag/_{I_1\cap I_2}.
 \end{equation}
-Explicitely, for every integer $n$, $\left(\Oca_1\InfQMag\Oca_2\right)(n)$
-(respectively, $\left(\Oca_1\SupQMag\Oca_2\right)(n)$) is the quotient of
-vector spaces $\KMag(n)/\left(I_1(n)+I_2(n)\right)$ (respectively,
-$\KMag(n)/\left(I_1(n)\cap I_2(n)\right)$).
+Explicitly, for every positive integer $n$,
+$\left(\Oca_1\InfQMag\Oca_2\right)(n)$ (resp.
+$\left(\Oca_1\SupQMag\Oca_2\right)(n)$) is the quotient of vector spaces
+$\KMag(n)/_{I_1(n)+I_2(n)}$ (resp.
+$\KMag(n)/_{I_1(n)\cap I_2(n)}$).
+\medbreak
 
@@
 \end{Theorem}
-
 \begin{proof}
-  The map $\mathcal{Q}:\IMag\to\QMag$ defined by $\mathcal{Q}(I)=\KMag/I$
-  is a bijection by definition of $\QMag$. Moreover, from
+    The map $\mathcal{Q}:\IMag\to\QMag$ defined by
+    $\mathcal{Q}(I) := \KMag/_I$ is a bijection by definition of
+    $\QMag$. Moreover, from
     Proposition~\ref{prop:order_relations_on_QMag_and_ideals},
@@
     $\left(\QMag,\OrdQMag\right)$ is a poset and $\mathcal{Q}$ is a
-  decreasing bijection. The tuple $\left(\IMag,\subseteq,\cap,+\right)$
-  being a lattice, the decreasing bijection $\mathcal{Q}$ induces
-  lattice operations on $\QMag$, precisely $\InfQMag$ and $\SupQMag$ by
-  definition.
+    decreasing bijection. The tuple
+    $\left(\IMag,\subseteq,\cap,+\right)$ being a lattice, the
+    decreasing bijection $\mathcal{Q}$ induces lattice operations on
+    $\QMag$, precisely $\InfQMag$ and $\SupQMag$ by definition.
 \end{proof}
+\medbreak
 
@@
 \subsection{Hilbert series and linear magmatic quotients}
+In order to show the Grassmann formula analog for $\LatQMag$, we need the
+following lemma.
+\medbreak
 
-In order to show the Grassman formula analog for $\LatQMag$, we need the
-following lemma.
-
-\begin{Lemma} \label{lem:lattice_structure_and_coefficients_of_Hiblert_series}
-  Let $\Oca_1$ and $\Oca_2$ be two elements of $\QMag$. For every integer
-  $n$, we have
-  \begin{equation} \label{equ:lattice_structure_and_coefficients_of_the_Hiblert_series}
-    \dim{\left(\Oca_1\InfQMag\Oca_2(n)\right)}+
-    \dim{\left(\Oca_1\SupQMag\Oca_2(n)\right)}=
+\begin{Lemma}
+    \label{lem:lattice_structure_and_coefficients_of_Hiblert_series}
+    Let $\Oca_1$ and $\Oca_2$ be two operads of $\QMag$. For every
+    positive integer $n$, we have
+    \begin{equation}
+    \label{equ:lattice_structure_and_coefficients_of_the_Hiblert_series}
+        \dim{\left(\left(\Oca_1\InfQMag\Oca_2\right)(n)\right)}+
+        \dim{\left(\left(\Oca_1\SupQMag\Oca_2\right)(n)\right)}=
         \dim{\left(\Oca_1(n)\right)}+\dim{\left(\Oca_2(n)\right)}.
@@
 \end{Lemma}
-
 \begin{proof}
-  Let $I_1$ and $I_2$ be the two operadic ideals of $\KMag$ such that
-  $\Oca_1$ and $\Oca_2$ are equal to $\KMag/I_1$ and $\KMag/I_2$,
-  respectively. For every integer $n$, we have
-  \[\begin{split}
+    Let $I_1, I_2 \in \IMag$ such that $\Oca_1 = \KMag/_{I_1}$ and
+    $\Oca_2 = \KMag/_{I_2}$. For every integer $n$, we have
+    \begin{equation}\begin{split}
         &\dim{\left(\Oca_1\InfQMag\Oca_2(n)\right)}+
             \dim{\left(\Oca_1\SupQMag\Oca_2(n)\right)}\\
-  &=\dim{\Big(\KMag(n)/\left(I_1+I_2\right)(n)\Big)}+
-  \dim{\Big(\KMag(n)/\left(I_1\cap I_2\right)(n)\Big)}\\
+        &=\dim{\Big(\KMag(n)/_{\left(I_1+I_2\right)(n)}\Big)}+
+            \dim{\Big(\KMag(n)/_{\left(I_1\cap I_2\right)(n)}\Big)}\\
         &=\dim{\left(\KMag(n)\right)}-\dim{\left(I_1(n)+I_2(n)\right)}
-  +\dim{\left(\KMag(n)\right)}-\dim{\left(I_1(n)\cap I_2(n)\right)}\\
-  &=\dim{\left(\KMag(n)\right)}-\dim{\left(I_1(n)\right)}+
-  \dim{\left(\KMag(n)\right)}-\dim{\left(I_2(n)\right)}\\
-  &=\dim{\Big(\KMag(n)/I_1(n)\Big)}+\dim{\Big(\KMag(n)/I_2(n)\Big)}\\
+            +\dim{\left(\KMag(n)\right)}
+            -\dim{\left(I_1(n)\cap I_2(n)\right)} \\
+        &=\dim{\left(\KMag(n)\right)}-\dim{\left(I_1(n)\right)}
+            + \dim{\left(\KMag(n)\right)}-\dim{\left(I_2(n)\right)}\\
+        &=\dim{\Big(\KMag(n)/_{I_1(n)}\Big)}
+            +\dim{\Big(\KMag(n)/_{I_2(n)}\Big)}\\
         &=\dim{\left(\Oca_1(n)\right)}+\dim{\left(\Oca_2(n)\right)}.
-  \end{split}\]
+    \end{split}\end{equation}
     The third equality is due to the Grassmann formula applied to the
@@
 \end{proof}
+\medbreak
 
-The Grassman formula analog for $\LatQMag$ is given by the following
-theorem.
+The Grassmann formula analog for $\LatQMag$ is given by the following
+statement.
+\medbreak
 
-\begin{Theorem} \label{thm:Grassmann_formula_for__Hilbert_series_of_QMag}
-  Let $\Oca_1$ and $\Oca_2$ be two elements of $\QMag$. We have
+\begin{Theorem}
+    \label{thm:Grassmann_formula_for__Hilbert_series_of_QMag}
+    Let $\Oca_1$ and $\Oca_2$ be two operads of $\QMag$. We have
     \begin{equation} \label{equ:lattice_structure_and_Hiblert_series}
-    \HilbertSeries_{\Oca_1\InfQMag\Oca_2}(t)+\HilbertSeries_{\Oca_1\SupQMag\Oca_2}(t)=\HilbertSeries_{\Oca_1}(t)+\HilbertSeries_{\Oca_2}(t).
+        \HilbertSeries_{\Oca_1\InfQMag\Oca_2}(t)
+        +\HilbertSeries_{\Oca_1\SupQMag\Oca_2}(t)
+        =\HilbertSeries_{\Oca_1}(t)+\HilbertSeries_{\Oca_2}(t).
     \end{equation}
 \end{Theorem}
-
 \begin{proof}
     We have
-  \[\begin{split}
-  \HilbertSeries_{\Oca_1\InfQMag\Oca_2}(t)+\HilbertSeries_{\Oca_1\SupQMag\Oca_2}(t)&=\sum_{n\in\N}\dim{\left(\Oca_1\InfQMag\Oca_2(n)\right)}t^n+\sum_{n\in\N}\dim{\left(\Oca_1\SupQMag\Oca_2(n)\right)}t^n\\
-  &=\sum_{n\in\N}\Big(\dim{\left(\Oca_1\InfQMag\Oca_2(n)\right)}+\dim{\left(\Oca_1\SupQMag\Oca_2(n)\right)}\Big)t^n\\
-  &=\sum_{n\in\N}\Big(\dim{\left(\Oca_1(n)\right)}+\dim{\left(\Oca_2(n)\right)}\Big)t^n\\
-  &=\sum_{n\in\N}\dim{\left(\Oca_1(n)\right)}t^n+\sum_{n\in\N}\dim{\left(\Oca_2(n)\right)}t^n\\
-  &=\HilbertSeries_{\Oca_1}(t)+\HilbertSeries_{\Oca_2}(t).
-  \end{split}\]
+    \begin{equation}\begin{split}
+        \HilbertSeries_{\Oca_1\InfQMag\Oca_2}(t)
+        +\HilbertSeries_{\Oca_1\SupQMag\Oca_2}(t)&
+        =\sum_{n\in\N}\dim{\left(\left(\Oca_1\InfQMag\Oca_2\right)(n)
+            \right)}t^n
+            +\sum_{n\in\N}\dim{\left(\left(\Oca_1\SupQMag\Oca_2\right)
+            (n)\right)}t^n\\
+        &=\sum_{n\in\N}\Big(\dim{\left(\Oca_1\InfQMag\Oca_2(n)\right)}
+            +\dim{\left(\left(\Oca_1\SupQMag\Oca_2\right)(n)
+        \right)}\Big)t^n\\
+        &=\sum_{n\in\N}\Big(\dim{\left(\Oca_1(n)\right)}
+            +\dim{\left(\Oca_2(n)\right)}\Big)t^n\\
+        &=\sum_{n\in\N}\dim{\left(\Oca_1(n)\right)}t^n+\sum_{n\in\N}
+            \dim{\left(\Oca_2(n)\right)}t^n\\
+        &=\HilbertSeries_{\Oca_1}(t)+\HilbertSeries_{\Oca_2}(t),
+    \end{split}\end{equation}
+    where the third equality is due to
+    Lemma~\ref{lem:lattice_structure_and_coefficients_of_Hiblert_series}.
 \end{proof}
-The third equality is due to Lemma~\ref{lem:lattice_structure_and_coefficients_of_Hiblert_series}.
+\medbreak
+
 % Hilbert series, enumeration, a little of rewrite systems, etc.

### 2018-07-19 Operads_rewrite.tex
Relecture partie 2

@@
 The operad $\Mag$ can be seen as the free operad generated by one binary
-element. It satisfies the following universality property. Let
+element~$\Product$. It satisfies the following universality property.
+Let
 \begin{math}
-    \GeneratingSet := \GeneratingSet(2) := \{\Product\}
+    \GeneratingSet := \GeneratingSet(2) := \left\{\Product'\right\}
 \end{math}
-be the graded set containing exactly one element $\Product$ of arity
+be the graded set containing exactly one element $\Product'$ of arity
 $2$. For any operad $\Oca$ and any map
@@
 $f = \phi \circ \Corolla$, where $\Corolla$ is the map sending
-$\Product$ to the unique binary tree of degree $1$ (and then, arity
+$\Product'$ to the unique binary tree of degree $1$ (and then, arity
 $2$). In other terms, the diagram

### 2018-07-20 CAs_operads.tex
Modifications après relecture des deux premières sections

@@
 \begin{Lemma} \label{lem:first_dimensions_CAs}
-    For any positive integers $\gamma$ and $n$ such that $\gamma \geq 2$
+    For all positive integers $\gamma$ and $n$ such that $\gamma \geq 2$
     and $n \leq \gamma + 1$,
@@
   The tuple $\LatCAs$ is a lattice, where $\InfCAs$ and $\SupCAs$ are
-  defined, for any positive integers $\gamma$ and $\gamma'$, by
+  defined, for all positive integers $\gamma$ and $\gamma'$, by
     \begin{equation}
@@
 
-\begin{Remark}
   The lattice $\left(\N,\mid, \gcd, \lcm\right)$ admits $1$ as minimum
@@
   $\As$ and is a quotient of $\Mag$.
-\end{Remark}
 
@@
     \end{math}
-    is nondecreasing. In particular, for any positive integers $\gamma$
+    is nondecreasing. In particular, for all positive integers $\gamma$
     and $\gamma'$, we have
@@
 
-\begin{Remark}
   Note that $\LatKCAs$ does not embed into a sub-lattice of $\LatQMag$,
@@
   relations $\LComb{3}-\RComb{3}$ and $\LComb{4}-\RComb{4}$.
-\end{Remark}
 

### 2018-07-20 Magmatic_operads.tex
Modifications après relecture des deux premières sections

@@
 $\Oca_2$ of $\QMag$, we denote by $\Hom\left(\Oca_1,\Oca_2\right)$ the
-set of operad morphism from $\Oca_1$ to~$\Oca_2$.
+set of linear operad morphism from $\Oca_1$ to~$\Oca_2$.
 \medbreak
@@
 \begin{proof}
-    The map $\mathcal{Q}:\IMag\to\QMag$ defined by
-    $\mathcal{Q}(I) := \KMag/_I$ is a bijection by definition of
-    $\QMag$. Moreover, from
+  The map $\Oca:\IMag\to\QMag$ defined by $\Oca(I) := \KMag/_I$ is a
+  bijection by definition of $\QMag$. Moreover, from
     Proposition~\ref{prop:order_relations_on_QMag_and_ideals},
     $\Oca_2\OrdQMag\Oca_1$ is equivalent to $I_1\subseteq I_2$, so that
-    $\left(\QMag,\OrdQMag\right)$ is a poset and $\mathcal{Q}$ is a
-    decreasing bijection. The tuple
-    $\left(\IMag,\subseteq,\cap,+\right)$ being a lattice, the
-    decreasing bijection $\mathcal{Q}$ induces lattice operations on
-    $\QMag$, precisely $\InfQMag$ and $\SupQMag$ by definition.
+    $\left(\QMag,\OrdQMag\right)$ is a poset and $\Oca$ is a decreasing
+    bijection. The tuple $\left(\IMag,\subseteq,\cap,+\right)$ being a
+    lattice, the decreasing bijection $\mathcal{Q}$ induces lattice
+    operations on $\QMag$, precisely $\InfQMag$ and $\SupQMag$ by
+    definition.
 \end{proof}

### 2018-07-20 Operads_rewrite.tex
Modifications après relecture des deux premières sections

@@
 
-When for any binary trees $\Tfr$, $\Sfr_1$, and $\Sfr_2$ such that
+When for all binary trees $\Tfr$, $\Sfr_1$, and $\Sfr_2$ such that
 $\Tfr \RewContextRT \Sfr_1$ and $\Tfr \RewContextRT \Sfr_2$, there
@@
 
-    \item Otherwise, let $\Tfr$ be the branching tree for $\RewContext'$
-    with the minimal degree and which is minimal with respect to the
-    order $\leq$. Remove $\Tfr$ from $\BranchingTrees$.
+  \item Otherwise, let $\Tfr$ be a branching tree for $\RewContext'$.
+    Remove $\Tfr$ from $\BranchingTrees$.
     \smallbreak
 
-    \item Let $\{\Sfr_1, \Sfr_2\}$ be the branching pair for $\Tfr$ such
-    that $\Sfr_1$ and $\Sfr_2$ are minimal with respect to the
-    order $\leq$.
+    \item Let $\{\Sfr_1, \Sfr_2\}$ be a branching pair for $\Tfr$.
     \smallbreak
 
-    \item Let $\overline{\Sfr_1}$ and $\overline{\Sfr_2}$ be two
-    different normal forms of $\Sfr_1$ and $\Sfr_2$, respectively.
+  \item Let $\overline{\Sfr_1}$ and $\overline{\Sfr_2}$ be normal forms
+    of $\Sfr_1$ and $\Sfr_2$, respectively.
     \smallbreak
@@
     \item \label{item:new_rewrite_rule_buchberger}
-    Add to $\Rew'$ the rewrite rule
+      If $\overline{\Sfr_1}$ is different from $\overline{\Sfr_2}$, add
+      to $\Rew'$ the rewrite rule
     \begin{math}

### 2018-07-20 Magmatic_operads.tex
Ajout preuve de l'injectivité de \Oca

@@
 \begin{proof}
-  The map $\Oca:\IMag\to\QMag$ defined by $\Oca(I) := \KMag/_I$ is a
-  bijection by definition of $\QMag$. Moreover, from
+  First, we observe that the map $\Oca:\IMag\to\QMag$ defined by
+  $\Oca(I) :=\KMag/_I$ is a bijection: it is surjective by definition of
+  $\QMag$ and it is injective since $\Oca(I_1)=\Oca(I_2)$ implies that
+  the kernel of the natural projection $\KMag\to\Oca(I_1)=\Oca(I_2)$ is
+  both equal to $I_1$ and $I_2$. Moreover, from
   Proposition~\ref{prop:order_relations_on_QMag_and_ideals},
@@
   bijection. The tuple $\left(\IMag,\subseteq,\cap,+\right)$ being a
-    lattice, the decreasing bijection $\mathcal{Q}$ induces lattice
-    operations on $\QMag$, precisely $\InfQMag$ and $\SupQMag$ by
-    definition.
+  lattice, the decreasing bijection $\Oca$ induces lattice operations on
+  $\QMag$, precisely $\InfQMag$ and $\SupQMag$ by definition.
 \end{proof}

### 2018-08-06 Operads_rewrite.tex
Ajout demo lemme terminaison

@@
 defined, for any $x \in \Oca(n)$ and $y_1, \dots, y_n \in \Oca$, by
-\begin{equation}
+\begin{equation} \label{equ:complete_composition}
     x \circ \left[y_1, \dots, y_n\right] :=
@@
 \Def{rewrite relation induced} by $\Rew$. Formally we have
-\begin{equation}
+\begin{equation} \label{equ:rewrite_relation_induced}
     \Tfr \circ_i
@@
 \begin{proof}
-    \Todo{à faire}
-    % 1. Montrer la compatibilité des compo aux mots prefixes
-    % 2. Supposer qu'il existe une chaine infinie de reecritures
-    % 3. Absurde car il n'existe qu'un nombre fini de mots sur {0, 2}.
+    Observe first that for any binary trees $\Tfr$ and $\Sfr$, the
+    prefix word of $\Tfr \circ_i \Sfr$ is obtained by replacing the
+    $i$th $\Zero$ of $\PrefixWord(\Tfr)$ by $\PrefixWord(\Sfr)$. For
+    this reason, and due to the
+    definition~\eqref{equ:complete_composition} of $\circ$, for any
+    binary trees $\Sfr$ and $\Rfr_1, \dots, \Rfr_n$ where $n$ is the
+    arity of $\Sfr$, the prefix word of
+    $\Sfr \circ \left[\Rfr_1, \dots, \Rfr_n\right]$ is obtained by
+    replacing from right to left each $\Zero$ of $\PrefixWord(\Sfr)$ by
+    the prefix words of each $\Rfr_i$. This, together with the
+    definition~\eqref{equ:rewrite_relation_induced} of the rewrite
+    relation $\RewContext$ induced by $\Rew$ and the hypothesis of the
+    statement of the lemma, implies that if $\Tfr$ and $\Tfr'$ are two
+    binary trees such that $\Tfr \RewContext \Tfr'$,
+    $\PrefixWord(\Tfr) > \PrefixWord\left(\Tfr'\right)$. This leads to
+    the fact that any chain
+    \begin{math}
+        \Tfr_0 \Rew \Tfr_1 \Rew \Tfr_2 \Rew \cdots
+    \end{math}
+    is finite since
+    \begin{math}
+        \Tfr_0 > \Tfr_1 > \Tfr_2 > \cdots
+    \end{math}
+    and there is a finite number of binary trees of a fixed arity.
+    Therefore, $\RewContext$ is terminating.
 \end{proof}

### 2018-08-06 Operads_rewrite.tex
Ajout demo lemme formes normales evitement de motifs

@@
     Let $\Rew$ be a set of rewrite rules on $\Mag$ and $\RewContext$ be
-    the rewrite relation induced by $\Rew$. Then, if $\RewContext$ is
-    terminating, $\NormalForms_{\RewContext}$ is the set of all the
-    binary trees that avoid all the trees appearing as left members
-    of $\Rew$.
+    the rewrite relation induced by $\Rew$. Then,
+    %if $\RewContext$ is terminating,
+    $\NormalForms_{\RewContext}$ is the set of all the binary trees that
+    avoid all the trees appearing as left members of~$\Rew$.
 \end{Lemma}
 \begin{proof}
-    \Todo{à faire}
+    Assume first that $\Tfr$ is a binary tree avoiding all the trees
+    appearing as left members of~$\Rew$. Then, due to the
+    definition~\eqref{equ:rewrite_relation_induced} of $\RewContext$,
+    $\Tfr$ is not rewritable by $\RewContext$. Hence, $\Tfr$ is a normal
+    form for $\RewContext$. Conversely, assume that
+    $\Tfr \in \NormalForms_{\RewContext}$. In this case, by definition
+    of a normal form, $\Tfr$ is not rewritable by $\RewContext$, so that
+    $\Tfr$ does not admit any occurrence of a tree appearing as a left
+    member of~$\Rew$.
 \end{proof}

### 2018-08-06 Operads_rewrite.tex
Ajout demo lemme convergence

@@
 When $\RewContext$ is terminating and confluent, $\RewContext$ is said
-\Def{convergent}. We shall use the following result appearing
-in~\cite{Gir16} specialized on rewrite relations on $\Mag$ to prove that
+\Def{convergent}. We shall use the following result to prove that
 a terminating rewrite relation is convergent.
@@
 \begin{proof}
-    \Todo{à faire}
+    The statement of the lemma is the specialization on rewrite
+    relations on $\Mag$ of a more general result about rewrite relations
+    on trees contained in~\cite{Gir16}.
 \end{proof}

### 2018-08-22 CAs_operads.tex
Modifs
Reorganisation derniere partie
MAJ intro

@@
 be embedded into quotient operads $\KCAs{\gamma}$ of $\KMag$. Formally,
-the operad $\KCAs{\gamma}$ is equal to $\KMag/I_{\gamma}$, where
+the operad $\KCAs{\gamma}$ is equal to $\KMag/_{I_{\gamma}}$, where
 $I_{\gamma}$ is the operadic ideal of $\KMag$ generated by
@@
 
-\begin{Theorem}
+\begin{Theorem} \label{thm:inclusion_lattice_CAs}
     The inclusion
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The \texorpdfstring{$3$}{3}-comb associative operad}
-\label{sec:CAs_3}
+\subsection{The \texorpdfstring{$3$}{3}-comb associative operad}
+\label{subsec:CAs_3}
 We now focus on the study of the operad $\CAs{3}$. By definition, this

### 2018-08-22 Conclusion.tex
Modifs
MAJ intro

@@
 \section*{Perspectives}
+\Todo{S: mettre à jour}
+
+\Todo{S: parler aussi des généralisation avec $2\Mag$ (arbres de Schröder)}
+
 Our first axis of perspectives consists in collecting properties about
@@
 
+\Todo{S: Placer ces résultats expérimentaux dans la partie sur CAs}
+
 A second axis concerns a complete understanding of $\CAs{3}$. We can

### 2018-08-22 Introduction.tex
Modifications
MAJ intro

@@
 satisfying among others the associativity law
-\begin{math}
-    (x_1 \Product x_2) \Product x_3 = x_1 \Product (x_2 \Product x_3)
-\end{math}.
+\begin{equation}
+    \left(x_1 \Product x_2\right) \Product x_3
+    =
+    x_1 \Product \left(x_2 \Product x_3\right).
+\end{equation}
 It is well-known that the associative algebras are representations of
@@
 the quotient of the magmatic operad $\Mag$ (the free operad of binary
-trees on the binary generator~$\Product$) by the operad congruence
-$\Congr$ satisfying
+trees on the binary generator~$\Product$) by the operad
+congruence~$\Congr$ satisfying
 \begin{equation} \label{equ:congruence_as}
@@
 the Tamari order is a partial order on the set of the binary trees
-having a fixed number of internal nodes $d$. This order is generated by
-the covering relation consisting in rewriting a tree $\Tfr$ into a tree
-$\Tfr'$ by replacing a subtree of $\Tfr$ of the form of the left member
-of~\eqref{equ:congruence_as} into a tree of the form of the right member
-of~\eqref{equ:congruence_as}. This transformation is known in a computer
-science context as the right rotation operation~\cite{Knu98} and
-intervenes in algorithms involving binary search trees~\cite{AVL62}. The
-partial order hence generated by the right rotation operation is known
-as the Tamari order~\cite{Tam62} and has a lot of combinatorial and
-algebraic properties (see for instance~\cite{HT72,Cha06}).
+having a fixed number of internal nodes $\gamma$. This order is
+generated by the covering relation consisting in rewriting a tree $\Tfr$
+into a tree $\Tfr'$ by replacing a subtree of $\Tfr$ of the form of the
+left member of~\eqref{equ:congruence_as} into a tree of the form of the
+right member of~\eqref{equ:congruence_as}. This transformation is known
+in a computer science context as the right rotation
+operation~\cite{Knu98} and intervenes in algorithms involving binary
+search trees~\cite{AVL62}. The partial order hence generated by the
+right rotation operation is known as the Tamari order~\cite{Tam62} and
+has a lot of combinatorial and algebraic properties (see for
+instance~\cite{HT72,Cha06}).
 \medbreak
@@
 
-This work is intended to be a first strike in the study of the eventual
-links between the Tamari order and some quotients of the operad $\Mag$.
-In the long run, we would like to study quotients $\Mag/_{\Congr}$ of
-$\Mag$ where $\Congr$ is an operad congruence generated by equivalence
-classes of trees of a fixed degree. In particular, we would like to know
-if $\Congr$ is generated by equivalence classes of trees forming
-intervals of the Tamari order leads to algebraic properties for
-$\Mag/_{\Congr}$ (like the description of orientations of its space of
-relations, nice bases and Hilbert series).
+This work is intended to study and collect the possible links between
+the Tamari order and some quotients of the operad $\Mag$. In the long
+run, we would like to study quotients $\Mag/_{\Congr}$ of $\Mag$ where
+$\Congr$ is an operad congruence generated by equivalence classes of
+trees of a fixed degree (that is, a fixed number of internal nodes). In
+particular, we would like to know if the fact that $\Congr$ is generated
+by equivalence classes of trees forming intervals of the Tamari order
+implies algebraic properties for $\Mag/_{\Congr}$ (like the description
+of orientations of its space of relations, nice bases, and Hilbert
+series).
 \medbreak
 
-We focus here on one of these quotients $\CAs{3}$ which is the operad
-describing the category of the algebras equipped with a binary product
-$\Product$ and subjected to the relation
-\begin{math}
-    ((x_1 \Product x_2) \Product x_3) \Product x_4
+To explore this vast research area, we select to follow in this paper
+the following directions. First, we consider the very general set of the
+quotients of $\Mag$ seen as a operad in the category of vector spaces.
+We show that these operads form a lattice, wherein its partial order
+relation is defined from the existence of operad morphisms
+(Theorem~\ref{thm:lattice_structure_of_QMag}). We also provide a
+Grassmann formula analog relating the Hilbert series of the operads of
+the lattice together with their infima and suprema
+(Theorem~\ref{thm:Grassmann_formula_for_Hilbert_series_of_QMag}).
+Besides, we focus on a special kind of quotients of $\Mag$, denoted by
+$\CAs{\gamma}$, defined by equating the left and right comb binary trees
+of a fixed degree $\gamma \geq 1$. These operads are called comb
+associative operads. For instance, $\CAs{3}$ is the operad describing
+the category of the algebras equipped with a binary product $\Product$
+subjected to the relation
+\begin{equation}
+    \left(\left(x_1 \Product x_2\right) \Product x_3\right) \Product x_4
     =
-    x_1 \Product (x_2 \Product (x_3 \Product x_4))
-\end{math}.
-This is a kind of associativity law in higher degree $d = 3$. This
-operad is generated by an equivalence class of trees which is not an
-interval for the Tamari order. As preliminary computer experiments show,
-$\CAs{3}$ has oscillating first dimensions
+    x_1 \Product \left(x_2 \Product \left(x_3 \Product x_4\right)\right).
+\end{equation}
+This is a kind of associativity law in higher degree $\gamma = 3$ so
+that $\CAs{3}$ can be seen as a generalization of $\As$ (which is equal
+to $\CAs{2}$). We first provide general results about the operads
+$\CAs{\gamma}$. In particular, we show that these operads form a lattice
+contained in the lattice of quotients of $\Mag$ aforementioned
+(Theorems~\ref{thm:lattice_CAs} and~\ref{thm:inclusion_lattice_CAs}). We
+focus in particular on the study of $\CAs{3}$. Observe that the
+congruence of this operad is generated by an equivalence class of trees
+which is not an interval for the Tamari order. As preliminary computer
+experiments show, $\CAs{3}$ has oscillating first dimensions
 (see~\eqref{equ:dimensions_CAs_3}), what is rather unusual among all
-known operads. In this paper, we provide an orientation of the space of
-relations of $\CAs{3}$. For this, we use rewrite systems on
-trees~\cite{BN98} and the Buchberger algorithm for operads~\cite{DK10}.
+known operads. We provide an orientation of the space of relations of
+$\CAs{3}$ (Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}), a
+description of a basis of the operad, and prove that its Hilbert series
+is rational.
+%
+\Todo{S: et parler de la réalisation si Christophe l'ajoute ?}
+%
+For all these, we use rewrite systems on trees~\cite{BN98} and the
+Buchberger algorithm for operads~\cite{DK10}. Finally, we continue the
+investigation of the quotients of $\Mag$ by regarding the quotients of
+$\Mag$ obtained by equating two trees of degree $3$. This leads to ten
+quotient operads of $\Mag$. We provide for some of these combinatorial
+realizations, mostly in terms of integer compositions.
 \medbreak
@@
 This text is presented as follows. Section~\ref{sec:operad_Mag} contains
-preliminaries about the magmatic operad and rewrite relations on trees.
-In Section~\ref{sec:CAs_d}, we define the operad $\CAs{3}$ as a
-particular case of a more general construction of generalizations
-$\CAs{d}$, $d \geq 1$, of $\As$. Finally, Section~\ref{sec:CAs_3}
-contains the orientation of the space of relations of
-$\CAs{3}$ (Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}). As
-consequences, we obtain for $\CAs{3}$
-the description of one of its Poincaré-Birkhoff-Witt bases
-(Proposition~\ref{prop:PBW_basis_CAs_3}) and the description of
-its Hilbert series (Proposition~\ref{prop:Hilbert_series_CAs_3}).
+preliminaries about operads, binary trees, the magmatic operad, and
+rewrite systems on binary trees. We also prove and recall some important
+lemmas about rewrite systems on trees used thereafter. In
+Section~\ref{sec:Magmatic_operads}, we study the set of all the
+quotients of $\Mag$ seen as an operad in the category of sets and its
+lattice structure. Section~\ref{sec:CAs_d} is the heart of this article
+and is devoted to the study of the comb associative operads
+$\CAs{\gamma}$. Finally, Section~\ref{sec:MAg_3} presents our results
+about the quotients of $\Mag$ obtained by equating two trees of
+degree~$3$.
 \medbreak
+
+Some of the results presented here were announced in~\cite{CCG18}.
+\medbreak
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection*{General notations and conventions}
+For any integers $a$ and $c$, $[a, c]$ denotes the set
+$\{b \in \N : a \leq b \leq c\}$ and $[n]$, the set $[1, n]$. The
+cardinality of a finite set $S$ is denoted by~$\# S$.
+\medbreak

### 2018-08-22 Magmatic_operads.tex
MAJ intro

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Linear magmatic operads}
-\label{sec:Magmatic_operads}
+\section{Linear magmatic operads} \label{sec:Magmatic_operads}
 In this section, we equip the set of quotients of the linear magmatic
@@
 \begin{Theorem}
-    \label{thm:Grassmann_formula_for__Hilbert_series_of_QMag}
+    \label{thm:Grassmann_formula_for_Hilbert_series_of_QMag}
     Let $\Oca_1$ and $\Oca_2$ be two operads of $\QMag$. We have

### 2018-08-23 Article.tex
Rédaction première partie opérades magmatiques
Debut 1re section
Partie 1 (chantier)
Partie 1 chantier (suite)
Remarques de Cyrille sur partie 1
Modification algo de Buchberger
Harmonisation 3 premières sections
Ajout mini-intro section comb associative operads
Modifications
Petites modifs
Relecture partie 2
Modifications après relecture des deux premières sections
Quotients de Mag 3
Modifs
Ajout MSC
Reorganisation derniere partie
Rédaction abstract

@@
 % Creation: may. 2018
-% Modifications: may. 2018, june 2018
+% Modifications: may. 2018, june 2018, july 2018, aug. 2018
 
@@
 \usepackage{tikz}
+\usetikzlibrary{calc}
 \usetikzlibrary{shapes}
@@
 \usetikzlibrary{decorations.pathmorphing}
+\usetikzlibrary{arrows.meta}
 
@@
 
+% Mathematical symbols
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \keywords{Operad; trees; Rewrite rule; Presentation; Enumeration.}
-\subjclass[2010]{\Todo{}}
+\subjclass[2010]{18D50, 68Q42, 05C05.}
 \date{\today}
@@
 
+\newcommand{\Angle}[1]{\left\langle#1\right\rangle}
+
 \newcommand{\Oca}{\mathcal{O}}
+\newcommand{\Afr}{\mathfrak{a}}
 \newcommand{\Rfr}{\mathfrak{r}}
@@
 \newcommand{\Tfr}{\mathfrak{t}}
+\newcommand{\BranchingTrees}{\mathfrak{P}}
 
@@
 \newcommand{\Mag}{\mathsf{Mag}}
+\newcommand{\KMag}{\K \Angle{\Mag}}
+\newcommand{\QMag}{\mathcal{Q}\left(\KMag\right)}
+\newcommand{\IMag}{\mathcal{I}\left(\KMag\right)}
 \newcommand{\As}{\mathsf{As}}
-\newcommand{\CAs}[1]{\mathsf{CAs}^{(#1)}}
+\newcommand{\CAs}[1]{\mathsf{CAs}^{\left(#1\right)}}
 \newcommand{\CAsAll}{\mathbf{CAs}}
+\newcommand{\KCAs}[1]{\K\CAs{#1}}
+\newcommand{\KCAsAll}{\K\CAsAll}
 \newcommand{\PrefixWord}{\mathrm{p}}
 \newcommand{\Deg}{\mathrm{deg}}
-\newcommand{\LComb}[1]{\mathfrak{c}^{(#1)}_{\diagup}}
-\newcommand{\RComb}[1]{\mathfrak{c}^{(#1)}_{\diagdown}}
-\newcommand{\LBranch}{\mathrm{lb}}
+\newcommand{\LComb}[1]{\mathfrak{c}^{\left(#1\right)}_{\diagup}}
+\newcommand{\RComb}[1]{\mathfrak{c}^{\left(#1\right)}_{\diagdown}}
+\newcommand{\LRank}{\mathrm{lr}}
 \newcommand{\RBranch}{\mathrm{rb}}
 \newcommand{\Catalan}{\mathrm{cat}}
-\newcommand{\OrdCAs}{\preceq}
+\newcommand{\OrdQMag}{\preceq_{\mathrm{incl}}}
+\newcommand{\InfQMag}{\wedge_{\mathrm{incl}}}
+\newcommand{\SupQMag}{\vee_{\mathrm{incl}}}
+\newcommand{\LatQMag}{\left(\QMag,\OrdQMag,\InfQMag,\SupQMag\right)}
+\newcommand{\OrdCAs}{\preceq_{\mathrm{div}}}
+\newcommand{\InfCAs}{\wedge_{\mathrm{div}}}
+\newcommand{\SupCAs}{\vee_{\mathrm{div}}}
+\newcommand{\LatCAs}{\left(\CAsAll,\OrdCAs,\InfCAs,\SupCAs\right)}
+\newcommand{\LatKCAs}{\left(\KCAsAll,\OrdCAs,\InfCAs,\SupCAs\right)}
+\newcommand{\Unit}{\mathds{1}}
+\newcommand{\Leaf}{\perp}
+\newcommand{\Corolla}{\mathrm{c}}
+\newcommand{\NormalForms}{\mathfrak{N}}
+\newcommand{\Hom}{\mathrm{Hom}}
+\newcommand{\Compositions}{\mathcal{C}}
 
@@
 \DeclareMathOperator{\RewContext}{\Rightarrow}
-\DeclareMathOperator{\RewContextRT}{\overset{*}{\RewContext}}
 \DeclareMathOperator{\RewContextT}{\overset{+}{\RewContext}}
+\DeclareMathOperator{\RewContextRT}{\overset{\ast}{\RewContext}}
+\DeclareMathOperator{\RewContextRST}{\overset{\ast}{\Leftrightarrow}}
 \DeclareMathOperator{\lcm}{lcm}
@@
 
-% Tree drawings.
+\newcommand{\Lightning}[1]{
+\mathfrak{c}^{(#1)}_{\begin{tikzpicture}[scale=.1, Centering]
+    \draw (0,0)--(-1,-2);
+    \draw (-1,-2)--(0,-2);
+    \draw (0,-2)--(-1,-4);
+\end{tikzpicture}}}
+
+% Tizk styles.
 \tikzstyle{Node}=[circle,draw=Col1!80,fill=Col1!8,inner sep=1pt,
@@
 \tikzstyle{Edge}=[draw=Col2!80,cap=round,thick]
+\tikzstyle{EdgeColorF}=[Edge,draw=Col6!90,ultra thick]
 \tikzstyle{Leaf}=[rectangle,draw=ColBlack!70,fill=ColBlack!16,
@@
 \tikzstyle{NodeST}=[font=\footnotesize]
+\tikzstyle{Injection}=[ColBlack!100,draw,
+{>[scale=1.5,length=4,width=5]}-{>[scale=1.5,length=4,width=5]}]
+\tikzstyle{Map}=[ColBlack!100,draw,-{>[scale=1.5,length=4,width=5]}]
+
+% Tree drawings.
+
+\newcommand{\TreeA}{
+\begin{tikzpicture}[xscale=.22,yscale=.23,Centering]
+    \node(0)at(0.00,-5.25){};
+    \node(2)at(2.00,-5.25){};
+    \node(4)at(4.00,-3.50){};
+    \node(6)at(6.00,-1.75){};
+    \node[NodeST](1)at(1.00,-3.50){\begin{math}\Product\end{math}};
+    \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
+    \node[NodeST](5)at(5.00,0.00){\begin{math}\Product\end{math}};
+    \draw[Edge](0)--(1);
+    \draw[Edge](1)--(3);
+    \draw[Edge](2)--(1);
+    \draw[Edge](3)--(5);
+    \draw[Edge](4)--(3);
+    \draw[Edge](6)--(5);
+    \node(r)at(5.00,1.31){};
+    \draw[Edge](r)--(5);
+\end{tikzpicture}}
+
+\newcommand{\TreeB}{
+\begin{tikzpicture}[xscale=.22,yscale=.23,Centering]
+    \node(0)at(0.00,-3.50){};
+    \node(2)at(2.00,-5.25){};
+    \node(4)at(4.00,-5.25){};
+    \node(6)at(6.00,-1.75){};
+    \node[NodeST](1)at(1.00,-1.75){\begin{math}\Product\end{math}};
+    \node[NodeST](3)at(3.00,-3.50){\begin{math}\Product\end{math}};
+    \node[NodeST](5)at(5.00,0.00){\begin{math}\Product\end{math}};
+    \draw[Edge](0)--(1);
+    \draw[Edge](1)--(5);
+    \draw[Edge](2)--(3);
+    \draw[Edge](3)--(1);
+    \draw[Edge](4)--(3);
+    \draw[Edge](6)--(5);
+    \node(r)at(5.00,1.31){};
+    \draw[Edge](r)--(5);
+\end{tikzpicture}}
+
+\newcommand{\TreeC}{
+\begin{tikzpicture}[xscale=.22,yscale=.18,Centering]
+    \node(0)at(0.00,-4.67){};
+    \node(2)at(2.00,-4.67){};
+    \node(4)at(4.00,-4.67){};
+    \node(6)at(6.00,-4.67){};
+    \node[NodeST](1)at(1.00,-2.33){\begin{math}\Product\end{math}};
+    \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
+    \node[NodeST](5)at(5.00,-2.33){\begin{math}\Product\end{math}};
+    \draw[Edge](0)--(1);
+    \draw[Edge](1)--(3);
+    \draw[Edge](2)--(1);
+    \draw[Edge](4)--(5);
+    \draw[Edge](5)--(3);
+    \draw[Edge](6)--(5);
+    \node(r)at(3.00,1.75){};
+    \draw[Edge](r)--(3);
+\end{tikzpicture}}
+
+\newcommand{\TreeD}{
+\begin{tikzpicture}[xscale=.22,yscale=.23,Centering]
+    \node(0)at(0.00,-1.75){};
+    \node(2)at(2.00,-5.25){};
+    \node(4)at(4.00,-5.25){};
+    \node(6)at(6.00,-3.50){};
+    \node[NodeST](1)at(1.00,0.00){\begin{math}\Product\end{math}};
+    \node[NodeST](3)at(3.00,-3.50){\begin{math}\Product\end{math}};
+    \node[NodeST](5)at(5.00,-1.75){\begin{math}\Product\end{math}};
+    \draw[Edge](0)--(1);
+    \draw[Edge](2)--(3);
+    \draw[Edge](3)--(5);
+    \draw[Edge](4)--(3);
+    \draw[Edge](5)--(1);
+    \draw[Edge](6)--(5);
+    \node(r)at(1.00,1.31){};
+    \draw[Edge](r)--(1);
+\end{tikzpicture}}
+
+\newcommand{\TreeE}{
+\begin{tikzpicture}[xscale=.22,yscale=.23,Centering]
+    \node(0)at(0.00,-1.75){};
+    \node(2)at(2.00,-3.50){};
+    \node(4)at(4.00,-5.25){};
+    \node(6)at(6.00,-5.25){};
+    \node[NodeST](1)at(1.00,0.00){\begin{math}\Product\end{math}};
+    \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
+    \node[NodeST](5)at(5.00,-3.50){\begin{math}\Product\end{math}};
+    \draw[Edge](0)--(1);
+    \draw[Edge](2)--(3);
+    \draw[Edge](3)--(1);
+    \draw[Edge](4)--(5);
+    \draw[Edge](5)--(3);
+    \draw[Edge](6)--(5);
+    \node(r)at(1.00,1.31){};
+    \draw[Edge](r)--(1);
+\end{tikzpicture}}
 
@@
 \begin{abstract}
-    The associative operad is the quotient of the magmatic operad by
-    the operad congruence identifying the two binary trees of degree
-    $2$. We introduce here a generalization of the associative operad
-    depending on a nonnegative integer $d$, called $d$-comb associative
-    operad, as the quotient of the magmatic operad by the operad
-    congruence identifying the left and the right comb binary trees of
-    degree $d$. We study the case $d = 3$ and provide an orientation
-    of its space of relations by using rewrite systems on trees and
-    the Buchberger algorithm for operads to obtain a convergent
-    rewrite system.
+  We study quotients of the magmatic operad, that is the free
+  nonsymmetric operad over one binary generator. In the linear setting,
+  we show that the set of these quotients admits a lattice structure and
+  we show the Grassmann formula for this lattice. In the nonlinear
+  setting, we define comb associative operads, indexed by nonegative
+  integres, as generalizations of the associative operad. We show that
+  the set of comb associative operads admits a lattice structure,
+  isomoprhic to the lattice of nonnegative integers equipped with the
+  division order, and we provide a finite convergent presentation for the
+  comb associative operad corresponding to $3$. Finally, we study
+  quotients of the magmatic operad by one relation of degree $3$ by
+  studying their Hilbert series and providing combinarotial realizations.
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\input{Magmatic_quotient_three}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \input{Conclusion}

### 2018-08-23 Introduction.tex
Rédaction abstract

@@
 Section~\ref{sec:Magmatic_operads}, we study the set of all the
-quotients of $\Mag$ seen as an operad in the category of sets and its
-lattice structure. Section~\ref{sec:CAs_d} is the heart of this article
-and is devoted to the study of the comb associative operads
+quotients of $\Mag$ seen as an operad in the category of vector spaces
+and its lattice structure. Section~\ref{sec:CAs_d} is the heart of this
+article and is devoted to the study of the comb associative operads
 $\CAs{\gamma}$. Finally, Section~\ref{sec:MAg_3} presents our results

### 2018-08-23 Introduction.tex
Ajout références Koszulité intro

@@
 binary trees and are hence in one-to-one correspondence with the
-elements of~$\As$.
+elements of~$\As$. Following the ideas developped by Anick for
+associative algebras~\cite{Ani86}, the description of an operad by mean
+of normal forms provides homological informations for this operad. One of
+the fundemental homological properties for operads is \Def{Koszulness}
+~\Todo{citer Kapranov Ginzburg}, generalizing Koszul associative algebras
+\cite{Pri70}: the convergent orientation of $\As$ proves that it is a
+Koszul operad~\cite{LV12}. 
 \medbreak

### 2018-08-24 CAs_operads.tex
Ajout références Koszulité intro
Suppression occurrences de poset

@@
 set of such operads admits a lattice structure, isomorphic to the lattice
-division for nonnegative integers. We also relate this lattice to the
-lattice of linear magmatic quotients.
+division for nonnegative integers. We relate this lattice to the
+lattice of linear magmatic quotients. We also provide a finite convergent
+orientation for the comb associative operad corresponding to $3$.
 \medbreak
@@
 morphisms betweeen its elements by mean of intermediate lemmas.
+\medbreak
 
@@
 \end{Lemma}
+
 \begin{proof}
@@
 \end{Proposition}
+
 \begin{proof}
@@
 
-In order to show that the poset $\left(\CAsAll, \OrdCAs\right)$ is also a
+In order to show that the $\left(\CAsAll, \OrdCAs\right)$ extends into a
 lattice, we relate $\left(\CAsAll, \OrdCAs\right)$ with the lattice of
@@
 when $ 1 \leq n \leq 14$. Hence, we get our following main result.
-\medbreak
 
@@
 the following consequences.
-\medbreak
 
@@
 of subtrees, we obtain the following result.
-\medbreak
 

### 2018-08-24 Magmatic_operads.tex
Corrections anglais, harmonisation notations, ect...
Suppression occurrences de poset

@@
 Recall that a \Def{lattice} is a tuple
-$\left(E,\leq,\wedge,\vee\right)$, where $\left(E,\leq\right)$ is a
-poset such that any two elements $e$ and $e'$ of $E$ admit a lower-bound
-$e\wedge e'$ and an upper-bound $e\vee e'$. In particular,
+$\left(E,\leq,\wedge,\vee\right)$, where $\leq$ is a partial order
+relation such that any two elements $e$ and $e'$ of $E$ admit a
+lower-bound $e\wedge e'$ and an upper-bound $e\vee e'$. In particular,
 $\left(\IMag,\subseteq,\cap,+\right)$ is a lattice, where $\cap$ and $+$
@@
 \end{Theorem}
+
 \begin{proof}
@@
   $\Oca_2\OrdQMag\Oca_1$ is equivalent to $I_1\subseteq I_2$, so that
-  $\left(\QMag,\OrdQMag\right)$ is a poset and $\Oca$ is a decreasing
-  bijection. The tuple $\left(\IMag,\subseteq,\cap,+\right)$ being a
-  lattice, the decreasing bijection $\Oca$ induces lattice operations on
-  $\QMag$, precisely $\InfQMag$ and $\SupQMag$ by definition.
+  $\OrdQMag$ is a partial order relation on $\QMag$ and $\Oca$ is a
+  decreasing bijection. The tuple $\left(\IMag,\subseteq,\cap,+\right)$
+  being a lattice, the decreasing bijection $\Oca$ induces lattice
+  operations on $\QMag$, precisely $\InfQMag$ and $\SupQMag$ by
+  definition.
 \end{proof}

### 2018-08-25 Conclusion.tex
Ajout termes
Premier jet conclusion

@@
 \section*{Perspectives}
-\Todo{S: mettre à jour}
 
@@
 
-Our first axis of perspectives consists in collecting properties about
-the operads $\CAs{d}$. A natural question consists in finding all the
-morphisms between the operads $\CAs{d}$. Some surjective morphisms are
-described by Proposition~\ref{prop:quotients_CAs_d} and we can hope to a
-full description of these, as well as some possible injections.
-Moreover, we can try to obtain a convergent orientation of
-$\CongrCAs{d}$ and general expressions of the Hilbert series of
-$\CAs{d}$ when $d \geq 4$. By computer exploration, we have the sequence
+Our first axis of perspectives consists in finding convergent
+presentations for $\CAs{d}$ operads in order to describe algebraic and
+combinatorial properties of these operads, \emph{e.g.} find explicit bases,
+compute Hilbert series, provide realizations, \emph{ect}... By computer
+exploration, we have already some informations in this direction: we have
+the sequence
 \begin{equation}
-    1, 1, 2, 5, 13, 35, 96, 264, 724, 1973, 5355, 14390
+    1, 1, 2, 5, 13, 35, 96, 264, 724, 1973, 5335, 14390, 38872, 105141, 
+    284929, 774254
 \end{equation}
@@
 \begin{equation}
-    1, 1, 2, 5, 14, 41, 124, 384, 1210, 3861, 12440
+1, 1, 2, 5, 14, 41, 124, 384, 1210, 3861, 12440, 40392, 131997, 
+433782, 1432696, 4752857
 \end{equation}
@@
 \begin{equation}
-    1, 1, 2, 5, 14, 42, 131, 420, 1375, 4576, 15431
+   1, 1, 2, 5, 14, 42, 131, 420, 1375, 4576, 15431, 52598, 
+   180895, 626862, 2186504, 7670138
 \end{equation}
@@
 only $\CAs{3}$ seems to have oscillating first dimensions. 
+\medbreak
+
+Following ideas existing for word rewriring~\cite{GGM15}, a second axis
+consists in allowing new generators in the orientations of $\CongrCAs{d}$
+in order to obtain finite convergent presentations for $d\geq 4$. More
+generally, we also would like to use this method for other magmatic
+quotients, such as the operad $\Mag^{\{3, 4\}}$ that we did not study
+entirely in Section~\ref{sec:MAg_3}.
+\medbreak
+
+A third axis for studying completion of magmatic operads is to use
+the lattice structure introduced in Section~\ref{sec:Magmatic_operads}.
+More precisely, assuming that we have completed the magmatic operads
+$\Oca_1$, $\Oca_2$ as well as the lower-bound $\Oca_2\InfQMag \Oca_2$,
+is there a procedure for completing the upper-bound
+$\Oca_1\SupQMag \Oca_2$? Of course, the same question also makes sense
+for the lattice of comb associative operads introduced in
+Section~\ref{sec:CAs_d}.
+\medbreak
+
+\Todo{C : Plus développer les aspects treillis de Tamari ?}
+In a last axis, we can consider further generalizations of $\As$ being
+quotients of $\Mag$ by congruences defined by identifying certain binary
+trees of a same fixed degree. A possible question is, as presented in
+the introduction, to investigate if combinatorial properties of the
+trees belonging to a same equivalence class imply algebraic properties
+on the obtained operads.
 \medbreak
@@
 \medbreak
-
-In a last axis, we can consider further generalizations of $\As$ being
-quotients of $\Mag$ by congruences defined by identifying certain binary
-trees of a same fixed degree. A possible question is, as presented in
-the introduction, to investigate if combinatorial properties of the
-trees belonging to a same equivalence class imply algebraic properties
-on the obtained operads.
-\medbreak

### 2018-08-27 CAs_operads.tex
Maj Intro et bib

@@
 
-In order to show that the $\left(\CAsAll, \OrdCAs\right)$ extends into a
+In order to show that $\left(\CAsAll, \OrdCAs\right)$ extends into a
 lattice, we relate $\left(\CAsAll, \OrdCAs\right)$ with the lattice of

### 2018-08-27 Introduction.tex
Maj Intro et bib

--- 2018-08-23 Introduction.tex
@@
 binary trees and are hence in one-to-one correspondence with the
-elements of~$\As$.
+elements of~$\As$. Following the ideas developed by Anick for
+associative algebras~\cite{Ani86}, the description of an operad by mean
+of normal forms provides homological information for this operad. One of
+the fundamental homological properties for operads is
+Koszulity~\cite{GK94}, generalizing Koszul associative
+algebras~\cite{Pri70}: the convergent orientation of $\As$ proves that
+it is a Koszul operad~\cite{LV12}.
 \medbreak

### 2018-08-27 Article.tex
Maj abstract

@@
   we show that the set of these quotients admits a lattice structure and
-  we show the Grassmann formula for this lattice. In the nonlinear
-  setting, we define comb associative operads, indexed by nonegative
-  integres, as generalizations of the associative operad. We show that
-  the set of comb associative operads admits a lattice structure,
-  isomoprhic to the lattice of nonnegative integers equipped with the
-  division order, and we provide a finite convergent presentation for the
-  comb associative operad corresponding to $3$. Finally, we study
-  quotients of the magmatic operad by one relation of degree $3$ by
-  studying their Hilbert series and providing combinarotial realizations.
+  we show an analog of the Grassmann formula for the dimensions of these
+  operads. In the nonlinear setting, we define comb associative operads,
+  that are operads indexed by nonnegative integers generalizing the
+  associative operad. We show that the set of comb associative operads
+  admits a lattice structure, isomorphic to the lattice of nonnegative
+  integers equipped with the division order, and we provide a finite
+  convergent presentation for the comb associative operad in
+  correspondence with $3$. Finally, we study quotients of the magmatic
+  operad by one relation of degree three by studying their Hilbert
+  series and providing combinatorial realizations.
 \end{abstract}

### 2018-08-27 Article.tex
Modifs

@@
 
+\newcommand{\Cca}{\mathcal{C}}
 \newcommand{\Oca}{\mathcal{O}}
@@
     We study quotients of the magmatic operad, that is the free
-  nonsymmetric operad over one binary generator. In the linear setting,
-  we show that the set of these quotients admits a lattice structure and
-  we show an analog of the Grassmann formula for the dimensions of these
-  operads. In the nonlinear setting, we define comb associative operads,
-  that are operads indexed by nonnegative integers generalizing the
-  associative operad. We show that the set of comb associative operads
-  admits a lattice structure, isomorphic to the lattice of nonnegative
-  integers equipped with the division order, and we provide a finite
+    nonsymmetric operad over one binary generator. In the linear
+    setting, we show that the set of these quotients admits a lattice
+    structure and we show an analog of the Grassmann formula for the
+    dimensions of these operads. In the nonlinear setting, we define
+    comb associative operads, that are operads indexed by nonnegative
+    integers generalizing the associative operad. We show that the set
+    of comb associative operads admits a lattice structure, isomorphic
+    to the lattice of nonnegative integers equipped with the division
+    order. Driven by computer experimentation, we provide a finite
     convergent presentation for the comb associative operad in
-  correspondence with $3$. Finally, we study quotients of the magmatic
+    correspondence with~$3$. Finally, we study quotients of the magmatic
     operad by one relation of degree three by studying their Hilbert

### 2018-08-27 Conclusion.tex
Modifs

@@
 combinatorial properties of these operads, \emph{e.g.} find explicit bases,
-compute Hilbert series, provide realizations, \emph{ect}... By computer
-exploration, we have already some informations in this direction: we have
-the sequence
-\begin{equation}
-    1, 1, 2, 5, 13, 35, 96, 264, 724, 1973, 5335, 14390, 38872, 105141, 
-    284929, 774254
-\end{equation}
-for the first dimensions for $\CAs{4}$. By applying the Buchberger
-algorithm on trees of degrees until $10$, we obtain that a convergent
-orientation of $\CongrCAs{4}$ has, arity by arity, the sequence
-\begin{math}
-    0, 0, 0, 0, 1, 1, 0, 3, 4, 5, 18, 22
-\end{math}
-for its first cardinalities. Moreover, for $\CAs{5}$, we get the
-sequence
-\begin{equation}
-1, 1, 2, 5, 14, 41, 124, 384, 1210, 3861, 12440, 40392, 131997, 
-433782, 1432696, 4752857
-\end{equation}
-of dimensions and the first cardinalities
-\begin{math}
-    0, 0, 0, 0, 0, 1, 1, 0, 0, 4, 5
-\end{math}
-for any convergent orientation of $\CongrCAs{5}$. Finally, for
-$\CAs{6}$, we get the sequence
-\begin{equation}
-   1, 1, 2, 5, 14, 42, 131, 420, 1375, 4576, 15431, 52598, 
-   180895, 626862, 2186504, 7670138
-\end{equation}
-of dimensions and the first cardinalities
-\begin{math}
-    0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0
-\end{math}
-for any convergent orientation of $\CongrCAs{6}$. We can notice that
-only $\CAs{3}$ seems to have oscillating first dimensions. 
-\medbreak
+compute Hilbert series, provide realizations, \emph{ect}...
 

### 2018-08-27 Operads_rewrite.tex
Reorganisation derniere partie
Modifs

@@
 the arities, sends the unit of $\Oca_1$ to the unit of $\Oca_2$, and
-commutes with partial composition maps. We say that $\Oca_2$ is a
+commutes with partial composition maps. A map $\phi : \Oca_1 \to \Oca_2$
+is an \Def{operad antimorphism} if it respects the arities, sends the
+unit of $\Oca_1$ to the unit of $\Oca_2$, and
+\begin{math}
+    \phi\left(x \circ_i y\right) = \phi(x) \circ_{|x|-i+1} \phi(y)
+\end{math}
+for all $x, y \in \Oca_1$ and $i \in [|x|]$. We say that $\Oca_2$ is a
 \Def{suboperad} of $\Oca_1$ if $\Oca_2$ is a subset of $\Oca_1$
@@
 is an element of the quotient operad
-\begin{equation}
+\begin{equation} \label{equ:quotient_operad_mag}
     \Oca := \Mag/_{\Congr}.
@@
 orientation of $\Congr$ if $\RewContext$ is convergent (resp.
-terminating, confluent). When $\Rew$ is a convergent orientation of
-$\Congr$, the set $\NormalForms_{\RewContext}$ of all normal forms of
-$\RewContext$ is called a \Def{Poincaré-Birkhoff-Witt basis} (or a
-\Def{PBW basis} for short) of the quotient operad $\Oca$
-(see~\cite{Hof10,DK10}). This forms a one-to-one correspondence between
-the sets $\NormalForms_{\RewContext}(n)$ and $\Oca(n)$, $n \geq 1$. In
-other words, a PBW basis offers a way to assign with each
-$\Congr$-equivalence class $[\Tfr]_{\Congr}$ a representative
+terminating, confluent).
+\medbreak
+
+When $\Rew$ is a convergent orientation of $\Congr$, the set
+$\NormalForms_{\RewContext}$ of all normal forms of $\RewContext$ is
+called a \Def{Poincaré-Birkhoff-Witt basis} (or a \Def{PBW basis} for
+short) of the quotient operad $\Oca$ (see~\cite{Hof10,DK10}). This forms
+a one-to-one correspondence between the sets
+$\NormalForms_{\RewContext}(n)$ and $\Oca(n)$, $n \geq 1$. In other
+words, a PBW basis offers a way to assign with each $\Congr$-equivalence
+class $[\Tfr]_{\Congr}$ a representative
 \begin{math}
@@
 \end{math}
+A \Def{combinatorial realization} of an operad $\Oca$ of the
+form~\eqref{equ:quotient_operad_mag} is an operad $\Cca$ isomorphic to
+$\Oca$ which admits an explicit description of its elements and an
+explicit description of its partial composition maps. The knowledge of a
+PBW basis $\Cca := \NormalForms_{\RewContext}$ of $\Oca$ provides a
+combinatorial realization $\Cca$ of $\Oca$. Indeed, the partial
+composition $\Tfr' \circ_i \Sfr'$ of two binary trees $\Tfr'$ and
+$\Sfr'$ of $\Cca$ is the tree obtained by grafting the root of $\Sfr'$
+onto the $i$th leaf of $\Tfr'$ and by rewriting by $\RewContext$ this
+tree as much as possible in order to obtain a normal form. This process
+is well-defined since, by hypothesis, $\RewContext$ is convergent.
 \medbreak

### 2018-08-27 CAs_operads.tex
Modifs
Maj partie CAs

@@
 
-  Note that $\LatKCAs$ does not embed into a sub-lattice of $\LatQMag$,
-  that is $\iota$ is not a lattice morphism. Consider for instance
-  $\gamma=3$ and $\gamma'=4$, then $\KCAs{\gamma}\InfCAs\KCAs{\gamma'}$
-  is equal to $\KCAs{2}=\K\As$, whereas
-  $\KCAs{\gamma}\InfQMag\KCAs{\gamma'}$ is quotient of $\KMag$ be the two
-  relations $\LComb{3}-\RComb{3}$ and $\LComb{4}-\RComb{4}$.
+Note that $\LatKCAs$ does not embed as a sub-lattice of $\LatQMag$, that
+is $\iota$ is not a lattice morphism. Consider for instance $\gamma = 3$
+and $\gamma' = 4$, then $\KCAs{\gamma} \InfCAs \KCAs{\gamma'}$ is equal
+to $\KCAs{2} = \K\As$, whereas $\KCAs{\gamma} \InfQMag \KCAs{\gamma'}$
+is a quotient of $\KMag$ be the two relations $\LComb{3} - \RComb{3}$
+and $\LComb{4} - \RComb{4}$.
+\medbreak
 
@@
 The Buchberger algorithm applied on binary trees of degrees $5$, $6$,
-and $7$ provides the new relations \\
+and $7$ provides the new relations \smallbreak
 \input{Buchberger_relations_5-7}
+\medbreak
 
-\noindent
-We claim that the rewrite relation $\RewContext$ induced by
-rewrite rule $\Rew$ satisfying~\eqref{equ:rew_1}, \eqref{equ:rew_2},
-\eqref{equ:rew_3}---\eqref{equ:rew_11} is convergent. First, for every
-relation $\Tfr \Rew \Tfr'$, we have
-$\PrefixWord(\Tfr) > \PrefixWord(\Tfr')$. Therefore, by
-Lemma~\ref{lem:prefix_word_termination}, $\RewContext$ is terminating.
-Moreover, the greatest degree of a tree appearing in $\Rew$ is~$7$ so
-that, from Lemma~\ref{lem:degree_confluence}, to show that $\RewContext$
-is convergent, it is enough to prove that each tree of degree at most
-$13$ admits exactly one normal form. Equivalently, this amounts to
-show that the number of normal forms of trees of arity $n$ is equal
-to $\#\CAs{3}(n)$. By computer exploration, we get the same sequence
+\begin{Theorem} \label{thm:convergent_rewrite_rule_CAs_3}
+    The set $\Rew$ of rewrite rules containing~\eqref{equ:rew_1},
+    \eqref{equ:rew_2}, \eqref{equ:rew_3}---\eqref{equ:rew_11} is a
+    convergent orientation of the congruence $\CongrCAs{3}$
+    of~$\CAs{3}$.
+\end{Theorem}
+\begin{proof}
+    Let us show that the rewrite relation $\RewContext$ induced by
+    $\Rew$ is convergent. First, for every relation $\Tfr \Rew \Tfr'$,
+    we have $\Tfr > \Tfr'$. Therefore, by
+    Lemma~\ref{lem:prefix_word_termination}, $\RewContext$ is
+    terminating. Moreover, the greatest degree of a tree appearing in
+    $\Rew$ is~$7$ so that, from Lemma~\ref{lem:degree_confluence}, to
+    show that $\RewContext$ is convergent, it is enough to prove that
+    each tree of degree at most $13$ admits exactly one normal form.
+    Equivalently, this amounts to show that the number of normal forms
+    of trees of arity $n$ is equal to $\#\CAs{3}(n)$. By computer
+    exploration, we get the same sequence
     \begin{equation} \label{equ:dimensions_CAs_3}
@@
     when $ 1 \leq n \leq 14$. Hence, we get our following main result.
-
-\begin{Theorem} \label{thm:convergent_rewrite_rule_CAs_3}
-    The rewrite rule $\Rew$ satisfying~\eqref{equ:rew_1},
-    \eqref{equ:rew_2}, \eqref{equ:rew_3}---\eqref{equ:rew_11} is a
-    convergent orientation of the congruence $\CongrCAs{3}$
-    of~$\CAs{3}$.
-\end{Theorem}
+\end{proof}
 \medbreak
@@
 \begin{equation}
-    0, 0, 0, 1, 1, 2, 3, 4, 0, \dots~.
+    0, 0, 0, 1, 1, 2, 3, 4, 0, 0, \dots~.
 \end{equation}
@@
 \end{Proposition}
+\begin{proof}
+    By definition of PBW bases and
+    Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}, the set
+    $\NormalForms_{\RewContext}$ is a PBW basis of $\CAs{3}$ where
+    $\RewContext$ is the rewrite relation induced by $\Rew$. Now, by
+    Lemma~\ref{lem:normal_forms_avoiding}, $\NormalForms_{\RewContext}$
+    can be described as the set of the trees avoiding the left members
+    of~$\Rew$, whence the statement.
+\end{proof}
 \medbreak
-
-From Proposition~\ref{prop:PBW_basis_CAs_3}, and by using a result
-of~\cite{Gir18} (see also~\cite{Row10,KP15}) describing a system of
-equations for the generating series of syntax trees avoiding some sets
-of subtrees, we obtain the following result.
 
@@
 \end{Proposition}
+\begin{proof}
+    From Proposition~\ref{prop:PBW_basis_CAs_3}, for any $n \geq 1$, the
+    dimension of $\CAs{3}(n)$ is the number of trees that avoid as
+    subtrees the left members of $\Rew$. Now, by using a result
+    of~\cite{Gir18} (see also~\cite{Row10,KP15}) providing a system of
+    equations for the generating series of the trees avoiding some sets
+    of subtrees, we obtain Expression~\eqref{equ:Hilbert_series_CAs_3}
+    for the considered family.
+\end{proof}
 \medbreak
@@
 \medbreak
+
+\Todo{S: réalisation combinatoire de $\CAs{3}$ à donner ici.}
+
+\Todo{S: résultats expérimentaux de quelques $\CAs{\gamma}$ à donner
+dans cette partie (ou peut être dans une sous-partie précédente ; à
+voir selon ce que ça donne).}
+
+%By computer exploration, we have already some information in this
+%direction: we have the sequence
+%\begin{equation}
+    %1, 1, 2, 5, 13, 35, 96, 264, 724, 1973, 5335, 14390, 38872, 105141,
+    %284929, 774254
+%\end{equation}
+%for the first dimensions for $\CAs{4}$. By applying the Buchberger
+%algorithm on trees of degrees until $10$, we obtain that a convergent
+%orientation of $\CongrCAs{4}$ has, arity by arity, the sequence
+%\begin{math}
+    %0, 0, 0, 0, 1, 1, 0, 3, 4, 5, 18, 22
+%\end{math}
+%for its first cardinalities. Moreover, for $\CAs{5}$, we get the
+%sequence
+%\begin{equation}
+%1, 1, 2, 5, 14, 41, 124, 384, 1210, 3861, 12440, 40392, 131997,
+%433782, 1432696, 4752857
+%\end{equation}
+%of dimensions and the first cardinalities
+%\begin{math}
+    %0, 0, 0, 0, 0, 1, 1, 0, 0, 4, 5
+%\end{math}
+%for any convergent orientation of $\CongrCAs{5}$. Finally, for
+%$\CAs{6}$, we get the sequence
+%\begin{equation}
+   %1, 1, 2, 5, 14, 42, 131, 420, 1375, 4576, 15431, 52598,
+   %180895, 626862, 2186504, 7670138
+%\end{equation}
+%of dimensions and the first cardinalities
+%\begin{math}
+    %0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0
+%\end{math}
+%for any convergent orientation of $\CongrCAs{6}$. We can notice that
+%only $\CAs{3}$ seems to have oscillating first dimensions.
+%\medbreak

### 2018-08-27 Conclusion.tex
Maj conclusion

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Perspectives}
-
-\Todo{S: parler aussi des généralisation avec $2\Mag$ (arbres de Schröder)}
-
-Our first axis of perspectives consists in finding convergent
-presentations for $\CAs{d}$ operads in order to describe algebraic and
-combinatorial properties of these operads, \emph{e.g.} find explicit bases,
-compute Hilbert series, provide realizations, \emph{ect}...
-
-Following ideas existing for word rewriring~\cite{GGM15}, a second axis
-consists in allowing new generators in the orientations of $\CongrCAs{d}$
-in order to obtain finite convergent presentations for $d\geq 4$. More
-generally, we also would like to use this method for other magmatic
-quotients, such as the operad $\Mag^{\{3, 4\}}$ that we did not study
-entirely in Section~\ref{sec:MAg_3}.
+\section*{Conclusion and perspectives}
+In this paper, we have considered some quotients of the magmatic operad
+in both the linear and the set-theoretic frameworks. We focused mainly
+our study on comb associative operads and collected properties by
+using computer exploration and rewrite systems on trees. There are many
+ways to extend this work. Here follow some few further research
+directions.
 \medbreak
 
-A third axis for studying completion of magmatic operads is to use
+A first research direction consists in finding convergent orientations
+of presentations for (all or most of) the $\CAs{\gamma}$ operads in
+order to describe algebraic and combinatorial properties of these
+operads (as describing explicit bases, computing Hilbert
+series, and providing combinatorial realizations). This has been
+done only in the case $\gamma = 3$. For some other cases, we only have
+conjectural and experimental data (see Section~\ref{?}).
+\Todo{S: compléter avec la bonne partie une fois qu'on aura ajouté ces
+données}.
+\medbreak
+
+Following ideas existing for word rewriting theory~\cite{GGM15}, a
+second axis consists in allowing new generators in the orientations of
+the operad congruence $\CongrCAs{\gamma}$ in order to obtain finite
+convergent orientations for their presentations when $\gamma \geq 4$.
+Indeed, the Buchberger semi-algorithm works by adding rewrite rules to a
+set of rewrite rules to obtain a convergent rewrite system. An orthogonal
+procedure consists rather in adding new generators (new labels for
+internal nodes in the trees) in order to obtain convergent rewrite
+systems. More generally, we also would like to use these ideas for other
+magmatic quotients, such as the operad $\Mag^{\{3, 4\}}$ that we did not
+study entirely in Section~\ref{sec:MAg_3}.
+\medbreak
+
+A third axis consists in studying if the completion of orientations of
+presentations of quotients of the magmatic operad maintains links with
 the lattice structure introduced in Section~\ref{sec:Magmatic_operads}.
-More precisely, assuming that we have completed the magmatic operads
-$\Oca_1$, $\Oca_2$ as well as the lower-bound $\Oca_2\InfQMag \Oca_2$,
-is there a procedure for completing the upper-bound
-$\Oca_1\SupQMag \Oca_2$? Of course, the same question also makes sense
+More precisely, assuming that we have completed the orientations of
+the presentations of the quotients $\Oca_1$ and $\Oca_2$ of $\Mag$,
+as well as the one of the lower-bound $\Oca_2 \InfQMag \Oca_2$, the
+question consists in designing an algorithm for computing a completion
+of an orientation of the presentation of the upper-bound
+$\Oca_1 \SupQMag \Oca_2$. Of course, the same question also makes sense
 for the lattice of comb associative operads introduced in
@@
 
-\Todo{C : Plus développer les aspects treillis de Tamari ?}
-In a last axis, we can consider further generalizations of $\As$ being
-quotients of $\Mag$ by congruences defined by identifying certain binary
-trees of a same fixed degree. A possible question is, as presented in
-the introduction, to investigate if combinatorial properties of the
-trees belonging to a same equivalence class imply algebraic properties
-on the obtained operads.
+Let us address now a perspective fitting more in a combinatorial
+context. As mentioned in the introduction of this article, we suspect
+that some combinatorial properties of quotients $\Mag/_{\Congr}$ of
+$\Mag$ derive from properties of the equivalence relation generating the
+operad congruence $\Congr$. More precisely, we would like to investigate
+if, when this equivalence relation is a set of Tamari intervals (or is
+closed by interval, or satisfies some other classical properties coming
+from poset theory), one harvests a nice description of the Hilbert
+series and of a combinatorial realization of $\Mag/_{\Congr}$.
 \medbreak
 
-\Todo{S: Placer ces résultats expérimentaux dans la partie sur CAs}
+A last research axis rely on the study on the $2$-magmatic operad
+$\TwoMag$, that is, the free operad generated by two binary elements.
+The analog of the associative operad in this context is the operad
+$\TwoAs$ (see~\cite{LR06}), defined as the quotient of $\TwoMag$ by
+the congruence saying that the two generators are associative. This
+operad has a nice combinatorial realization in terms of alternating
+bicolored Schröder trees. The question consists here in generalizing
+our main results for the quotients of $\TwoMag$ and the generalizations
+of $\TwoAs$ (definition of analog of comb associative operads and
+study of its presentations).
+\medbreak
 
-A second axis concerns a complete understanding of $\CAs{3}$. We can
-try to construct an explicit basis of this operad.
-Proposition~\ref{prop:PBW_basis_CAs_3} describes a basis in terms of
-trees avoiding some patterns but, we can hope to find a simpler
-description. This includes the description of a family of combinatorial
-objects forming a basis of $\CAs{3}$ and an adequate definition of a
-partial composition map $\circ_i$ on these. Moreover, a natural
-question is to explore the suboperads $\CAs{3}$ in the category of
-vector spaces.
-\medbreak
+\Todo{S: attention, on emploie souvent l'expression "presentation" et
+"completion of presentation" mais on a jamais vraiment défini ce qu'est
+une presentation et ce qu'est une orientation d'une complétion. C'est
+facile, mais il faudrait le faire (préliminaires). Il faudrait d'ailleurs
+utiliser plutôt l'expression "convergent orientation of a presentation"
+plutôt que "convergent orientation".}

### 2018-08-28 Introduction.tex
Changement Koszulity -> Koszulness dans l'intro

--- 2018-08-23 Introduction.tex
@@
 binary trees and are hence in one-to-one correspondence with the
-elements of~$\As$.
+elements of~$\As$. Following the ideas developed by Anick for
+associative algebras~\cite{Ani86}, the description of an operad by mean
+of normal forms provides homological information for this operad. One of
+the fundamental homological properties for operads is
+Koszulness~\cite{GK94}, generalizing Koszul associative
+algebras~\cite{Pri70}: the convergent orientation of $\As$ proves that
+it is a Koszul operad~\cite{LV12}.
 \medbreak

### 2018-08-28 Introduction.tex
Correction coquilles intro

@@
 (see~\eqref{equ:dimensions_CAs_3}), what is rather unusual among all
-known operads. We provide an orientation of the space of relations of
-$\CAs{3}$ (Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}), a
-description of a basis of the operad, and prove that its Hilbert series
+known operads. We provide a convergent orientation of the space of
+relations of $\CAs{3}$ (Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}),
+a description of a basis of the operad, and prove that its Hilbert series
 is rational.

### 2018-08-28 CAs_operads.tex
Lemme 3.2.6

@@
 \end{Lemma}
+
+\Todo{Christophe : je vous propose cette démo}
+\begin{proof}
+    We consider the rewrite rule $\LComb{\gamma} \Rew \RComb{\gamma}$ 
+    on $\Mag$. First, we show that 
+    \begin{equation} \label{eq:rewriting_invariant}
+        \Tfr \RewContext \Tfr' 
+        \mbox{ implies that }
+        \LRank\left(\Tfr'\right) = \LRank\left(\Tfr\right) 
+        \, \pmod{\bar{\gamma}}.
+    \end{equation}
+    Indeed for all $\Tfr \in \Mag$, there exist binary trees 
+    $\Tfr_1, \dots, \Tfr_{\LRank\left(\Tfr\right)}$ such that
+    \begin{math}
+      \Tfr = 
+      \left[\, |,\Tfr_1, \dots, \Tfr_{\LRank\left(\Tfr\right)} \right].
+    \end{math}
+    Thus if $\Tfr \RewContext \Tfr'$, then one of the 
+    two following cases occurs :
+    \begin{enumerate}[label={(\it\roman*)}]
+        \item there exist $\Tfr_i'$ such that
+            \begin{math}
+              \Tfr' = \LComb{\LRank\left(\Tfr\right)} \circ 
+              \left[\, | ,\Tfr_1, \dots, \Tfr_i',\dots, 
+                    \Tfr_{\LRank\left(\Tfr\right)}
+              \right] \mbox{ so } 
+              \LRank\left(\Tfr'\right) = \LRank\left(\Tfr\right);
+            \end{math}
+        \item there exist $i$ such that
+            \begin{math} 
+              \Tfr' = \LComb{\LRank\left(\Tfr\right)-\bar{\gamma}} \circ
+              \left[ | ,\Tfr_1, \dots, 
+                 \RComb{\bar{\gamma}} \circ 
+                 [\Tfr_{i},\dots, \Tfr_{i+\bar{\gamma}}]
+                 ,\dots, \Tfr_{\LRank\left(\Tfr\right)}
+              \right]\\
+              \mbox{ so }
+              \LRank\left(\Tfr'\right) = 
+              \LRank\left(\Tfr\right) - \bar{\gamma} = 
+              \LRank\left(\Tfr\right) \pmod{\bar{\gamma}}
+            \end{math}.
+    \end{enumerate} 
+    This concludes the proof of~\ref{eq:rewriting_invariant}.  
+    \smallbreak
+
+    We deduce from~\ref{eq:rewriting_invariant} that the equivalence 
+    relation $r$ defined by 
+    \begin{equation}
+        r(\Tfr, \Tfr') \mbox{ if and only if } 
+        \LRank\left(\Tfr'\right) = \LRank\left(\Tfr\right) 
+        \, \pmod{\bar{\gamma}}
+    \end{equation}
+    contains the relation $\RewContext$ and thus its transitive 
+    and symmetric closure, which is $\CongrCAs{\gamma}$.
+\end{proof}
 

### 2018-09-01 CAs_operads.tex
Harmonisation presentation/orientation

@@
 lattice of linear magmatic quotients. We also provide a finite convergent
-orientation for the comb associative operad corresponding to $3$.
+presentation of the comb associative operad corresponding to $3$.
 \medbreak
@@
 
-\Todo{Christophe : je vous propose cette démo}
 \begin{proof}
@@
         \Tfr \RewContext \Tfr' 
-        \mbox{ implies that }
+        \mbox{ implies }
         \LRank\left(\Tfr'\right) = \LRank\left(\Tfr\right) 
@@
     \end{equation}
-    Indeed for all $\Tfr \in \Mag$, there exist binary trees 
-    $\Tfr_1, \dots, \Tfr_{\LRank\left(\Tfr\right)}$ such that
+    Indeed, for all $\Tfr \in \Mag$, let
+    $\Tfr_1, \dots, \Tfr_{\LRank\left(\Tfr\right)}$ be the binary trees
+    such that
     \begin{math}
@@
     \end{math}
-    Thus if $\Tfr \RewContext \Tfr'$, then one of the 
-    two following cases occurs :
+    Thus, if $\Tfr \RewContext \Tfr'$, then one of the following two
+    cases occurs:
     \begin{enumerate}[label={(\it\roman*)}]
-        \item there exist $\Tfr_i'$ such that
+        \item there exists $\Tfr_i'$ such that
             \begin{math}
@@
                     \Tfr_{\LRank\left(\Tfr\right)}
-              \right] \mbox{ so } 
+              \right] \mbox{, so that } 
               \LRank\left(\Tfr'\right) = \LRank\left(\Tfr\right);
             \end{math}
-        \item there exist $i$ such that
+        \item there exists $i$ such that
             \begin{math} 
@@
                  ,\dots, \Tfr_{\LRank\left(\Tfr\right)}
-              \right]\\
-              \mbox{ so }
+              \right]
+              \mbox{, so that }\\
               \LRank\left(\Tfr'\right) = 
@@
     \end{enumerate} 
-    This concludes the proof of~\ref{eq:rewriting_invariant}.  
+    This concludes the proof of~\eqref{eq:rewriting_invariant}.  
     \smallbreak
 
-    We deduce from~\ref{eq:rewriting_invariant} that the equivalence 
+    We deduce from~\eqref{eq:rewriting_invariant} that the equivalence 
     relation $r$ defined by 
@@
     \end{equation}
-    contains the relation $\RewContext$ and thus its transitive 
-    and symmetric closure, which is $\CongrCAs{\gamma}$.
-\end{proof}
-
-\begin{proof}
-  We consider the rewrite rule $\LComb{\gamma} \Rew \RComb{\gamma}$ on
-  $\Mag$.
-    \smallbreak
-
-    First, we show that $\Tfr \RewContext \Tfr'$ implies that
-    $\LRank\left(\Tfr'\right) - \LRank\left(\Tfr\right)$ is
-    divisible by $\bar{\gamma}$. \Todo{à faire.}
-    \smallbreak
-
-    Assume that $\Tfr \RewContextRT \Tfr'$, so that there exist binary trees
-    $\Tfr_1$, \dots, $\Tfr_k$ such that $\Tfr_1 = \Tfr$,
-    $\Tfr_k = \Tfr'$ and for every $i \in [k - 1]$, we have
-    $\Tfr_i\RewContext \Tfr_{i + 1}$. The integer
-    \begin{math}
-        \LRank\left(\Tfr_{i + 1}\right)
-        -
-        \LRank\left(\Tfr_i\right)
-    \end{math}
-    is divisible by $\bar{\gamma}$ from the first part of the proof, so
-    that $\LRank\left(\Tfr'\right) - \LRank\left(\Tfr\right)$ is
-    divisible by~$\bar{\gamma}$.
-    \smallbreak
-
-    Assume that $\Tfr \RewContextRST \Tfr'$, so that there exist binary trees
-    $\Tfr_1$, \dots, $\Tfr_k$ such that $\Tfr_1 = \Tfr$,
-    $\Tfr_k = \Tfr'$ and for every $i \in [k - 1]$, we have
-    $\Tfr_i \RewContextRT \Tfr_{i + 1}$ or $\Tfr_{i + 1} \RewContextRT
-    \Tfr_i$. From the second part of the proof, the integer
-    \begin{math}
-        \LRank\left(\Tfr_{i + 1}\right)
-        -
-        \LRank\left(\Tfr_i\right)
-    \end{math}
-    is divisible by $\bar{\gamma}$, so that
-    $\LRank\left(\Tfr'\right) - \LRank\left(\Tfr\right)$ is
-    divisible by~$\bar{\gamma}$.
-    \smallbreak
-
-    The congruence $\CongrCAs{\gamma}$ is the equivalence relation
-    induced by the rewrite relation $\RewContext$ induced by the rewrite
-    rule $\LComb{\gamma} \Rew \RComb{\gamma}$, that is we have $\Tfr
-    \CongrCAs{\gamma} \Tfr'$ if and only if $\Tfr \RewContextRST \Tfr'$.
-    Hence, from the third part of the proof, $\Tfr \CongrCAs{\gamma}
-    \Tfr'$ implies that
-    \begin{math}
-        \LRank\left(\Tfr'\right) - \LRank\left(\Tfr\right)
-    \end{math}
-    is divisible by~$\bar{\gamma}$.
+    contains the relation $\RewContext$, so that it contains its
+    transitive symmetric closure. The latter is $\CongrCAs{\gamma}$,
+    which concludes the proof of Lemma~\ref{lem:left_rank_and_CongrCAs}.
 \end{proof}
@@
     \eqref{equ:rew_2}, \eqref{equ:rew_3}---\eqref{equ:rew_11} is a
-    convergent orientation of the congruence $\CongrCAs{3}$
-    of~$\CAs{3}$.
+    convergent presentation of~$\CAs{3}$.
 \end{Theorem}

### 2018-09-01 Conclusion.tex
Harmonisation presentation/orientation

@@
 
-A first research direction consists in finding convergent orientations
-of presentations for (all or most of) the $\CAs{\gamma}$ operads in
+A first research direction consists in finding convergent presentations
+for (all or most of) the $\CAs{\gamma}$ operads in
 order to describe algebraic and combinatorial properties of these
@@
 Following ideas existing for word rewriting theory~\cite{GGM15}, a
-second axis consists in allowing new generators in the orientations of
-the operad congruence $\CongrCAs{\gamma}$ in order to obtain finite
-convergent orientations for their presentations when $\gamma \geq 4$.
-Indeed, the Buchberger semi-algorithm works by adding rewrite rules to a
-set of rewrite rules to obtain a convergent rewrite system. An orthogonal
-procedure consists rather in adding new generators (new labels for
-internal nodes in the trees) in order to obtain convergent rewrite
-systems. More generally, we also would like to use these ideas for other
-magmatic quotients, such as the operad $\Mag^{\{3, 4\}}$ that we did not
-study entirely in Section~\ref{sec:MAg_3}.
+second axis consists in allowing new generators for the operads
+$\CAs{\gamma}$ in order to obtain finite convergent presentations
+when $\gamma \geq 4$. Indeed, the Buchberger semi-algorithm works by
+adding rewrite rules to a set of rewrite rules to obtain a convergent
+rewrite system. An orthogonal procedure consists rather in adding new
+generators (new labels for internal nodes in the trees) in order to
+obtain convergent rewrite systems. More generally, we also would like to
+use these ideas for other magmatic quotients, such as the operad
+$\Mag^{\{3, 4\}}$ that we did not study entirely in
+Section~\ref{sec:MAg_3}.
 \medbreak
 
-A third axis consists in studying if the completion of orientations of
-presentations of quotients of the magmatic operad maintains links with
+A third axis consists in studying if the completion of presentations of
+quotients of the magmatic operad maintains links with
 the lattice structure introduced in Section~\ref{sec:Magmatic_operads}.
-More precisely, assuming that we have completed the orientations of
-the presentations of the quotients $\Oca_1$ and $\Oca_2$ of $\Mag$,
+More precisely, assuming that we have completed the presentations of
+the quotients $\Oca_1$ and $\Oca_2$ of $\Mag$,
 as well as the one of the lower-bound $\Oca_2 \InfQMag \Oca_2$, the
 question consists in designing an algorithm for computing a completion
-of an orientation of the presentation of the upper-bound
+of a presentation of the upper-bound
 $\Oca_1 \SupQMag \Oca_2$. Of course, the same question also makes sense
@@
 \medbreak
-
-\Todo{S: attention, on emploie souvent l'expression "presentation" et
-"completion of presentation" mais on a jamais vraiment défini ce qu'est
-une presentation et ce qu'est une orientation d'une complétion. C'est
-facile, mais il faudrait le faire (préliminaires). Il faudrait d'ailleurs
-utiliser plutôt l'expression "convergent orientation of a presentation"
-plutôt que "convergent orientation".}

### 2018-09-01 Operads_rewrite.tex
Maj partie CAs
Harmonisation presentation/orientation

@@
     the rewrite relation induced by $\Rew$. Then,
-    %if $\RewContext$ is terminating,
     $\NormalForms_{\RewContext}$ is the set of all the binary trees that
@@
 orientation of $\Congr$ if $\RewContext$ is convergent (resp.
-terminating, confluent).
+terminating, confluent). In the sequel, we use the terminology of a
+\Def{presentation} of a magmatic operad $\Oca$: it is the data of an
+operad congruence $\Congr$ such that $\Oca$ is isomorphic to 
+\begin{math}
+  \Mag/_{\Congr}.
+\end{math}
+For simplicity, we say that a convergent (resp. terminating, confluent)
+orientation of $\Congr$ is a \Def{convergent} (resp. \Def{terminating},
+\Def{confluent}) \Def{presentation} of $\Oca$.
 \medbreak

### 2018-09-01 CAs_operads.tex
partie 3.3

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The \texorpdfstring{$3$}{3}-comb associative operad}
-\label{subsec:CAs_3}
-We now focus on the study of the operad $\CAs{3}$. By definition, this
-operad is the quotient of $\Mag$ by the operad congruence spanned by the
-relation
+\subsection{Completion of comb associative operads}
+We are now looking for finite convergent presentation of comb associative
+ operads.
+By definition, the operad $\CAs{\gamma}$ is the quotient of $\Mag$ by the 
+operad congruence spanned by the relation
 \begin{equation} \label{equ:rew_1}
-    \begin{tikzpicture}[xscale=.22,yscale=.23,Centering]
-        \node(0)at(0.00,-5.25){};
-        \node(2)at(2.00,-5.25){};
-        \node(4)at(4.00,-3.50){};
-        \node(6)at(6.00,-1.75){};
-        \node[NodeST](1)at(1.00,-3.50){\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
-        \node[NodeST](5)at(5.00,0.00){\begin{math}\Product\end{math}};
-        \draw[Edge](0)--(1);
-        \draw[Edge](1)--(3);
-        \draw[Edge](2)--(1);
-        \draw[Edge](3)--(5);
-        \draw[Edge](4)--(3);
-        \draw[Edge](6)--(5);
-        \node(r)at(5.00,1.5){};
-        \draw[Edge](r)--(5);
-    \end{tikzpicture}
+    \LComb{\gamma}
     \enspace \Rew \enspace
-    \begin{tikzpicture}[xscale=.22,yscale=.23,Centering]
-        \node(0)at(0.00,-1.75){};
-        \node(2)at(2.00,-3.50){};
-        \node(4)at(4.00,-5.25){};
-        \node(6)at(6.00,-5.25){};
-        \node[NodeST](1)at(1.00,0.00){\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
-        \node[NodeST](5)at(5.00,-3.50){\begin{math}\Product\end{math}};
-        \draw[Edge](0)--(1);
-        \draw[Edge](2)--(3);
-        \draw[Edge](3)--(1);
-        \draw[Edge](4)--(5);
-        \draw[Edge](5)--(3);
-        \draw[Edge](6)--(5);
-        \node(r)at(1.00,1.5){};
-        \draw[Edge](r)--(1);
-    \end{tikzpicture}\,.
+    \RComb{\gamma}\,.
 \end{equation}
@@
 \begin{equation} \label{equ:branching_pair_CAs_3}
-    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
-        \node(0)at(0.00,-7.20){};
-        \node(2)at(2.00,-7.20){};
-        \node(4)at(4.00,-5.40){};
-        \node(6)at(6.00,-3.60){};
-        \node(8)at(8.00,-1.80){};
-        \node[NodeST](1)at(1.00,-5.40){\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,-3.60){\begin{math}\Product\end{math}};
-        \node[NodeST](5)at(5.00,-1.80){\begin{math}\Product\end{math}};
-        \node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
-        \draw[Edge](0)--(1);
-        \draw[Edge](1)--(3);
-        \draw[Edge](2)--(1);
-        \draw[Edge](3)--(5);
-        \draw[Edge](4)--(3);
-        \draw[Edge](5)--(7);
-        \draw[Edge](6)--(5);
-        \draw[Edge](8)--(7);
-        \node(r)at(7.00,1.35){};
-        \draw[Edge](r)--(7);
-    \end{tikzpicture}
+    \LComb{\gamma+1}
     \enspace \RewContext \enspace
@@
         \node(2)at(2.00,-4.50){};
-        \node(4)at(4.00,-4.50){};
         \node(6)at(6.00,-6.75){};
@@
         \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
-        \node[NodeST](5)at(5.00,-2.25){\begin{math}\Product\end{math}};
+        \node[NodeST](5)at(5.30,-1.4){\begin{math}\gamma\end{math}};
         \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
@@
         \draw[Edge](2)--(1);
-        \draw[Edge](4)--(5);
-        \draw[Edge](5)--(3);
         \draw[Edge](6)--(7);
-        \draw[Edge](7)--(5);
+        \draw[Edge, dashed](7)--(3);
         \draw[Edge](8)--(7);
@@
     \qquad \mbox{and} \qquad
-    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
-        \node(0)at(0.00,-7.20){};
-        \node(2)at(2.00,-7.20){};
-        \node(4)at(4.00,-5.40){};
-        \node(6)at(6.00,-3.60){};
-        \node(8)at(8.00,-1.80){};
-        \node[NodeST](1)at(1.00,-5.40){\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,-3.60){\begin{math}\Product\end{math}};
-        \node[NodeST](5)at(5.00,-1.80){\begin{math}\Product\end{math}};
-        \node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
-        \draw[Edge](0)--(1);
-        \draw[Edge](1)--(3);
-        \draw[Edge](2)--(1);
-        \draw[Edge](3)--(5);
-        \draw[Edge](4)--(3);
-        \draw[Edge](5)--(7);
-        \draw[Edge](6)--(5);
-        \draw[Edge](8)--(7);
-        \node(r)at(7.00,1.35){};
-        \draw[Edge](r)--(7);
-    \end{tikzpicture}
+    \LComb{\gamma+1}
     \enspace \RewContext \enspace
@@
         \node(0)at(0.00,-3.60){};
-        \node(2)at(2.00,-5.40){};
         \node(4)at(4.00,-7.20){};
@@
         \node[NodeST](1)at(1.00,-1.80){\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,-3.60){\begin{math}\Product\end{math}};
+        \node[NodeST](3)at(3.25,-2.90){\begin{math}\gamma\end{math}};
         \node[NodeST](5)at(5.00,-5.40){\begin{math}\Product\end{math}};
@@
         \draw[Edge](1)--(7);
-        \draw[Edge](2)--(3);
-        \draw[Edge](3)--(1);
+        \draw[Edge,dashed](5)--(1);
         \draw[Edge](4)--(5);
-        \draw[Edge](5)--(3);
         \draw[Edge](6)--(5);
@@
 operads~\cite[Section 3.7]{DK10} with respect to the lexicographic order
-on prefix words. Following this algorithm, we need to put the right
+on prefix words. We first focus on the special case $\gamma = 3$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{The \texorpdfstring{$3$}{3}-comb associative operad}
+\label{subsubsec:CAs_3}
+Following the Buchberger algorithm, we need to put the right
 members of~\eqref{equ:branching_pair_CAs_3} in relation by $\Rew$. To
@@
 
-\Todo{S: résultats expérimentaux de quelques $\CAs{\gamma}$ à donner
-dans cette partie (ou peut être dans une sous-partie précédente ; à
-voir selon ce que ça donne).}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Higher comb asociative operads}
+
+We run the same algorithm for $\CAs{\gamma}$ when $\gamma \geq 4$.
+We obtain the following results.
+
+\begin{center}
+  \begin{math}
+    \begin{array}{|c|l|}
+      \hline
+      \gamma & \mbox{The sequence of first cardinalities of } 
+       \CAs{\gamma} \mbox{completion}\\ \hline
+      3 & 0, 0, 0, 1, 1, 2, 3, 4, 0, 0, \dots \\ \hline
+      4 & 0, 0, 0, 0, 1, 1, 0, 3, 4, 5, 18, 22, 11, 12, 15, 19, 25, 36,
+       44, 52, 68, 79, 93, 105, 106, 109 \\ \hline
+      5 & 0, 0, 0, 0, 0, 1, 1, 0, 0, 4, 5, 8, 18, 31, 36, 48, 73, 111,
+       172, 272, 455, 783 \\ \hline
+      6 & 0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 5, 6, 11, 23, 30, 48, 73, 
+      117, 204, 348, 589, 1004 \\ \hline
+      7 & 0, 0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 6, 7, 16, 24, 32, 49, 
+      88, 150, 261, 475, 854\\ \hline
+      8 & 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0, 7, 8, 21, 29, 
+      34, 53, 93, 172, 311, 565\\ \hline
+      9 & 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0, 0, 8, 9, 28, 
+      30, 36, 57, 101, 185, 348, 648\\ \hline
+    \end{array}
+  \end{math}
+\end{center}
+
+From these computer explorations, we conjecture that this algorithm
+doesn't provide a finite convergent presentation of $\CAs{\gamma}$, 
+when $\gamma \geq 4$.
+
+However, this completion algorithm depends on the other we choose. 
+We might found a finite presentation using a different order.
+
+\Todo{Expliquer algo et résultats}
+
+We conjecture that there is no finite and convergent presentation
+of $\CAs{\gamma}$ with one generator when $\gamma \geq 4$.
+We discuss the cases with more then one generator in the perspectives.
 
@@
 %\end{equation}
-%for the first dimensions for $\CAs{4}$. By applying the Buchberger
-%algorithm on trees of degrees until $10$, we obtain that a convergent
-%orientation of $\CongrCAs{4}$ has, arity by arity, the sequence
-%\begin{math}
-    %0, 0, 0, 0, 1, 1, 0, 3, 4, 5, 18, 22
-%\end{math}
-%for its first cardinalities. Moreover, for $\CAs{5}$, we get the
+%for the first dimensions for $\CAs{4}$. Moreover, for $\CAs{5}$, 
+%we get the
 %sequence

### 2018-09-02 CAs_operads.tex
Quelques corrections d'anglais

@@
       \gamma & \mbox{The sequence of first cardinalities of } 
-       \CAs{\gamma} \mbox{completion}\\ \hline
+       \CAs{\gamma} \mbox{completions}\\ \hline
       3 & 0, 0, 0, 1, 1, 2, 3, 4, 0, 0, \dots \\ \hline
@@
 From these computer explorations, we conjecture that this algorithm
-doesn't provide a finite convergent presentation of $\CAs{\gamma}$, 
+does not provide a finite convergent presentation of $\CAs{\gamma}$, 
 when $\gamma \geq 4$.

### 2018-09-02 CAs_operads.tex
partie 3.3

@@
 However, this completion algorithm depends on the other we choose.
-We might found a finite presentation using a different order.
+In order to find out if the completion algorithm leads to a finite 
+presentation using a different order, we run the following algorithm.
 
-\Todo{Expliquer algo et résultats}
+For every branching pair $(\Tfr_1, \Tfr_2)$ which is not joinable,
+we recursively try to find a completion of $\Rew$ with
+the new rule $\Tfr_1 \Rew  \Tfr_2$ and than with the new rule 
+$\Tfr_2 \Rew  \Tfr_1$. If at any moment the rewrite relation induced by
+$\Rew$ loops then we simply reject it.
+
+\Todo{résultats}
 

### 2018-09-03 CAs_operads.tex
Quelques corrections d'anglais

--- 2018-09-02 CAs_operads.tex
@@
 
-However, this completion algorithm depends on the other we choose. 
-We might found a finite presentation using a different order.
+However, this completion algorithm depends on the order we choose.
+In order to find out if the completion algorithm leads to a finite 
+convergent presentation using a different order, we run the following
+algorithm.
 
-\Todo{Expliquer algo et résultats}
+For every branching pair $(\Tfr_1, \Tfr_2)$ which is not joinable,
+we recursively try to find a completion of $\Rew$ with
+the new rule $\Tfr_1 \Rew  \Tfr_2$ and with the new rule 
+$\Tfr_2 \Rew  \Tfr_1$. If at any moment the rewrite relation induced by
+$\Rew$ loops then we simply reject it.
+
+\Todo{résultats}
 

### 2018-09-03 CAs_operads.tex
MAJ partie 3.3

@@
 \label{subsubsec:CAs_3}
-Following the Buchberger algorithm, we need to put the right
-members of~\eqref{equ:branching_pair_CAs_3} in relation by $\Rew$. To
-respect the lexicographic property of the prefix words, this leads to
-the new relation
-\begin{equation} \label{equ:rew_2}
-    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
-        \node(0)at(0.00,-3.60){};
-        \node(2)at(2.00,-5.40){};
-        \node(4)at(4.00,-7.20){};
-        \node(6)at(6.00,-7.20){};
-        \node(8)at(8.00,-1.80){};
-        \node[NodeST](1)at(1.00,-1.80){\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,-3.60){\begin{math}\Product\end{math}};
-        \node[NodeST](5)at(5.00,-5.40){\begin{math}\Product\end{math}};
-        \node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
-        \draw[Edge](0)--(1);
-        \draw[Edge](1)--(7);
-        \draw[Edge](2)--(3);
-        \draw[Edge](3)--(1);
-        \draw[Edge](4)--(5);
-        \draw[Edge](5)--(3);
-        \draw[Edge](6)--(5);
-        \draw[Edge](8)--(7);
-        \node(r)at(7.00,1.5){};
-        \draw[Edge](r)--(7);
-    \end{tikzpicture}
-    \enspace \Rew \enspace
-    \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
-        \node(0)at(0.00,-4.50){};
-        \node(2)at(2.00,-4.50){};
-        \node(4)at(4.00,-4.50){};
-        \node(6)at(6.00,-6.75){};
-        \node(8)at(8.00,-6.75){};
-        \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
-        \node[NodeST](5)at(5.00,-2.25){\begin{math}\Product\end{math}};
-        \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
-        \draw[Edge](0)--(1);
-        \draw[Edge](1)--(3);
-        \draw[Edge](2)--(1);
-        \draw[Edge](4)--(5);
-        \draw[Edge](5)--(3);
-        \draw[Edge](6)--(7);
-        \draw[Edge](7)--(5);
-        \draw[Edge](8)--(7);
-        \node(r)at(3.00,1.74){};
-        \draw[Edge](r)--(3);
-    \end{tikzpicture}\,.
-\end{equation}
-The Buchberger algorithm applied on binary trees of degrees $5$, $6$,
-and $7$ provides the new relations \smallbreak
-\input{Buchberger_relations_5-7}
+
+The Buchberger algorithm applied on binary trees of degrees $4$ to $7$ 
+provides the new relations \smallbreak
+\input{Buchberger_relations_CAs3}
 \medbreak
@@
     The set $\Rew$ of rewrite rules containing~\eqref{equ:rew_1},
-    \eqref{equ:rew_2}, \eqref{equ:rew_3}---\eqref{equ:rew_11} is a
+    and \eqref{equ:rew_2}---\eqref{equ:rew_11} is a
     convergent presentation of~$\CAs{3}$.
@@
 \begin{center}
-  \begin{math}
+  \begin{math} \label{arr:completions_CAs}
     \begin{array}{|c|l|} 
@@
 \end{center}
+\medbreak
 
@@
 does not provide a finite convergent presentation of $\CAs{\gamma}$, 
-when $\gamma \geq 4$.
+when $\gamma \ge 4$.
 
@@
 
-\Todo{résultats}
-
+We did not found a finite presentation for $\CAs{4}$, $\CAs{5}$ and 
+$\CAs{6}$ until arity $12$. 
 We conjecture that there is no finite and convergent presentation
@@
 We discuss the cases with more then one generator in the perspectives.
+\medbreak
 
-%By computer exploration, we have already some information in this
-%direction: we have the sequence
-%\begin{equation}
-    %1, 1, 2, 5, 13, 35, 96, 264, 724, 1973, 5335, 14390, 38872, 105141,
-    %284929, 774254
-%\end{equation}
-%for the first dimensions for $\CAs{4}$. Moreover, for $\CAs{5}$, 
-%we get the
-%sequence
-%\begin{equation}
-%1, 1, 2, 5, 14, 41, 124, 384, 1210, 3861, 12440, 40392, 131997,
-%433782, 1432696, 4752857
-%\end{equation}
-%of dimensions and the first cardinalities
-%\begin{math}
-    %0, 0, 0, 0, 0, 1, 1, 0, 0, 4, 5
-%\end{math}
-%for any convergent orientation of $\CongrCAs{5}$. Finally, for
-%$\CAs{6}$, we get the sequence
-%\begin{equation}
-   %1, 1, 2, 5, 14, 42, 131, 420, 1375, 4576, 15431, 52598,
-   %180895, 626862, 2186504, 7670138
-%\end{equation}
-%of dimensions and the first cardinalities
-%\begin{math}
-    %0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0
-%\end{math}
-%for any convergent orientation of $\CongrCAs{6}$. We can notice that
-%only $\CAs{3}$ seems to have oscillating first dimensions.
-%\medbreak
+Thanks to the partial completions we compute in table
+\eqref{arr:completions_CAs}, we can compute the following first 
+dimensions of $\CAs{\gamma}$.
+\begin{center}
+  \begin{math} \label{arr:dimensions_CAs}
+    \begin{array}{|c|l|} 
+      \hline
+      \gamma & \mbox{The sequence of first cardinalities of } 
+       \CAs{\gamma}\\ \hline
+      4 & 1, 1, 2, 5, 13, 35, 96, 264, 724, 1973, 5335, 14390, 38872,
+          105141, 284929, 774254, 2111088,\\
+        & 5778420, 15882100, 43837388, 121507230 \\ \hline
+      5 & 1, 1, 2, 5, 14, 41, 124, 384, 1210, 3861, 12440, 40392, 131997,
+          433782, 1432696, 4752857, \\ 
+        & 15829261, 52905635, 177395246 \\ \hline
+      6 & 1, 1, 2, 5, 14, 42, 131, 420, 1375, 4576, 15431, 52598, 180895,
+          626862, 2186504, 7670138, \\ 
+        & 27041833, 95764569 \\ \hline
+      7 & 1, 1, 2, 5, 14, 42, 132, 428, 1420, 4796, 16432, 56966, 199444,
+          704140, 2503914, 8959699, \\
+        & 32236657, 116551168\\ \hline
+      8 & 1, 1, 2, 5, 14, 42, 132, 429, 1429, 4851, 16718, 58331, 205632,
+          731272, 2620176, 9449688, \\
+        & 34276116, 124958386\\ \hline
+      9 & 1, 1, 2, 5, 14, 42, 132, 429, 1430, 4861, 16784, 58695, 207452,
+          739840, 2658936, 9620232, \\
+        & 35011566, 128082515\\ \hline
+    \end{array}
+  \end{math}
+\end{center}

### 2018-09-03 Introduction.tex
Ajout remerciements
Quelques corrections sur l'intro, sections 1 et 2

@@
 associative algebras~\cite{Ani86}, the description of an operad by mean
-of normal forms provides homological information for this operad. One of
+of normal forms provides homological informations for this operad. One of
 the fundamental homological properties for operads is
 Koszulness~\cite{GK94}, generalizing Koszul associative
-algebras~\cite{Pri70}: the convergent orientation of $\As$ proves that
-it is a Koszul operad~\cite{LV12}.
+algebras~\cite{Pri70}: the convergent orientation
+of~\eqref{equ:congruence_as} proves that $\As$ is a Koszul
+operad~\cite{LV12}.
 \medbreak
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection*{Acknoledgements}
+The authors wish to thank Maxime Lucas for helpfull discussions and
+Vladimir Dotsenko for his mark of interest to this work.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection*{General notations and conventions}

### 2018-09-03 Magmatic_operads.tex
Quelques corrections sur l'intro, sections 1 et 2

@@
 operad over one binary generator. By definition, for each arity $n$,
-$\KMag(n)$ is the vector space with basis $\Mag(n)$, and the
+$\KMag(n)$ is the vector space with basis $\Mag(n)$ and the
 compositions maps of $\KMag$ extend by linearity the ones of $\Mag$.
@@
 
-We denote by $\IMag$ the set of operadic ideals of $\KMag$, and we set
+We denote by $\IMag$ the set of operadic ideals of $\KMag$ and we set
 \begin{equation} \label{equ:definition_of_QMag}
@@
 $\Oca_2$ of $\QMag$, we denote by $\Hom\left(\Oca_1,\Oca_2\right)$ the
-set of linear operad morphism from $\Oca_1$ to~$\Oca_2$.
+set of linear operad morphisms from $\Oca_1$ to~$\Oca_2$.
 \medbreak

### 2018-09-03 Operads_rewrite.tex
Quelques corrections mineures
Correction erreur compilation
Quelques corrections sur l'intro, sections 1 et 2

@@
     x \circ \left[y_1, \dots, y_n\right] :=
-    \left(\dots \left(\left(x \circ_n y_n\right)
-    \circ_{n - 1} y_{n - 1}\right) \dots\right) \circ_1 y_1.
+    \left(\cdots \left(\left(x \circ_n y_n\right)
+    \circ_{n - 1} y_{n - 1}\right) \cdots\right) \circ_1 y_1.
 \end{equation}
@@
 
-Let $\Rew$ be a set of rewrite rules and $\RewContext$ be rewrite
+Let $\Rew$ be a set of rewrite rules and $\RewContext$ be the rewrite
 relation induced by $\Rew$. Since $\RewContext$ is in particular a
@@
 \end{equation}
-A set of rewrite rules $\Rew$ is an \Def{orientation} of $\Congr$ if
-$\RewContextRST$ and $\Congr$ are equal as binary relations, where
-$\RewContext$ is the rewrite relation induced by $\Rew$. Moreover,
+A set of rewrite rules $\Rew$ on $\Mag$ is an \Def{orientation} of
+$\Congr$ if $\RewContextRST$ and $\Congr$ are equal as binary relations,
+where $\RewContext$ is the rewrite relation induced by $\Rew$. Moreover,
 $\Rew$ is a \Def{convergent} (resp. \Def{terminating}, \Def{confluent})
@@
 terminating, confluent). In the sequel, we use the terminology of a
-\Def{presentation} of a magmatic operad $\Oca$: it is the data of an
-operad congruence $\Congr$ such that $\Oca$ is isomorphic to 
+\Def{presentation} of an operad $\Oca$ generated by one binary generator:
+it is the data of an operad congruence $\Congr$ of $\Mag$ such that
+$\Oca$ is isomorphic to
 \begin{math}
@@
 
-  \item Otherwise, let $\Tfr$ be a branching tree for $\RewContext'$.
-    Remove $\Tfr$ from $\BranchingTrees$.
+  \item\label{item:choice_branching_tree} Otherwise, let $\Tfr$ be a
+    branching tree for $\RewContext'$. Remove $\Tfr$ from
+    $\BranchingTrees$.
     \smallbreak
 
-    \item Let $\{\Sfr_1, \Sfr_2\}$ be a branching pair for $\Tfr$.
+  \item\label{item:choice_branching_pair} Let $\{\Sfr_1, \Sfr_2\}$ be a
+    branching pair for $\Tfr$.
     \smallbreak
 
-  \item Let $\overline{\Sfr_1}$ and $\overline{\Sfr_2}$ be normal forms
-    of $\Sfr_1$ and $\Sfr_2$, respectively.
+  \item\label{item:computed_normal_forms} Let $\overline{\Sfr_1}$ and
+    $\overline{\Sfr_2}$ be normal forms of $\Sfr_1$ and $\Sfr_2$,
+    respectively.
     \smallbreak
@@
 \end{enumerate}
-The set of rewrite rules $\Rew'$ outputted by this semi-algorithm is the
+The set of rewrite rules $\Rew'$ outputted by this semi-algorithm is a
 \Def{completion} of $\Rew$. By Lemma~\ref{lem:degree_confluence},
@@
 completion depend on the total order $\leq$ on the binary trees of a
-same arity.
+same arity, the choices at steps~\ref{item:choice_branching_tree}
+and~\ref{item:choice_branching_pair} as well as the computed normal forms
+at step~\ref{item:computed_normal_forms}.
 \medbreak

### 2018-09-03 CAs_operads.tex
Quelques corrections

@@
 
-As explained in Section~\ref{sec:operad_Mag}, a set-theoreic operad can
+As explained in Section~\ref{sec:operad_Mag}, a set-theoretic operad can
 be embedded into a linear operad, so that the operads $\CAs{\gamma}$ can
@@
 
-Note that $\LatKCAs$ does not embed as a sub-lattice of $\LatQMag$, that
+Note that $\LatKCAs$ does not embed as a sublattice of $\LatQMag$, that
 is $\iota$ is not a lattice morphism. Consider for instance $\gamma = 3$
-and $\gamma' = 4$, then $\KCAs{\gamma} \InfCAs \KCAs{\gamma'}$ is equal
-to $\KCAs{2} = \K\As$, whereas $\KCAs{\gamma} \InfQMag \KCAs{\gamma'}$
-is a quotient of $\KMag$ be the two relations $\LComb{3} - \RComb{3}$
-and $\LComb{4} - \RComb{4}$.
+and $\gamma' = 4$, so that $\KCAs{\gamma} \InfCAs \KCAs{\gamma'}$ is
+equal to $\KCAs{2} = \K\As$, whereas
+$\KCAs{\gamma} \InfQMag \KCAs{\gamma'}$ is the quotient of $\KMag$ by the
+two relations $\LComb{3} - \RComb{3}$ and $\LComb{4} - \RComb{4}$.
 \medbreak
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Higher comb asociative operads}
+\subsubsection{Higher comb associative operads}
 

### 2018-09-03 Magmatic_operads.tex
Quelques corrections

@@
 
+The union of generating sets of the two operadic ideals $I_1$ and $I_2$
+is a generating set of $I_1+I_2$, so that the union of generating
+relations for the two operads $\Oca_1$ and $\Oca_2$ of $\QMag$ forms a
+generating set for the relations of $\Oca_1\InfQMag\Oca_2$. However, we
+do not know how to perform the same method for computing generating
+relations for $\Oca_1\SupQMag\Oca_2$ since we do not know how to compute
+generating sets of the intersection of two operadic ideals.
+\medbreak
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-09-04 CAs_operads.tex
Fin relecture Cyrille

@@
 \begin{Lemma} \label{lem:surjective_morphisms_CAs}
-    Let $\gamma$ and $\gamma'$ be two positive integers. If
-    $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$ is an operad morphism, then
-    it is surjective and is unique.
+    Let $\gamma$ and $\gamma'$ be two positive integers. If there exists
+    an operad morphism $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$, then it
+    is surjective and unique.
 \end{Lemma}
@@
     The operad $\CAs{\gamma'}$ is generated by one binary generator
-    $[\Product]_{\CongrCAs{\gamma'}}$, which is the image of $\Product$
-    in $\CAs{\gamma'}$. Hence, $\varphi$ is entirely determined by the
-    image $\varphi\left([\Product]_{\CongrCAs{\gamma'}}\right)$.
-    Moreover, $\varphi([\Product]_{\CongrCAs{\gamma'}})$ has to be of
-    arity $2$ in $\CAs{\gamma}$, so that we necessarily have
+    $[\Product]_{\CongrCAs{\gamma'}}$, which is the image of the binary
+    generator $\Product$ of $\Mag$ in $\CAs{\gamma'}$. Hence, $\varphi$
+    is entirely determined by the image
+    $\varphi\left([\Product]_{\CongrCAs{\gamma'}}\right)$. Moreover,
+    $\varphi([\Product]_{\CongrCAs{\gamma'}})$ has to be of arity $2$ in
+    $\CAs{\gamma}$, so that we necessarily have
     \begin{math}
@@
     Hence, if $\varphi$ exists, it is the unique operad morphism from
-    $\CAs{\gamma'}$ to $\CAs{\gamma}$. In this case,
-    $[\Product]_{\CongrCAs{\gamma'}}$ being in the image of $\varphi$,
-    the latter is surjective.
+    $\CAs{\gamma'}$ to $\CAs{\gamma}$ determined by the previous formula.
+    In this case, $[\Product]_{\CongrCAs{\gamma}}$ being in the image of
+    $\varphi$, the latter is surjective.
 \end{proof}
@@
     $\bar{\gamma} \mid \bar{\gamma'}$. If
-    $\LComb{\gamma'}\CongrCAs{\gamma}\RComb{\gamma'}$, from
-    Lemma~\ref{lem:left_rank_and_CongrCAs},
+    $\LComb{\gamma'}\CongrCAs{\gamma}\RComb{\gamma'}$, $\gamma$ is
+    smaller than $\gamma'$ (this is a consequence of the existence of a
+    surjective morphism $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$ and
+    Lemma~\ref{lem:first_dimensions_CAs}). From
+    Lemma~\ref{lem:left_rank_and_CongrCAs}, we deduce that
     \begin{math}
@@
 By definition, the operad $\CAs{\gamma}$ is the quotient of $\Mag$ by the 
-operad congruence spanned by the relation
+operad congruence spanned by the rewrite rule
 \begin{equation} \label{equ:rew_1}
@@
 However, the rewrite relation $\RewContext$ induced by $\Rew$ is not
-confluent. Indeed, we have
+confluent for $\gamma\geq 3$. Indeed, we have
 \begin{equation} \label{equ:branching_pair_CAs_3}
@@
 on prefix words. We first focus on the special case $\gamma = 3$.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The Buchberger algorithm applied on binary trees of degrees $4$ to $7$ 
-provides the new relations \smallbreak
+provides the new rewrite rules \smallbreak
 \input{Buchberger_relations_CAs3}
@@
     Equivalently, this amounts to show that the number of normal forms
-    of trees of arity $n$ is equal to $\#\CAs{3}(n)$. By computer
+    of trees of arity $n\leq 14$ is equal to $\#\CAs{3}(n)$. By computer
     exploration, we get the same sequence
@@
     for $\#\CAs{3}(n)$ and for the numbers of normal forms of arity $n$,
-    when $ 1 \leq n \leq 14$. Hence, we get our following main result.
+    when $ 1 \leq n \leq 14$, which proves
+    Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}.
 \end{proof}
@@
 \end{equation}
-We obtain from Theorem~\ref{thm:convergent_rewrite_rule_CAs_3} also
+We also obtain from Theorem~\ref{thm:convergent_rewrite_rule_CAs_3} 
 the following consequences.
@@
 \subsubsection{Higher comb associative operads}
+\label{sec:higher_comb_associative_operads}
 
@@
 
-We did not found a finite presentation for $\CAs{4}$, $\CAs{5}$ and 
+We did not find a finite presentation for $\CAs{4}$, $\CAs{5}$ and 
 $\CAs{6}$ until arity $12$. 
@@
 
-Thanks to the partial completions we compute in table
+Thanks to the partial completions presented in table
 \eqref{arr:completions_CAs}, we can compute the following first 

### 2018-09-04 CAs_operads.tex
Fin relecture Cyrille

@@
 \subsection{Completion of comb associative operads}
-We are now looking for finite convergent presentation of comb associative
- operads.
-By definition, the operad $\CAs{\gamma}$ is the quotient of $\Mag$ by the 
-operad congruence spanned by the rewrite rule
+We are now looking for finite convergent presentations of comb
+associative operads. By definition, the operad $\CAs{\gamma}$ is the
+quotient of $\Mag$ by the operad congruence spanned by the rewrite rule
 \begin{equation} \label{equ:rew_1}
@@
     The set $\Rew$ of rewrite rules containing~\eqref{equ:rew_1},
-    and \eqref{equ:rew_2}---\eqref{equ:rew_11} is a
+    and \eqref{equ:rew_2}---\eqref{equ:rew_11} is a finite
     convergent presentation of~$\CAs{3}$.
@@
 $\CAs{6}$ until arity $12$. 
-We conjecture that there is no finite and convergent presentation
+We conjecture that there is no finite convergent presentation
 of $\CAs{\gamma}$ with one generator when $\gamma \geq 4$.

### 2018-09-04 Operads_rewrite.tex
Fin relecture Cyrille

@@
 \Def{presentation} of an operad $\Oca$ generated by one binary generator:
-it is the data of an operad congruence $\Congr$ of $\Mag$ such that
-$\Oca$ is isomorphic to
+it is the data of a generating set of an operad congruence $\Congr$ of
+$\Mag$ such that $\Oca$ is isomorphic to
 \begin{math}
@@
 \end{math}
-For simplicity, we say that a convergent (resp. terminating, confluent)
+A presentation is said to be \Def{finite} if it is a finite set. For
+simplicity, we say that a convergent (resp. terminating, confluent)
 orientation of $\Congr$ is a \Def{convergent} (resp. \Def{terminating},

### 2018-09-04 Article.tex
Maj partie CAs
Maj conclusion
Relecture

@@
 % Creation: may. 2018
-% Modifications: may. 2018, june 2018, july 2018, aug. 2018
+% Modifications: may. 2018, june 2018, july 2018, aug. 2018, sep.2018
 
@@
 \newcommand{\GeneratingSet}{\mathfrak{G}}
-\newcommand{\FreeOperad}{\mathrm{F}}
-\newcommand{\Mag}{\mathsf{Mag}}
+
+\newcommand{\FreeOperad}{\mathbf{F}}
+\newcommand{\Mag}{\mathbf{Mag}}
+\newcommand{\TwoMag}{2\Mag}
 \newcommand{\KMag}{\K \Angle{\Mag}}
@@
 \newcommand{\IMag}{\mathcal{I}\left(\KMag\right)}
-\newcommand{\As}{\mathsf{As}}
-\newcommand{\CAs}[1]{\mathsf{CAs}^{\left(#1\right)}}
+\newcommand{\As}{\mathbf{As}}
+\newcommand{\TwoAs}{2\As}
 \newcommand{\CAsAll}{\mathbf{CAs}}
+\newcommand{\CAs}[1]{\CAsAll^{\left(#1\right)}}
 \newcommand{\KCAs}[1]{\K\CAs{#1}}
 \newcommand{\KCAsAll}{\K\CAsAll}
+
 \newcommand{\PrefixWord}{\mathrm{p}}
@@
 \newcommand{\Catalan}{\mathrm{cat}}
-\newcommand{\OrdQMag}{\preceq_{\mathrm{incl}}}
-\newcommand{\InfQMag}{\wedge_{\mathrm{incl}}}
-\newcommand{\SupQMag}{\vee_{\mathrm{incl}}}
+\newcommand{\OrdQMag}{\preceq_{\mathrm{i}}}
+\newcommand{\InfQMag}{\wedge_{\mathrm{i}}}
+\newcommand{\SupQMag}{\vee_{\mathrm{i}}}
 \newcommand{\LatQMag}{\left(\QMag,\OrdQMag,\InfQMag,\SupQMag\right)}
-\newcommand{\OrdCAs}{\preceq_{\mathrm{div}}}
-\newcommand{\InfCAs}{\wedge_{\mathrm{div}}}
-\newcommand{\SupCAs}{\vee_{\mathrm{div}}}
+\newcommand{\OrdCAs}{\preceq_{\mathrm{d}}}
+\newcommand{\InfCAs}{\wedge_{\mathrm{d}}}
+\newcommand{\SupCAs}{\vee_{\mathrm{d}}}
 \newcommand{\LatCAs}{\left(\CAsAll,\OrdCAs,\InfCAs,\SupCAs\right)}
@@
     correspondence with~$3$. Finally, we study quotients of the magmatic
-    operad by one relation of degree three by studying their Hilbert
-    series and providing combinatorial realizations.
+    operad by one cubic relation by expressing their Hilbert series and
+    providing combinatorial realizations.
 \end{abstract}

### 2018-09-04 CAs_operads.tex
Relecture

@@
 In this section, we define comb associative operads and we show that the
-set of such operads admits a lattice structure, isomorphic to the lattice
-division for nonnegative integers. We relate this lattice to the
-lattice of linear magmatic quotients. We also provide a finite convergent
-presentation of the comb associative operad corresponding to $3$.
+set of such operads admits a lattice structure, isomorphic to the
+lattice division for nonnegative integers. We relate this lattice to the
+lattice of linear magmatic quotients. We also provide a finite
+convergent presentation of the comb associative operad corresponding
+to~$3$.
 \medbreak
@@
 Let, for any integer $\gamma \geq 1$, the binary trees $\LComb{\gamma}$
-and $\RComb{\gamma}$ be respectively the left and the right comb of
+and $\RComb{\gamma}$ be respectively the left and the right combs of
 degree $\gamma$. These trees are depicted as
@@
 Notice that $\CongrCAs{1}$ is trivial so that
-$\CAs{1} = \Mag$ and that $\CongrCAs{2}$ is the operad congruence
+$\CAs{1} = \Mag$, and that $\CongrCAs{2}$ is the operad congruence
 defining $\As$ so that $\CAs{2} = \As$. Let also
@@
 \subsection{Lattice of comb associative operads}
-
-In order to introduce the lattice structure of $\CAsAll$, we study operad
-morphisms betweeen its elements by mean of intermediate lemmas.
+In order to introduce a lattice structure on $\CAsAll$, we begin by
+studying operad morphisms between its elements by mean of intermediate
+lemmas.
 \medbreak
@@
 \end{Lemma}
-
 \begin{proof}
@@
     degree $d$ has arity $n := d + 1$, one has
-    $\# \CAs{\gamma}(n) = \# \Mag(n) = \Catalan(n)$ with $n \leq \gamma$.
-    Besides, by definition of $\CongrCAs{\gamma}$, all the
-    $\CongrCAs{\gamma}$-equivalence classes of binary trees of degree
-    $\gamma$ are trivial, except one consisting in the pair
+    $\# \CAs{\gamma}(n) = \# \Mag(n) = \Catalan(n)$ with
+    $n \leq \gamma$. Besides, by definition of $\CongrCAs{\gamma}$, all
+    the $\CongrCAs{\gamma}$-equivalence classes of binary trees of
+    degree $\gamma$ are trivial, except one consisting in the pair
     $\left\{\LComb{\gamma}, \RComb{\gamma}\right\}$. Therefore, since a
@@
 \end{Proposition}
-
 \begin{proof}
@@
 $\lcm$ the least common multiple operators, respectively.
+\medbreak
 
-Recall that
-$\LRank(\Tfr)$ denotes the left rank of a binary tree $\Tfr$, defined in
-Section~\ref{sec:operad_Mag}. Besides, to simplify the notation,
-we shall write $\bar{a}$ instead of $a - 1$ for any integer $a$.
+Recall that $\LRank(\Tfr)$ denotes the left rank of a binary tree
+$\Tfr$, defined in Section~\ref{sec:operad_Mag}. Besides, to simplify
+the notation, we shall write $\bar{a}$ instead of $a - 1$ for any
+integer~$a$.
 \medbreak
@@
     \end{math}
+    \Todo{S: notation ? Je n'ai pas encore bien relu cette démo.}
     Thus, if $\Tfr \RewContext \Tfr'$, then one of the following two
@@
     We deduce from~\eqref{eq:rewriting_invariant} that the equivalence
-    relation $r$ defined by 
+    relation $\simeq$ defined by
     \begin{equation}
-        r(\Tfr, \Tfr') \mbox{ if and only if } 
+        \Tfr \simeq \Tfr' \mbox{ if and only if }
         \LRank\left(\Tfr'\right) = \LRank\left(\Tfr\right)
@@
             \draw[Edge](r)--(13);
-            %
-            %\node[fit=(1)(3),rotate fit=0,inner sep=0pt,
-                %rounded corners,draw=Col5!80]{};
-            %\node[fit=(5)(7),rotate fit=0,inner sep=0pt,
-                %rounded corners,draw=Col5!80]{};
-            %\node[fit=(9)(11),rotate fit=0,inner sep=0pt,
-                %rounded corners,draw=Col5!80]{};
         \end{tikzpicture}
@@
             \draw[Edge](r)--(9);
-            %
-            %\node[fit=(1)(3),rotate fit=0,inner sep=0pt,
-                %rounded corners,draw=Col5!80]{};
-            %\node[fit=(5)(7),rotate fit=0,inner sep=0pt,
-                %rounded corners,draw=Col5!80]{};
-            %\node[fit=(11)(13),rotate fit=0,inner sep=0pt,
-                %rounded corners,draw=Col5!80]{};
         \end{tikzpicture} \\
@@
             \draw[Edge](r)--(5);
-            %
-            %\node[fit=(1)(3),rotate fit=0,inner sep=0pt,
-                %rounded corners,draw=Col5!80]{};
-            %\node[fit=(7)(9),rotate fit=0,inner sep=0pt,
-                %rounded corners,draw=Col5!80]{};
-            %\node[fit=(11)(13),rotate fit=0,inner sep=0pt,
-                %rounded corners,draw=Col5!80]{};
         \end{tikzpicture}
@@
             \draw[Edge](r)--(1);
-            %
-            %\node[fit=(3)(5),rotate fit=0,inner sep=0pt,
-                %rounded corners,draw=Col5!80]{};
-            %\node[fit=(7)(9),rotate fit=0,inner sep=0pt,
-                %rounded corners,draw=Col5!80]{};
-            %\node[fit=(11)(13),rotate fit=0,inner sep=0pt,
-                %rounded corners,draw=Col5!80]{};
         \end{tikzpicture}
@@
 
-The lattice $\left(\N,\mid, \gcd, \lcm\right)$ admits $1$ as minimum
+The lattice $\left(\N, \mid, \gcd, \lcm\right)$ admits $1$ as minimum
 element and $0$ as maximum element: any nonnegative integer is
@@
 $\As$ and is a quotient of $\Mag$.
+\medbreak
 
-We terminate this section by relating the lattice
-$\LatQMag$ introduced in Section~\ref{sec:Magmatic_operads} to the
-lattice $\LatCAs$.
-
-As explained in Section~\ref{sec:operad_Mag}, a set-theoretic operad can
+We end this section by relating the lattice $\LatQMag$ introduced in
+Section~\ref{sec:Magmatic_operads} with the lattice $\LatCAs$. As
+explained in Section~\ref{sec:operad_Mag}, a set-theoretic operad can
 be embedded into a linear operad, so that the operads $\CAs{\gamma}$ can
@@
 $I_{\gamma}$ is the operadic ideal of $\KMag$ generated by
-$\LComb{\gamma}-\RComb{\gamma}$.
-
-We obtain a new lattice $\LatKCAs$, where $\KCAsAll$ is the set of all
-operads $\KCAs{\gamma}$. In this linear framework, the condition
-$\KCAs{\gamma}\OrdCAs\KCAs{\gamma'}$ means that the dimension of the
-space $\text{hom}\left(\KCAs{\gamma'},\KCAs{\gamma}\right)$ is equal to
-$1$. Hence, $\LatKCAs$ is related to $\LatQMag$ by the following
-theorem.
+$\LComb{\gamma}-\RComb{\gamma}$. We obtain a new lattice $\LatKCAs$,
+where $\KCAsAll$ is the set of all operads $\KCAs{\gamma}$. In this
+linear framework, the condition $\KCAs{\gamma}\OrdCAs\KCAs{\gamma'}$
+means that the dimension of the space
+$\Hom\left(\KCAs{\gamma'},\KCAs{\gamma}\right)$ is equal to $1$. Hence,
+$\LatKCAs$ is related to $\LatQMag$ by the following theorem.
+\medbreak
 
@@
         \draw[Edge](6)--(7);
-        \draw[Edge, dashed](7)--(3);
+        \draw[Edge, dotted](7)--(3);
         \draw[Edge](8)--(7);
@@
         \draw[Edge](1)--(7);
-        \draw[Edge,dashed](5)--(1);
+        \draw[Edge,dotted](5)--(1);
         \draw[Edge](4)--(5);
@@
 and the two right members of~\eqref{equ:branching_pair_CAs_3} form a
-branching pair which is not joinable.
+branching pair which is not joinable (since these two trees are
+normal forms of $\RewContext$).
 \medbreak
@@
 on prefix words. We first focus on the special case $\gamma = 3$.
+\medbreak
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We obtain the following results.
+\medbreak
 
+\Todo{S:remettre la table en forme.}
 \begin{center}
@@
 does not provide a finite convergent presentation of $\CAs{\gamma}$,
-when $\gamma \ge 4$.
-
-However, this completion algorithm depends on the order we choose.
-In order to find out if the completion algorithm leads to a finite 
-convergent presentation using a different order, we run the following
-algorithm.
-
-For every branching pair $(\Tfr_1, \Tfr_2)$ which is not joinable,
-we recursively try to find a completion of $\Rew$ with
-the new rule $\Tfr_1 \Rew  \Tfr_2$ and with the new rule 
-$\Tfr_2 \Rew  \Tfr_1$. If at any moment the rewrite relation induced by
-$\Rew$ loops then we simply reject it.
-
-We did not find a finite presentation for $\CAs{4}$, $\CAs{5}$ and 
-$\CAs{6}$ until arity $12$. 
-We conjecture that there is no finite convergent presentation
-of $\CAs{\gamma}$ with one generator when $\gamma \geq 4$.
-We discuss the cases with more then one generator in the perspectives.
+when $\gamma \geq 4$.
 \medbreak
 
+\Todo{S: j'ai un peu réécrit les explications suivantes, vérifier que
+je n'ai pas introduit de bétise(s).}
+However, the completion algorithm we used depends on the chosen order on
+the trees. In order to find out if the completion algorithm leads to a
+finite convergent presentation using a different order, we run the
+following algorithm. For every branching pair $(\Tfr_1, \Tfr_2)$ which
+is not joinable, we recursively try to find a completion of $\Rew$ by
+adding either the rule $\Tfr_1 \Rew  \Tfr_2$ or $\Tfr_2 \Rew  \Tfr_1$.
+If at any moment the rewrite relation induced by $\Rew$ is no
+antisymmetric, we simply reject it.
+\medbreak
+
+We did not find a finite presentation for $\CAs{4}$, $\CAs{5}$, and
+$\CAs{6}$ until arity $12$. We conjecture that there is no finite
+convergent presentation of $\CAs{\gamma}$ with one generator when
+$\gamma \geq 4$. We discuss the cases with more than one generator in
+the perspectives.
+\medbreak
+
+\Todo{S: la numérotation de la table n'apparait pas (mais je m'occuperai
+de la faire marcher quand je ferai la remise en forme.}
 Thanks to the partial completions presented in table
@@
       \hline
-      \gamma & \mbox{The sequence of first cardinalities of } 
+      \gamma & \mbox{The sequence of first dimensions of }
        \CAs{\gamma}\\ \hline
@@
 \end{center}
+\medbreak
+
+\Todo{S:remettre la table en forme.}
+\Todo{S: pourquoi rappeler $\CAs{3}$ dans la table d'avant et pas dans
+celle-ci ?}

### 2018-09-04 Introduction.tex
Relecture

@@
 of~\eqref{equ:congruence_as} proves that $\As$ is a Koszul
-operad~\cite{LV12}.
+operad~\cite{DK10,LV12}.
 \medbreak
@@
 
-To explore this vast research area, we select to follow in this paper
+To explore this vast research area, we select to pursue in this paper
 the following directions. First, we consider the very general set of the
-quotients of $\Mag$ seen as a operad in the category of vector spaces.
+quotients of $\Mag$ seen as an operad in the category of vector spaces.
 We show that these operads form a lattice, wherein its partial order
@@
 For all these, we use rewrite systems on trees~\cite{BN98} and the
-Buchberger algorithm for operads~\cite{DK10}. Finally, we continue the
+Buchberger algorithm for operads~\cite{DK10}. We expose some
+experimental results obtained with the help of the computer for some
+operads $\CAs{\gamma}$ with $\gamma \geq 4$. Finally, we continue the
 investigation of the quotients of $\Mag$ by regarding the quotients of
@@
 Vladimir Dotsenko for his mark of interest to this work.
+\medbreak
 

### 2018-09-04 Magmatic_operads.tex
Relecture

@@
 In this section, we equip the set of quotients of the linear magmatic
-operad with a lattice structure. We also show the Grassmann formula
+operad with a lattice structure. We also show a Grassmann formula
 analog for this lattice.
@@
 $\KMag(n)$ is the vector space with basis $\Mag(n)$ and the
-compositions maps of $\KMag$ extend by linearity the ones of $\Mag$.
+compositions maps of $\KMag$ are the extensions by linearity the ones
+of~$\Mag$.
 \medbreak
@@
   dimension at most~$1$, it contains a nonzero morphism if and only if
-  the morphism $\overline{\varphi}:\Oca_1\to\Oca_2$ satisfying
-  $\overline{\varphi}([\Product]_{I_1})=[\Product]_{I_2}$ is well
-  -defined, which means that $\Oca_2\OrdQMag\Oca_1$ is equivalent to this
+  the morphism $\bar{\varphi}:\Oca_1\to\Oca_2$ satisfying
+  $\bar{\varphi}([\Product]_{I_1})=[\Product]_{I_2}$ is well-defined,
+  which means that $\Oca_2\OrdQMag\Oca_1$ is equivalent to this
   condition. Moreover, by the universal property of the quotient,
-  $\overline{\varphi}$ is well-defined if and only if $I_1$ is included
+  $\bar{\varphi}$ is well-defined if and only if $I_1$ is included
   in the kernel of the morphism $\varphi:\KMag\to\Oca_2$ defined by
   $\varphi(\Product)=[\Product]_{I_1}$. This kernel is equal to
-  $I_2$, so that $\overline{\varphi}$ is well-defined if and only if
+  $I_2$, so that $\bar{\varphi}$ is well-defined if and only if
   $I_1$ is included in $I_2$, which concludes the proof.
@@
 
-Given two operad $\Oca_1=\KMag/_{I_1}$ and $\Oca_2=\KMag/_{I_2}$ of
+\Todo{S: je l'écris ici pour l'écrire quelque part: on devrait
+homogénéiser l'usage des $:=$ et des $=$.}
+Given two operads $\Oca_1=\KMag/_{I_1}$ and $\Oca_2=\KMag/_{I_2}$ of
 $\QMag$, let us define
-\begin{equation} \label{equ:definition_of_lattice_operations_of_QMag}
+\begin{equation} \label{equ:inf_QMag}
     \Oca_1\InfQMag \Oca_2 := \KMag/_{I_1+I_2}
-    \qquad \mbox{and} \qquad
+\end{equation}
+and
+\begin{equation} \label{equ:sup_QMag}
     \Oca_1\SupQMag \Oca_2 := \KMag/_{I_1\cap I_2}.
@@
 \end{Theorem}
-
 \begin{proof}
@@
 \subsection{Hilbert series and linear magmatic quotients}
-In order to show the Grassmann formula analog for $\LatQMag$, we need the
+In order to show a Grassmann formula analog for $\LatQMag$, we need the
 following lemma.
@@
 \medbreak
-
-% Hilbert series, enumeration, a little of rewrite systems, etc.

### 2018-09-04 Operads_rewrite.tex
Relecture

--- 2018-09-03 Operads_rewrite.tex
@@
 $\Deg(\Tfr)$) of a binary tree $\Tfr$ is its number of leaves (resp.
-internal nodes). We shall draw binary trees the root to the top. For
-instance,
+internal nodes). A binary tree $\Tfr$ is \Def{quadratic} (resp.
+\Def{cubic}) if $\Deg(\Tfr) = 2$ (resp. $\Deg(\Tfr) = 3$). We shall draw
+binary trees the root to the top. For instance,
 \begin{equation}
@@
     \end{tikzpicture}
-    \xmapsto{\; \PrefixWord \;}
+    \enspace \xmapsto{\; \PrefixWord \;} \enspace
     \Two \Two \Zero \Two \Zero \Zero \Two \Two \Two \Zero \Zero \Two
@@
     \end{tikzpicture}
-    \xmapsto{\; \LRank\; } 3.
+    \enspace \xmapsto{\; \LRank\; } \enspace 3.
 \end{equation}
@@
 $\RewContextRST$) the transitive (resp. reflexive and transitive,
-reflexive, symmetric, and sitive) closure of $\RewContext$.
+reflexive, symmetric, and transitive) closure of $\RewContext$.
 \medbreak
@@
 orientation of $\Congr$ if $\RewContext$ is convergent (resp.
-terminating, confluent). In the sequel, we use the terminology of a
-\Def{presentation} of an operad $\Oca$ generated by one binary generator:
-it is the data of an operad congruence $\Congr$ of $\Mag$ such that
-$\Oca$ is isomorphic to
-\begin{math}
-  \Mag/_{\Congr}.
-\end{math}
-For simplicity, we say that a convergent (resp. terminating, confluent)
-orientation of $\Congr$ is a \Def{convergent} (resp. \Def{terminating},
-\Def{confluent}) \Def{presentation} of $\Oca$.
+terminating, confluent). A \Def{presentation} of the quotient operad
+$\Oca$ of the form~\eqref{equ:quotient_operad_mag} is the data of a
+generating set for the operad congruence $\Congr$. Observe that
+any orientation of $\Congr$ is a presentation of $\Oca$, so that the
+above nomenclature (\Def{convergent}, \Def{terminating}, and
+\Def{confluent}) still holds for presentations. A presentation is said
+to be \Def{finite} if it is a finite set.
 \medbreak
@@
 
-  \item\label{item:choice_branching_pair} Let $\{\Sfr_1, \Sfr_2\}$ be a
-    branching pair for $\Tfr$.
+    \item\label{item:choice_branching_pair} Let $\{\Sfr_1, \Sfr_2\}$ be
+    a branching pair for $\Tfr$.
     \smallbreak
 
-  \item\label{item:computed_normal_forms} Let $\overline{\Sfr_1}$ and
-    $\overline{\Sfr_2}$ be normal forms of $\Sfr_1$ and $\Sfr_2$,
+    \item\label{item:computed_normal_forms} Let $\bar{\Sfr_1}$ and
+    $\bar{\Sfr_2}$ be normal forms of $\Sfr_1$ and $\Sfr_2$,
     respectively.
@@
     \item \label{item:new_rewrite_rule_buchberger}
-      If $\overline{\Sfr_1}$ is different from $\overline{\Sfr_2}$, add
+    If $\bar{\Sfr_1}$ is different from $\bar{\Sfr_2}$, add
     to $\Rew'$ the rewrite rule
     \begin{math}
-        \max_\leq \left\{\overline{\Sfr_1}, \overline{\Sfr_2}\right\}
+        \max_\leq \left\{\bar{\Sfr_1}, \bar{\Sfr_2}\right\}
         \Rew'
-        \min_\leq \left\{\overline{\Sfr_1}, \overline{\Sfr_2}\right\}.
+        \min_\leq \left\{\bar{\Sfr_1}, \bar{\Sfr_2}\right\}.
     \end{math}
@@
     \item Add to $\BranchingTrees$ all new branching trees of degrees at
-    most $2 \Deg(\Rew') - 1$ created by the rewrite rule of
+    most $2 \Deg(\Rew') - 1$ created by the rewrite rule created in
     Step~\ref{item:new_rewrite_rule_buchberger}.
@@
 completion depend on the total order $\leq$ on the binary trees of a
-same arity, the choices at steps~\ref{item:choice_branching_tree}
-and~\ref{item:choice_branching_pair} as well as the computed normal forms
-at step~\ref{item:computed_normal_forms}.
+same arity, the choices at Steps~\ref{item:choice_branching_tree}
+and~\ref{item:choice_branching_pair} as well as the computed normal
+forms at Step~\ref{item:computed_normal_forms}.
 \medbreak
+
+\Todo{S: je crois qu'il faudrait préciser les choix que l'on fait aux
+étapes (3), (4) et (5).}

### 2018-09-05 Introduction.tex
MAJ

@@
 Grassmann formula analog relating the Hilbert series of the operads of
-the lattice together with their infima and suprema
+the lattice together with their lower-bound and upper-bound
 (Theorem~\ref{thm:Grassmann_formula_for_Hilbert_series_of_QMag}).
@@
 $\CAs{\gamma}$, defined by equating the left and right comb binary trees
-of a fixed degree $\gamma \geq 1$. These operads are called comb
+of a fixed degree $\gamma \geq 1$.
+Observe that since $\CAs{2}=\As$, the operads $\CAs{\gamma}$ can be seen
+as generalizations of $\As$. These operads are called comb
 associative operads. For instance, $\CAs{3}$ is the operad describing
@@
 \end{equation}
-This is a kind of associativity law in higher degree $\gamma = 3$ so
-that $\CAs{3}$ can be seen as a generalization of $\As$ (which is equal
-to $\CAs{2}$). We first provide general results about the operads
-$\CAs{\gamma}$. In particular, we show that these operads form a lattice
-contained in the lattice of quotients of $\Mag$ aforementioned
+We first provide general results about the
+operads $\CAs{\gamma}$. In particular, we show that these operads form a
+a lattice which embeds as a poset in the lattice of the quotients of
+$\Mag$ aforementioned
 (Theorems~\ref{thm:lattice_CAs} and~\ref{thm:inclusion_lattice_CAs}). We
@@
 %
-\Todo{S: et parler de la réalisation si Christophe l'ajoute ?}
+\Todo{Parler des formes normales}
 %
@@
 The authors wish to thank Maxime Lucas for helpfull discussions and
-Vladimir Dotsenko for his mark of interest to this work.
+Vladimir Dotsenko for his marks of interest and his bibliographic
+suggestions.
 \medbreak

### 2018-09-05 Operads_rewrite.tex
MAJ

@@
 orientation of $\Congr$ if $\RewContext$ is convergent (resp.
-terminating, confluent). A \Def{presentation} of the quotient operad
-$\Oca$ of the form~\eqref{equ:quotient_operad_mag} is the data of a
-generating set for the operad congruence $\Congr$. Observe that
+terminating, confluent). We call \Def{presentation} of a quotient
+operad $\Oca$ of the form~\eqref{equ:quotient_operad_mag} the data of
+a generating set for the operad congruence $\Congr$. Observe that
 any orientation of $\Congr$ is a presentation of $\Oca$, so that the
@@
 \medbreak
-
-\Todo{S: je crois qu'il faudrait préciser les choix que l'on fait aux
-étapes (3), (4) et (5).}

### 2018-09-05 Magmatic_operads.tex
MAJ

@@
 relations for the two operads $\Oca_1$ and $\Oca_2$ of $\QMag$ forms a
-generating set for the relations of $\Oca_1\InfQMag\Oca_2$. However, we
-do not know how to perform the same method for computing generating
-relations for $\Oca_1\SupQMag\Oca_2$ since we do not know how to compute
-generating sets of the intersection of two operadic ideals.
+generating set for the relations of $\Oca_1\InfQMag\Oca_2$. However, the
+authors do not know how to compute a generating set of the intersection
+of ideals (it is not the intersection of generating relations), so that
+we do not know how to compute generating relations for
+$\Oca_1\SupQMag\Oca_2$.
 \medbreak

### 2018-09-05 CAs_operads.tex
MAJ

@@
         \mbox{ implies }
-        \LRank\left(\Tfr'\right) = \LRank\left(\Tfr\right)
+        \LRank\left(\Tfr'\right) \pmod{\bar{\gamma}} = \LRank\left(\Tfr\right)
         \, \pmod{\bar{\gamma}}.
@@
       \Tfr =
+       \LComb{\LRank\left(\Tfr\right)} \circ
       \left[\, |,\Tfr_1, \dots, \Tfr_{\LRank\left(\Tfr\right)} \right].
     \end{math}
-    \Todo{S: notation ? Je n'ai pas encore bien relu cette démo.}
     Thus, if $\Tfr \RewContext \Tfr'$, then one of the following two
@@
     \begin{enumerate}[label={(\it\roman*)}]
-        \item there exists $\Tfr_i'$ such that
+    \item the rewrite step is applied on one of the trees $\Tfr_i$,
+      that is there exists $\Tfr_i'$ such that
             \begin{math}
@@
             \end{math}
-        \item there exists $i$ such that
+          \item the rewrite step is applied in the left branch beginning
+            at the root, that is there exists $i$ such that
             \begin{math}
@@
         \Tfr \simeq \Tfr' \mbox{ if and only if }
-        \LRank\left(\Tfr'\right) = \LRank\left(\Tfr\right)
-        \, \pmod{\bar{\gamma}}
+        \LRank\left(\Tfr'\right) \pmod{\bar{\gamma}} =
+        \LRank\left(\Tfr\right) \, \pmod{\bar{\gamma}}
     \end{equation}
@@
 Taylor expansion of~\eqref{equ:Hilbert_series_CAs_3} shows that
-$\# \CAs{3}(n) = n + 3$.
+\begin{equation}
+  \# \CAs{3}(n) = n + 3.
+  \end{equation}
 \medbreak
@@
       \gamma & \mbox{The sequence of first cardinalities of }
-       \CAs{\gamma} \mbox{completions}\\ \hline
+       \CAs{\gamma} \mbox{completion}\\ \hline
       3 & 0, 0, 0, 1, 1, 2, 3, 4, 0, 0, \dots \\ \hline
@@
 does not provide a finite convergent presentation of $\CAs{\gamma}$,
-when $\gamma \geq 4$.
+when $\gamma \geq 4$. We point out that for $\CAs{4}$ new
+rewrite rules still appear at degree $41$. Moreover, the total number of
+rewrite rules at degree $41$ is $3149$.
 \medbreak
 
-\Todo{S: j'ai un peu réécrit les explications suivantes, vérifier que
-je n'ai pas introduit de bétise(s).}
 However, the completion algorithm we used depends on the chosen order on
@@
 finite convergent presentation using a different order, we run the
-following algorithm. For every branching pair $(\Tfr_1, \Tfr_2)$ which
-is not joinable, we recursively try to find a completion of $\Rew$ by
-adding either the rule $\Tfr_1 \Rew  \Tfr_2$ or $\Tfr_2 \Rew  \Tfr_1$.
-If at any moment the rewrite relation induced by $\Rew$ is no
-antisymmetric, we simply reject it.
+following backtracking algorithm. For every branching pair
+$(\Tfr_1, \Tfr_2)$ which is not joinable, we recursively try to find a
+completion of $\Rew$ by adding either the rule
+$\Tfr_1 \Rew  \Tfr_2$ or $\Tfr_2 \Rew  \Tfr_1$.
+If at any moment the rewrite relation $\RewContext$ induced by $\Rew$
+loops (that is $\RewContext$ is not antisymmetric), we simply reject it.
 \medbreak

### 2018-09-05 Introduction.tex
MAJ

@@
 relations of $\CAs{3}$ (Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}),
-a description of a basis of the operad, and prove that its Hilbert series
-is rational.
-%
-\Todo{Parler des formes normales}
-%
-For all these, we use rewrite systems on trees~\cite{BN98} and the
-Buchberger algorithm for operads~\cite{DK10}. We expose some
-experimental results obtained with the help of the computer for some
-operads $\CAs{\gamma}$ with $\gamma \geq 4$. Finally, we continue the
+a description of a basis of the operad in terms of normal forms, and
+prove that its Hilbert series is rational. For all these, we use rewrite
+systems on trees~\cite{BN98} and the Buchberger algorithm for
+operads~\cite{DK10}. We expose some experimental results obtained with
+the help of the computer for some operads $\CAs{\gamma}$ with
+$\gamma \geq 4$. Finally, we continue the
 investigation of the quotients of $\Mag$ by regarding the quotients of

### 2018-09-07 Article.tex
MAJ
Restructuration fichiers

@@
 \usepackage{xcolor}
-\input{Colors}
+
+\definecolor{ColBlack}{RGB}{0,0,0} % Black.
+\definecolor{ColWhite}{RGB}{255,255,255} % White.
+\definecolor{Col1}{RGB}{133,6,6} % Rouge sang.
+\definecolor{Col2}{RGB}{198,8,0} % Rouge ponceau.
+\definecolor{Col3}{RGB}{174,74,52} % Rouge tomette.
+\definecolor{Col4}{RGB}{103,113,121} % Gris de Payne.
+\definecolor{Col5}{RGB}{90,94,107} % Ardoise.
+\definecolor{Col6}{RGB}{70,63,50} % Taupe.
+
+\newcommand{\ColBlack}[1]{\textcolor{ColBlack}{#1}}
+\newcommand{\ColWhite}[1]{\textcolor{ColWhite}{#1}}
+\newcommand{\ColA}[1]{\textcolor{Col1}{#1}}
+\newcommand{\ColB}[1]{\textcolor{Col2}{#1}}
+\newcommand{\ColC}[1]{\textcolor{Col3}{#1}}
+\newcommand{\ColD}[1]{\textcolor{Col4}{#1}}
+\newcommand{\ColE}[1]{\textcolor{Col5}{#1}}
+\newcommand{\ColF}[1]{\textcolor{Col6}{#1}}
 
@@
 
+% Reduce first verical spacing of multicols.
+\setlength\multicolsep{0pt}
+
 % Numbering of equations.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Comb associative operads}
-\keywords{Operad; trees; Rewrite rule; Presentation; Enumeration.}
+\title[Quotients of the magmatic operad]
+      {Quotients of the magmatic operad:\\
+        lattice structures and convergent rewrite systems}
+\keywords{Operad; Tree; Lattice; Rewrite rule; Presentation; Enumeration.}
 \subjclass[2010]{18D50, 68Q42, 05C05.}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{Tools}
+% Tools macros.
+\newcommand{\Todo}[1]{\textcolor{Col1}{{\tt TODO: $[$#1$]$}}}
+\newcommand{\Hide}[1]{\textcolor{Col4}{\tt [hidden]}}
 
+% Format macros.
+\newcommand{\Def}[1]{\textcolor{Col3}{\em #1}}
+\newcommand{\OEIS}[1]{\href{http://oeis.org/#1}{{\bf #1}}}
+\newcommand{\Arxiv}[1]{\href{https://arxiv.org/abs/#1}{\tt arXiv:#1}}
+
+% Tikz for vertical centering.
+\tikzstyle{Centering}=[{baseline={([yshift=-0.5ex]current
+    bounding box.center)}}]
+
+% Other.
 \newcommand{\N}{\mathbb{N}}
@@
 % Tree drawings.
-
 \newcommand{\TreeA}{

### 2018-09-07 Mag_quotients.tex
Restructuration (2)

--- 2018-09-05 Magmatic_operads.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Linear magmatic operads} \label{sec:Magmatic_operads}
+\section{Linear quotients of the magmatic operad}
+\label{sec:Magmatic_operads}
 In this section, we equip the set of quotients of the linear magmatic
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Lattice of linear magmatic quotients}
+\subsection{Lattice structure}
 The \Def{linear magmatic operad}, written $\KMag$, is the free linear
@@
 
-\Todo{S: je l'écris ici pour l'écrire quelque part: on devrait
-homogénéiser l'usage des $:=$ et des $=$.}
 Given two operads $\Oca_1=\KMag/_{I_1}$ and $\Oca_2=\KMag/_{I_2}$ of
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Hilbert series and linear magmatic quotients}
+\subsection{Hilbert series and Grassmann formula}
 In order to show a Grassmann formula analog for $\LatQMag$, we need the

### 2018-09-07 Introduction.tex
Passe introduction

@@
 the Tamari order and some quotients of the operad $\Mag$. In the long
-run, we would like to study quotients $\Mag/_{\Congr}$ of $\Mag$ where
+run, the goal is to study quotients $\Mag/_{\Congr}$ of $\Mag$ where
 $\Congr$ is an operad congruence generated by equivalence classes of
@@
 implies algebraic properties for $\Mag/_{\Congr}$ (like the description
-of orientations of its space of relations, nice bases, and Hilbert
+of orientations of its space of relations, of nice bases, and of Hilbert
 series).
@@
 quotients of $\Mag$ seen as an operad in the category of vector spaces.
-We show that these operads form a lattice, wherein its partial order
-relation is defined from the existence of operad morphisms
+We show that this set of operads forms a lattice, wherein its partial
+order relation is defined from the existence of operad morphisms
 (Theorem~\ref{thm:lattice_structure_of_QMag}). We also provide a
@@
 $\CAs{\gamma}$, defined by equating the left and right comb binary trees
-of a fixed degree $\gamma \geq 1$.
-Observe that since $\CAs{2}=\As$, the operads $\CAs{\gamma}$ can be seen
-as generalizations of $\As$. These operads are called comb
-associative operads. For instance, $\CAs{3}$ is the operad describing
-the category of the algebras equipped with a binary product $\Product$
-subjected to the relation
+of a fixed degree $\gamma \geq 1$. Observe that since $\CAs{2}=\As$, the
+operads $\CAs{\gamma}$ can be seen as generalizations of $\As$. These
+operads are called comb associative operads. For instance, $\CAs{3}$ is
+the operad describing the category of the algebras equipped with a
+binary product $\Product$ subjected to the relation
 \begin{equation}
@@
 \end{equation}
-We first provide general results about the
-operads $\CAs{\gamma}$. In particular, we show that these operads form a
-a lattice which embeds as a poset in the lattice of the quotients of
-$\Mag$ aforementioned
-(Theorems~\ref{thm:lattice_CAs} and~\ref{thm:inclusion_lattice_CAs}). We
-focus in particular on the study of $\CAs{3}$. Observe that the
-congruence of this operad is generated by an equivalence class of trees
-which is not an interval for the Tamari order. As preliminary computer
-experiments show, $\CAs{3}$ has oscillating first dimensions
-(see~\eqref{equ:dimensions_CAs_3}), what is rather unusual among all
-known operads. We provide a convergent orientation of the space of
-relations of $\CAs{3}$ (Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}),
-a description of a basis of the operad in terms of normal forms, and
-prove that its Hilbert series is rational. For all these, we use rewrite
-systems on trees~\cite{BN98} and the Buchberger algorithm for
-operads~\cite{DK10}. We expose some experimental results obtained with
-the help of the computer for some operads $\CAs{\gamma}$ with
-$\gamma \geq 4$. Finally, we continue the
-investigation of the quotients of $\Mag$ by regarding the quotients of
-$\Mag$ obtained by equating two trees of degree $3$. This leads to ten
-quotient operads of $\Mag$. We provide for some of these combinatorial
-realizations, mostly in terms of integer compositions.
+We first provide general results about the operads $\CAs{\gamma}$. In
+particular, we show that the set of these operads forms a lattice which
+embeds as a poset in the lattice of the quotients of $\Mag$
+aforementioned (Theorems~\ref{thm:lattice_CAs}
+and~\ref{thm:inclusion_lattice_CAs}). We focus in particular on the
+study of $\CAs{3}$. Observe that the congruence defining this operad is
+generated by an equivalence class of trees which is not an interval for
+the Tamari order. As preliminary computer experiments show, $\CAs{3}$
+has oscillating first dimensions (see~\eqref{equ:dimensions_CAs_3}),
+what is rather unusual among all known operads. We provide a convergent
+orientation of the space of relations of $\CAs{3}$
+(Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}), a description of a
+basis of the operad in terms of normal forms, and prove that its Hilbert
+series is rational. For all these, we use rewrite systems on
+trees~\cite{BN98} and the Buchberger algorithm for operads~\cite{DK10}.
+We expose some experimental results obtained with the help of the
+computer for some operads $\CAs{\gamma}$ with $\gamma \geq 4$. Finally,
+we continue the investigation of the quotients of $\Mag$ by regarding
+the quotients of $\Mag$ obtained by equating two trees of degree $3$.
+This leads to ten quotient operads of $\Mag$. We provide for some of
+these combinatorial realizations, mostly in terms of integer
+compositions.
 \medbreak
@@
 \subsubsection*{Acknoledgements}
-The authors wish to thank Maxime Lucas for helpfull discussions and
+The authors wish to thank Maxime Lucas for helpful discussions and
 Vladimir Dotsenko for his marks of interest and his bibliographic

### 2018-09-07 Operads_rewrite.tex
Passe partie 1

@@
 \Def{nonsymmetric operad} for short) is a graded set
-\begin{equation}
+\begin{math}
     \Oca = \bigsqcup_{n \geq 1} \Oca(n)
-\end{equation}
+\end{math}
 together with maps
@@
 $\Oca$ containing $\GeneratingSet$. When $\Oca = \Oca^\GeneratingSet$,
-we say that $\GeneratingSet$ is a \Def{generating set} of $\Oca$. In
-this case, and when additionally $\GeneratingSet$ is minimal among all
-the subsets of $\Oca$ satisfying this property, $\GeneratingSet$ is a
-\Def{minimal} generating set of $\Oca$. An \Def{operad congruence} is an
-equivalence relation $\Congr$ on $\Oca$ such that $\Congr$ respects the
-arities, and for any $x, x', y, y' \in \Oca$ such that $x \Congr x'$ and
-$y \Congr y'$, $x \circ_i y$ is $\Congr$-equivalent to $x' \circ_i y'$
-for any valid integer $i$. Given an operad congruence $\Congr$, the
+we say that $\GeneratingSet$ is a \Def{generating set} of $\Oca$. An
+\Def{operad congruence} is an equivalence relation $\Congr$ on $\Oca$
+such that $\Congr$ respects the arities, and for any
+$x, x', y, y' \in \Oca$ such that $x \Congr x'$ and $y \Congr y'$,
+$x \circ_i y$ is $\Congr$-equivalent to $x' \circ_i y'$ for any valid
+integer $i$. Given an operad congruence $\Congr$, the
 \Def{quotient operad} $\Oca/_{\Congr}$ of $\Oca$ by $\Congr$ is the
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Binary trees and magmatic operad}
+\subsection{Binary trees and the magmatic operad}
 A \Def{binary tree} is either the \Def{leaf} $\Leaf$ or a pair
@@
 \begin{equation}
-    \begin{tikzpicture}[xscale=.15,yscale=.18,Centering]
+    \begin{tikzpicture}[xscale=.15,yscale=.16,Centering]
         \node(0)at(0.00,-4.50){};
@@
         \draw[Edge](8)--(7);
-        \node(r)at(5.00,2){};
+        \node(r)at(5.00,2.25){};
         \draw[Edge](r)--(5);
@@
 \begin{equation} \label{equ:example_composition_mag}
-    \begin{tikzpicture}[xscale=.15,yscale=.18,Centering]
+    \begin{tikzpicture}[xscale=.15,yscale=.16,Centering]
         \node(0)at(0.00,-4.50){};
@@
     \enspace = \enspace
-    \begin{tikzpicture}[xscale=.15,yscale=.14,Centering]
+    \begin{tikzpicture}[xscale=.15,yscale=.12,Centering]
         \node(0)at(0.00,-6.00){};
@@
 \begin{equation}
-    \begin{tikzpicture}[xscale=1.3,yscale=1.1,Centering]
+    \begin{tikzpicture}[xscale=1.3,yscale=0.9,Centering]
         \node(G)at(0,0){\begin{math}\GeneratingSet\end{math}};
@@
 \begin{equation}
-    \begin{tikzpicture}[xscale=.15,yscale=.14,Centering]
+    \begin{tikzpicture}[xscale=.15,yscale=.12,Centering]
         \node(0)at(0.00,-6.00){};
@@
 \begin{equation}
-    \begin{tikzpicture}[xscale=.15,yscale=.14,Centering]
+    \begin{tikzpicture}[xscale=.15,yscale=.12,Centering]
         \node(0)at(0.00,-9.00){};
@@
 \begin{equation} \label{equ:example_rewrite_rule}
-    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
+    \begin{tikzpicture}[xscale=.22,yscale=.21,Centering]
         \node(0)at(0.00,-3.50){};
@@
     \enspace \Rew \enspace
-    \begin{tikzpicture}[xscale=.22,yscale=.22,Centering]
+    \begin{tikzpicture}[xscale=.22,yscale=.21,Centering]
         \node(0)at(0.00,-1.75){};
@@
 \begin{equation} \label{equ:example_rewrite_step}
-    \begin{tikzpicture}[xscale=.19,yscale=.14,Centering]
+    \begin{tikzpicture}[xscale=.22,yscale=.12,Centering]
         \node(0)at(0.00,-9.00){};
@@
     \enspace \RewContext \enspace
-    \begin{tikzpicture}[xscale=.19,yscale=.14,Centering]
+    \begin{tikzpicture}[xscale=.22,yscale=.12,Centering]
         \node(0)at(0.00,-9.00){};
@@
 Let $\Rew$ be a set of rewrite rules and $\RewContext$ be the rewrite
-relation induced by $\Rew$. Since $\RewContext$ is in particular a
+relation induced by $\Rew$. Since~$\RewContext$ is in particular a
 binary relation on $\Mag$, the classical notations about closures apply
@@
 $\RewContextRST$) the transitive (resp. reflexive and transitive,
-reflexive, symmetric, and transitive) closure of $\RewContext$.
+and reflexive, symmetric, and transitive) closure of~$\RewContext$.
 \medbreak
@@
 \end{equation}
-we say that $\RewContext$ is terminating. To establish the termination
-of a rewrite relation, we will use the following criterion.
+we say that $\RewContext$ is \Def{terminating}. To establish the
+termination of a rewrite relation, we will use the following criterion.
 \medbreak
@@
     \begin{math}
-        \Tfr_0 \Rew \Tfr_1 \Rew \Tfr_2 \Rew \cdots
+        \Tfr_0 \RewContext \Tfr_1 \RewContext \Tfr_2 \RewContext \cdots
     \end{math}
@@
 orientation of $\Congr$ if $\RewContext$ is convergent (resp.
-terminating, confluent). We call \Def{presentation} of a quotient
-operad $\Oca$ of the form~\eqref{equ:quotient_operad_mag} the data of
-a generating set for the operad congruence $\Congr$. Observe that
-any orientation of $\Congr$ is a presentation of $\Oca$, so that the
-above nomenclature (\Def{convergent}, \Def{terminating}, and
+terminating, confluent). In this text, we call \Def{presentation} of a
+quotient operad $\Oca$ of the form~\eqref{equ:quotient_operad_mag} the
+data of a generating set for the operad congruence $\Congr$. Observe
+that any orientation of $\Congr$ is a presentation of $\Oca$, so that
+the above nomenclature (\Def{convergent}, \Def{terminating}, and
 \Def{confluent}) still holds for presentations. A presentation is said

### 2018-09-07 CAs_operads.tex
MAJ
Restructuration (3)
Réalisation CAs^(3)

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Lattice of comb associative operads}
@@
        \LComb{\LRank\left(\Tfr\right)} \circ
-      \left[\, |,\Tfr_1, \dots, \Tfr_{\LRank\left(\Tfr\right)} \right].
+      \left[\, \Leaf \, \Tfr_1, \dots,
+      \Tfr_{\LRank\left(\Tfr\right)} \right].
     \end{math}
@@
               \Tfr' = \LComb{\LRank\left(\Tfr\right)} \circ
-              \left[\, | ,\Tfr_1, \dots, \Tfr_i',\dots,
+              \left[\, \Leaf ,\Tfr_1, \dots, \Tfr_i',\dots,
                     \Tfr_{\LRank\left(\Tfr\right)}
@@
               \Tfr' = \LComb{\LRank\left(\Tfr\right)-\bar{\gamma}} \circ
-              \left[ | ,\Tfr_1, \dots,
+              \left[ \Leaf ,\Tfr_1, \dots,
                  \RComb{\bar{\gamma}} \circ
@@
       \CAs{\gamma}\InfCAs\CAs{\gamma'}
-      =\CAs{\gcd \left(\bar{\gamma}, \bar{\gamma'}\right)}
+      :=\CAs{\gcd \left(\bar{\gamma}, \bar{\gamma'}\right)}
     \end{equation}
@@
       \CAs{\gamma}\SupCAs\CAs{\gamma'}
-      =\CAs{\lcm \left(\bar{\gamma}, \bar{\gamma'}\right)}.
+      :=\CAs{\lcm \left(\bar{\gamma}, \bar{\gamma'}\right)}.
     \end{equation}
@@
 provides the new rewrite rules \smallbreak
-\input{Buchberger_relations_CAs3}
+\input{Completion_CAs3}
 \medbreak
@@
 
-\Todo{S: réalisation combinatoire de $\CAs{3}$ à donner ici.}
+For arity $n\geq 11$, the normal forms are composed of the following
+family of $n-1$ trees
+\Todo{dessiner arbres}
+\begin{equation}\label{equ:normal_forms_type_A}
+  A
+\end{equation}
+and the following family of four trees
+\begin{equation}\label{equ:normal_forms_type_B}
+  B
+  \end{equation}
 
+Indeed, each of these trees avoids the left membres of the convergent
+presentation given in Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}.
+Moreover, we have the following.
+\medbreak
+
+\begin{Proposition}
+  The family~\eqref{equ:normal_forms_type_B} is absorbing for each
+  partial composition.
+  \end{Proposition}
+
+\begin{proof}
+  None of the trees of type~\eqref{equ:normal_forms_type_A}
+  contains the left or the right member of the congruence relation
+  $\CongrCAs{3}$, so that they are alone in their equivalence classes.
+  Moreover, the trees of type~\eqref{equ:normal_forms_type_B}
+  contain the right member of $\CongrCAs{3}$, so that the composition of
+  such a tree with anothter tree is not alone in its
+  equivalence class, and thus it does not belong to the
+  family~\eqref{equ:normal_forms_type_A}.
+\end{proof}
+
+By computer explorations, we are able to conjecture the multiplication
+tables of each partial compositions. However, the obtained tables are not
+simply described. For instance, the partial composition
+$\Tfr\circ_i\Tfr'$ with $\Tfr$ of type~\eqref{equ:normal_forms_type_A}
+and $\Tfr'$ of type~\eqref{equ:normal_forms_type_B} is described by $36$
+cases depending on the values of various parameters associated to $\Tfr$,
+$\Tfr'$ and $i$.
+
+\medbreak
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
        \CAs{\gamma} \mbox{completion}\\ \hline
+      1 & 0, 1, 0, 0, \dots \\ \hline
+      2 & 0, 0, 1, 0, 0, \dots \\ \hline
       3 & 0, 0, 0, 1, 1, 2, 3, 4, 0, 0, \dots \\ \hline
@@
        \CAs{\gamma}\\ \hline
+      1 & 1, 1, 2, 5, 14, 42, 132, 429, 1430, 4862, \dots \\ \hline
+      2 & 1, 1, 1, \dots \\ \hline
+      3 & 1, 1, 2, 4, 8, 14, 20, 19, 16, 14,
+          14, 15, 16, 17, \dots \\ \hline
       4 & 1, 1, 2, 5, 13, 35, 96, 264, 724, 1973, 5335, 14390, 38872,
@@
 \Todo{S:remettre la table en forme.}
-\Todo{S: pourquoi rappeler $\CAs{3}$ dans la table d'avant et pas dans
-celle-ci ?}

### 2018-09-07 CAs_operads.tex
FN

@@
 
-For arity $n\geq 11$, the normal forms are composed of the following
-family of $n-1$ trees
-\Todo{dessiner arbres}
+Let us describe the normal forms for arity $n\geq 11$. For that, we 
+consider the following "zig-zag" of degree $k \geq 0$ 
+\Todo{Dessins}
+\begin{equation}
+  z_k :=.
+\end{equation}
+For instance, $z_3$ and $z_4$ are the following trees
+\begin{equation}
+.
+\end{equation}
+The normal forms are decomposed in two families. 
+The first family is the set of the $n-1$ trees 
+$\left(z_k \circ_{k+1} z_{n-1-k}\right)_{1 \leq k \leq n-1}$, 
+pictured as follows
 \begin{equation}\label{equ:normal_forms_type_A}
-  A
-\end{equation}
-and the following family of four trees
+   z_k \circ_{k+1} z_{n-1-k} = dessin.
+\end{equation}
+The second family is composed of the following four trees
 \begin{equation}\label{equ:normal_forms_type_B}
-  B
-  \end{equation}
-
+  \RComb{n-1}, \qquad
+  \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
+    \node(0)at(0.00,-4.50){};
+    \node(2)at(2.00,-4.50){};
+    \node(8)at(8.00,-6.75){};
+    \node(10)at(5,-9){};
+    \node(11)at(7,-9){};
+    \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
+    \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
+    \node[NodeST](5)at(6.5,-1.4){\begin{math}n-2\end{math}};
+    \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
+    \node(9)at(6,-6.75){};
+    \draw[Edge](0)--(1);
+    \draw[Edge](1)--(3);
+    \draw[Edge](2)--(1);
+    \draw[Edge](7)--(9);
+    \draw[Edge, dotted](7)--(3);
+    \draw[Edge](8)--(7);
+    \node(r)at(3.00,1.74){};
+    \draw[Edge](r)--(3);
+  \end{tikzpicture}, \qquad
+  \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
+    \node(0)at(0.00,-4.50){};
+    \node(2)at(2.00,-4.50){};
+    \node(8)at(8.00,-6.75){};
+    \node(10)at(5,-9){};
+    \node(11)at(7,-9){};
+    \node(1)at(1.00,-2.25){};
+    \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
+    \node[NodeST](5)at(6.5,-1.4){\begin{math}n-2\end{math}};
+    \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
+    \node[NodeST](9)at(6,-6.75){\begin{math}\Product\end{math}};
+    \draw[Edge](1)--(3);
+    \draw[Edge](7)--(9);
+    \draw[Edge](9)--(10);
+    \draw[Edge](9)--(11);
+    \draw[Edge, dotted](7)--(3);
+    \draw[Edge](8)--(7);
+    \node(r)at(3.00,1.74){};
+    \draw[Edge](r)--(3);
+  \end{tikzpicture}, \qquad
+  \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
+    \node(0)at(0.00,-4.50){};
+    \node(2)at(2.00,-4.50){};
+    \node(8)at(8.00,-6.75){};
+    \node(10)at(5,-9){};
+    \node(11)at(7,-9){};
+    \node[NodeST](1)at(1.00,-2.25){\begin{math}\Product\end{math}};
+    \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
+    \node[NodeST](5)at(6.5,-1.4){\begin{math}n-3\end{math}};
+    \node[NodeST](7)at(7.00,-4.50){\begin{math}\Product\end{math}};
+    \node[NodeST](9)at(6,-6.75){\begin{math}\Product\end{math}};
+    \draw[Edge](0)--(1);
+    \draw[Edge](1)--(3);
+    \draw[Edge](2)--(1);
+    \draw[Edge](7)--(9);
+    \draw[Edge](9)--(10);
+    \draw[Edge](9)--(11);
+    \draw[Edge, dotted](7)--(3);
+    \draw[Edge](8)--(7);
+    \node(r)at(3.00,1.74){};
+    \draw[Edge](r)--(3);
+  \end{tikzpicture}.
+\end{equation}
 Indeed, each of these trees avoids the left membres of the convergent

### 2018-09-07 CAs_operads.tex
MAJ

@@
 \end{equation}
-The normal forms are decomposed in two families. 
+The normal forms are decomposed into two families. 
 The first family is the set of the $n-1$ trees 
@@
 \end{equation}
-Indeed, each of these trees avoids the left membres of the convergent
-presentation given in Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}.
-Moreover, we have the following.
+Indeed, each of these $n+3$ trees avoids the left membres of the
+convergent presentation given in
+Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}. Moreover, we have the
+following.
 \medbreak

### 2018-09-07 Mag_quotients.tex
Passe partie 2

@@
 $\KMag/_I \in \QMag$ and $x \in \KMag$, we denote by $[x]_I$ the
-$I$-equivalence of $x$. Observe that $\KMag/_I$ is generated as an
-operad by $[\Product]_I$. Moreover, given two  elements $\Oca_1$ and
-$\Oca_2$ of $\QMag$, we denote by $\Hom\left(\Oca_1,\Oca_2\right)$ the
-set of linear operad morphisms from $\Oca_1$ to~$\Oca_2$.
+$I$-equivalence class of $x$. Observe that $\KMag/_I$ is generated as an
+operad by $[\Product]_I$ (where, recall, $\Product$ is the binary
+generator of $\Mag$ and thus also of $\KMag$). Moreover, given two
+elements $\Oca_1$ and $\Oca_2$ of $\QMag$, we denote by
+$\Hom\left(\Oca_1,\Oca_2\right)$ the set of linear operad morphisms from
+$\Oca_1$ to~$\Oca_2$.
 \medbreak
@@
         \psi([\Product]_{I_1}) =\mu[\Product]_{I_2}
-        = \left(\mu/\lambda\right)\varphi([\Product]_{I_1}).
+        = \left(\mu \lambda^{-1}\right)\varphi([\Product]_{I_1}).
     \end{math}
@@
     that is there is a nonzero scalar such that
-    $\varphi([\Product]_{I_1}) =\lambda[\Product]_{I_2}$, we have
-    $\varphi(1/\lambda[\Product]_{I_1}) =[\Product]_{I_2}$, so that
-    $\varphi$ is surjective.
+    \begin{math}
+        \varphi\left([\Product]_{I_1}\right) = \lambda[\Product]_{I_2},
+    \end{math}
+    we have
+    \begin{math}
+        \varphi\left(\lambda^{-1}[\Product]_{I_1}\right)
+        = [\Product]_{I_2},
+    \end{math}
+    so that $\varphi$ is surjective.
 \end{proof}
@@
     the morphism $\bar{\varphi}:\Oca_1\to\Oca_2$ satisfying
-  $\bar{\varphi}([\Product]_{I_1})=[\Product]_{I_2}$ is well-defined,
-  which means that $\Oca_2\OrdQMag\Oca_1$ is equivalent to this
-  condition. Moreover, by the universal property of the quotient,
-  $\bar{\varphi}$ is well-defined if and only if $I_1$ is included
-  in the kernel of the morphism $\varphi:\KMag\to\Oca_2$ defined by
-  $\varphi(\Product)=[\Product]_{I_1}$. This kernel is equal to
-  $I_2$, so that $\bar{\varphi}$ is well-defined if and only if
-  $I_1$ is included in $I_2$, which concludes the proof.
+    \begin{math}
+        \bar{\varphi}\left([\Product]_{I_1}\right) = [\Product]_{I_2}
+    \end{math}
+    is well-defined, which means that $\Oca_2\OrdQMag\Oca_1$ is
+    equivalent to this condition. Moreover, by the universal property
+    of the quotient, $\bar{\varphi}$ is well-defined if and only if
+    $I_1$ is included in the kernel of the morphism
+    $\varphi:\KMag\to\Oca_2$ defined by
+    \begin{math}
+        \varphi(\Product) = [\Product]_{I_1}.
+    \end{math}
+    \Todo{S: plutôt $[\Product]_{I_2}$ ??}
+    This kernel is equal to $I_2$, so that $\bar{\varphi}$ is
+    well-defined if and only if $I_1$ is included in $I_2$, which
+    concludes the proof.
 \end{proof}
@@
 $\left(\Oca_1\InfQMag\Oca_2\right)(n)$ (resp.
-$\left(\Oca_1\SupQMag\Oca_2\right)(n)$) is the quotient of vector spaces
+$\left(\Oca_1\SupQMag\Oca_2\right)(n)$) is the quotient vector space
 $\KMag(n)/_{I_1(n)+I_2(n)}$ (resp.
@@
     First, we observe that the map $\Oca:\IMag\to\QMag$ defined by
-  $\Oca(I) :=\KMag/_I$ is a bijection: it is surjective by definition of
-  $\QMag$ and it is injective since $\Oca(I_1)=\Oca(I_2)$ implies that
-  the kernel of the natural projection $\KMag\to\Oca(I_1)=\Oca(I_2)$ is
-  both equal to $I_1$ and $I_2$. Moreover, from
+    $\Oca(I) := \KMag/_I$ is a bijection: it is surjective by definition
+    of $\QMag$ and it is injective since
+    \begin{math}
+        \Oca\left(I_1\right) = \Oca\left(I_2\right)
+    \end{math}
+    implies that the kernel of the natural projection
+    \begin{math}
+        \KMag\to\Oca\left(I_1\right) = \Oca\left(I_2\right)
+    \end{math}
+    is equal to both $I_1$ and $I_2$. Moreover, from
     Proposition~\ref{prop:order_relations_on_QMag_and_ideals},
@@
     $\OrdQMag$ is a partial order relation on $\QMag$ and $\Oca$ is a
-  decreasing bijection. The tuple $\left(\IMag,\subseteq,\cap,+\right)$
-  being a lattice, the decreasing bijection $\Oca$ induces lattice
-  operations on $\QMag$, precisely $\InfQMag$ and $\SupQMag$ by
-  definition.
+    decreasing bijection. The tuple
+    $\left(\IMag,\subseteq,\cap,+\right)$ being a lattice, the
+    decreasing bijection $\Oca$ induces lattice operations on $\QMag$,
+    precisely $\InfQMag$ and $\SupQMag$ by definition.
 \end{proof}
@@
 
-The union of generating sets of the two operadic ideals $I_1$ and $I_2$
+The union of the generating sets of two operadic ideals $I_1$ and $I_2$
 is a generating set of $I_1+I_2$, so that the union of generating
@@
 authors do not know how to compute a generating set of the intersection
-of ideals (it is not the intersection of generating relations), so that
-we do not know how to compute generating relations for
-$\Oca_1\SupQMag\Oca_2$.
+of ideals (it is not the intersection of the generating relations), so
+that we do not know how to compute generating relations
+for~$\Oca_1\SupQMag\Oca_2$.
 \medbreak
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{Lemma}
-    \label{lem:lattice_structure_and_coefficients_of_Hiblert_series}
+    \label{lem:lattice_structure_and_coefficients_of_Hilbert_series}
     Let $\Oca_1$ and $\Oca_2$ be two operads of $\QMag$. For every
-    positive integer $n$, we have
+    positive integer~$n$, we have
     \begin{equation}
@@
     Let $I_1, I_2 \in \IMag$ such that $\Oca_1 = \KMag/_{I_1}$ and
-    $\Oca_2 = \KMag/_{I_2}$. For every integer $n$, we have
+    $\Oca_2 = \KMag/_{I_2}$. For every positive integer $n$, we have
     \begin{equation}\begin{split}
-        &\dim{\left(\Oca_1\InfQMag\Oca_2(n)\right)}+
+        \dim & {\left(\Oca_1\InfQMag\Oca_2(n)\right)}+
             \dim{\left(\Oca_1\SupQMag\Oca_2(n)\right)}\\
@@
         +\HilbertSeries_{\Oca_1\SupQMag\Oca_2}(t)&
-        =\sum_{n\in\N}\dim{\left(\left(\Oca_1\InfQMag\Oca_2\right)(n)
+        =\sum_{n \geq 1}\dim{\left(\left(\Oca_1\InfQMag\Oca_2\right)(n)
             \right)}t^n
-            +\sum_{n\in\N}\dim{\left(\left(\Oca_1\SupQMag\Oca_2\right)
+            +\sum_{n \geq 1}\dim{\left(\left(\Oca_1\SupQMag\Oca_2\right)
             (n)\right)}t^n\\
-        &=\sum_{n\in\N}\Big(\dim{\left(\Oca_1\InfQMag\Oca_2(n)\right)}
+        &=\sum_{n \geq 1}\Big(\dim{\left(\Oca_1\InfQMag\Oca_2(n)\right)}
             +\dim{\left(\left(\Oca_1\SupQMag\Oca_2\right)(n)
         \right)}\Big)t^n\\
-        &=\sum_{n\in\N}\Big(\dim{\left(\Oca_1(n)\right)}
+        &=\sum_{n \geq 1}\Big(\dim{\left(\Oca_1(n)\right)}
             +\dim{\left(\Oca_2(n)\right)}\Big)t^n\\
-        &=\sum_{n\in\N}\dim{\left(\Oca_1(n)\right)}t^n+\sum_{n\in\N}
+        &=\sum_{n \geq 1}\dim{\left(\Oca_1(n)\right)}t^n+\sum_{n \geq 1}
             \dim{\left(\Oca_2(n)\right)}t^n\\
@@
     where the third equality is due to
-    Lemma~\ref{lem:lattice_structure_and_coefficients_of_Hiblert_series}.
+    Lemma~\ref{lem:lattice_structure_and_coefficients_of_Hilbert_series}.
 \end{proof}
 \medbreak
+
+\Todo{S: ce thm est une "série génératriciation" du lemme précédent. Je
+serais d'avis de supprimer ce lemme et de montrer directement le thm.
+Avec l'espace gagné, je propose de donner pour cette partie un exemple:
+deux quotients --- linéaires --- de Mag dont on donne les séries
+de Hilbert (quitte à ne pas les démontrer, mais pour illustrer le thm).}

### 2018-09-07 Operads_rewrite.tex
Passe partie 2

@@
 this semi-algorithm never stops. Notice also that the computed
-completion depend on the total order $\leq$ on the binary trees of a
+completion depends on the total order $\leq$ on the binary trees of a
 same arity, the choices at Steps~\ref{item:choice_branching_tree}

### 2018-09-07 CAs_operads.tex
Passe partie 3 (avant lem 3.2.4)

@@
 set of such operads admits a lattice structure, isomorphic to the
-lattice division for nonnegative integers. We relate this lattice to the
-lattice of linear magmatic quotients. We also provide a finite
-convergent presentation of the comb associative operad corresponding
-to~$3$.
+lattice of division for nonnegative integers. We relate this lattice to
+the one of the linear magmatic quotients considered in the previous
+section. We also provide a finite convergent presentation of the comb
+associative operad corresponding to~$3$.
 \medbreak
@@
     the $\CongrCAs{\gamma}$-equivalence classes of binary trees of
-    degree $\gamma$ are trivial, except one consisting in the pair
-    $\left\{\LComb{\gamma}, \RComb{\gamma}\right\}$. Therefore, since a
-    binary tree of degree $d$ has arity $n := \gamma + 1$,
+    degree $\gamma$ are trivial, except one due to the fact that
+    $\LComb{\gamma} \ne \RComb{\gamma}$ and
+    $\LComb{\gamma} \CongrCAs{\gamma} \RComb{\gamma}$. Therefore, since
+    a binary tree of degree $\gamma$ has arity $n := \gamma + 1$,
     \begin{math}
@@
     Hence, if $\varphi$ exists, it is the unique operad morphism from
-    $\CAs{\gamma'}$ to $\CAs{\gamma}$ determined by the previous formula.
-    In this case, $[\Product]_{\CongrCAs{\gamma}}$ being in the image of
-    $\varphi$, the latter is surjective.
+    $\CAs{\gamma'}$ to $\CAs{\gamma}$ determined by the image of
+    $[\Product]_{\CongrCAs{\gamma'}}$. In this case,
+    $[\Product]_{\CongrCAs{\gamma}}$ being in the image of $\varphi$,
+    the latter is surjective.
 \end{proof}
@@
     \end{math}
-    for any binary tree $\Tfr$.
-    Since
+    for any binary tree $\Tfr$. Since
     \begin{math}

### 2018-09-08 CAs_operads.tex
Dessins partie 3 (1/2)

@@
 \begin{equation}
-  z_k :=.
-\end{equation}
-For instance, $z_3$ and $z_4$ are the following trees
-\begin{equation}
-.
+  z_k := \Product \circ_1 ( \Product \circ_2 ( \Product 
+  \circ_1 ( \Product \circ_2 \cdots
+  \Product ) \cdots ).
+\end{equation}
+For instance, $z_4$ and $z_5$ are the following trees
+\begin{equation}
+	\begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
+		\node(0)at(0.00,-3.60){};
+		\node(2)at(2.00,-7.20){};
+		\node(4)at(4.00,-7.20){};
+		\node(6)at(6.00,-5.40){};
+		\node(8)at(8.00,-1.80){};
+		\node[NodeST](1)at(1.00,-1.80){\begin{math}\Product\end{math}};
+		\node[NodeST](3)at(3.00,-5.40){\begin{math}\Product\end{math}};
+		\node[NodeST](5)at(5.00,-3.60){\begin{math}\Product\end{math}};
+		\node[NodeST](7)at(7.00,0.00){\begin{math}\Product\end{math}};
+		\draw[Edge](0)--(1);
+		\draw[Edge](1)--(7);
+		\draw[Edge](2)--(3);
+		\draw[Edge](3)--(5);
+		\draw[Edge](4)--(3);
+		\draw[Edge](5)--(1);
+		\draw[Edge](6)--(5);
+		\draw[Edge](8)--(7);
+		\node(r)at(7.00,1.35){};
+		\draw[Edge](r)--(7);
+	\end{tikzpicture}
+	\qquad \mbox{and} \qquad
+	\begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
+		\node(0)at(0.00,-3.67){};
+		\node(10)at(10.00,-1.83){};
+		\node(2)at(2.00,-7.33){};
+		\node(4)at(4.00,-9.17){};
+		\node(6)at(6.00,-9.17){};
+		\node(8)at(8.00,-5.50){};
+		\node[NodeST](1)at(1.00,-1.83){\begin{math}\Product\end{math}};
+		\node[NodeST](3)at(3.00,-5.50){\begin{math}\Product\end{math}};
+		\node[NodeST](5)at(5.00,-7.33){\begin{math}\Product\end{math}};
+		\node[NodeST](7)at(7.00,-3.67){\begin{math}\Product\end{math}};
+		\node[NodeST](9)at(9.00,0.00){\begin{math}\Product\end{math}};
+		\draw[Edge](0)--(1);
+		\draw[Edge](1)--(9);
+		\draw[Edge](10)--(9);
+		\draw[Edge](2)--(3);
+		\draw[Edge](3)--(7);
+		\draw[Edge](4)--(5);
+		\draw[Edge](5)--(3);
+		\draw[Edge](6)--(5);
+		\draw[Edge](7)--(1);
+		\draw[Edge](8)--(7);
+		\node(r)at(9.00,1.38){};
+		\draw[Edge](r)--(9);
+	\end{tikzpicture}.
 \end{equation}

### 2018-09-09 CAs_operads.tex
Dessins partie 3 (2/2)
Relecture partie 3 (avant prop. 3.2.7)

@@
     an operad morphism $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$, then it
-    is surjective and unique.
+    is surjective and satisfies
+    \begin{math}
+        \varphi\left(\left[\Tfr\right]_{\CongrCAs{\gamma'}}\right)
+        = \left[\Tfr\right]_{\CongrCAs{\gamma}}
+    \end{math}
+    for any binary tree~$\Tfr$.
 \end{Lemma}
@@
     $[\Product]_{\CongrCAs{\gamma}}$ being in the image of $\varphi$,
-    the latter is surjective.
+    the latter is surjective. Finally, it follows that $\varphi$ sends
+    $\left[\Tfr\right]_{\CongrCAs{\gamma'}}$ to
+    $\left[\Tfr\right]_{\CongrCAs{\gamma}}$ by induction on the degree
+    of the binary tree~$\Tfr$.
 \end{proof}
@@
     Assume that $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$ is an operad
-    morphism. By Lemma~\ref{lem:surjective_morphisms_CAs}, $\varphi$
-    satisfies
-    \begin{math}
-        \varphi\left(\left[\Tfr\right]_{\CongrCAs{\gamma'}}\right)
-        = \left[\Tfr\right]_{\CongrCAs{\gamma}}
-    \end{math}
-    for any binary tree $\Tfr$. Since
-    \begin{math}
+    morphism. Since
+    \begin{math}
+      \LComb{\gamma'} \CongrCAs{\gamma'} \RComb{\gamma'},
+    \end{math}
+    we have
+    \begin{equation} \label{equ:morphism_CAs}
         \varphi\left(
@@
         \left[\RComb{\gamma'}\right]_{\CongrCAs{\gamma'}}
-        \right),
-    \end{math}
-    we have
-    \begin{math}
+        \right).
+    \end{equation}
+    Now, by using Lemma~\ref{lem:surjective_morphisms_CAs}, we obtain
+    from~\eqref{equ:morphism_CAs} the relation
+    \begin{equation}
         \left[\LComb{\gamma'}\right]_{\CongrCAs{\gamma}}
@@
         \left[\RComb{\gamma'}\right]_{\CongrCAs{\gamma}},
-    \end{math}
-    which is equivalent to the fact that
-    \begin{math}
-        \LComb{\gamma'} \CongrCAs{\gamma} \RComb{\gamma'}.
-    \end{math}
+    \end{equation}
+    saying that
+    \begin{math}
+        \LComb{\gamma'} \CongrCAs{\gamma} \RComb{\gamma'}
+    \end{math}
+    as excepted.
     \smallbreak
@@
     The binary relation $\OrdCAs$ is reflexive since there exists the
-    identity morphism of $\CAs{\gamma}$ for every positive integer
+    identity morphism on $\CAs{\gamma}$ for every positive integer
     $\gamma$. Let us now assume that
@@
 Recall that $\LRank(\Tfr)$ denotes the left rank of a binary tree
-$\Tfr$, defined in Section~\ref{sec:operad_Mag}. Besides, to simplify
+$\Tfr$, as defined in Section~\ref{sec:operad_Mag}. Besides, to simplify
 the notation, we shall write $\bar{a}$ instead of $a - 1$ for any
@@
 \begin{Lemma}\label{lem:left_rank_and_CongrCAs}
-    Let $\gamma$ be a positive integer and let $\Tfr$ and
-    $\Tfr'$ be two binary trees. If $\Tfr \CongrCAs{\gamma} \Tfr'$, then
-    \begin{equation}
+    Let $\gamma$ be a positive integer and let $\Tfr$ and $\Tfr'$ be two
+    binary trees. If $\Tfr \CongrCAs{\gamma} \Tfr'$, then
+    \begin{equation} \label{equ:left_rank_and_CongrCAs}
         \LRank(\Tfr) \pmod{\bar{\gamma}}
@@
 \begin{proof}
-  We consider the rewrite rule $\LComb{\gamma} \Rew \RComb{\gamma}$
-    on $\Mag$. First, we show that
-    \begin{equation} \label{eq:rewriting_invariant}
-        \Tfr \RewContext \Tfr'
-        \mbox{ implies }
-        \LRank\left(\Tfr'\right) \pmod{\bar{\gamma}} = \LRank\left(\Tfr\right)
-        \, \pmod{\bar{\gamma}}.
-    \end{equation}
-    Indeed, for all $\Tfr \in \Mag$, let
-    $\Tfr_1, \dots, \Tfr_{\LRank\left(\Tfr\right)}$ be the binary trees
-    such that
+    Consider here the rewrite rule $\Rew$ on $\Mag$ satisfying
+    $\LComb{\gamma} \Rew \RComb{\gamma}$. Let us show that the rewrite
+    relation $\RewContext$ induced by $\Rew$ is such that
+    $\Tfr \RewContext \Tfr'$ implies~\eqref{equ:left_rank_and_CongrCAs}.
+    Any binary tree $\Tfr$ decomposes as
     \begin{math}
@@
         \LComb{\LRank\left(\Tfr\right)} \circ
-      \left[\, \Leaf \, \Tfr_1, \dots,
-      \Tfr_{\LRank\left(\Tfr\right)} \right].
-    \end{math}
-    Thus, if $\Tfr \RewContext \Tfr'$, then one of the following two
-    cases occurs:
+        \left[\Leaf, \Tfr_1, \dots,
+        \Tfr_{\LRank\left(\Tfr\right)} \right]
+    \end{math}
+    where the $\Tfr_i$ are binary trees. Now, if
+    $\Tfr \RewContext \Tfr'$, then one among the following two cases
+    occurs.
     \begin{enumerate}[label={(\it\roman*)}]
-    \item the rewrite step is applied on one of the trees $\Tfr_i$,
-      that is there exists $\Tfr_i'$ such that
-            \begin{math}
-              \Tfr' = \LComb{\LRank\left(\Tfr\right)} \circ
-              \left[\, \Leaf ,\Tfr_1, \dots, \Tfr_i',\dots,
+        \item The rewrite step is applied into one of the trees
+        $\Tfr_i$, that is there exists $\Tfr_i'$ such that
+        \begin{math}
+            \Tfr' = \LComb{\LRank\left(\Tfr\right)}
+            \circ \left[\Leaf, \Tfr_1, \dots, \Tfr_i', \dots,
                 \Tfr_{\LRank\left(\Tfr\right)}
-              \right] \mbox{, so that }
-              \LRank\left(\Tfr'\right) = \LRank\left(\Tfr\right);
-            \end{math}
-          \item the rewrite step is applied in the left branch beginning
-            at the root, that is there exists $i$ such that
-            \begin{math}
-              \Tfr' = \LComb{\LRank\left(\Tfr\right)-\bar{\gamma}} \circ
-              \left[ \Leaf ,\Tfr_1, \dots,
-                 \RComb{\bar{\gamma}} \circ
-                 [\Tfr_{i},\dots, \Tfr_{i+\bar{\gamma}}]
-                 ,\dots, \Tfr_{\LRank\left(\Tfr\right)}
             \right]
-              \mbox{, so that }\\
+        \end{math}
+        so that
+        \begin{math}
+            \LRank\left(\Tfr'\right) = \LRank\left(\Tfr\right).
+        \end{math}
+        \item The rewrite step is applied into the left branch
+          beginning
+            at the root of $\Tfr$, that is there exists $i$ such that
+            \begin{math}
+                \Tfr' = \LComb{\LRank\left(\Tfr\right)-\bar{\gamma}}
+                \circ \left[\Leaf, \Tfr_1, \dots, \RComb{\bar{\gamma}}
+                \circ
+                \left[\Tfr_{i},\dots, \Tfr_{i+\bar{\gamma}}\right],
+                \dots, \Tfr_{\LRank\left(\Tfr\right)} \right]
+            \end{math}
+            so that
+            \begin{math}
                 \LRank\left(\Tfr'\right) =
@@
     \end{enumerate}
-    This concludes the proof of~\eqref{eq:rewriting_invariant}.
-    \smallbreak
-
-    We deduce from~\eqref{eq:rewriting_invariant} that the equivalence
-    relation $\simeq$ defined by
-    \begin{equation}
-        \Tfr \simeq \Tfr' \mbox{ if and only if }
-        \LRank\left(\Tfr'\right) \pmod{\bar{\gamma}} =
-        \LRank\left(\Tfr\right) \, \pmod{\bar{\gamma}}
-    \end{equation}
-    contains the relation $\RewContext$, so that it contains its
-    transitive symmetric closure. The latter is $\CongrCAs{\gamma}$,
-    which concludes the proof of Lemma~\ref{lem:left_rank_and_CongrCAs}.
+    This implies~\eqref{equ:left_rank_and_CongrCAs}. Finally, since
+    $\CongrCAs{\gamma}$ is the reflexive, symmetric, and transitive
+    closure of~$\RewContext$, the statement of the lemma follows.
 \end{proof}
@@
 consider the following "zig-zag" of degree $k \geq 0$
-\Todo{Dessins}
 \begin{equation}
@@
 The first family is the set of the $n-1$ trees
-$\left(z_k \circ_{k+1} z_{n-1-k}\right)_{1 \leq k \leq n-1}$,
-pictured as follows
+$\left(z_k \circ_{k+1} z_{n-1-k}\right)_{1 \leq k \leq n-1}$.
+For example,
 \begin{equation}\label{equ:normal_forms_type_A}
-   z_k \circ_{k+1} z_{n-1-k} = dessin.
+   z_8 \circ_{9} z_{3} =
+   \begin{tikzpicture}[xscale=.18,yscale=.16,Centering]
+      \node(0)at(0.00,-5.56){};
+      \node(10)at(10.00,-19.44){};
+      \node(12)at(12.00,-13.89){};
+      \node(14)at(14.00,-8.33){};
+      \node(16)at(16.00,-8.33){};
+      \node(18)at(18.00,-13.89){};
+      \node(2)at(2.00,-11.11){};
+      \node(20)at(20.00,-13.89){};
+      \node(22)at(22.00,-11.11){};
+      \node(24)at(24.00,-5.56){};
+      \node(4)at(4.00,-16.67){};
+      \node(6)at(6.00,-22.22){};
+      \node(8)at(8.00,-22.22){};
+      \node(19)at(19.00,-11){};
+      \node[NodeST](1)at(1.00,-2.78){\begin{math}\Product\end{math}};
+      \node[NodeST](11)at(11.00,-11.11){\begin{math}\Product\end{math}};
+      \node[NodeST](13)at(13.00,-5.56){\begin{math}\Product\end{math}};
+      \node[NodeST](15)at(15.00,0.00){\begin{math}\Product\end{math}};
+      \node[NodeST](17)at(17.00,-5.56){\begin{math}\Product\end{math}};
+      \node[NodeST](21)at(21.00,-8.33){\begin{math}\Product\end{math}};
+      \node[NodeST](23)at(23.00,-2.78){\begin{math}\Product\end{math}};
+      \node[NodeST](3)at(3.00,-8.33){\begin{math}\Product\end{math}};
+      \node[NodeST](5)at(5.00,-13.89){\begin{math}\Product\end{math}};
+      \node[NodeST](7)at(7.00,-19.44){\begin{math}\Product\end{math}};
+      \node[NodeST](9)at(9.00,-16.67){\begin{math}\Product\end{math}};
+      \draw[Edge](0)--(1);
+      \draw[Edge](1)--(15);
+      \draw[Edge](10)--(9);
+      \draw[Edge](11)--(3);
+      \draw[Edge](12)--(11);
+      \draw[Edge](13)--(1);
+      \draw[Edge](14)--(13);
+      \draw[Edge](16)--(17);
+      \draw[Edge](17)--(23);
+      \draw[Edge](19)--(21);
+      \draw[Edge](2)--(3);
+      \draw[Edge](21)--(17);
+      \draw[Edge](22)--(21);
+      \draw[Edge](23)--(15);
+      \draw[Edge](24)--(23);
+      \draw[Edge](3)--(13);
+      \draw[Edge](4)--(5);
+      \draw[Edge](5)--(11);
+      \draw[Edge](6)--(7);
+      \draw[Edge](7)--(9);
+      \draw[Edge](8)--(7);
+      \draw[Edge](9)--(5);
+      \node(r)at(15.00,2.08){};
+      \draw[Edge](r)--(15);
+    \end{tikzpicture}.
 \end{equation}

### 2018-09-09 CAs_operads.tex
Relecture partie 3 (avant partie 3.3)

@@
 \begin{Lemma}\label{lem:left_rank_and_CongrCAs}
-    Let $\gamma$ be a positive integer and let $\Tfr$ and $\Tfr'$ be two
+    Let $\gamma \geq 2$ be an integer and let $\Tfr$ and $\Tfr'$ be two
     binary trees. If $\Tfr \CongrCAs{\gamma} \Tfr'$, then
@@
 \begin{Proposition} \label{prop:division_CAs}
-    Let $\gamma$ and $\gamma'$ be two positive integers. Then, there
+    Let $\gamma$ and $\gamma'$ be two positive integers such that
+    $\gamma \geq 2$. Then, there
     exists a morphism $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$ if and
@@
     $\bar{\gamma} \mid \bar{\gamma'}$. If
-    $\LComb{\gamma'}\CongrCAs{\gamma}\RComb{\gamma'}$, $\gamma$ is
-    smaller than $\gamma'$ (this is a consequence of the existence of a
-    surjective morphism $\varphi:\CAs{\gamma'} \to \CAs{\gamma}$ and
-    Lemma~\ref{lem:first_dimensions_CAs}). From
-    Lemma~\ref{lem:left_rank_and_CongrCAs}, we deduce that
-    \begin{math}
+    \begin{math}
+        \LComb{\gamma'}\CongrCAs{\gamma}\RComb{\gamma'},
+    \end{math}
+    as a consequence of the existence of a surjective morphism $\varphi$
+    from $\CAs{\gamma'}$ to $\CAs{\gamma}$ and
+    Lemmas~\ref{lem:first_dimensions_CAs}
+    and~\ref{lem:surjective_morphisms_CAs}, one has $\gamma' = 1$ or
+    $\gamma \leq \gamma'$. Since
+    \begin{equation}
         \LRank\left(\LComb{\gamma'}\right)
         - \LRank\left(\RComb{\gamma'}\right)
-        = \bar{\gamma'}
-    \end{math}
-    is divisible by $\bar{\gamma}$, which shows the direct implication.
+        = \gamma' - 1
+        = \bar{\gamma'},
+    \end{equation}
+    by using Lemma~\ref{lem:left_rank_and_CongrCAs}, we deduce that
+    $\bar{\gamma'}$ is divisible by $\bar{\gamma}$, which shows the
+    direct implication.
     \smallbreak
 
-    Conversely, if
-    $\bar{\gamma} \mid \bar{\gamma'}$, the rewrite
-    rule $\LComb{\gamma} \Rew \RComb{\gamma}$ induces the
-    sequence
+    Conversely, if $\bar{\gamma} \mid \bar{\gamma'}$, the rewrite rule
+    $\Rew$ on $\Mag$ satisfying $\LComb{\gamma} \Rew \RComb{\gamma}$
+    induces the sequence
     \begin{multline}
@@
     \end{multline}
-    of rewriting steps, where squared regions denotes left or right
-    comb trees of degree $\gamma - 1$. Hence, we have
-    $\LComb{\gamma'}\CongrCAs{\gamma}\RComb{\gamma'}$.
+    of rewrite steps, where squared regions denotes left or right
+    comb trees of degree $\gamma - 1$. Hence, since
+    $\CongrCAs{\gamma}$ is the reflexive, symmetric, and transitive
+    closure of $\RewContext$, we
+    have~$\LComb{\gamma'}\CongrCAs{\gamma}\RComb{\gamma'}$.
 \end{proof}
@@
 The lattice $\left(\N, \mid, \gcd, \lcm\right)$ admits $1$ as minimum
-element and $0$ as maximum element: any nonnegative integer is
-divisible by $1$ and divides $0$. The corresponding property for
-$\LatCAs$ is that it admits $\As=\CAs{2}$ as minimum element and $\Mag=
-\CAs{1}$ as maximum element: any comb associative operad projects onto
-$\As$ and is a quotient of $\Mag$.
+element and $0$ as maximum element since any nonnegative integer is
+divisible by $1$ and divides $0$. These properties translate as follows
+for $\LatCAs$: the minimum element is $\As=\CAs{2}$ and the maximum
+element is $\Mag=\CAs{1}$. Algebraically, this says that any comb
+associative operad projects onto $\As$ and is a quotient of~$\Mag$.
 \medbreak
@@
 is $\iota$ is not a lattice morphism. Consider for instance $\gamma = 3$
-and $\gamma' = 4$, so that $\KCAs{\gamma} \InfCAs \KCAs{\gamma'}$ is
-equal to $\KCAs{2} = \K\As$, whereas
-$\KCAs{\gamma} \InfQMag \KCAs{\gamma'}$ is the quotient of $\KMag$ by the
-two relations $\LComb{3} - \RComb{3}$ and $\LComb{4} - \RComb{4}$.
+and $\gamma' = 4$, so that
+\begin{equation}
+    \KCAs{3} \InfCAs \KCAs{4} = \KCAs{2} = \K\Angle{\As},
+\end{equation}
+whereas
+\begin{equation}
+    \KCAs{3} \InfQMag \KCAs{4} =
+    \KMag/_I
+\end{equation}
+where $I$ is the ideal of $\KMag$ generated by
+$\LComb{3} - \RComb{3}$ and $\LComb{4} - \RComb{4}$.
 \medbreak

### 2018-09-09 Operads_rewrite.tex
Relecture partie 3 (avant partie 3.3)

@@
 $\NormalForms_{\RewContext}$ of all normal forms of $\RewContext$ is
-called a \Def{Poincaré-Birkhoff-Witt basis} (or a \Def{PBW basis} for
-short) of the quotient operad $\Oca$ (see~\cite{Hof10,DK10}). This forms
-a one-to-one correspondence between the sets
+called a \Def{Poincaré-Birkhoff-Witt basis}~\cite{Hof10,DK10} (or a
+\Def{PBW basis} for short) of the quotient operad $\Oca$. This forms a
+one-to-one correspondence between the sets
 $\NormalForms_{\RewContext}(n)$ and $\Oca(n)$, $n \geq 1$. In other

### 2018-09-09 CAs_operads.tex
Relecture partie 3 (avant partie 3.3.2)

@@
 operads~\cite[Section 3.7]{DK10} with respect to the lexicographic order
-on prefix words. We first focus on the special case $\gamma = 3$.
+on prefix words. We first focus on the special case~$\gamma = 3$.
 \medbreak
@@
     for $\#\CAs{3}(n)$ and for the numbers of normal forms of arity $n$,
-    when $ 1 \leq n \leq 14$, which proves
-    Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}.
+    when $ 1 \leq n \leq 14$, which proves the statement of the
+    theorem.
 \end{proof}
@@
 \end{equation}
-We also obtain from Theorem~\ref{thm:convergent_rewrite_rule_CAs_3}
-the following consequences.
+We also obtain from Theorem~\ref{thm:convergent_rewrite_rule_CAs_3} the
+following consequences.
 \medbreak
@@
     The set of the trees avoiding as subtrees the ones appearing as
-    left members of $\Rew$ is a Poincaré-Birkhoff-Witt basis
-    of~$\CAs{3}$.
+    left members of $\Rew$ is a PBW basis of~$\CAs{3}$.
 \end{Proposition}
@@
 
-Let us describe the normal forms for arity $n\geq 11$. For that, we
-consider the following "zig-zag" of degree $k \geq 0$
-\begin{equation}
-  z_k := \Product \circ_1 ( \Product \circ_2 ( \Product
-  \circ_1 ( \Product \circ_2 \cdots
-  \Product ) \cdots ).
-\end{equation}
-For instance, $z_4$ and $z_5$ are the following trees
-\begin{equation}
+Let us describe the elements of the PBW basis of $\CAs{3}$ for arity
+$n \geq 11$. By Proposition~\ref{prop:PBW_basis_CAs_3}, these elements
+are the normal forms of the rewrite relation induced by $\Rew$. Let for
+any $d \geq 0$, the binary tree $\Zfr_d$ defined recursively by
+\begin{equation}
+    \Zfr_d :=
+    \begin{cases}
+        \Leaf & \mbox{if } d = 0, \\
+        \Zfr_{d - 1}
+        \circ_{\left\lfloor \frac{d}{2} \right\rfloor + 1} \Product
+        & \mbox{otherwise}.
+    \end{cases}
+\end{equation}
+For instance,
+\begin{equation}
+    \Zfr_4 =
     \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
@@
     \qquad \mbox{and} \qquad
+    \Zfr_5 =
     \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
@@
 \end{equation}
-The normal forms are decomposed into two families.
-The first family is the set of the $n-1$ trees
-$\left(z_k \circ_{k+1} z_{n-1-k}\right)_{1 \leq k \leq n-1}$.
-For example,
-\begin{equation}\label{equ:normal_forms_type_A}
-   z_8 \circ_{9} z_{3} =
+The normal forms split into two families. The first one is the set
+of the $n - 1$ trees of the form
+\begin{equation} \label{equ:normal_forms_type_A}
+    \Zfr_d \circ_{d + 1} \Zfr_{n - 1 - d},
+\end{equation}
+for any $d \in [n - 1]$. For example, for $n = 12$,
+\begin{equation}
+    z_8 \circ_9 z_3 =
     \begin{tikzpicture}[xscale=.18,yscale=.16,Centering]
@@
         \node[NodeST](1)at(1.00,-2.78){\begin{math}\Product\end{math}};
-      \node[NodeST](11)at(11.00,-11.11){\begin{math}\Product\end{math}};
-      \node[NodeST](13)at(13.00,-5.56){\begin{math}\Product\end{math}};
+        \node[NodeST](11)at(11.00,-11.11)
+            {\begin{math}\Product\end{math}};
+        \node[NodeST](13)at(13.00,-5.56)
+            {\begin{math}\Product\end{math}};
         \node[NodeST](15)at(15.00,0.00){\begin{math}\Product\end{math}};
-      \node[NodeST](17)at(17.00,-5.56){\begin{math}\Product\end{math}};
-      \node[NodeST](21)at(21.00,-8.33){\begin{math}\Product\end{math}};
-      \node[NodeST](23)at(23.00,-2.78){\begin{math}\Product\end{math}};
+        \node[NodeST](17)at(17.00,-5.56)
+            {\begin{math}\Product\end{math}};
+        \node[NodeST](21)at(21.00,-8.33)
+            {\begin{math}\Product\end{math}};
+        \node[NodeST](23)at(23.00,-2.78)
+            {\begin{math}\Product\end{math}};
         \node[NodeST](3)at(3.00,-8.33){\begin{math}\Product\end{math}};
@@
         \draw[Edge](9)--(5);
-      \node(r)at(15.00,2.08){};
+        \node(r)at(15.00,2.25){};
         \draw[Edge](r)--(15);
-    \end{tikzpicture}.
-\end{equation}
-The second family is composed of the following four trees
+    \end{tikzpicture}
+\end{equation}
+is a tree of this first family. The second family contains the
+following four trees
 \begin{equation}\label{equ:normal_forms_type_B}
@@
         \draw[Edge](r)--(3);
-  \end{tikzpicture}, \qquad
+    \end{tikzpicture}\,, \qquad
     \begin{tikzpicture}[xscale=.22,yscale=.20,Centering]
@@
 \end{equation}
-Indeed, each of these $n+3$ trees avoids the left membres of the
+Observe that each of these $n + 4$ trees avoids the left members of the
 convergent presentation given in
@@
 
-\begin{Proposition}
-  The family~\eqref{equ:normal_forms_type_B} is absorbing for each
-  partial composition.
+\begin{Proposition} \label{prop:absorbing_normal_forms_type_B}
+    For any two trees $\Tfr$ and $\Tfr'$ of the
+    form~\eqref{equ:normal_forms_type_B} and $i \in [|\Tfr|]$, the
+    normal form for the rewrite relation induced by $\Rew$ of
+    $\Tfr \circ_i \Tfr'$ is a tree of the
+    form~\eqref{equ:normal_forms_type_B}.
 \end{Proposition}
-
 \begin{proof}
-  None of the trees of type~\eqref{equ:normal_forms_type_A}
-  contains the left or the right member of the congruence relation
-  $\CongrCAs{3}$, so that they are alone in their equivalence classes.
-  Moreover, the trees of type~\eqref{equ:normal_forms_type_B}
-  contain the right member of $\CongrCAs{3}$, so that the composition of
-  such a tree with anothter tree is not alone in its
-  equivalence class, and thus it does not belong to the
-  family~\eqref{equ:normal_forms_type_A}.
+    None of the trees of the form~\eqref{equ:normal_forms_type_A}
+    contain the left or the right member of the rewrite
+    rule~\eqref{equ:rew_1} generating the congruence relation
+    $\CongrCAs{3}$. Hence, these trees are alone in their equivalence
+    classes. Moreover, the trees of the
+    form~\eqref{equ:normal_forms_type_B} contain the right member of
+    the rewrite rule~\eqref{equ:rew_1} generating the congruence
+    relation $\CongrCAs{3}$, so that the composition of such a tree
+    with another tree is not alone in its equivalence class, and thus
+    it does not belong to the family~\eqref{equ:normal_forms_type_A}.
 \end{proof}
-
-By computer explorations, we are able to conjecture the multiplication
-tables of each partial compositions. However, the obtained tables are not
-simply described. For instance, the partial composition
-$\Tfr\circ_i\Tfr'$ with $\Tfr$ of type~\eqref{equ:normal_forms_type_A}
-and $\Tfr'$ of type~\eqref{equ:normal_forms_type_B} is described by $36$
-cases depending on the values of various parameters associated to $\Tfr$,
-$\Tfr'$ and $i$.
-
-\medbreak
+\medbreak
+
+Proposition~\ref{prop:absorbing_normal_forms_type_B} says that the
+family of trees~\eqref{equ:normal_forms_type_B} is absorbing
+for the partial composition.
+\medbreak
+
+Computer explorations allow us to conjecture the multiplication table
+of the exhibited PBW basis of $\CAs{3}$. However, we do note have a
+simple description of this table. For instance, the partial composition
+$\Tfr\circ_i\Tfr'$ where $\Tfr$ is a tree of the
+form~\eqref{equ:normal_forms_type_A} and $\Tfr'$ is a tree of the
+form~\eqref{equ:normal_forms_type_B} can be fully described by $36$
+cases depending on the values of various parameters associated with
+$\Tfr$, $\Tfr'$, and~$i$.
+\medbreak
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-09-10 CAs_operads.tex
Relecture partie 3 (fin)

@@
     z_8 \circ_9 z_3 =
-    \begin{tikzpicture}[xscale=.18,yscale=.16,Centering]
+    \begin{tikzpicture}[xscale=.18,yscale=.14,Centering]
         \node(0)at(0.00,-5.56){};
@@
         \draw[Edge](9)--(5);
-        \node(r)at(15.00,2.25){};
+        \node(r)at(15.00,2.5){};
         \draw[Edge](r)--(15);
@@
 \label{sec:higher_comb_associative_operads}
-
-We run the same algorithm for $\CAs{\gamma}$ when $\gamma \geq 4$.
-We obtain the following results.
-\medbreak
-
-\Todo{S:remettre la table en forme.}
-\begin{center}
-  \begin{math} \label{arr:completions_CAs}
-    \begin{array}{|c|l|}
-      \hline
-      \gamma & \mbox{The sequence of first cardinalities of }
-       \CAs{\gamma} \mbox{completion}\\ \hline
-      1 & 0, 1, 0, 0, \dots \\ \hline
-      2 & 0, 0, 1, 0, 0, \dots \\ \hline
-      3 & 0, 0, 0, 1, 1, 2, 3, 4, 0, 0, \dots \\ \hline
-      4 & 0, 0, 0, 0, 1, 1, 0, 3, 4, 5, 18, 22, 11, 12, 15, 19, 25, 36,
-       44, 52, 68, 79, 93, 105, 106, 109 \\ \hline
-      5 & 0, 0, 0, 0, 0, 1, 1, 0, 0, 4, 5, 8, 18, 31, 36, 48, 73, 111,
-       172, 272, 455, 783 \\ \hline
-      6 & 0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 5, 6, 11, 23, 30, 48, 73,
-      117, 204, 348, 589, 1004 \\ \hline
-      7 & 0, 0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 6, 7, 16, 24, 32, 49,
-      88, 150, 261, 475, 854\\ \hline
-      8 & 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0, 7, 8, 21, 29,
-      34, 53, 93, 172, 311, 565\\ \hline
-      9 & 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 0, 0, 0, 0, 0, 0, 8, 9, 28,
-      30, 36, 57, 101, 185, 348, 648\\ \hline
-    \end{array}
-  \end{math}
-\end{center}
-\medbreak
-
-From these computer explorations, we conjecture that this algorithm
-does not provide a finite convergent presentation of $\CAs{\gamma}$,
-when $\gamma \geq 4$. We point out that for $\CAs{4}$ new
-rewrite rules still appear at degree $41$. Moreover, the total number of
-rewrite rules at degree $41$ is $3149$.
+Let us provide here some experimental data. First,
+Table~\ref{tab:dimensions_CAs} shows the first dimensions of the
+operads $\CAs{\gamma}$ for $\gamma \in [9]$.
+\begin{table}[ht]
+    \centering
+    \footnotesize
+    \setlength{\tabcolsep}{.35em}
+    \begin{tabular}{c||ccccccccccccccccc}
+        $\gamma$ & \multicolumn{17}{c}{Dimensions of $\CAs{\gamma}$}
+        \\ \hline \hline
+        1 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 429 & 1430 & 4862
+        & 16796 & 58786 & 208012 & 742900 & 2674440 & 9694845
+        & 35357670
+        \\
+        2 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1
+        & 1 & 1
+        \\
+        3 & 1 & 1 & 2 & 4 & 8 & 14 & 20 & 19 & 16 & 14 &
+        14 & 15 & 16 & 17 & 18 & 19 & 20
+        \\
+        4 & 1 & 1 & 2 & 5 & 13 & 35 & 96 & 264 & 724 & 1973 & 5335
+        & 14390 & 38872 & 105141 & 284929 & 774254 & 2111088
+        %& 5778420 & 15882100 & 43837388 & 121507230
+        \\
+        5 & 1 & 1 & 2 & 5 & 14 & 41 & 124 & 384 & 1210 & 3861 & 12440
+        & 40392 & 131997 & 433782 & 1432696 & 4752857
+        & 15829261
+        %& 52905635 & 177395246
+        \\
+        6 & 1 & 1 & 2 & 5 & 14 & 42 & 131 & 420 & 1375 & 4576 & 15431
+        & 52598 & 180895 & 626862 & 2186504 & 7670138
+        & 27041833
+        %& 95764569
+        \\
+        7 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 428 & 1420 & 4796 & 16432
+        & 56966 & 199444 & 704140 & 2503914 & 8959699
+        & 32236657
+        %& 116551168
+        \\
+        8 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 429 & 1429 & 4851 & 16718
+        & 58331 & 205632 & 731272 & 2620176 & 9449688 & 34276116
+        %& 124958386
+        \\
+        9 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 429 & 1430 & 4861 & 16784
+        & 58695 & 207452 & 739840 & 2658936 & 9620232 & 35011566
+        %& 128082515
+    \end{tabular}
+    \medbreak
+
+    \caption{\footnotesize
+    The sequences of the cardinalities, arity by arity, of the
+    dimensions of~$\CAs{\gamma}$.}
+    \label{tab:dimensions_CAs}
+\end{table}
+\medbreak
+
+Moreover, we run the same completion algorithm for $\CAs{\gamma}$ as
+the one considered in Section~\ref{subsubsec:CAs_3}, now for
+$\gamma \in [9]$. Table~\ref{tab:cardinalities_completion_CAs} shows
+the number of rewrite rules needed to obtain complete orientations.
+\begin{table}[ht]
+    \centering
+    \footnotesize
+    \setlength{\tabcolsep}{.35em}
+    \begin{tabular}{c||ccccccccccccccccccccccccccc}
+        $\gamma$ & \multicolumn{27}{c}{
+        Cardinalities of completions of $\CAs{\gamma}$}
+        \\ \hline \hline
+        1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
+        & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
+        \\
+        2 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
+        & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
+        \\
+        3 & 0 & 0 & 0 & 1 & 1 & 2 & 3 & 4 & 0 & 0 & 0 & 0 & 0 & 0 & 0
+        & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
+        \\
+        4 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 3 & 4 & 5 & 18 & 22 & 11 & 12
+        & 15 & 19 & 25 & 36 & 44 & 52 & 68 & 79 & 93 & 105 & 106 & 109
+        \\
+        5 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 4 & 5 & 8 & 18 & 31
+        & 36 & 48 & 73 & 111 & 172 & 272 & 455 & 783
+        \\
+        6 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 5 & 6 & 11
+        & 23 & 30 & 48 & 73 & 117 & 204 & 348 & 589 & 1004
+        \\
+        7 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 0 & 6 & 7
+        & 16 & 24 & 32 & 49 & 88 & 150 & 261 & 475 & 854
+        \\
+        8 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 0 & 0
+        & 7 & 8 & 21 & 29 & 34 & 53 & 93 & 172 & 311 & 565
+        \\
+        9 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 0
+        & 0 & 0 & 8 & 9 & 28 & 30 & 36 & 57 & 101 & 185 & 348 & 648
+    \end{tabular}
+    \medbreak
+
+    \caption{\footnotesize
+    The sequences of the cardinalities, arity by arity, of the rewrite
+    rules being completions of orientations of~$\CongrCAs{\gamma}$.}
+    \label{tab:cardinalities_completion_CAs}
+\end{table}
+\Todo{S: erreur dans la table pour $\gamma = 1$ ? Il doit y avoir que
+des $0$, j'ai corrigé. Vérifier.}
+\Todo{S: il faut équilibrer la table. Toutes les suites doivent avoir
+la même longueur. (ou alors, il est toléré d'avoir des suites plus
+courtes à mesure que $\gamma$ augmente... mais non ici.)}
+From these computer explorations, we conjecture that the algorithm we
+use does not provide a finite convergent presentation of $\CAs{\gamma}$,
+when $\gamma \geq 4$. We point out that for $\CAs{4}$ new rewrite
+rules still appear in arity $42$. Moreover, the total number of rewrite
+rules at this arity is~$3149$.
 \medbreak
@@
 $\Tfr_1 \Rew  \Tfr_2$ or $\Tfr_2 \Rew  \Tfr_1$.
-If at any moment the rewrite relation $\RewContext$ induced by $\Rew$
+If at any moment the rewrite relation $\RewContext$ induced by~$\Rew$
 loops (that is $\RewContext$ is not antisymmetric), we simply reject it.
-\medbreak
-
-We did not find a finite presentation for $\CAs{4}$, $\CAs{5}$, and
+We do not find any finite presentation for $\CAs{4}$, $\CAs{5}$, and
 $\CAs{6}$ until arity $12$. We conjecture that there is no finite
-convergent presentation of $\CAs{\gamma}$ with one generator when
-$\gamma \geq 4$. We discuss the cases with more than one generator in
-the perspectives.
-\medbreak
-
-\Todo{S: la numérotation de la table n'apparait pas (mais je m'occuperai
-de la faire marcher quand je ferai la remise en forme.}
-Thanks to the partial completions presented in table
-\eqref{arr:completions_CAs}, we can compute the following first
-dimensions of $\CAs{\gamma}$.
-\begin{center}
-  \begin{math} \label{arr:dimensions_CAs}
-    \begin{array}{|c|l|}
-      \hline
-      \gamma & \mbox{The sequence of first dimensions of }
-       \CAs{\gamma}\\ \hline
-      1 & 1, 1, 2, 5, 14, 42, 132, 429, 1430, 4862, \dots \\ \hline
-      2 & 1, 1, 1, \dots \\ \hline
-      3 & 1, 1, 2, 4, 8, 14, 20, 19, 16, 14,
-          14, 15, 16, 17, \dots \\ \hline
-      4 & 1, 1, 2, 5, 13, 35, 96, 264, 724, 1973, 5335, 14390, 38872,
-          105141, 284929, 774254, 2111088,\\
-        & 5778420, 15882100, 43837388, 121507230 \\ \hline
-      5 & 1, 1, 2, 5, 14, 41, 124, 384, 1210, 3861, 12440, 40392, 131997,
-          433782, 1432696, 4752857, \\
-        & 15829261, 52905635, 177395246 \\ \hline
-      6 & 1, 1, 2, 5, 14, 42, 131, 420, 1375, 4576, 15431, 52598, 180895,
-          626862, 2186504, 7670138, \\
-        & 27041833, 95764569 \\ \hline
-      7 & 1, 1, 2, 5, 14, 42, 132, 428, 1420, 4796, 16432, 56966, 199444,
-          704140, 2503914, 8959699, \\
-        & 32236657, 116551168\\ \hline
-      8 & 1, 1, 2, 5, 14, 42, 132, 429, 1429, 4851, 16718, 58331, 205632,
-          731272, 2620176, 9449688, \\
-        & 34276116, 124958386\\ \hline
-      9 & 1, 1, 2, 5, 14, 42, 132, 429, 1430, 4861, 16784, 58695, 207452,
-          739840, 2658936, 9620232, \\
-        & 35011566, 128082515\\ \hline
-    \end{array}
-  \end{math}
-\end{center}
-\medbreak
-
-\Todo{S:remettre la table en forme.}
+convergent presentation of $\CAs{\gamma}$ when
+$\gamma \geq 4$.
+\medbreak
+
+\Todo{S: j'ai supprimé les remarques concernant les générateurs multiples
+car on n'en a pas du tout parlé pour l'instant. Ça a plus sa place
+dans les persp.}

### 2018-09-10 Conclusion.tex
Fin relecture Cyrille
Relecture conclusion

@@
 A first research direction consists in finding convergent presentations
-for (all or most of) the $\CAs{\gamma}$ operads in
-order to describe algebraic and combinatorial properties of these
-operads (as describing explicit bases, computing Hilbert
-series, and providing combinatorial realizations). This has been
-done only in the case $\gamma = 3$. For some other cases, we only have
-conjectural and experimental data (see Section~\ref{?}).
-\Todo{S: compléter avec la bonne partie une fois qu'on aura ajouté ces
-données}.
+for (all or most of) the operads $\CAs{\gamma}$ in
+order to describe algebraic and combinatorial properties of them (as
+describing explicit bases, computing Hilbert series, and providing
+combinatorial realizations). This has been done only in the case
+$\gamma = 3$. For some other cases, we only have conjectural and
+experimental data (see
+Section~\ref{sec:higher_comb_associative_operads}).
 \medbreak
@@
 the quotients $\Oca_1$ and $\Oca_2$ of $\Mag$,
-as well as the one of the lower-bound $\Oca_2 \InfQMag \Oca_2$, the
+as well as the one of the lower-bound $\Oca_1 \InfQMag \Oca_2$, the
 question consists in designing an algorithm for computing a completion
@@
 
-A last research axis rely on the study on the $2$-magmatic operad
+A last research axis relies on the study on the $2$-magmatic operad
 $\TwoMag$, that is, the free operad generated by two binary elements.
 The analog of the associative operad in this context is the operad
-$\TwoAs$ (see~\cite{LR06}), defined as the quotient of $\TwoMag$ by
-the congruence saying that the two generators are associative. This
-operad has a nice combinatorial realization in terms of alternating
-bicolored Schröder trees. The question consists here in generalizing
-our main results for the quotients of $\TwoMag$ and the generalizations
-of $\TwoAs$ (definition of analog of comb associative operads and
-study of its presentations).
+$\TwoAs$~\cite{LR06} defined as the quotient of $\TwoMag$ by the
+congruence saying that the two generators are associative. This operad
+has a nice combinatorial realization in terms of alternating bicolored
+Schröder trees. The question consists here in generalizing our main
+results for the quotients of $\TwoMag$ and the generalizations of
+$\TwoAs$ (that is, the definition of analogs of comb associative operads
+and the study of their presentations).
 \medbreak

### 2018-09-10 CAs_operads.tex
Corrections 3.3.1

@@
 \end{equation}
-Observe that each of these $n + 4$ trees avoids the left members of the
+Observe that each of these $n + 3$ trees avoids the left members of the
 convergent presentation given in
@@
 \begin{Proposition} \label{prop:absorbing_normal_forms_type_B}
-    For any two trees $\Tfr$ and $\Tfr'$ of the
-    form~\eqref{equ:normal_forms_type_B} and $i \in [|\Tfr|]$, the
-    normal form for the rewrite relation induced by $\Rew$ of
+    For any two trees $\Tfr$ and $\Tfr'$, if one of them is of the
+    form~\eqref{equ:normal_forms_type_B} and $i \in [|\Tfr|]$, then
+    the normal form for the rewrite relation induced by $\Rew$ of
     $\Tfr \circ_i \Tfr'$ is a tree of the

### 2018-09-10 CAs_operads.tex
Corrections 3.3.2

@@
         & 15 & 19 & 25 & 36 & 44 & 52 & 68 & 79 & 93 & 105 & 106 & 109
+        & 107
         \\
@@
 $\CAs{6}$ until arity $12$. We conjecture that there is no finite
-convergent presentation of $\CAs{\gamma}$ when
-$\gamma \geq 4$.
-\medbreak
-
-\Todo{S: j'ai supprimé les remarques concernant les générateurs multiples
-car on n'en a pas du tout parlé pour l'instant. Ça a plus sa place
-dans les persp.}
+convergent presentation of $\CAs{\gamma}$ with one generator when
+$\gamma \geq 4$. We discuss the cases with more than one generator in
+the perspectives.
+\medbreak

### 2018-09-10 Mag_quotients.tex
MAJ

@@
     \begin{math}
-        \varphi(\Product) = [\Product]_{I_1}.
+        \varphi(\Product) = [\Product]_{I_2}.
     \end{math}
-    \Todo{S: plutôt $[\Product]_{I_2}$ ??}
     This kernel is equal to $I_2$, so that $\bar{\varphi}$ is
@@
 \subsection{Hilbert series and Grassmann formula}
-In order to show a Grassmann formula analog for $\LatQMag$, we need the
-following lemma.
+The statement of the Grassmann formula analog for $\LatQMag$ is the
+following.
 \medbreak
 
-\begin{Lemma}
-    \label{lem:lattice_structure_and_coefficients_of_Hilbert_series}
-    Let $\Oca_1$ and $\Oca_2$ be two operads of $\QMag$. For every
-    positive integer~$n$, we have
+\begin{Theorem}
+    \label{thm:Grassmann_formula_for_Hilbert_series_of_QMag}
+    Let $\Oca_1$ and $\Oca_2$ be two operads of $\QMag$. We have
+    \begin{equation} \label{equ:lattice_structure_and_Hiblert_series}
+        \HilbertSeries_{\Oca_1\InfQMag\Oca_2}(t)
+        +\HilbertSeries_{\Oca_1\SupQMag\Oca_2}(t)
+        =\HilbertSeries_{\Oca_1}(t)+\HilbertSeries_{\Oca_2}(t).
+    \end{equation}
+\end{Theorem}
+\begin{proof}
+  Let $I_1, I_2 \in \IMag$ be such that $\Oca_1 = \KMag/_{I_1}$ and
+    $\Oca_2 = \KMag/_{I_2}$. For every nonnegative integer $n$, we have
   \begin{equation}
@@
   \end{equation}
-\end{Lemma}
-\begin{proof}
-    Let $I_1, I_2 \in \IMag$ such that $\Oca_1 = \KMag/_{I_1}$ and
-    $\Oca_2 = \KMag/_{I_2}$. For every positive integer $n$, we have
+  Indeed,
     \begin{equation}\begin{split}
@@
     subspaces $I_1(n)$ and $I_2(n)$ of $\KMag(n)$.
-\end{proof}
-\medbreak
+    \smallbreak
 
-The Grassmann formula analog for $\LatQMag$ is given by the following
-statement.
-\medbreak
-
-\begin{Theorem}
-    \label{thm:Grassmann_formula_for_Hilbert_series_of_QMag}
-    Let $\Oca_1$ and $\Oca_2$ be two operads of $\QMag$. We have
-    \begin{equation} \label{equ:lattice_structure_and_Hiblert_series}
-        \HilbertSeries_{\Oca_1\InfQMag\Oca_2}(t)
-        +\HilbertSeries_{\Oca_1\SupQMag\Oca_2}(t)
-        =\HilbertSeries_{\Oca_1}(t)+\HilbertSeries_{\Oca_2}(t).
-    \end{equation}
-\end{Theorem}
-\begin{proof}
-    We have
-    \begin{equation}\begin{split}
-        \HilbertSeries_{\Oca_1\InfQMag\Oca_2}(t)
-        +\HilbertSeries_{\Oca_1\SupQMag\Oca_2}(t)&
-        =\sum_{n \geq 1}\dim{\left(\left(\Oca_1\InfQMag\Oca_2\right)(n)
-            \right)}t^n
-            +\sum_{n \geq 1}\dim{\left(\left(\Oca_1\SupQMag\Oca_2\right)
-            (n)\right)}t^n\\
-        &=\sum_{n \geq 1}\Big(\dim{\left(\Oca_1\InfQMag\Oca_2(n)\right)}
-            +\dim{\left(\left(\Oca_1\SupQMag\Oca_2\right)(n)
-        \right)}\Big)t^n\\
-        &=\sum_{n \geq 1}\Big(\dim{\left(\Oca_1(n)\right)}
-            +\dim{\left(\Oca_2(n)\right)}\Big)t^n\\
-        &=\sum_{n \geq 1}\dim{\left(\Oca_1(n)\right)}t^n+\sum_{n \geq 1}
-            \dim{\left(\Oca_2(n)\right)}t^n\\
-        &=\HilbertSeries_{\Oca_1}(t)+\HilbertSeries_{\Oca_2}(t),
-    \end{split}\end{equation}
-    where the third equality is due to
-    Lemma~\ref{lem:lattice_structure_and_coefficients_of_Hilbert_series}.
+    From
+    \eqref{equ:lattice_structure_and_coefficients_of_the_Hiblert_series},
+    and for every nonnegative integer $n$, the terms of degree $n$ in the
+    left and right members
+    of~\eqref{thm:Grassmann_formula_for_Hilbert_series_of_QMag} are
+    equal, which proves
+    Theorem~\ref{thm:Grassmann_formula_for_Hilbert_series_of_QMag}.
 \end{proof}

### 2018-09-10 Mag_quotients.tex
MAJ

@@
   Let $I_1, I_2 \in \IMag$ be such that $\Oca_1 = \KMag/_{I_1}$ and
-    $\Oca_2 = \KMag/_{I_2}$. For every nonnegative integer $n$, we have
+    $\Oca_2 = \KMag/_{I_2}$. For every positive integer $n$, we have
   \begin{equation}
@@
     \eqref{equ:lattice_structure_and_coefficients_of_the_Hiblert_series},
-    and for every nonnegative integer $n$, the terms of degree $n$ in the
+    and for every positive integer $n$, the terms of degree $n$ in the
     left and right members

### 2018-09-11 Mag_quotients.tex
MAJ

@@
 
-\Todo{S: ce thm est une "série génératriciation" du lemme précédent. Je
-serais d'avis de supprimer ce lemme et de montrer directement le thm.
-Avec l'espace gagné, je propose de donner pour cette partie un exemple:
-deux quotients --- linéaires --- de Mag dont on donne les séries
-de Hilbert (quitte à ne pas les démontrer, mais pour illustrer le thm).}
+We terminate this section with an example illustrating the previous
+constructions in the case where the characteristic of the
+field $\K$ is different from $2$. For that, we introduce various operads,
+which requires the following notations, also used in
+Section~\ref{sec:CAs_d}. Let, for any integer $\gamma \geq 1$, the binary
+trees $\LComb{\gamma}$ and $\RComb{\gamma}$ be respectively the left and
+the right combs of degree $\gamma$. These trees are depicted as
+\begin{equation}
+    \LComb{\gamma} = \enspace
+    \begin{tikzpicture}[xscale=.26,yscale=.3,Centering]
+        \node(0)at(0.00,-5.25){};
+        \node(2)at(2.00,-5.25){};
+        \node(4)at(4.00,-3.50){};
+        \node(6)at(6.00,-1.75){};
+        \node[NodeST](1)at(1.00,-3.50){\begin{math}\Product\end{math}};
+        \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
+        \node[NodeST](5)at(5.00,0.00){\begin{math}\Product\end{math}};
+        \draw[Edge](0)--(1);
+        \draw[Edge,dotted](1)edge[]node[font=\tiny]{
+            \begin{math}\gamma\! -\! 1\end{math}\hspace*{.6cm}}(3);
+        \draw[Edge](2)--(1);
+        \draw[Edge](3)--(5);
+        \draw[Edge](4)--(3);
+        \draw[Edge](6)--(5);
+        \node(r)at(5.00,1.5){};
+        \draw[Edge](r)--(5);
+    \end{tikzpicture}
+    \qquad \mbox{and} \qquad
+    \RComb{\gamma} =
+    \begin{tikzpicture}[xscale=.26,yscale=.3,Centering]
+        \node(0)at(0.00,-1.75){};
+        \node(2)at(2.00,-3.50){};
+        \node(4)at(4.00,-5.25){};
+        \node(6)at(6.00,-5.25){};
+        \node[NodeST](1)at(1.00,0.00){\begin{math}\Product\end{math}};
+        \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
+        \node[NodeST](5)at(5.00,-3.50){\begin{math}\Product\end{math}};
+        \draw[Edge](0)--(1);
+        \draw[Edge](2)--(3);
+        \draw[Edge](3)--(1);
+        \draw[Edge](4)--(5);
+        \draw[Edge,dotted](5)edge[]node[font=\tiny]{
+            \hspace*{.6cm}\begin{math}\gamma\! -\! 1\end{math}}(3);
+        \draw[Edge](6)--(5);
+        \node(r)at(1.00,1.5){};
+        \draw[Edge](r)--(1);
+    \end{tikzpicture}\,,
+\end{equation}
+where the values on the dotted edges denote the number of internal
+nodes they contain.
+
+We define the \Def{anti-associative operad} by
+\begin{equation}
+  \label{equ:anti-associative_operad}
+  \AAs:=\KMag/_{\IAAs}
+\end{equation}
+where $\IAAs$ is the ideal spanned by
+\begin{math}
+  \LComb{3}+\RComb{3}
+\end{math}.
+\Todo{Illustrer avec la représentation graphique ?}
+
+We define the \Def{2-nihilpotente operad} by
+\begin{equation}
+  \label{equ:2-nihilpotente_operad}
+  \NiHil:=\KMag/_{\INiHil}
+  \end{equation}
+where $\INiHil$ is the ideal spanned by the two trees $\LComb{3}$ and
+$\RComb{3}$.
+\Todo{Est-ce qu'il faut rajouter le 2 dans la macro désignant cette
+  opérade ? De plus, Samuele,\\
+  pourrais-tu rajouter la référence de Loday ?}
+We easily check that we have
+\begin{equation}
+  \label{equ:Hilbert_series_of_NiHil}
+  \HilbertSeries_{\NiHil}(t)=t+t^2.
+\end{equation}
+\Todo{Est-ce bien la bonne série ? Samuele, tu avais l'air de dire que
+  c'était plutôt $t+2t^2$}
+
+Finally, for every integer $\gamma\geq 2$, we define the
+\Def{$\gamma$-right comb operad} $\RC{\gamma}$ as follows. For every
+arity $n$, we let
+\begin{equation}
+  \RC{\gamma}(n):=
+    \begin{cases}
+        \As(n) &
+        \mbox{if } n \leq \gamma-1, \\
+        \RComb{n}
+            & \mbox{otherwise},
+    \end{cases}
+\end{equation}
+and the partial composition $\Tfr_1 \circ_i \Tfr_2$ is the partial
+composition of $\Tfr_1$ and $\Tfr_2$ in $\Mag$ if the integer
+\begin{math}
+  n:=|\Tfr_1|+|\Tfr_2| 
+\end{math}
+is strictly smaller than $\gamma$, and $\RComb{n}$, otherwise.
+\medbreak
+
+\begin{Lemma}
+  \label{lem:presentation_of_RC}
+  We have
+  \begin{equation}
+  \label{equ:presentation_of_RC}
+  \NiHil:=\KMag/_{\IRCC{\gamma}}
+  \end{equation}
+  where $\IRC{\gamma}$ is the ideal spanned by the elements
+  $\Tfr-\RComb{\gamma}$, where $\Tfr$ runs over all the trees of arity
+  $\gamma$.
+\end{Lemma}
+
+\begin{proof}
+  \Todo{todo}
+\end{proof}
+
+\medbreak
+The lower-bound and the upper-bound of $\As$ and $\AAs$ are given by the
+following.
+\begin{Theorem}
+  \label{thm:example_lattice}
+  We have
+  \begin{equation}
+    \label{equ:example_lower-bound}
+    \As\InfQMag\AAs=\NiHil
+  \end{equation}
+  and
+  \begin{equation}
+    \label{equ:example_upper-bound}
+    \As\SupQMag\AAs=\RC{3}.
+    \end{equation}
+  \end{Theorem}
+
+\begin{proof}
+  First, we show~\eqref{equ:example_lower-bound}. By definition of the
+  lower-bound $\InfQMag$, the ideal of relations of $\As\InfQMag\AAs$
+  is spanned by the two elements $\LComb{3}-\RComb{3}$ and
+  $\LComb{3}+\RComb{3}$. By linear transformations applied to these
+  generators, the ideal of relations of $\As\InfQMag\AAs$ is spanned by
+  $\LComb{3}$ and $\RComb{3}$, that is it is equal to $\INiHil$, which
+  proves~\eqref{equ:example_lower-bound}.
+
+\smallbreak
+Now, we show~\eqref{equ:example_upper-bound}. We denote by
+\begin{math}
+  \pi:\KMag\to\RC{3}
+\end{math}
+the natural projection. Let $\Tfr$ be a tree of arity $3$. Then,
+$\Tfr-\RComb{\gamma}$ belongs to the ideals $\IAs$ and $\IAAs$ of
+relations of $\As$ and $\AAs$, respectively. Indeed, every
+tree of arity $3$ to the same element $\RComb{\gamma}$. Hence, by
+definition of the upper-bound $\SupQMag$, $\pi$ induces a surjective
+operad morphism
+\begin{math}
+  \overline{\pi}:\As\SupQMag\AAs\to\RC{3}
+\end{math}.
+We conclude using a dimension argument: by definition, the Hilbert series
+of $\RC{3}$ is equal to
+\begin{equation}
+  \label{equ:Hilbert_series_of_RC3}
+  t+t^2+2t^3+\sum_{n\geq 4}t^n
+\end{equation}
+and from the Grassmann formula analog given in
+Theorem~\ref{thm:Grassmann_formula_for_Hilbert_series_of_QMag}, we check
+that the Hilbert series of $\As\SupQMag\AAs$ is also equal
+to~\eqref{equ:Hilbert_series_of_RC3}. Hence, $\overline{\pi}$ is an
+isomorphism, which proves~\eqref{equ:example_upper-bound}.
+  \end{proof}
+\medbreak

### 2018-09-11 Mag_quotients.tex
MAJ

@@
 \begin{equation}
+  \label{equ:compositions_of_RC}
   \RC{\gamma}(n):=
@@
         \As(n) &
-        \mbox{if } n \leq \gamma-1, \\
+        \mbox{if } n \leq \gamma, \\
         \RComb{n}
@@
   \label{lem:presentation_of_RC}
-  We have
+  We have an isomorphism
   \begin{equation}
   \label{equ:presentation_of_RC}
-  \NiHil:=\KMag/_{\IRCC{\gamma}}
+  \RC{\gamma}\simeq\KMag/_{\IRCC{\gamma}}
   \end{equation}
-  where $\IRC{\gamma}$ is the ideal spanned by the elements
-  $\Tfr-\RComb{\gamma}$, where $\Tfr$ runs over all the trees of arity
-  $\gamma$.
+  where $\IRCC{\gamma}$ is the ideal spanned by the elements
+  $\Tfr-\RComb{\gamma}$, where $\Tfr$ runs over all the binary trees of
+  arity $\gamma+1$. In other words, $\RC{\gamma}$ is a combinatorial
+  realization of
+  \begin{math}
+    \KMag/_{\IRCC{\gamma}}.
+    \end{math}
 \end{Lemma}
@@
 \begin{proof}
-  \Todo{todo}
+  Let $R^{(\gamma)}$ be the set of rewrite rules
+  $\Tfr\Rew\RComb{\gamma}$, where $\Tfr$ runs over all the binary trees
+  of arity $\gamma+1$ different from $\RComb{\gamma}$. The unique normal
+  form of arity $n\geq\gamma+1$ for  $R^{(\gamma)}$ is equal to
+  $\RComb{n}$, so that $R^{(\gamma)}$ is a convergent presentation of
+  \begin{math}
+    \KMag/_{\IRC{\gamma}}.
+  \end{math}
+  Moreover, the normal forms of arity $n\leq\gamma$ are all the trees of
+  arity $n$ and, by using the convergent presentation
+  $R^{(\gamma)}$, we see that the compositions of
+  \begin{math}
+    \KMag/_{\IRC{\gamma}}
+  \end{math}
+  satisfy~\eqref{equ:compositions_of_RC}. Hence, $R^{(\gamma)}$ is also a
+  convergent presentation of
+  \begin{math}
+    \RC{\gamma}
+  \end{math}
+  which proves Lemma~\ref{lem:presentation_of_RC}.
 \end{proof}

### 2018-09-11 Mag_quotients.tex
MAJ

@@
 
-We terminate this section with an example illustrating the previous
-constructions in the case where the characteristic of the
-field $\K$ is different from $2$. For that, we introduce various operads,
-which requires the following notations, also used in
-Section~\ref{sec:CAs_d}. Let, for any integer $\gamma \geq 1$, the binary
-trees $\LComb{\gamma}$ and $\RComb{\gamma}$ be respectively the left and
-the right combs of degree $\gamma$. These trees are depicted as
+We terminate this section with an example illustrating the lattice
+constructions on $\QMag$ in the case where the
+characteristic of the field $\K$ is different from $2$. For that, we
+introduce various operads, which requires the following notations, also
+used in Section~\ref{sec:CAs_d}. Let, for any integer $\gamma \geq 1$,
+the binary trees $\LComb{\gamma}$ and $\RComb{\gamma}$ be respectively
+the left and the right combs of degree $\gamma$. These trees are depicted
+as
 \begin{equation}
@@
 \Todo{Illustrer avec la représentation graphique ?}
+\medbreak
+
+\begin{Lemma}
+\label{lem:properties_of_AAs}
+\end{Lemma}
+
+\begin{proof}
+\Todo{todo}
+\end{proof}
+\medbreak
 
@@
     \begin{cases}
-        \As(n) &
+        \KMag(n) &
         \mbox{if } n \leq \gamma, \\
-        \RComb{n}
+        \K\Angle{\RComb{n}}
             & \mbox{otherwise},
@@
 \end{math}
-is strictly smaller than $\gamma$, and $\RComb{n}$, otherwise.
+is smaller than or equal to $\gamma$, and $\RComb{n}$, otherwise.
 \medbreak
@@
 \medbreak
-The lower-bound and the upper-bound of $\As$ and $\AAs$ are given by the
-following.
+The lower-bound and the upper-bound of $\As$ and $\AAs$ in the lattice
+$\LatQMag$ are given by the following.
 \begin{Theorem}
@@
     \label{equ:example_lower-bound}
-    \As\InfQMag\AAs=\NiHil
+    \KAs\InfQMag\AAs=\NiHil
   \end{equation}
@@
     \label{equ:example_upper-bound}
-    \As\SupQMag\AAs=\RC{3}.
+    \KAs\SupQMag\AAs=\RC{3}.
     \end{equation}
@@
   First, we show~\eqref{equ:example_lower-bound}. By definition of the
-  lower-bound $\InfQMag$, the ideal of relations of $\As\InfQMag\AAs$
-  is spanned by the two elements $\LComb{3}-\RComb{3}$ and
-  $\LComb{3}+\RComb{3}$. By linear transformations applied to these
-  generators, the ideal of relations of $\As\InfQMag\AAs$ is spanned by
-  $\LComb{3}$ and $\RComb{3}$, that is it is equal to $\INiHil$, which
+  lower-bound $\InfQMag$, the ideal of relations of
+  $\KAs\InfQMag\AAs$ is spanned by the two elements
+  $\LComb{3}-\RComb{3}$ and $\LComb{3}+\RComb{3}$. By linear
+  transformations applied to these generators, the ideal of relations of
+  $\KAs\InfQMag\AAs$ is spanned by $\LComb{3}$ and $\RComb{3}$,
+  that is it is equal to $\INiHil$, which
   proves~\eqref{equ:example_lower-bound}.
@@
 \end{math}
-the natural projection. Let $\Tfr$ be a tree of arity $3$. Then,
-$\Tfr-\RComb{\gamma}$ belongs to the ideals $\IAs$ and $\IAAs$ of
-relations of $\As$ and $\AAs$, respectively. Indeed, every
-tree of arity $3$ to the same element $\RComb{\gamma}$. Hence, by
-definition of the upper-bound $\SupQMag$, $\pi$ induces a surjective
-operad morphism
+the natural projection. Let $\Tfr$ be a tree of arity $3$. From
+Lemma~\ref{lem:presentation_of_RC}, the kernel of $\pi$ is spanned by
+the elements $\alpha_{\Tfr}:=\Tfr-\RComb{3}$, where $\Tfr$ is a binary
+tree of arity $4$. The elements $\alpha_{\Tfr}$ belong to the ideal
+$\IAs$ of relations of $\KAs$ and to the ideal $\IAAs$ since both
+$[\Tfr]_{\IAAs}$ and $[\RComb{3}]_{\IAAs}$ are equal to $[0]_{\IAAs}$
+from Lemma~\ref{lem:properties_of_AAs}. Hence, the kernel of $\pi$ is
+included in $\IAs\cap\IAAs$, so that, by definition of the upper-bound
+$\SupQMag$, $\pi$ induces a surjective operad morphism
 \begin{math}

### 2018-09-11 Mag_quotients.tex
MAJ

@@
 \begin{math}
-  \LComb{3}+\RComb{3}
+  \LComb{2}+\RComb{2}
 \end{math}.
 \Todo{Illustrer avec la représentation graphique ?}
-\medbreak
-
-\begin{Lemma}
-\label{lem:properties_of_AAs}
-\end{Lemma}
-
-\begin{proof}
-\Todo{todo}
-\end{proof}
+Using the Buchberger algorithm for operads~\cite[Section 3.7]{DK10}, we
+check that the set of rewrite rules
+\begin{equation}
+  \label{equ:convergent_presentation_of_AAS}
+  \left\{\LComb{2}\Rew -\RComb{2},\
+  \RComb{3}\Rew 0
+  \right\}
+\end{equation}
+is a convergent presentation of $\AAs$. We point out that this statement
+is false if the characteristic of $\K$ is equal to $2$. Moreover, using
+the convergent presentation~\eqref{equ:convergent_presentation_of_AAS},
+we have
+  \begin{equation}
+    \label{equ:Hilbert_series_of_AAS}
+    \HilbertSeries_{\AAs}(t)=t+t^2+t³.
+    \end{equation}
 \medbreak
@@
 is smaller than or equal to $\gamma$, and $\RComb{n}$, otherwise.
+Moreover, by definition of the $\gamma$-right comb operad, we have
+\begin{equation}
+  \label{equ:Hilbert_series_of_RC}
+  \HilbertSeries_{\RC{\gamma}}(t)=\sum_{1\leq n\leq\gamma}\Catalan(n) t^n
+  +\sum_{n\geq\gamma+1}t^n.
+  \end{equation}
 \medbreak

### 2018-09-11 Mag_quotients.tex
MAJ

@@
   pourrais-tu rajouter la référence de Loday ?}
-We easily check that we have
+We have
 \begin{equation}
@@
 \Todo{Est-ce bien la bonne série ? Samuele, tu avais l'air de dire que
-  c'était plutôt $t+2t^2$}
+  c'était plutôt $t+2t^2$. Ou peut-être que NiHil est la $1$-
+  nihilipotente opérade ?}
 
@@
   arity $n$ and, by using the convergent presentation
-  $R^{(\gamma)}$, we see that the compositions of
+  $R^{(\gamma)}$, the compositions of
   \begin{math}
@@
   \begin{math}
-  \pi:\KMag\to\RC{3}
+    \pi:\KMag\to\KAs\SupQMag\AAs
   \end{math}
-the natural projection. Let $\Tfr$ be a tree of arity $3$. From
+  the natural projection. Let $\Tfr$ be a tree of arity $4$. From
   Lemma~\ref{lem:presentation_of_RC}, the kernel of $\pi$ is spanned by
@@
   $\IAs$ of relations of $\KAs$ and to the ideal $\IAAs$ since both
-$[\Tfr]_{\IAAs}$ and $[\RComb{3}]_{\IAAs}$ are equal to $[0]_{\IAAs}$
-from Lemma~\ref{lem:properties_of_AAs}. Hence, the kernel of $\pi$ is
-included in $\IAs\cap\IAAs$, so that, by definition of the upper-bound
-$\SupQMag$, $\pi$ induces a surjective operad morphism
+  $[\Tfr]_{\IAAs}$ and $[\RComb{3}]_{\IAAs}$ are equal to $[0]_{\IAAs}$.
+  The last statement is shown using the convergent
+  presentation~\eqref{equ:convergent_presentation_of_AAS}. Hence, the kernel
+  of $\pi$ is included in $\IAs\cap\IAAs$, so that, by definition of the
+  upper-bound $\SupQMag$, $\pi$ induces a surjective operad morphism
   \begin{math}

### 2018-09-11 CAs_operads.tex
MAJ

@@
 
-Let, for any integer $\gamma \geq 1$, the binary trees $\LComb{\gamma}$
-and $\RComb{\gamma}$ be respectively the left and the right combs of
-degree $\gamma$. These trees are depicted as
-\begin{equation}
-    \LComb{\gamma} = \enspace
-    \begin{tikzpicture}[xscale=.26,yscale=.3,Centering]
-        \node(0)at(0.00,-5.25){};
-        \node(2)at(2.00,-5.25){};
-        \node(4)at(4.00,-3.50){};
-        \node(6)at(6.00,-1.75){};
-        \node[NodeST](1)at(1.00,-3.50){\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
-        \node[NodeST](5)at(5.00,0.00){\begin{math}\Product\end{math}};
-        \draw[Edge](0)--(1);
-        \draw[Edge,dotted](1)edge[]node[font=\tiny]{
-            \begin{math}\gamma\! -\! 1\end{math}\hspace*{.6cm}}(3);
-        \draw[Edge](2)--(1);
-        \draw[Edge](3)--(5);
-        \draw[Edge](4)--(3);
-        \draw[Edge](6)--(5);
-        \node(r)at(5.00,1.5){};
-        \draw[Edge](r)--(5);
-    \end{tikzpicture}
-    \qquad \mbox{and} \qquad
-    \RComb{\gamma} =
-    \begin{tikzpicture}[xscale=.26,yscale=.3,Centering]
-        \node(0)at(0.00,-1.75){};
-        \node(2)at(2.00,-3.50){};
-        \node(4)at(4.00,-5.25){};
-        \node(6)at(6.00,-5.25){};
-        \node[NodeST](1)at(1.00,0.00){\begin{math}\Product\end{math}};
-        \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
-        \node[NodeST](5)at(5.00,-3.50){\begin{math}\Product\end{math}};
-        \draw[Edge](0)--(1);
-        \draw[Edge](2)--(3);
-        \draw[Edge](3)--(1);
-        \draw[Edge](4)--(5);
-        \draw[Edge,dotted](5)edge[]node[font=\tiny]{
-            \hspace*{.6cm}\begin{math}\gamma\! -\! 1\end{math}}(3);
-        \draw[Edge](6)--(5);
-        \node(r)at(1.00,1.5){};
-        \draw[Edge](r)--(1);
-    \end{tikzpicture}\,,
-\end{equation}
-where the values on the dotted edges denote the number of internal
-nodes they contain. We shall employ this drawing convention in the
-sequel, combined with the convention stipulating that dotted edges
+As in Section~\ref{sec:Magmatic_operads}, the left and the right combs of
+degree $\gamma$ are denoted by $\LComb{\gamma}$ and $\RComb{\gamma}$,
+respectively. In the sequel , we shall employ the drawing convention
+introduced after~\eqref{equ:left_and_right_combs}: the values on dotted
+edges in a binary tree denote the number of internal nodes they contain.
+Moreover, we also employ the convention stipulating that dotted edges
 with no value have any number of internal nodes. Let us now define for

### 2018-09-11 Mag_quotients.tex
MAJ

@@
 \begin{equation}
+  \label{equ:left_and_right_combs}
     \LComb{\gamma} = \enspace
@@
 
+We first recall that the \Def{linear associative operad} is
+\begin{equation}
+  \label{equ:linear_associative_operad}
+  \KAs:=\KMag/_{\IAs}
+\end{equation}
+where $\IAs$ is the ideal spanned
+\begin{math}
+  \LComb{2}-\RComb{2},
+\end{math}
+and that its Hilbert series is
+\Todo{référence ?}
+\begin{equation}
+    \label{equ:Hilbert_series_of_As}
+    \HilbertSeries_{\KAs}(t)=\sum_{n\geq 1}t^n,
+    \end{equation}
+
 We define the \Def{anti-associative operad} by
@@
 \end{math}.
-\Todo{Illustrer avec la représentation graphique ?}
 Using the Buchberger algorithm for operads~\cite[Section 3.7]{DK10}, we
@@
   \begin{equation}
-    \label{equ:Hilbert_series_of_AAS}
+    \label{equ:Hilbert_series_of_AAs}
     \HilbertSeries_{\AAs}(t)=t+t^2+t³.
@@
   \end{equation}
-where $\INiHil$ is the ideal spanned by the two trees $\LComb{3}$ and
-$\RComb{3}$.
+where $\INiHil$ is the ideal spanned by the two trees $\LComb{2}$ and
+$\RComb{2}$.
 \Todo{Est-ce qu'il faut rajouter le 2 dans la macro désignant cette
@@
   \label{equ:presentation_of_RC}
-  \RC{\gamma}\simeq\KMag/_{\IRCC{\gamma}}
+  \RC{\gamma}\simeq\KMag/_{\IRC{\gamma}}
   \end{equation}
-  where $\IRCC{\gamma}$ is the ideal spanned by the elements
+  where $\IRC{\gamma}$ is the ideal spanned by the elements
   $\Tfr-\RComb{\gamma}$, where $\Tfr$ runs over all the binary trees of
@@
   \begin{math}
-    \KMag/_{\IRCC{\gamma}}.
+    \KMag/_{\IRC{\gamma}}.
     \end{math}
@@
   \end{math}
-  Moreover, the normal forms of arity $n\leq\gamma$ are all the trees of
-  arity $n$ and, by using the convergent presentation
+  Moreover, the normal forms of arity $n\leq\gamma$ are all the trees
+  of arity $n$ and, by using the convergent presentation
   $R^{(\gamma)}$, the compositions of
@@
 \begin{proof}
-  First, we show~\eqref{equ:example_lower-bound}. By definition of the
-  lower-bound $\InfQMag$, the ideal of relations of
-  $\KAs\InfQMag\AAs$ is spanned by the two elements
-  $\LComb{3}-\RComb{3}$ and $\LComb{3}+\RComb{3}$. By linear
-  transformations applied to these generators, the ideal of relations of
-  $\KAs\InfQMag\AAs$ is spanned by $\LComb{3}$ and $\RComb{3}$,
-  that is it is equal to $\INiHil$, which
-  proves~\eqref{equ:example_lower-bound}.
+  First, we show~\eqref{equ:example_lower-bound}. The ideal of relations
+  of $\KAs\InfQMag\AAs$ is equal to $\IAs+\IAAs$, so that it is spanned
+  by the two elements $\LComb{2}-\RComb{2}$ and $\LComb{2}+\RComb{2}$. By
+  linear transformations applied to these generators, $\IAs+\IAAs$ is
+  spanned by $\LComb{2}$ and $\RComb{2}$, that is it is equal to
+  $\INiHil$, which proves~\eqref{equ:example_lower-bound}.
 
@@
   \end{math}
-  the natural projection. Let $\Tfr$ be a tree of arity $4$. From
-  Lemma~\ref{lem:presentation_of_RC}, the kernel of $\pi$ is spanned by
-  the elements $\alpha_{\Tfr}:=\Tfr-\RComb{3}$, where $\Tfr$ is a binary
-  tree of arity $4$. The elements $\alpha_{\Tfr}$ belong to the ideal
-  $\IAs$ of relations of $\KAs$ and to the ideal $\IAAs$ since both
-  $[\Tfr]_{\IAAs}$ and $[\RComb{3}]_{\IAAs}$ are equal to $[0]_{\IAAs}$.
-  The last statement is shown using the convergent
-  presentation~\eqref{equ:convergent_presentation_of_AAS}. Hence, the kernel
-  of $\pi$ is included in $\IAs\cap\IAAs$, so that, by definition of the
-  upper-bound $\SupQMag$, $\pi$ induces a surjective operad morphism
+  the natural projection. Let $\Tfr$ be a tree of arity $4$ and let
+  us define $\alpha_{\Tfr}:=\Tfr-\RComb{3}$. The elements $\alpha_{\Tfr}$
+  belong to $\IAs$ and to $\IAAs$ since both $[\Tfr]_{\IAAs}$ and to
+  $[\RComb{3}]_{\IAAs}$ are equal to $[0]_{\IAAs}$. The last statement is
+  shown using the convergent
+  presentation~\eqref{equ:convergent_presentation_of_AAS}. Hence, the
+  ideal generated by the elements $\alpha_{\Tfr}$ is included in 
+  $\IAs\cap\IAAs=\ker(\pi)$, so that $\pi$ induces a surjective morphism
   \begin{math}
-    \overline{\pi}:\As\SupQMag\AAs\to\RC{3}
-  \end{math}.
-  We conclude using a dimension argument: by definition, the Hilbert series
-  of $\RC{3}$ is equal to
-  \begin{equation}
-    \label{equ:Hilbert_series_of_RC3}
-    t+t^2+2t^3+\sum_{n\geq 4}t^n
-  \end{equation}
-  and from the Grassmann formula analog given in
-  Theorem~\ref{thm:Grassmann_formula_for_Hilbert_series_of_QMag}, we check
-  that the Hilbert series of $\As\SupQMag\AAs$ is also equal
-  to~\eqref{equ:Hilbert_series_of_RC3}. Hence, $\overline{\pi}$ is an
+    \overline{\pi}:\RC{3}\to\KAs\SupQMag\AAs
+  \end{math}
+  from Lemma~\ref{lem:presentation_of_RC}. We conclude using Hilbert
+  series: $\HilbertSeries_{\KAs\SupQMag\AAs}(t)$ is computed
+  using the Grassmann formula analog with
+  Formulas~\eqref{equ:Hilbert_series_of_As},
+  \eqref{equ:Hilbert_series_of_AAs} and
+  ~\eqref{equ:Hilbert_series_of_NiHil} and it turns out to be equal to
+  $\HilbertSeries_{\RC{3}}(t)$ which is given
+  in~\eqref{equ:Hilbert_series_of_RC}. Hence, $\overline{\pi}$ is an
   isomorphism, which proves~\eqref{equ:example_upper-bound}.

### 2018-09-11 CAs_operads.tex
Corrections 3.3.2 et 4

@@
 \end{table}
-\Todo{S: erreur dans la table pour $\gamma = 1$ ? Il doit y avoir que
-des $0$, j'ai corrigé. Vérifier.}
-\Todo{S: il faut équilibrer la table. Toutes les suites doivent avoir
+\Todo{S : il faut équilibrer la table. Toutes les suites doivent avoir
 la même longueur. (ou alors, il est toléré d'avoir des suites plus
@@
 $\CAs{6}$ until arity $12$. We conjecture that there is no finite
-convergent presentation of $\CAs{\gamma}$ with one generator when
-$\gamma \geq 4$. We discuss the cases with more than one generator in
-the perspectives.
-\medbreak
+convergent presentation of $\CAs{\gamma}$ when $\gamma \geq 4$ and when
+ the left and the right members of the rewriting rules are trees
+ belonging to $\Mag$.
+\medbreak

### 2018-09-11 CAs_operads.tex
TODOS 3.3.2

@@
 \label{sec:higher_comb_associative_operads}
-Let us provide here some experimental data. First,
-Table~\ref{tab:dimensions_CAs} shows the first dimensions of the
-operads $\CAs{\gamma}$ for $\gamma \in [9]$.
-\begin{table}[ht]
-    \centering
-    \footnotesize
-    \setlength{\tabcolsep}{.35em}
-    \begin{tabular}{c||ccccccccccccccccc}
-        $\gamma$ & \multicolumn{17}{c}{Dimensions of $\CAs{\gamma}$}
-        \\ \hline \hline
-        1 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 429 & 1430 & 4862
-        & 16796 & 58786 & 208012 & 742900 & 2674440 & 9694845
-        & 35357670
-        \\
-        2 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1
-        & 1 & 1
-        \\
-        3 & 1 & 1 & 2 & 4 & 8 & 14 & 20 & 19 & 16 & 14 &
-        14 & 15 & 16 & 17 & 18 & 19 & 20
-        \\
-        4 & 1 & 1 & 2 & 5 & 13 & 35 & 96 & 264 & 724 & 1973 & 5335
-        & 14390 & 38872 & 105141 & 284929 & 774254 & 2111088
-        %& 5778420 & 15882100 & 43837388 & 121507230
-        \\
-        5 & 1 & 1 & 2 & 5 & 14 & 41 & 124 & 384 & 1210 & 3861 & 12440
-        & 40392 & 131997 & 433782 & 1432696 & 4752857
-        & 15829261
-        %& 52905635 & 177395246
-        \\
-        6 & 1 & 1 & 2 & 5 & 14 & 42 & 131 & 420 & 1375 & 4576 & 15431
-        & 52598 & 180895 & 626862 & 2186504 & 7670138
-        & 27041833
-        %& 95764569
-        \\
-        7 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 428 & 1420 & 4796 & 16432
-        & 56966 & 199444 & 704140 & 2503914 & 8959699
-        & 32236657
-        %& 116551168
-        \\
-        8 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 429 & 1429 & 4851 & 16718
-        & 58331 & 205632 & 731272 & 2620176 & 9449688 & 34276116
-        %& 124958386
-        \\
-        9 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 429 & 1430 & 4861 & 16784
-        & 58695 & 207452 & 739840 & 2658936 & 9620232 & 35011566
-        %& 128082515
-    \end{tabular}
-    \medbreak
-
-    \caption{\footnotesize
-    The sequences of the cardinalities, arity by arity, of the
-    dimensions of~$\CAs{\gamma}$.}
-    \label{tab:dimensions_CAs}
-\end{table}
-\medbreak
-
-Moreover, we run the same completion algorithm for $\CAs{\gamma}$ as
-the one considered in Section~\ref{subsubsec:CAs_3}, now for
-$\gamma \in [9]$. Table~\ref{tab:cardinalities_completion_CAs} shows
+
+We run the same algorithm for $\CAs{\gamma}$ when $\gamma \in [9]$.
+Table~\ref{tab:cardinalities_completion_CAs} shows
 the number of rewrite rules needed to obtain complete orientations.
+\medbreak
+
 \begin{table}[ht]
@@
     \end{tabular}
-    \medbreak
-
     \caption{\footnotesize
@@
 \end{table}
-\Todo{S : il faut équilibrer la table. Toutes les suites doivent avoir
-la même longueur. (ou alors, il est toléré d'avoir des suites plus
-courtes à mesure que $\gamma$ augmente... mais non ici.)}
+
 From these computer explorations, we conjecture that the algorithm we
@@
 rules still appear in arity $42$. Moreover, the total number of rewrite
-rules at this arity is~$3149$.
+rules at this arity is~$3149$. Our program was too slow to 
+compute further the completions of $\CAs{5}$, $\CAs{6}$, $\CAs{7}$, and
+$\CAs{8}$.
 \medbreak
@@
 \medbreak
+
+Thanks to the partial completions presented in table
+\ref{tab:cardinalities_completion_CAs}, we can compute the following 
+first dimensions of $\CAs{\gamma}$. Table~\ref{tab:dimensions_CAs}
+ shows the first dimensions of the
+operads $\CAs{\gamma}$ for $\gamma \in [9]$.
+\begin{table}[ht]
+    \centering
+    \footnotesize
+    \setlength{\tabcolsep}{.35em}
+    \begin{tabular}{c||ccccccccccccccccc}
+        $\gamma$ & \multicolumn{17}{c}{Dimensions of $\CAs{\gamma}$}
+        \\ \hline \hline
+        1 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 429 & 1430 & 4862
+        & 16796 & 58786 & 208012 & 742900 & 2674440 & 9694845
+        & 35357670
+        \\
+        2 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1
+        & 1 & 1
+        \\
+        3 & 1 & 1 & 2 & 4 & 8 & 14 & 20 & 19 & 16 & 14 &
+        14 & 15 & 16 & 17 & 18 & 19 & 20
+        \\
+        4 & 1 & 1 & 2 & 5 & 13 & 35 & 96 & 264 & 724 & 1973 & 5335
+        & 14390 & 38872 & 105141 & 284929 & 774254 & 2111088
+        %& 5778420 & 15882100 & 43837388 & 121507230
+        \\
+        5 & 1 & 1 & 2 & 5 & 14 & 41 & 124 & 384 & 1210 & 3861 & 12440
+        & 40392 & 131997 & 433782 & 1432696 & 4752857
+        & 15829261
+        %& 52905635 & 177395246
+        \\
+        6 & 1 & 1 & 2 & 5 & 14 & 42 & 131 & 420 & 1375 & 4576 & 15431
+        & 52598 & 180895 & 626862 & 2186504 & 7670138
+        & 27041833
+        %& 95764569
+        \\
+        7 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 428 & 1420 & 4796 & 16432
+        & 56966 & 199444 & 704140 & 2503914 & 8959699
+        & 32236657
+        %& 116551168
+        \\
+        8 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 429 & 1429 & 4851 & 16718
+        & 58331 & 205632 & 731272 & 2620176 & 9449688 & 34276116
+        %& 124958386
+        \\
+        9 & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 429 & 1430 & 4861 & 16784
+        & 58695 & 207452 & 739840 & 2658936 & 9620232 & 35011566
+        %& 128082515
+    \end{tabular}
+    \medbreak
+
+    \caption{\footnotesize
+    The sequences of the cardinalities, arity by arity, of the
+    dimensions of~$\CAs{\gamma}$.}
+    \label{tab:dimensions_CAs}
+\end{table}
+\medbreak

### 2018-09-12 Mag_quotients.tex
Relecture exemples Grassmann

@@
 We terminate this section with an example illustrating the lattice
-constructions on $\QMag$ in the case where the
-characteristic of the field $\K$ is different from $2$. For that, we
-introduce various operads, which requires the following notations, also
-used in Section~\ref{sec:CAs_d}. Let, for any integer $\gamma \geq 1$,
-the binary trees $\LComb{\gamma}$ and $\RComb{\gamma}$ be respectively
-the left and the right combs of degree $\gamma$. These trees are depicted
-as
+constructions on $\QMag$ in the case where the characteristic of the
+field $\K$ is different from $2$. For that, we introduce various
+operads, which requires the following notations, also used in
+Section~\ref{sec:CAs_d}. Let, for any integer $\gamma \geq 1$, the
+binary trees $\LComb{\gamma}$ and $\RComb{\gamma}$ be respectively the
+left and the right combs of degree $\gamma$. These trees are depicted as
 \begin{equation}
@@
 \end{equation}
-where the values on the dotted edges denote the number of internal
-nodes they contain.
+where the values on the dotted edges denote the number of internal nodes
+they contain.
+\medbreak
 
 We first recall that the \Def{linear associative operad} is
-\begin{equation}
-  \label{equ:linear_associative_operad}
+\begin{equation} \label{equ:linear_associative_operad}
     \KAs:=\KMag/_{\IAs}
@@
 and that its Hilbert series is
-\Todo{référence ?}
-\begin{equation}
-    \label{equ:Hilbert_series_of_As}
+\begin{equation} \label{equ:Hilbert_series_of_As}
     \HilbertSeries_{\KAs}(t)=\sum_{n\geq 1}t^n,
 \end{equation}
-
 We define the \Def{anti-associative operad} by
@@
     \label{equ:convergent_presentation_of_AAS}
-  \left\{\LComb{2}\Rew -\RComb{2},\
-  \RComb{3}\Rew 0
-  \right\}
+    \left\{\LComb{2}\Rew -\RComb{2}, \; \RComb{3}\Rew 0 \right\}
 \end{equation}
@@
 we have
-  \begin{equation}
-    \label{equ:Hilbert_series_of_AAs}
-    \HilbertSeries_{\AAs}(t)=t+t^2+t³.
+\begin{equation} \label{equ:Hilbert_series_of_AAs}
+    \HilbertSeries_{\AAs}(t)=t+t^2+t^3.
 \end{equation}
-\medbreak
-
-We define the \Def{2-nihilpotente operad} by
-\begin{equation}
-  \label{equ:2-nihilpotente_operad}
-  \NiHil:=\KMag/_{\INiHil}
+Let us consider the \Def{2-nilpotent operad}~\cite{Zin12} defined by
+\begin{equation} \label{equ:2-nilpotent_operad}
+    \TwoNil:=\KMag/_{\INiHil}
 \end{equation}
 where $\INiHil$ is the ideal spanned by the two trees $\LComb{2}$ and
-$\RComb{2}$.
-\Todo{Est-ce qu'il faut rajouter le 2 dans la macro désignant cette
-  opérade ? De plus, Samuele,\\
-  pourrais-tu rajouter la référence de Loday ?}
-We have
-\begin{equation}
-  \label{equ:Hilbert_series_of_NiHil}
-  \HilbertSeries_{\NiHil}(t)=t+t^2.
+$\RComb{2}$. We have
+\begin{equation} \label{equ:Hilbert_series_of_NiHil}
+    \HilbertSeries_{\TwoNil}(t)=t+t^2.
 \end{equation}
-\Todo{Est-ce bien la bonne série ? Samuele, tu avais l'air de dire que
-  c'était plutôt $t+2t^2$. Ou peut-être que NiHil est la $1$-
-  nihilipotente opérade ?}
-
 Finally, for every integer $\gamma\geq 2$, we define the
@@
 arity $n$, we let
-\begin{equation}
-  \label{equ:compositions_of_RC}
+\begin{equation} \label{equ:compositions_of_RC}
     \RC{\gamma}(n):=
@@
         \mbox{if } n \leq \gamma, \\
-        \K\Angle{\RComb{n}}
-            & \mbox{otherwise},
+        \K\Angle{\RComb{n}} & \mbox{otherwise},
     \end{cases}
 \end{equation}
+\Todo{S: plutôt $\K\Angle{\RComb{n - 1}}$ pour avoir les bonnes arités,
+non ?}
 and the partial composition $\Tfr_1 \circ_i \Tfr_2$ is the partial
@@
 \end{math}
-is smaller than or equal to $\gamma$, and $\RComb{n}$, otherwise.
+\Todo{S : je crois qu'il manque un "$-1$ ici, non ?}
+is smaller than or equal to $\gamma$, is and $\RComb{n}$, otherwise.
 Moreover, by definition of the $\gamma$-right comb operad, we have
-\begin{equation}
-  \label{equ:Hilbert_series_of_RC}
-  \HilbertSeries_{\RC{\gamma}}(t)=\sum_{1\leq n\leq\gamma}\Catalan(n) t^n
-  +\sum_{n\geq\gamma+1}t^n.
+\begin{equation} \label{equ:Hilbert_series_of_RC}
+    \HilbertSeries_{\RC{\gamma}}(t)=
+    \sum_{1\leq n\leq\gamma}\Catalan(n) t^n +\sum_{n\geq\gamma+1}t^n.
 \end{equation}
@@
 
-\begin{Lemma}
-  \label{lem:presentation_of_RC}
+\begin{Lemma} \label{lem:presentation_of_RC}
     We have an isomorphism
-  \begin{equation}
-  \label{equ:presentation_of_RC}
+    \begin{equation} \label{equ:presentation_of_RC}
         \RC{\gamma}\simeq\KMag/_{\IRC{\gamma}}
@@
     where $\IRC{\gamma}$ is the ideal spanned by the elements
-  $\Tfr-\RComb{\gamma}$, where $\Tfr$ runs over all the binary trees of
-  arity $\gamma+1$. In other words, $\RC{\gamma}$ is a combinatorial
-  realization of
+    $\Tfr-\RComb{\gamma}$, where $\Tfr$ runs over all the binary trees
+    of arity $\gamma+1$. In other words, $\RC{\gamma}$ is a
+    combinatorial realization of
     \begin{math}
@@
 \end{Lemma}
-
 \begin{proof}
-  Let $R^{(\gamma)}$ be the set of rewrite rules
-  $\Tfr\Rew\RComb{\gamma}$, where $\Tfr$ runs over all the binary trees
-  of arity $\gamma+1$ different from $\RComb{\gamma}$. The unique normal
-  form of arity $n\geq\gamma+1$ for  $R^{(\gamma)}$ is equal to
-  $\RComb{n}$, so that $R^{(\gamma)}$ is a convergent presentation of
+    Let $\Rew$ be the set of rewrite rules $\Tfr\Rew\RComb{\gamma}$,
+    where $\Tfr$ runs over all the binary trees of arity $\gamma+1$
+    different from $\RComb{\gamma}$. The unique normal
+    form of arity $n\geq\gamma+1$ for the rewrite relation $\RewContext$
+    induced by $\Rew$ is $\RComb{n}$, so that $\Rew$ is a convergent
+    presentation of
     \begin{math}
@@
     \end{math}
-  Moreover, the normal forms of arity $n\leq\gamma$ are all the trees
-  of arity $n$ and, by using the convergent presentation
-  $R^{(\gamma)}$, the compositions of
+    \Todo{S: "$n - 1$" aussi ici ?}
+    Moreover, the normal forms for $\RewContext$ of arity $n\leq\gamma$
+    are all the trees of arity $n$ and, by using the convergent
+    presentation $\Rew$, the compositions of
     \begin{math}
@@
     \end{math}
-  satisfy~\eqref{equ:compositions_of_RC}. Hence, $R^{(\gamma)}$ is also a
-  convergent presentation of
-  \begin{math}
-    \RC{\gamma}
-  \end{math}
-  which proves Lemma~\ref{lem:presentation_of_RC}.
+    satisfy~\eqref{equ:compositions_of_RC}. Hence, $\Rew$ is also a
+    convergent presentation of $\RC{\gamma}$ which proves the statement
+    of the lemma.
 \end{proof}
+\medbreak
+\Todo{S: définir d'abord dans le cadre ensembliste puis considérer son
+analogue linéaire ?}
 
+The lower-bound and the upper-bound of $\As$ and $\AAs$ in the lattice
+$\LatQMag$ are described by the following.
 \medbreak
-The lower-bound and the upper-bound of $\As$ and $\AAs$ in the lattice
-$\LatQMag$ are given by the following.
-\begin{Theorem}
-  \label{thm:example_lattice}
+
+\begin{Theorem} \label{thm:example_lattice}
     We have
-  \begin{equation}
-    \label{equ:example_lower-bound}
-    \KAs\InfQMag\AAs=\NiHil
+    \begin{equation} \label{equ:example_lower-bound}
+        \KAs\InfQMag\AAs=\TwoNil
     \end{equation}
     and
-  \begin{equation}
-    \label{equ:example_upper-bound}
+    \begin{equation} \label{equ:example_upper-bound}
         \KAs\SupQMag\AAs=\RC{3}.
@@
 \end{Theorem}
+\begin{proof}
+    The ideal of relations of $\KAs\InfQMag\AAs$ is equal to
+    $\IAs+\IAAs$, so that it is spanned by the two elements
+    $\LComb{2}-\RComb{2}$ and $\LComb{2}+\RComb{2}$. By linear
+    transformations applied to these generators, $\IAs+\IAAs$ is spanned
+    by $\LComb{2}$ and $\RComb{2}$, that is, it is equal to $\INiHil$,
+    which proves~\eqref{equ:example_lower-bound}.
+    \smallbreak
 
-\begin{proof}
-  First, we show~\eqref{equ:example_lower-bound}. The ideal of relations
-  of $\KAs\InfQMag\AAs$ is equal to $\IAs+\IAAs$, so that it is spanned
-  by the two elements $\LComb{2}-\RComb{2}$ and $\LComb{2}+\RComb{2}$. By
-  linear transformations applied to these generators, $\IAs+\IAAs$ is
-  spanned by $\LComb{2}$ and $\RComb{2}$, that is it is equal to
-  $\INiHil$, which proves~\eqref{equ:example_lower-bound}.
-
-  \smallbreak
-  Now, we show~\eqref{equ:example_upper-bound}. We denote by
+    Let us now denote by
     \begin{math}
@@
     \end{math}
-  the natural projection. Let $\Tfr$ be a tree of arity $4$ and let
-  us define $\alpha_{\Tfr}:=\Tfr-\RComb{3}$. The elements $\alpha_{\Tfr}$
-  belong to $\IAs$ and to $\IAAs$ since both $[\Tfr]_{\IAAs}$ and to
-  $[\RComb{3}]_{\IAAs}$ are equal to $[0]_{\IAAs}$. The last statement is
-  shown using the convergent
-  presentation~\eqref{equ:convergent_presentation_of_AAS}. Hence, the
-  ideal generated by the elements $\alpha_{\Tfr}$ is included in 
-  $\IAs\cap\IAAs=\ker(\pi)$, so that $\pi$ induces a surjective morphism
+    the natural projection. Let $\Tfr$ be a tree of arity $4$ and let us
+    define $\alpha_{\Tfr}:=\Tfr-\RComb{3}$. The elements
+    $\alpha_{\Tfr}$ belong to $\IAs$ and to $\IAAs$ since both
+    $[\Tfr]_{\IAAs}$ and to $[\RComb{3}]_{\IAAs}$ are equal to
+    $[0]_{\IAAs}$. The last statement is shown by using the convergent
+    presentation~\eqref{equ:convergent_presentation_of_AAS} of $\AAs$.
+    Hence, the ideal generated by the elements $\alpha_{\Tfr}$ is
+    included in $\IAs\cap\IAAs=\ker(\pi)$, so that $\pi$ induces a
+    surjective morphism
     \begin{math}
-    \overline{\pi}:\RC{3}\to\KAs\SupQMag\AAs
+        \bar{\pi}:\RC{3}\to\KAs\SupQMag\AAs
     \end{math}
-  from Lemma~\ref{lem:presentation_of_RC}. We conclude using Hilbert
-  series: $\HilbertSeries_{\KAs\SupQMag\AAs}(t)$ is computed
-  using the Grassmann formula analog with
+    from Lemma~\ref{lem:presentation_of_RC}. We conclude by using
+    Hilbert series: $\HilbertSeries_{\KAs\SupQMag\AAs}(t)$ is computed
+    by using the Grassmann formula analog with
     Formulas~\eqref{equ:Hilbert_series_of_As},
-  \eqref{equ:Hilbert_series_of_AAs} and
-  ~\eqref{equ:Hilbert_series_of_NiHil} and it turns out to be equal to
-  $\HilbertSeries_{\RC{3}}(t)$ which is given
-  in~\eqref{equ:Hilbert_series_of_RC}. Hence, $\overline{\pi}$ is an
+    \eqref{equ:Hilbert_series_of_AAs},
+    and~\eqref{equ:Hilbert_series_of_NiHil}, and it turns out to be
+    equal to $\HilbertSeries_{\RC{3}}(t)$ which is given
+    in~\eqref{equ:Hilbert_series_of_RC}. Hence, $\bar{\pi}$ is an
     isomorphism, which proves~\eqref{equ:example_upper-bound}.

### 2018-09-12 Mag_quotients.tex
MAJ

@@
 \end{equation}
-Finally, for every integer $\gamma\geq 2$, we define the
+We introduce, for every integer $\gamma\geq 2$, the (nonlinear)
 \Def{$\gamma$-right comb operad} $\RC{\gamma}$ as follows. For every
@@
     \begin{cases}
-        \KMag(n) &
+        \Mag(n) &
         \mbox{if } n \leq \gamma, \\
-        \K\Angle{\RComb{n}} & \mbox{otherwise},
+        \RComb{n-1} & \mbox{otherwise},
     \end{cases}
 \end{equation}
-\Todo{S: plutôt $\K\Angle{\RComb{n - 1}}$ pour avoir les bonnes arités,
-non ?}
 and the partial composition $\Tfr_1 \circ_i \Tfr_2$ is the partial
@@
 \end{math}
-\Todo{S : je crois qu'il manque un "$-1$ ici, non ?}
+\Todo{S : je crois qu'il manque un "$-1$ ici, non ?
+  Cy : il me semble qu'ici c'est bon puisqu'il s'agit de l'arité}
 is smaller than or equal to $\gamma$, is and $\RComb{n}$, otherwise.
@@
     \begin{equation} \label{equ:presentation_of_RC}
-        \RC{\gamma}\simeq\KMag/_{\IRC{\gamma}}
+        \RC{\gamma}\simeq\Mag/_{\CongrRC{\gamma}}
     \end{equation}
-    where $\IRC{\gamma}$ is the ideal spanned by the elements
-    $\Tfr-\RComb{\gamma}$, where $\Tfr$ runs over all the binary trees
-    of arity $\gamma+1$. In other words, $\RC{\gamma}$ is a
+    where $\CongrRC{\gamma}$ is the smallest operad congruence satisfying
+    $\Tfr\CongrRC{\gamma}\RComb{\gamma}$, where $\Tfr$ runs over all the
+    binary trees of arity $\gamma+1$. In other words, $\RC{\gamma}$ is a
     combinatorial realization of
     \begin{math}
-        \KMag/_{\IRC{\gamma}}.
+        \Mag/_{\CongrRC{\gamma}}.
     \end{math}
@@
     form of arity $n\geq\gamma+1$ for the rewrite relation $\RewContext$
-    induced by $\Rew$ is $\RComb{n}$, so that $\Rew$ is a convergent
+    induced by $\Rew$ is $\RComb{n-1}$, so that $\Rew$ is a convergent
     presentation of
     \begin{math}
-        \KMag/_{\IRC{\gamma}}.
+        \Mag/_{\CongrRC{\gamma}}.
     \end{math}
-    \Todo{S: "$n - 1$" aussi ici ?}
     Moreover, the normal forms for $\RewContext$ of arity $n\leq\gamma$
@@
     \begin{math}
-        \KMag/_{\IRC{\gamma}}
+        \Mag/_{\CongrRC{\gamma}}
     \end{math}
@@
 \medbreak
-\Todo{S: définir d'abord dans le cadre ensembliste puis considérer son
-analogue linéaire ?}
+
+Now, we define the \Def{linear $\gamma$-right comb operad} $\KRC{\gamma}$
+as the linear operad spanned by $\RC{\gamma}$. In particular, its Hilbert
+series is given in~\eqref{equ:Hilbert_series_of_RC}, and
+Lemma~\ref{lem:presentation_of_RC} implies that we have
+\begin{math}
+  \KRC{\gamma}=\KAs/_{\IRC{\gamma}}
+\end{math}
+where $\IRC{\gamma}$ is the ideal spanned by the elements
+$\Tfr-\RComb{\gamma}$, where $\Tfr$ runs over all binary trees of arity
+$\gamma+1$.
+\medbreak
 
@@
     \begin{equation} \label{equ:example_upper-bound}
-        \KAs\SupQMag\AAs=\RC{3}.
+        \KAs\SupQMag\AAs=\KRC{3}.
     \end{equation}
@@
     $[\Tfr]_{\IAAs}$ and to $[\RComb{3}]_{\IAAs}$ are equal to
-    $[0]_{\IAAs}$. The last statement is shown by using the convergent
+    $[0]_{\IAAs}$. The last statement is shown using the convergent
     presentation~\eqref{equ:convergent_presentation_of_AAS} of $\AAs$.
-    Hence, the ideal generated by the elements $\alpha_{\Tfr}$ is
-    included in $\IAs\cap\IAAs=\ker(\pi)$, so that $\pi$ induces a
-    surjective morphism
+    Hence, the ideal generated by the elements $\alpha_{\Tfr}$, that is
+    the ideal of relations of $\KRC{3}$, is included in
+    $\IAs\cap\IAAs=\ker(\pi)$, so that $\pi$ induces a surjective
+    morphism
     \begin{math}
-        \bar{\pi}:\RC{3}\to\KAs\SupQMag\AAs
+        \bar{\pi}:\KRC{3}\to\KAs\SupQMag\AAs.
     \end{math}
-    from Lemma~\ref{lem:presentation_of_RC}. We conclude by using
-    Hilbert series: $\HilbertSeries_{\KAs\SupQMag\AAs}(t)$ is computed
-    by using the Grassmann formula analog with
+    We conclude by using Hilbert series:
+    $\HilbertSeries_{\KAs\SupQMag\AAs}(t)$ is computed by using the
+    Grassmann formula analog with
     Formulas~\eqref{equ:Hilbert_series_of_As},
@@
     and~\eqref{equ:Hilbert_series_of_NiHil}, and it turns out to be
-    equal to $\HilbertSeries_{\RC{3}}(t)$ which is given
+    equal to $\HilbertSeries_{\KRC{3}}(t)$ which is given
     in~\eqref{equ:Hilbert_series_of_RC}. Hence, $\bar{\pi}$ is an

### 2018-09-12 CAs_operads.tex
Petites modifs

@@
 following backtracking algorithm. For every branching pair
-$(\Tfr_1, \Tfr_2)$ which is not joinable, we recursively try to find a
-completion of $\Rew$ by adding either the rule
+$\left\{\Tfr_1, \Tfr_2\right\}$ which is not joinable, we recursively
+try to find a completion of $\Rew$ by adding either the rule
 $\Tfr_1 \Rew  \Tfr_2$ or $\Tfr_2 \Rew  \Tfr_1$.
@@
 convergent presentation of $\CAs{\gamma}$ when $\gamma \geq 4$ and when
- the left and the right members of the rewriting rules are trees
+the left and the right members of the rewrite rules are trees
 belonging to $\Mag$.
@@
 
-Thanks to the partial completions presented in table
-\ref{tab:cardinalities_completion_CAs}, we can compute the following 
-first dimensions of $\CAs{\gamma}$. Table~\ref{tab:dimensions_CAs}
- shows the first dimensions of the
+Thanks to the partial completions presented in
+Table~\ref{tab:cardinalities_completion_CAs}, we can compute the
+following first dimensions of $\CAs{\gamma}$.
+Table~\ref{tab:dimensions_CAs} shows the first dimensions of the
 operads $\CAs{\gamma}$ for $\gamma \in [9]$.
@@
     \caption{\footnotesize
-    The sequences of the cardinalities, arity by arity, of the
-    dimensions of~$\CAs{\gamma}$.}
+    The sequences, arity by arity, of the dimensions of~$\CAs{\gamma}$.}
     \label{tab:dimensions_CAs}

### 2018-09-13 Operads_rewrite.tex
MAJ
Relecture section quotients de degré de 3

@@
 Nevertheless, operads can be defined in the category of $\K$-vector
-spaces, where $\K$ denotes in all this text a commutative field. We call
+spaces. We call
 them \Def{linear operads} and we study a class of such operads in
@@
     terminating and all its branching pairs are joinable, $\RewContext$
-    is convergent.
+    is confluent.
 \end{Lemma}

### 2018-09-13 Operads_rewrite.tex
MAJ

@@
 When $\Rew$ is a convergent orientation of $\Congr$, the set
-$\NormalForms_{\RewContext}$ of all normal forms of $\RewContext$ is
+$\NormalForms_{\RewContext}$ of all normal forms for $\RewContext$ is
 called a \Def{Poincaré-Birkhoff-Witt basis}~\cite{Hof10,DK10} (or a

### 2018-09-13 CAs_operads.tex
MAJ

@@
 the operad $\KCAs{\gamma}$ is equal to $\KMag/_{I_{\gamma}}$, where
-$I_{\gamma}$ is the operadic ideal of $\KMag$ generated by
+$I_{\gamma}$ is the operad ideal of $\KMag$ generated by
 $\LComb{\gamma}-\RComb{\gamma}$. We obtain a new lattice $\LatKCAs$,

### 2018-09-13 Mag_quotients.tex
MAJ
Petites modifs

@@
 
-We denote by $\IMag$ the set of operadic ideals of $\KMag$ and we set
+We denote by $\IMag$ the set of operad ideals of $\KMag$ and we set
 \begin{equation} \label{equ:definition_of_QMag}
@@
 $\left(\IMag,\subseteq,\cap,+\right)$ is a lattice, where $\cap$ and $+$
-are the intersection and the sum of operadic ideals, respectively.
+are the intersection and the sum of operad ideals, respectively.
 \medbreak
@@
 
-The union of the generating sets of two operadic ideals $I_1$ and $I_2$
+The union of the generating sets of two operad ideals $I_1$ and $I_2$
 is a generating set of $I_1+I_2$, so that the union of generating
@@
 \begin{math}
-    n:=|\Tfr_1|+|\Tfr_2|
+    n:=|\Tfr_1|+|\Tfr_2|-1
 \end{math}
-\Todo{S : je crois qu'il manque un "$-1$ ici, non ?
-  Cy : il me semble qu'ici c'est bon puisqu'il s'agit de l'arité}
-is smaller than or equal to $\gamma$, is and $\RComb{n}$, otherwise.
+is smaller than or equal to $\gamma$, and $\RComb{n}$ otherwise.
 Moreover, by definition of the $\gamma$-right comb operad, we have

### 2018-09-13 Mag_quotients.tex
MAJ

@@
 \end{equation}
-as the set of the quotients of the linear magmatic operad. Given
+as the set of all quotients of the linear magmatic operad. Given
 $\KMag/_I \in \QMag$ and $x \in \KMag$, we denote by $[x]_I$ the
@@
 Recall that a \Def{lattice} is a tuple
-$\left(E,\leq,\wedge,\vee\right)$, where $\leq$ is a partial order
+$\left(E,\leq,\wedge,\vee\right)$ where $\leq$ is a partial order
 relation such that any two elements $e$ and $e'$ of $E$ admit a

### 2018-09-13 Mag_quotients.tex
MAJ

@@
 
-The union of the generating sets of two operad ideals $I_1$ and $I_2$
+The union of generating sets of two operad ideals $I_1$ and $I_2$
 is a generating set of $I_1+I_2$, so that the union of generating

### 2018-09-13 Mag_quotients.tex
MAJ

@@
 of ideals (it is not the intersection of the generating relations), so
-that we do not know how to compute generating relations
+that we do not know any general method to compute generating relations
 for~$\Oca_1\SupQMag\Oca_2$.

### 2018-09-13 Mag_quotients.tex
MAJ

@@
 We terminate this section with an example illustrating the lattice
-constructions on $\QMag$ in the case where the characteristic of the
-field $\K$ is different from $2$. For that, we introduce various
+constructions on $\QMag$. For that, we introduce various
 operads, which requires the following notations, also used in
@@
 \begin{equation} \label{equ:linear_associative_operad}
-    \KAs:=\KMag/_{\IAs}
+    \KAs:=\KMag/_{\IAs},
 \end{equation}
@@
     \label{equ:anti-associative_operad}
-    \AAs:=\KMag/_{\IAAs}
+    \AAs:=\KMag/_{\IAAs},
 \end{equation}
@@
 \begin{equation} \label{equ:2-nilpotent_operad}
-    \TwoNil:=\KMag/_{\INiHil}
+    \TwoNil:=\KMag/_{\INiHil},
 \end{equation}
@@
     \begin{equation} \label{equ:presentation_of_RC}
-        \RC{\gamma}\simeq\Mag/_{\CongrRC{\gamma}}
+        \RC{\gamma}\simeq\Mag/_{\CongrRC{\gamma}},
     \end{equation}
@@
 where $\IRC{\gamma}$ is the ideal spanned by the elements
-$\Tfr-\RComb{\gamma}$, where $\Tfr$ runs over all binary trees of arity
-$\gamma+1$.
+$\Tfr-\RComb{\gamma}$, with $\Tfr$ a binary tree of arity $\gamma+1$.
 \medbreak

### 2018-09-13 Mag_quotients.tex
MAJ

@@
 
-The lower-bound and the upper-bound of $\As$ and $\AAs$ in the lattice
+The lower-bound and the upper-bound of $\KAs$ and $\AAs$ in the lattice
 $\LatQMag$ are described by the following.
@@
     $\alpha_{\Tfr}$ belong to $\IAs$ and to $\IAAs$ since both
-    $[\Tfr]_{\IAAs}$ and to $[\RComb{3}]_{\IAAs}$ are equal to
+    $[\Tfr]_{\IAAs}$ and $[\RComb{3}]_{\IAAs}$ are equal to
     $[0]_{\IAAs}$. The last statement is shown using the convergent

### 2018-09-13 Article.tex
Restructuration (2)
Passe partie 3 (avant lem 3.2.4)
Relecture partie 3 (avant prop. 3.2.7)
Relecture partie 3 (avant partie 3.3)
Relecture partie 3 (avant partie 3.3.2)
Relecture Partie 4 (debut)
MAJ
Relecture exemples Grassmann
Petites modifs

@@
 \usepackage[english]{babel}
-\usepackage{amsmath,amsfonts,amssymb,amsthm,shuffle}
+\usepackage{amsmath,amsfonts,amssymb,amsthm,bm,shuffle}
 \usepackage[T1]{fontenc}
@@
 \newcommand{\Tfr}{\mathfrak{t}}
+\newcommand{\Zfr}{\mathfrak{z}}
 \newcommand{\BranchingTrees}{\mathfrak{P}}
+
+\newcommand{\LambdaB}{\bm{\lambda}}
+\newcommand{\MuB}{\bm{\mu}}
+\newcommand{\NuB}{\bm{\nu}}
 
@@
 \newcommand{\KMag}{\K \Angle{\Mag}}
+\newcommand{\KAs}{\K \Angle{\As}}
 \newcommand{\QMag}{\mathcal{Q}\left(\KMag\right)}
@@
 \newcommand{\As}{\mathbf{As}}
+\newcommand{\AAs}{\mathbf{AAs}}
+\newcommand{\TwoNil}{2\mathbf{Nil}}
+\newcommand{\RC}[1]{\mathbf{RC}^{\left(#1\right)}}
+\newcommand{\KRC}[1]{\K\langle\RC{#1}\rangle}
 \newcommand{\TwoAs}{2\As}
@@
 \newcommand{\CAs}[1]{\CAsAll^{\left(#1\right)}}
-\newcommand{\KCAs}[1]{\K\CAs{#1}}
-\newcommand{\KCAsAll}{\K\CAsAll}
+\newcommand{\KCAs}[1]{\K\langle\CAs{#1}\rangle}
+\newcommand{\KCAsAll}{\K\langle\CAsAll\rangle}
 
@@
 \newcommand{\Deg}{\mathrm{deg}}
-\newcommand{\LComb}[1]{\mathfrak{c}^{\left(#1\right)}_{\diagup}}
-\newcommand{\RComb}[1]{\mathfrak{c}^{\left(#1\right)}_{\diagdown}}
+\newcommand{\LComb}[1]{\mathfrak{c}^{\left(#1\right)}_{
+\begin{tikzpicture}[xscale=.2,yscale=.17,Centering]
+    \draw[Edge](0,0)--(-1,-1);
+\end{tikzpicture}
+}}
+\newcommand{\RComb}[1]{\mathfrak{c}^{\left(#1\right)}_{
+\begin{tikzpicture}[xscale=.2,yscale=.17,Centering]
+    \draw[Edge](0,0)--(1,-1);
+\end{tikzpicture}
+}}
 \newcommand{\LRank}{\mathrm{lr}}
@@
 \newcommand{\Unit}{\mathds{1}}
-\newcommand{\Leaf}{\perp}
+\newcommand{\Leaf}{{
+\begin{tikzpicture}[xscale=.2,yscale=.22,Centering]
+    \draw[Edge](0,0)--(0,-1);
+\end{tikzpicture}
+}}
 \newcommand{\Corolla}{\mathrm{c}}
@@
 
-\newcommand{\CongrCAs}[1]{\Congr^{(#1)}}
+\newcommand{\CongrCAs}[1]{\Congr^{\left(#1\right)}}
+\newcommand{\CongrRC}[1]{\Congr_{\left(#1\right)}}
+\newcommand{\INiHil}{I_{\TwoNil}}
+\newcommand{\IAs}{I_{\KAs}}
+\newcommand{\IAAs}{I_{\AAs}}
+\newcommand{\IRC}[1]{I_{\RC{#1}}}
 
 \newcommand{\Lightning}[1]{
-\mathfrak{c}^{(#1)}_{\begin{tikzpicture}[scale=.1, Centering]
-    \draw (0,0)--(-1,-2);
-    \draw (-1,-2)--(0,-2);
-    \draw (0,-2)--(-1,-4);
+\mathfrak{c}^{\left(#1\right)}_{\begin{tikzpicture}[scale=.1, Centering]
+    \draw[Edge](0,0)--(-1,-2);
+    \draw[Edge](-1,-2)--(0,-2);
+    \draw[Edge](0,-2)--(-1,-4);
 \end{tikzpicture}}}
@@
     to the lattice of nonnegative integers equipped with the division
-    order. Driven by computer experimentation, we provide a finite
+    order. Driven by computer experimentations, we provide a finite
     convergent presentation for the comb associative operad in
@@
 
+\begin{small}
 \tableofcontents
+\end{small}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{Magmatic_operads}
+\input{Mag_quotients}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{Magmatic_quotient_three}
+\input{Cubic_quotients}
 

### 2019-01-21 CAs_operads.tex
MAJ
Correction Acknowledgements et preuve proposition 3.2.5

@@
     identity morphism on $\CAs{\gamma}$ for every positive integer
-    $\gamma$. Let us now assume that
-    $\varphi:\CAs{\gamma''} \to \CAs{\gamma'}$ and
-    $\psi:\CAs{\gamma'} \to \CAs{\gamma}$ are two operad morphisms. By
-    Lemma~\ref{lem:morphism_CAs}, one has
-    $\LComb{\gamma''} \CongrCAs{\gamma'} \RComb{\gamma''}$ and
-    $\LComb{\gamma'} \CongrCAs{\gamma} \RComb{\gamma'}$. This implies
-    that $\CongrCAs{\gamma}$ is coarser than $\CongrCAs{\gamma'}$ and
-    that $\CongrCAs{\gamma'}$ is coarser that $\CongrCAs{\gamma''}$. Now,
-    again by Lemma~\ref{lem:morphism_CAs}, $\psi \circ \varphi$ is an
-    operad morphism. Hence, $\OrdCAs$ is transitive. Finally, let us
-    assume that there exist morphisms
-    $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$ and
+    $\gamma$. It is transitive since the composite of operad morphisms is
+    an operad morphism. Finally, let us assume that there exist  tow
+    morphisms $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$ and
     $\psi:\CAs{\gamma}\to\CAs{\gamma'}$. In particular,
@@
 
-However, the completion algorithm we used depends on the chosen order on
+However, the completion algorithm we use depends on the chosen order on
 the trees. In order to find out if the completion algorithm leads to a

### 2019-01-21 Introduction.tex
Relecture exemples Grassmann
Correction Acknowledgements et preuve proposition 3.2.5

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection*{Acknoledgements}
+\subsubsection*{Acknowledgements}
 The authors wish to thank Maxime Lucas for helpful discussions and
@@
 $\{b \in \N : a \leq b \leq c\}$ and $[n]$, the set $[1, n]$. The
-cardinality of a finite set $S$ is denoted by~$\# S$.
+cardinality of a finite set $S$ is denoted by~$\# S$. In all this
+work, $\K$ is a field of characteristic zero.
 \medbreak

### 2019-01-21 Response.tex
Ajout fichier reponse rapporteur

% Author: Cyrille Chenavier, Christophe Cordero, Samuele Giraudo
% Creation: jan. 2019
% Modifications: jan. 2019

\documentclass[10pt,reqno]{amsart}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[utf8x]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath,amsfonts,amssymb,amsthm,shuffle}
\usepackage[T1]{fontenc}
\usepackage[math]{anttor}

% Layout.
\usepackage[top=3.5cm,bottom=3.5cm,left=3.4cm,right=3.4cm]{geometry}

% Colors of hyperlinks.
\usepackage[dvipsnames]{xcolor}

\usepackage[hyperindex=true,frenchlinks=true,colorlinks=true,
citecolor=Col2,linkcolor=Col3,urlcolor=Col4,linktocpage,
pagebackref=true]{hyperref}

% Tikz.
\usepackage{tikz}
\usetikzlibrary{shapes}
\usetikzlibrary{fit}
\usetikzlibrary{decorations.pathmorphing}

% Misc.
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{wasysym}
\usepackage{stmaryrd}
\usepackage{cite}
\usepackage{subfig}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{cancel}
\usepackage{xspace}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Line space.
\linespread{1.15}
\renewcommand{\arraystretch}{1.4}

% Vertical space for equations.
\setlength{\abovedisplayskip}{5pt}
\setlength{\belowdisplayskip}{5pt}

% Alphabetic footnote marks.
\renewcommand{\thefootnote}{\alph{footnote}}

% To allow cutting equations in several pages.
\allowdisplaybreaks

% Numbering of equations.
\numberwithin{equation}{subsection}

% Depth of the table of contents.
\setcounter{tocdepth}{2}

% Indentation in the table of contents.
\makeatletter
\def\l@section{\@tocline{1}{3pt}{1pc}{5pc}{}}
\def\l@subsection{\@tocline{2}{2pt}{2pc}{5pc}{}}
\makeatother

% Environments definitions.
\newtheorem{Theorem}{Theorem}[subsection]
\newtheorem{Proposition}[Theorem]{Proposition}
\newtheorem{Lemma}[Theorem]{Lemma}

% Better comparison symbols.
\renewcommand{\leq}{\leqslant}
\renewcommand{\geq}{\geqslant}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[Response to Referees]
    {Response to referee comments \\
    and \\
    changes report}
\keywords{}
\subjclass[2010]{}
\date{\today}
\author{Cyrille Chenavier \and Christophe Cordero \and Samuele Giraudo}
\address{\scriptsize Université Paris-Est, LIGM (UMR $8049$), CNRS,
    ENPC, ESIEE Paris, UPEM, F-$77454$, Marne-la-Vallée, France}
\email{cyrille.chenavier@u-pem.fr}
\email{christophe.cordero@u-pem.fr}
\email{samuele.giraudo@u-pem.fr}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\maketitle

Please find here the modifications made to the manuscript
``Quotients of the magmatic operad: lattice structures and convergent
rewrite systems'' submitted to Experimental Mathematics, following
the comments of the reviewer.
\bigbreak

\end{document}

### 2019-01-21 Response.tex
Maj response

@@
 
+\begin{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\item `` {\it
+The allusions in two places to "intervals in the Tamari order" are
+rather strange. If you have any evidence or hint that this could be a
+good condition, please tell the reader.
+}''
+\smallbreak
+
+For the while, we have no general result connecting the quotients of
+the magmatic operad and intervals of Tamari lattices but we suspect
+that there is a link between the properties of the equated trees
+with respect to the Tamari order and the description of the quotient
+operad. This question was actually one of the starting points of this
+work, and the research rather leads up to the presented results.
+\medbreak
+
+\end{itemize}
+
 \end{document}

### 2019-01-21 Response.tex
Response

@@
 
+\item `` {\it
+In my humble opinion, when doing so, one should cite carefully what 
+is being used (language, package, etc), just like articles are cited.
+}''
+\smallbreak
+
+We do not use a particular package. We added 
+"All our computer programs are made from scratch in OCaml" in the 
+introduction. 
+\medbreak
+
+\item `` {\it
+The definition of $z_d$ page 20 needs to be checked (composition index)
+}''
+\smallbreak
+
+The index was wrong. We changed "d/2" into "d-1/2".
+\medbreak
+
+\item `` {\it
+About table of numbers page 23, do you see any interesting patterns ? 
+possible formulas ? rationality of generating series ?
+}''
+\smallbreak
+
+No ! Even with the package gfun on Mapple, we do not 
+see any pattern, formulas, $\dots$
+\medbreak
+
+\item `` {\it
+In section 4, the sentence "The reader can check" (repeated 4 times) 
+is a bit terse. This is certainly feasible by hand. The reader would 
+appreciate to be given hints of arguments for confluence (no critical 
+pair ?) and termination. Or maybe there are available software that 
+can swallow this kind of rewriting system and check that is is closed ?
+}''
+\smallbreak
+
+We added the "using the Buchberger algorithm for operads" for the first 
+occurrence of "The reader can check". It is easy to run the algorithm 
+by hand on those examples.
+\medbreak
+
+\item `` {\it
+Question: make a statement about the non-isomorphism (as set-operads 
+or as k-linear-operads) between the 4 quotients indexed by compositions.
+}''
+\smallbreak
+
+?
+\medbreak
+
+\item `` {\it
+For the conjecture of section 4.3, up to which arity was it verified ?
+}''
+\smallbreak
+
+Until arity 40 ! We added it in the article.
+\medbreak
+
 \end{itemize}

### 2019-01-21 Response.tex
Réponse questions Cyrille

@@
 
+\item "{\it
+  Page 9, is this completion or rewriting systems an operadic avatar of
+  Knuth-Bendix procedure ?
+}''
+  \smallbreak
+
+ Yes, in essence, this is the same thing but the terminology differs from
+ the context: for term rewriting ystems or word rewriting systems, the
+ classical terminology in the litterature is ``Knuth-Bendix procedure''
+ and for linear structures, such  such as polynomial algebras,
+ noncommutative algebras or operads, the classical terminology is
+ ''Buchberger procedure".
+ \medbreak
+
+\item ''{\it
+  A reference for the name "Grassmann formula" would be welcome (page 12)
+}''
+  \smallbreak
+
+  Ok, we add it!
+  \medbreak
+
+\item ''{\it
+  In the proof of Prop. 3.2.5, why not use that the composite of a
+  morphism is a morphism ?
+}''
+  \smallbreak
+
+  This is a good remark: we changed the text!
+  \medbreak
+
 \item `` {\it

### 2019-01-21 Mag_quotients.tex
MAJ
Réponse questions Cyrille

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Linear quotients of the magmatic operad}
+\section{Quotients of the linear magmatic operad}
 \label{sec:Magmatic_operads}
@@
     \end{split}\end{equation}
-    The third equality is due to the Grassmann formula applied to the
-    subspaces $I_1(n)$ and $I_2(n)$ of $\KMag(n)$.
+    The third equality is due to the Grassmann
+    formula~\cite{lang2002algebra} applied to the subspaces $I_1(n)$ and
+    $I_2(n)$ of $\KMag(n)$.
     \smallbreak

### 2019-01-23 Response.tex
Corrections apres rapport

@@
 \item `` {\it
+The standard indexing for Catalan numbers is
+cat(n)=binomial(2n,n)/(n+1). Please respect this convention.
+}''
+\smallbreak
+
+We have changed this, as suggested by the reviewer. The convention is
+now respected. Moreover, we have provided an updated version of
+the statement of Lemma~3.2.1.
+\medbreak
+
+\item `` {\it
+In the proof of Lemma 1.3.1, say that p(t) > p(t') means t > t'
+}''
+\smallbreak
+
+This precision has been added to the proof of the lemma.
+\medbreak
+
+\item `` {\it
+In the proof of Lemma 1.3.4, refer to a precise Theorem in [Gir16]
+}''
+\smallbreak
+
+The precise reference has been added.
+\medbreak
+
+\item `` {\it
 In my humble opinion, when doing so, one should cite carefully what
@@
 We do not use a particular package. We added
-"All our computer programs are made from scratch in OCaml" in the 
-introduction. 
+``All our computer programs are made from scratch in {\sc Caml}
+and {\sc Python}'' in the introduction.
 \medbreak
@@
   This is a good remark: we changed the text!
+  \medbreak
+
+\item ''{\it
+What are the squared regions (page 17) ? I did not look at the colored article.
+}''
+  \smallbreak
+
+  This was a mistake because, indeed, there are no squared regions. we
+  change ``squared regions'' by ``dotted edges''.
+  \medbreak
+
+  \item ''{\it
+Maybe it would be a good idea to add the words in $\{0,2\}$ below the relations in the large figure of page 19 ?
+}''
+  \smallbreak
+  The words in correspondence with the trees of the relations have been
+  written.
   \medbreak

### 2019-01-23 CAs_operads.tex
Règles CAs3, écriture pefix word
Corrections
Écriture complétion CAs3 prefix word
Corrections apres rapport

@@
         \# \CAs{\gamma}(n) =
-        \begin{cases}
-            \Catalan(n)
-                & \mbox{ if } n \leq \gamma, \\
-            \Catalan(\gamma + 1) - 1
-                & \mbox{ otherwise } (n = \gamma + 1).
-        \end{cases}
-    \end{equation}
+        \Catalan(n - 1) - \delta_{n, \gamma + 1},
+    \end{equation}
+    where $\delta_{x, y}$ is the Kronecker delta.
 \end{Lemma}
@@
     degree $d$ has arity $n := d + 1$, one has
-    $\# \CAs{\gamma}(n) = \# \Mag(n) = \Catalan(n)$ with
+    $\# \CAs{\gamma}(n) = \# \Mag(n) = \Catalan(n - 1)$ with
     $n \leq \gamma$. Besides, by definition of $\CongrCAs{\gamma}$, all
@@
         = \# \Mag(\gamma + 1) - 1
-        = \Catalan(\gamma + 1) - 1.
-    \end{math}
+        = \Catalan(\gamma + 1 - 1) - 1
+        = \Catalan(n - 1) - 1
+    \end{math}
+    as stated.
 \end{proof}
@@
     \end{multline}
-    of rewrite steps, where squared regions denotes left or right
+    of rewrite steps, where dotted edges denotes left or right
     comb trees of degree $\gamma - 1$. Hence, since
@@
 
+Using prefix words, these new relations write as
+\begin{multicols}{2}
+\begin{small}
+\begin{equation}
+    22020200 \Rew 220020200,
+\end{equation}
+\begin{equation}
+    20202202000 \Rew 20202020200,
+\end{equation}
+\begin{equation}
+    20220200200 \Rew 20202020200,
+\end{equation}
+\begin{equation}
+    2020220020200 \Rew 2020202022000,
+\end{equation}
+\begin{equation}
+    2022002020200 \Rew 2020202200200,
+\end{equation}
+
+\begin{equation}
+    2202200020200 \Rew 2200202020200,
+\end{equation}
+\begin{equation}
+    202020202200200 \Rew 202020202022000,
+\end{equation}
+\begin{equation}
+    202020220022000 \Rew 202020202020200,
+\end{equation}
+\begin{equation}
+    220020202200200 \Rew 220020202022000,
+\end{equation}
+\begin{equation}
+    220200202020200 \Rew 220020202022000.
+\end{equation}
+\end{small}
+\end{multicols}
+\medbreak
+
 \begin{Theorem} \label{thm:convergent_rewrite_rule_CAs_3}
@@
         \Zfr_{d - 1}
-        \circ_{\left\lfloor \frac{d}{2} \right\rfloor + 1} \Product
+        \circ_{\left\lfloor \frac{d-1}{2} \right\rfloor + 1} \Product
         & \mbox{otherwise}.

### 2019-01-23 Introduction.tex
Corrections
Corrections apres rapport

@@
 (Theorem~\ref{thm:lattice_structure_of_QMag}). We also provide a
-Grassmann formula analog relating the Hilbert series of the operads of
-the lattice together with their lower-bound and upper-bound
+Grassmann formula (see for instance~\cite{Lan02} analog relating the
+Hilbert series of the operads of the lattice together with their
+lower-bound and upper-bound
 (Theorem~\ref{thm:Grassmann_formula_for_Hilbert_series_of_QMag}).
@@
 We expose some experimental results obtained with the help of the
-computer for some operads $\CAs{\gamma}$ with $\gamma \geq 4$. Finally,
-we continue the investigation of the quotients of $\Mag$ by regarding
-the quotients of $\Mag$ obtained by equating two trees of degree $3$.
-This leads to ten quotient operads of $\Mag$. We provide for some of
-these combinatorial realizations, mostly in terms of integer
-compositions.
+computer for some operads $\CAs{\gamma}$ with $\gamma \geq 4$.
+All our computer programs are made from scratch in {\sc Caml} and
+{\sc Python}. Finally, we continue the investigation of the quotients
+of $\Mag$ by regarding the quotients of $\Mag$ obtained by equating two
+trees of degree $3$. This leads to ten quotient operads of $\Mag$. We
+provide for some of these combinatorial realizations, mostly in terms
+of integer compositions.
 \medbreak

### 2019-01-23 Mag_quotients.tex
Corrections apres rapport

@@
     The third equality is due to the Grassmann
-    formula~\cite{lang2002algebra} applied to the subspaces $I_1(n)$ and
+    formula~\cite{Lan02} applied to the subspaces $I_1(n)$ and
     $I_2(n)$ of $\KMag(n)$.
@@
     \HilbertSeries_{\RC{\gamma}}(t)=
-    \sum_{1\leq n\leq\gamma}\Catalan(n) t^n +\sum_{n\geq\gamma+1}t^n.
+    \sum_{1\leq n\leq\gamma}\Catalan(n - 1) t^n +\sum_{n\geq\gamma+1}t^n.
 \end{equation}

### 2019-01-23 Operads_rewrite.tex
Corrections apres rapport

@@
 the $\Sfr_i$ onto the $i$th leaves of $\Tfr$. The unit of $\Mag$ is the
-leaf. The number of binary trees of arity $n \geq 1$ is the $n$th
-Catalan number $\Catalan(n)$ and hence, the Hilbert series of $\Mag$ is
+leaf. The number of binary trees of arity $n \geq 1$ is the $(n - 1)$st
+Catalan number $\Catalan(n - 1)$ and hence, the Hilbert series of
+$\Mag$ is
 \begin{equation}
     \HilbertSeries_{\Mag}(t)
-    = \sum_{n \geq 1} \Catalan(n) t^n
+    = \sum_{n \geq 1} \Catalan(n - 1) t^n
     = \sum_{n \geq 1} \binom{2n - 1}{n - 1} \frac{1}{n} t^n.
@@
     binary trees such that $\Tfr \RewContext \Tfr'$,
-    $\PrefixWord(\Tfr) > \PrefixWord\left(\Tfr'\right)$. This leads to
-    the fact that any chain
+    $\PrefixWord(\Tfr) > \PrefixWord\left(\Tfr'\right)$. This means
+    that $\Tfr > \Tfr'$ and leads to the fact that any chain
     \begin{math}
@@
     relations on $\Mag$ of a more general result about rewrite relations
-    on trees contained in~\cite{Gir16}.
+    appearing in~\cite[Lemma 1.2.1.]{Gir16}.
 \end{proof}

### 2019-01-24 Response.tex
Modifs apres revision

@@
 
-\documentclass[10pt,reqno]{amsart}
+\documentclass[11pt,reqno]{amsart}
 
@@
 
+First of all, we would like to thank the reviewer for its time and its
+careful reading. Its suggestions improve the paper.
+\medbreak
+
 Please find here the modifications made to the manuscript
@@
 \begin{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\item `` {\it
+They were obviously obtained through an expert and
+heavy use of computer software.
+In my humble opinion, when doing so, one should cite carefully what
+is being used (language, package, etc), just like articles are cited.
+}''
+\smallbreak
+
+We do not use a particular package. We added
+``All our computer programs are made from scratch in {\sc Caml}
+and {\sc Python}'' in the introduction.
+\medbreak
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \item `` {\it
@@
 
-\item `` {\it
-In my humble opinion, when doing so, one should cite carefully what
-is being used (language, package, etc), just like articles are cited.
-}''
-\smallbreak
-
-We do not use a particular package. We added
-``All our computer programs are made from scratch in {\sc Caml}
-and {\sc Python}'' in the introduction.
-\medbreak
-
-\item "{\it
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\item ``{\it
   Page 9, is this completion or rewriting systems an operadic avatar of
@@
 
- Yes, in essence, this is the same thing but the terminology differs from
+In essence, this is the same thing but the terminology differs from
 the context: for term rewriting ystems or word rewriting systems, the
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \item ''{\it
@@
 
-  Ok, we add it!
+A reference has been added.
 \medbreak
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \item ''{\it
@@
 
-  This is a good remark: we changed the text!
+This is a good remark: we changed the text.
 \medbreak
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \item ''{\it
-What are the squared regions (page 17) ? I did not look at the colored article.
+What are the squared regions (page 17) ? I did not look at the colored
+article.
 }''
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \item ''{\it
-Maybe it would be a good idea to add the words in $\{0,2\}$ below the relations in the large figure of page 19 ?
+Maybe it would be a good idea to add the words in $\{0,2\}$ below the
+relations in the large figure of page 19 ?
 }''
 \smallbreak
+
 The words in correspondence with the trees of the relations have been
@@
 
-The index was wrong. We changed "d/2" into "d-1/2".
+Indeed, you are right, the index was wrong. We changed "d/2" into
+"d-1/2".
 \medbreak
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \item `` {\it
@@
 
-No ! Even with the package gfun on Mapple, we do not
-see any pattern, formulas, $\dots$
+It seems that it is not the case. Even with the package gfun on
+Maple, we do not see any pattern, formulas, \dots
 \medbreak
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \item `` {\it
@@
 We added the "using the Buchberger algorithm for operads" for the first
-occurrence of "The reader can check". It is easy to run the algorithm
-by hand on those examples.
+occurrence of "The reader can check". It is quite easy to run the
+algorithm by hand on those examples.
 \medbreak
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \item `` {\it
@@
 
-?
+This is a good suggestion. We have added a small section (4.2.5) to
+explain this property.
 \medbreak
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \item `` {\it
@@
 
-Until arity 40 ! We added it in the article.
+Until arity 40. We have added this information in the article.
 \medbreak

### 2019-01-24 Response.tex
Réponses
Response
Petite correction Response.tex

@@
 
-First of all, we would like to thank the reviewer for its time and its
-careful reading. Its suggestions improve the paper.
+First of all, we would like to thank the reviewer for his time and his
+careful reading. His suggestions improve the paper.
 \medbreak
@@
 
-We added the "using the Buchberger algorithm for operads" for the first
-occurrence of "The reader can check". It is quite easy to run the
-algorithm by hand on those examples.
+We added the information "using the Buchberger algorithm for operads" for
+the first occurrence of "The reader can check". It is quite easy to run
+the algorithm by hand on those examples.
 \medbreak
